### 2013-04-19 ms.tex
Initial manuscript (corresponding to v2 pdf) from Danny.

%TODO
%update tables
%reread text

%\documentclass[10pt,iop]{emulateapj}
\documentclass[preprint]{aastex}
%\usepackage{rotating}
\usepackage{url}
\usepackage{multirow}
\usepackage{amsmath}
%\usepackage{graphicx}
%\usepackage[figuresright]{rotating}
%\usepackage{rotating}
%%\usepackage{natbib}

%\citestyle{aa}

%\bibliographystyle{apj_w_etal}

\newcommand{\etal}{{et al.\/}}
\newcommand{\Prob}{\mathtt{P}}
\newcommand{\logL}{\log\mathcal{L}}
\newcommand{\unit}[1]{\footnotesize #1}
\newcommand{\PAPER}{\mathrm{PAPER}}
\bibliographystyle{apj_w_etal}

	% End definitions

%\slugcomment{DRAFT: \today}

\shorttitle{PSA64}
\shortauthors{Jacobs et al.}

\begin{document}

%\title{The Reionization flux scale in the Southern Sky}
\title{A southern hemisphere flux scale for 21cm epoch of reionization experiments}
\author{
Daniel C. Jacobs\altaffilmark{1},
Aaron R. Parsons\altaffilmark{2},
James E. Aguirre\altaffilmark{3},
Zaki Ali\altaffilmark{2},
Richard F. Bradley\altaffilmark{4,5,6},
Chris L.  Carilli\altaffilmark{7},
Dave DeBoer\altaffilmark{8},
Matthew Dexter\altaffilmark{8},
Nicole E. Gugliucci\altaffilmark{5},
Dave MacMahon\altaffilmark{8},
Jason Manley\altaffilmark{9},
David F. Moore\altaffilmark{3},
Jonathan C. Pober\altaffilmark{2},
Irina I. Stefan\altaffilmark{10},
William P. Walbrugh\altaffilmark{9}}

\altaffiltext{1}{School of Earth and Space Exploration, Arizona State U., Tempe, AZ}
\altaffiltext{2}{Astronomy Dept., U. California, Berkeley, CA}
\altaffiltext{3}{Dept. of Physics and Astronomy, U. Pennsylvania, Philadelphia, PA}
\altaffiltext{4}{Dept. of Electrical and Computer Engineering, U. Virginia, Charlottesville, VA}
\altaffiltext{5}{National Radio Astronomy Obs., Charlottesville, VA}
\altaffiltext{6}{Dept. of Astronomy, U. Virginia, Charlottesville, VA}
\altaffiltext{7}{National Radio Astronomy Obs., Socorro, NM}
\altaffiltext{8}{Radio Astronomy Lab., U. California, Berkeley, CA}
\altaffiltext{9}{Square Kilometer Array, South Africa Project, Cape Town, South Africa}
\altaffiltext{10}{Cavendish Lab., Cambridge, UK}

\begin{abstract}
We present the first spectral measurements from the Precision Array for Probing the Epoch of Reionization (PAPER) in South Africa observed in July and September of 2011.  The spectra are determined by calibrating directly to a nearby source, eliminating the error-prone primary beam correction.  The global flux calibration, bootstrapped from catalog data of 5 bright sources, is estimated to be accurate to 3.2\%.  Comparing with prior measurements, 45 out of 58 sources observed are found to confirm and refine a spectral index model. This includes Pictor A which provides a key flux reference for PAPER's EoR power spectrum. Combining catalog data at other frequencies with the PAPER data we are able to estimate the flux model parameters to an uncertainty of 2.4\%. This accuracy, which is ultimately limited by the uncertainty of the many prior measurements used to estimate the flux scale, is an order of magnitude improvement on previous estimates.  
\end{abstract}

\keywords{dark ages, reionization, first stars --- catalogs --- instrumentation: interferometers}

Numerous radio telescopes are now exploring the prospects for
using measurements of highly redshifted 21cm emission to inform our understanding
of cosmic reionization in the redshift range $6< z<12$, corresponding to radio frequencies below 200MHz (see reviews in  \citet{Furlanetto:2006p2267,Morales:2010p8093,Pritchard:2012p9555}) .  
These include telescopes aiming to measure the global temperature change of 
21cm emission during the Epoch of Reionization (EoR), such as
the Compact Reionization Experiment (CoRE) and
the Experiment to Detect the Global EoR Signature (EDGES; \citealt{Bowman:2010p8546}),
and interferometers aiming to measure the power spectrum of 21-cm EoR emission, such as
the Giant Metre-wave Radio Telescope (GMRT;
\citealt{Paciga:2011p9470,Paciga:2013p9627})\footnote{\url{http://gmrt.ncra.tifr.res.in/}},
the LOw Frequency ARray (LOFAR; \citealt{Yatawatta:2013p9699})\footnote{\url{http://www.lofar.org/}},
the Murchison Widefield Array (MWA;  \citealt{Bowman:2012p9138}; \citealt{Tingay:2013p9022}))\footnote{\url{http://www.mwatelescope.org/}}, 
and 
the Donald C. Backer Precision Array for Probing the Epoch of Reionization (PAPER;
\citealt{Parsons:2010p6757})\footnote{\url{http://eor.berkeley.edu/}}. Both PAPER and the MWA are located in the southern hemisphere at radio quiet reserves being prepared for the upcoming Square Kilometer Array.  At these low frequencies the Southern sky is much less well known than the North, with the most extensive surveying work being conducted  by the EoR experiments themselves \citep{Jacobs:2011p8438,Williams:2012p8768}.

Neutral hydrogen is visible during reionization as $\sim$30mK excess surface brightness over the CMB punctuated both spectrally and spatially by regions of zero emission.
This patchy signal is predicted to be visible everywhere on the sky at size scales up to degrees, or about $0.1$cMpc$^{-1}$.   To increase the surface brightness sensitivity without building costly dishes, MWA, PAPER and LOFAR have chosen to use combinations of phased and/or correlated dipoles. By design also cover much wider fields of view ($>10$\arcdeg) and bandwidths ($\sim 100$\% fractional) than traditional dish telescopes.   As the elements can not be physically pointed, the apparent flux scale varies across the sky. This direction dependent gain is currently uncertain to 20\% or higher \citep{Jacobs:2013p9713}.  The ideal solution is to use a wide-grid of well-known calibrators to map the primary beam and set the flux scale.  
%The position dependent gain varies for each instrument.   LOFAR and MWA have a range of electrically steerable beams each with a different shape. For MWA and LOFAR, the number of high quality calibration sources is more important.  PAPER has a single broad, 45\arcdeg wide, primary beam; sources at nearby declinations sample the same primary beam many times.
% This will in turn provide a wide base to assess the accuracy of the primary calibrator which sets the overall amplitude of the EoR power spectrum.

However, catalog source fluxes at 150MHz are also inaccurate to the 20\% level, particularly at southern declinations ($<-20$\arcdeg) . Historically, the best EoR band data were by \citet{Slee:1995p7541} with Culgoora Circular Array\footnote{Known during daylight hours as Culgoora Radio Heliograph} and various higher frequency measurements with Parkes.  These data are typically uncertain to 10\% or higher and provide little coverage of the EoR band beyond a single narrow-band data point.

PAPER, in its maximum redundancy configuration, has a very broad beam with large regular grating side-lobes and is therefor limited to using the few sources above $\sim$50 Jy for flux calibration. The best calibrator for most observations is Pictor A. For this source the current best EoR band measurement is uncertain to 12\% and appears to imply spectral flattening in the EoR band \citep{Perley:1997p9312}.

More recent surveys include narrow-band surveys by the GMRT and Mauritius, a deep survey of the region near Hydra A by the 32 antenna MWA prototype \cite{Williams:2012p8768} and a wide field survey by PAPER, also with 32 elements \cite{Jacobs:2011p8438}. Several sub-channels were provided in the Williams catalog, though with 60-80\% error bars ---large compared to the 30\% uncertainty on their wide band measurements.  The latter cover the band and spatial scales relevant to EoR measurements but are limited by the accuracy of the primary beam \citep{Jacobs:2013p9713}.

A method for decoupling uncertain fluxes from the uncertain beam has been described by \citet{Pober:2012p8800}. In simulation the method was able to achieve 3 to 10\% accuracy in measuring the primary beam, depending on the number of antennae and other variables. The Pober method emphasized the need for many repeated measurements of each alt-az pointing. Further investigation is under way to improve and implement this method and would be greatly aided by the availability of precise flux measurements unaffected by primary beam uncertainty. This paper reports a set of flux measurements where a primary beam model has not been used to estimate the flux, but instead are directly calibrated to a single calibrator making the track through the beam.

The spectra were measured by PAPER, a dedicated EoR experiment 
that employs drift-scanning, dual-polarization dipole antennas 
tuned for efficient operation over a 120--170-MHz band located in the South African Karoo desert
on the Square Kilometer Array
South Africa (SKA-SA) reserve, 100km north of the small town of Carnarvon.
The PAPER array has grown from 16 elements deployed in early 2009 to a
64-element imaging array in 2011 (see Figure \ref{fig:antpos}). Since November 2011 it has been arranged in a maximally redundant grid configuration to make deep power spectral integrations.  
\begin{figure*}\centering
\includegraphics[width=0.85\columnwidth]{plots/antpos.png}
\caption{The 64-antenna, minimum-redundancy PAPER array at Karoo Radio Observatory site in South Africa used for these observations.
}\label{fig:antpos}
\end{figure*}

In this paper our primary goal is to provide a subset of accurate fluxes suitable for EoR power spectrum and catalog calibration.  After recording the data used in this paper, PAPER was reconfigured into a redundant layout optimized to detect a small number of power spectrum bins at high precision, an arrangement which trades imaging dynamic range for power spectrum sensitivity. As such it is only able to easily distinguish the very brightest sources on the sky a step necessary for setting the overall flux scale. Of these, Pictor A is one of the most useful, being bright, minimally resolved and far from from confusing structure.

The data  include new measurements of Pictor A that are uncertain to 3.5\%, close to the level of the most precise higher frequency measurements by \citet{Wills:1975p9314}. Using these new measurements we update the spectral calibration model to an accuracy of 2.5\%. As validation of this method, we also measure a selection of 58 additional sources at the same Declination.  The primary beam is calibrated using a single common source (J2331-416), thus limiting the declination probed to $-45 \pm 5$\arcdeg.  The flux scale is set by Monte Carlo fitting to a subset of sources, all of which are calibrated to the Baars et al scale. In \S\ref{sec:Observations} we describe the instrumental setup, observations and analysis method followed. In \S\ref{sec:fits} we compare the spectra with available data followed by conclusions in \S\ref{sec:Conclusion}.

%This declination limit removes the necessity of correcting for a primary beam model and allows us to calculate more precise fluxes that provide a reference standard for future work.

 \section{Observations and Data Reduction}
 \label{sec:Observations}
 Measurements are derived from observations using  the east-west dipole arms of 64 PAPER antennas 
deployed in the Karoo Radio Observatory site in South Africa (see Figure \ref{fig:antpos}).  
A 100-MHz band from 100-200MHz was
correlated with 2048 frequency channels and integrated for 10.7 seconds before visibilities were stored.
Observations included here on  July 4, 2011, running
from JD2455748.17 to JD2455748.72. and October 17, 2011 running from JD2455852.2 to JD2455852.6.
In both seasons two antennas were omitted owing to malfunctioning signal path. This 20 hour long combined dataset provides observations provides complete hour angle coverage for the entire 24 hours of Right Ascension. The July portion of the dataset comes from the same observing campaign described by \cite{Pober:2013p9567} and \cite{Stefan:2012p9707}. 
%July (\#40,\#55), September (\#7,\#28)

%COMPRESSION
\textbf{Compression}\\
In pre-processing, we use delay/delay-rate (DDR) filters \citep{Parsons:2009p7859} to identify
radio-frequency interference (RFI) events, and as part of a data compression
technique that reduces data volume by over a factor of 40.  A more detailed description may be found in Appendix A of \cite{Parsons2013b}, which uses the same compression method on PAPER power spectrum observations. Here we summarize the process.

First, we remove known RFI transmission bands and analog filter edges, and then 
 flag outliers at 6$\sigma$ to remove RFI events.
Next, we suppress foreground emission by applying a DDR filter to remove delays and delay-rates 
within the horizon limit of a 300-m baseline (the maximum length of any PAPER baseline).
We derive a second set of RFI flags by masking 4$\sigma$ outliers in these residuals and apply these flags back
to the unfiltered data.  Finally, we compress the data by applying a 
DDR filter preserving emission within the horizon limit of a 300-m baseline, deconvolving to suppress 
flagging artifacts, and down-sampling the result in time/frequency domain to the critical Nyquist rate of
the DDR filter.
The result is that the 2048 original frequency channels become 203, and the
60 original time samples per 10-minute file become 14.

%CALIBRATION
\textbf{Antenna calibration}\\
Antennae delays and amplitudes were found by fitting a point source visibility model to Centaurus A, Pictor A, and Fornax A.  Each source is imperfectly modeled by a single point-source, but the solution differences are minimized by averaging over the three independent solutions. These same calibration solutions have also been successfully applied in the power spectrum analysis by Pober (2013) and Centaurus A imaging by Stefan (2013).

%BEAMFORMING,FILTERING, AVERAGING
\textbf{Source Selection}\\

To provide a basis for establishing the accuracy of the Pictor measurement we measured more sources.  Specifically, we choose sources from the Molonglo Reference Catalog \cite[MRC]{Large:1981p7798} that are within 5\arcdeg in declination of a common calibrator (J2331-416) and have a flux extrapolated from 408MHz greater than 10Jy assuming a power law spectral index of -1.\footnote{Most radio
  sources in this band have power law spectra $S(\nu) =
  \left(\frac{\nu}{\nu_0}\right)^\alpha$.  The 5\arcdeg distance between source and calibrator was chosen as a balance between number of sources included and the known smoothness of the beam.   The average spectral index
  for radio sources in this band is $-0.8$.} This selection contains 62 sources in a narrow stripe that passes through the majority of the southern EoR fields, much of the galaxy and Centaurus A.

\textbf{Beamforming}\\
Spectral time-series are computed by beam-forming to the selected sky locations. A beam is formed by phasing baselines to the desired location and summing over baselines.  %Samples were only included if there was a calibrator sample within 5\arcdeg in altitude/azimuth.   By using both seasons of data we were able to match all measurements with calibrator measurements, making this cut moot. 
 These complex spectra are then delay-delay rate filtered to remove spectrally smooth sources far from phase center \citep{Parsons:2009p7859} (cf the LOFAR de-mixing approach \cite{Offringa:2012p9691})  producing a time dependent spectrum. This is then averaged in time,  weighting by a model of the primary beam. This down-weighting, or multiplying by the primary beam, should be clearly distinguished from up-weighting, which we are at pains to avoid.  Weighting by another factor of the primary beam is an effective approximation of inverse-variance weighting \citep{Pober:2012p8800} and reduces the contribution of noisy low elevation measurements.  The result is equivalent to a very long earth rotation synthesis image with a single image pixel. When combined with the filtering it is a robust and simple method for measuring spectra of unresolved sources. 
\begin{figure}
\includegraphics[width=0.9\textwidth]{plots/PicA_Oct2011_uv_coverage.png}
\caption{The effective uv coverage, showing the relative contributions of each baseline when beam-forming on Pictor over a 9.6 hour synthesis in the October observing session. \label{fig:uv_coverage}}
\end{figure}

The beam-forming method assumes the target is a point source. Our primary target, Pictor A, is slightly resolved by PAPER, and merits closer attention. Pictor A is a double-lobed radio galaxy with a main lobe separation of 7\arcmin. As we see in Figure \ref{fig:pic_perley}, it is nearly unresolved by PAPER's 15\arcmin synthesized beam. However, given the high SNR of the observations, resolution effects are observers, in a slight decrease in flux on the longest ($\sim$300m) baselines. We account for this by weighting baselines in the beam form step according to a model of structure observed by \citet{Perley:1997p9312} at 330MHz, which they found to be consistent with their more limited 74MHz images as well as the detailed high frequency maps.  The normalized image is Fourier transformed and sampled at the desired uv spacing by spline interpolation. These samples are used to weight each baseline contribution in the baseline sum. The result is an estimate of the total integrated flux for Pictor A. Where the resolution is highest, at the top of the band, the correction is 3\%. At the bottom of the band, where the resolution size has grown to 19\arcmin, the correction is only 0.6\%. The resulting spectrum is shown in Figure \ref{fig:pic_spectrum}a.
\begin{figure}
\includegraphics[width=0.96\textwidth]{plots/picA_Perley.png}
\caption{Pictor A imaged at 330MHz by the VLA \citep{Perley:1997p9312}. Black circle indicates PAPER resolution at the 150MHz, dashed, the resolution at 185MHz.  To correct for the small residual structure in the PAPER measurements we interpolated the PAPER baselines in the uv plane. At the highest frequency this led to a 3\% correction, at the lowest frequency, 0.6\%.  \label{fig:pic_perley}}
\end{figure}

%BANDPASS CALIBRATION
\textbf{Spectral calibration}\\
\label{sec:Calibration}
The gain of each channel is the product of an overall instrumental passband and the spectral dependence of the primary beam in the direction of the source.  Sources sharing the same track through the primary beam will have the same average spectral gain function resulting from frequency dependent primary beam attenuation.   We matched each measured source spectrum time sample to the nearest sample (in altitude/azimuth) of a calibrator source (J2331-416)\footnote{This source was chosen for the amount of data found in the literature and the apparent smoothness of the spectrum.}.  We then, average the two matched data streams in time.  Since both tracks make the same slice through the primary beam, they will have the same average effective gain. Assuming a power law model for J2331-416 (33Jy $\alpha=-0.76$), we compute a bandpass gain.  After calibrating the raw 203 channel spectra with this bandpass, we average into 10MHz sub-bands between 120 and 180 MHz, computing the standard deviation as an estimate of the error.

\textbf{Catalogs}\\
Data for prior comparison was pulled from two major sources. Catalog values for Pictor A, and the flux calibration sources were pulled directly from the NASA/IPAC Extragalactic Database (NED) \footnote{\url{http://ned.ipac.caltech.edu/}}. Cross-matching radio sources between bands is made difficult by changes in resolution, spectral curvature, and resolved multi-scale structure.  For a small number of sources these problems can be ameliorated by inspection of the spectra, source names, coordinates,  and originating publications. However for a large sample of sources this becomes unwieldily and prone to error. Thus for the larger number of samples we make use of the Vollmer et al meta-catalog which takes pains to match multi-wavelength observations \citep{Vollmer:2010p6422}.% given the known source dimensions and spectral properties as well as telescope bandwidth and spatial resolutions.

\textbf{Flux Scale}\\
\label{sec:flux_scale}
At this stage each source flux is tied to a model fit on the catalog values of J2331-416. The accuracy of this fit and the implied uncertainty in the flux scale limits the accuracy of the PAPER measurements..  To refine the flux scale, we bootstrap a single global flux scale correction factor using 5 sources selected for their brightness, spectral linearity and data availability\footnote{Calibration sources: 2250-412,2331-416,2140-434,0007-446,0704-427}. To build a more complete spectral model we go beyond the data found in SPECFIND, using all spectral measurements below 2GHz found in the NED database.  These catalog measurements are primarily by Parkes, and Molonglo with the best precision coming from the Wills fluxes at 538 and 634 MHz (when available). Where error bars are not given, we assume uncertainty of 25\%.

As described in the Appendix, we fit spectral index models for all sources (using catalog data) simultaneously with a global PAPER flux scale factor (using the PAPER data). We fit the model using a Markov Chain Monte Carlo sampler to sample the posterior probability of PAPER data ($SPAPER_{\nu}$) and catalog values ($Scat_{\nu}$) given a spectral index model for each source and a global flux scale factor ($g$) ($S_\PAPER^\textrm{calibrated} = g S_\PAPER$). The resulting flux scale distribution function is shown in Figure \ref{fig:gain}. The 76\% confidence limit on this flux scale, relative to the J2331-413 calibration, is  $-0.01 ^{+0.11}_{-0.17}$ dB, or a 3.24\% multiplicative error on every calibrated PAPER measurement.

The calibrated spectra are plotted in Figures \ref{fig:srcs1},\ref{fig:srcs2}, \& \ref{fig:srcs3} and the data are listed in Table \ref{tab:data}.  See the Appendix for details on this fitting procedure and definition of terms.  The resulting Pictor A spectrum ranges in precision from 6.5\% at 125MHz to 4.7\% at 185MHz. At least half of this error is due to uncertainty in the flux scale.  %\footnote{Of the 315 data points in this catalog, 7 fluxes points are negative. All three occur quite close to Centaurus A, which has large structure on degree scales in this region and is the brightest sources in the sky. These sources have been flagged and removed from further analysis.}

%The Pictor track is calibrated to 2331-416 ($S_{150}=33.8$Jy,$\alpha=-0.76$) and the Hydra A track to 0231-126 ($S_{150}=21$Jy,$\alpha=-0.7$).  
%    cal['0213-132'] = 21 * (fq/.150)**-0.7  
%    cal['1932-464'] = 93.7 * (fq/.150)**-0.82 
%    #cal['2331-416'] = 31.9 * (fq/.150)**-0.69
%    cal['2331-416'] = 33.9 * (fq/.150)**-0.76
%COMPARISON WITH DATA

 \section{Spectral Results}
 \label{sec:fits}
The primary purpose of this observation is to produce a high quality Pictor A spectrum. As a verification measure we have observed many other sources at the same declination for comparison against previous observations.  Our comparison metric will be the degree to which the PAPER data are consistent with previous observations,given a model and, if consistent, they improve on the precision of our spectral model parameters.

To compare with observations at other frequencies we must assume a spectral model. The prevailing spectral model for low frequency radio sources is a single power law due to synchrotron emission, though curvature or other deviation from a power-law is not-uncommon.   To establish a baseline model, we fit a spectral model to prior catalog data from the spectrally and spatially cross-matched meta-catalog by \citet{Vollmer:2010p6422} using the MCMC method described in \S \ref{sec:flux_scale} and the Appendix. Confidence contours for these fits are shown in grey in Figs. \ref{fig:SI_contour_1} - \ref{fig:SI_contour_4}.  In general these are lower limits on the possible precision, as the Vollmer catalog emphasizes minimization of cross-match error but at the cost of excluding data points.  The fit is then performed again with both PAPER and catalog data, shown in black on the same Figures. The values are given in Table \ref{tab:fits}.

%0008-421#
%1243-412#
%1247-401#
%1315-460
%TODO round up the source counts
In the 59 sources measured, four demonstrated poor convergence fitting a single spectral index to both the PAPER data and prior catalog data. In three cases\footnote{1243-412,1247-401,1315-460} %TODO update
these sources are in the Centaurus A/galactic plane region. Though the beam forming method provides relatively high dynamic range of $\sim$100:1 it is unable to distinguish between these sources and the bright diffuse Centaurus and galactic structure. The last source, 0008-421, was not detected by previous PAPER observations and exhibits flattening at higher frequencies, most likely due to synchrotron self-absorption \citep{Jacobs:2011p8438} .  The remaining 94\% MCMC chains arrived at a stable posterior distribution. The spectral index parameters for these chains are given in table \ref{tab:fits}.

Inspecting the confidence contours we find that, for the vast majority ($\sim 75$\%), the PAPER measurements confirm the power law extrapolation from higher frequencies. The remaining 25\% either A) have large PAPER error bars and therefor provide no new information or B) do not agree with the spectral index model.  To understand where most measurements fall on this spectrum we numerically quantify the overall model improvement derived from the addition of the PAPER data as 
\begin{align}
\textrm{Improvement} &= \left(\textrm{Precision increase}\right) \left(\textrm{Catalog agreement}\right)\\
&= \left(\frac{1}{Area(\textrm{PAPER})} - \frac{1}{Area(\textrm{Cat})}\right) \left( Area(\PAPER \cap \textrm{Cat}) \right)
\end{align}

We quantify the fit {\em precision increase} as the change in the contour figure of merit, defined as the inverse area of the confidence contour. Meanwhile, {\em catalog agreement} is the fraction of the PAPER confidence interval that overlaps the catalog confidence interval.  Thus, for example, in a PAPER fit that overlaps the catalog confidence contour by 41\% but increases in precision (confidence area shrinks) by a factor of 3, the resulting {\em improvement} will be 0.123.

In these sources, the improvement index ranges from a max of 6.9 to -0.022. 10\% of sources showed negative improvement, suggesting that PAPER data have added to uncertainty (see Figure \ref{fig:SI_contour_bad}). 12\% of sources have exactly zero improvement, which indicates that the PAPER data have pulled the fit far from the model preferred by the catalog data (see Fig. \ref{fig:SI_contour_new}).  The spectral models of these sources have not been included in Table \ref{tab:fits}.  The remainder of the spectral fits are included for completeness, but given the range of quality found, particularly near the Galactic plane and Centaurus A, should be used with utmost caution.

However, the majority of source 78\% have positive improvement index, indicating strong confirmation of the extrapolated spectrum (see Figures  \ref{fig:SI_contour_1} - \ref{fig:SI_contour_4}).  Pictor A is in the middle of this group  with an improvement of 0.39 ---only 14 sources show stronger confirmation.  The flux model is $S150=$388 $\pm$ 9.4Jy, $\alpha=-0.77\pm0.02$. The combination of several independent PAPER data points near 150MHz with previous catalog measurements results in this estimated uncertainty of 2.4\%. This uncertainty is dominated by agreement between the 2 Wills measurements near 600MHz which are accurate to 2\% and the five PAPER measurements, which are accurate to ~5\%.

 \section{Discussion and Conclusions}
 \label{sec:Conclusion}

Direct measurements of the Pictor A spectrum are key to correctly setting the flux scale of PAPER and other EoR experiments. Existing EoR band measurements are accurate to 20\% implying a 40\% uncertainty in the absolute power spectrum level.  Here we have provided new measurements of Pictor A that are accurate to 2.4\%;  388 $\pm$ 9.4Jy on the \citet{Baars:1977p9678} scale. The PAPER measurement has a precision of $<$1\%; the majority of the uncertainty comes in setting the absolute flux scale from prior data.

We also take advantage of multiple PAPER observations to measure the next  61 brightest, previously cataloged, sources. These sources are distributed over the full 24 hours of Right Ascension coverage but are within 5 degrees declination of Pictor A.  Using a Bayesian analysis we conclude that most of these are consistent with previous measurements and provide useful new constraints. However, in the remainder, the simple spectral model fails to adequately describe the data. In most cases the proximity to bright or extended structures implies side lobe contamination.  Therefore, though we include the model parameters, they are not meant to be definitive, but provide confidence that the reported PAPER flux values are on the correct global scale.

\begin{figure*}
\centering
\includegraphics[width=0.9\textwidth]{plots/2250-412_2331-416_2140-434_0007-446_0704-427_gain_mcmc_chain_gain_conf.png}

\caption{The marginalized PAPER flux scale factor posterior probability distribution function bootstrapped from the NED database listings for 2250-412,2331-416,2140-434,0007-446 and 0704-427 below 2GHz.  \label{fig:gain}}
\end{figure*}

\begin{figure*}[htbp]
\includegraphics[width=0.49\textwidth]{plots/pictor_spectrum.png}
\includegraphics[width=0.49\textwidth]{plots/pic_SI_MCMC.png}
\caption{Using new PAPER results to constrain the spectrum of Pictor A.
On the left, the PAPER Pictor A spectrum with 2$\sigma$ error bars (x) and  MCMC fits (grey cloud). Inset allows comparison between the 10MHz averaged points with the 403kHz points (grey). The oscillations in the PAPER spectrum are residual side lobe contamination from other sources and are well represented by the error bars.  The most reliable prior measurements (dots) are those by \cite{Wills:1975p9314} at 580MHz and 635MHz \citep{Perley:1997p9312}. The rest are from with Culgoora \cite{Slee:1995p7541} or Parkes  \cite{Otrupcek:1991p8780} and have been set to the (extrapolated) \citet{Baars:1977p9678} scale by  \cite{Kuehr:1981p9628}. A sub-sample of MCMC fits are shown in blue. On the right, the grey contour indicates the 76\% confidence interval for 150MHz flux and spectral index given the prior data. Black folds in the PAPER data. }
\label{fig:pic_spectrum}
\end{figure*}

%%calibrators
%%2250-412_2331-416_0043-424
%\begin{figure*}[htbp]
%\includegraphics[width=0.2\textwidth]{plots/2250-412_calfit.png}
%\includegraphics[width=0.2\textwidth]{plots/2250-412_SI_MCMC.png}
%\includegraphics[width=0.2\textwidth]{plots/2331-416_calfit.png}
%\includegraphics[width=0.2\textwidth]{plots/2331-416_SI_MCMC.png}\\
%\includegraphics[width=0.2\textwidth]{plots/0043-424_calfit.png}
%\includegraphics[width=0.2\textwidth]{plots/0043-424_SI_MCMC.png}
%\includegraphics[width=0.2\textwidth]{plots/1932-464_calfit.png}
%\includegraphics[width=0.2\textwidth]{plots/1932-464_SI_MCMC.png}
%
%\caption{Sources used to calculate the flux scale. Catalog data for the three sources are used to simultaneously fit a 
%single spectral index gain model for each source (grey contours) and a single PAPER gain parameter  .\label{fig:cals} }
%
%\end{figure*}
%add calibrator

\section*{Acknowledgements}
The PAPER project is supported by the National Science Foundation (awards 0804508, 1129258, and 1125558), and a generous grant from the Mt. Cuba Astronomical Association.

This work makes use of ]the ``MCMC Hammer"
	emcee python library \citep[  \url{http://danfm.ca/emcee/}]{ForemanMackey:2012p8684}  and the NASA/IPAC Extragalactic Database (NED) which is operated by the Jet Propulsion Laboratory, California Institute of Technology, under contract with the National Aeronautics and Space Administration.

\section*{Appendix: Model Fitting}
In this paper we estimate spectral model parameters and flux calibration in a Bayesian way by calculating and marginalizing the posterior probability of the data, past and present, given a spectral and instrumental model.   This method offers improved repeatability by specifying a single objective function that represents the quality of the model fit and naturally defines the errors on the parameters \citep{Hogg:2010p8759}.   See  \citet{Mackay:2003p9717}  or \citet{Sivia:2006p9736} for more on Bayesian analysis methods and an excellent astrophysical example by \cite{Press:1997p9783}.

In general an experiment measures data $D$ and given some model of the statistics of the measurement one usually assigns an error bar defining the probability of getting that data, given a model $M$.  Given all the new data, and prior data, there will be a new optimal set of model parameters $M$ with associated error bars.  In general, these error bars are a parameterization of a probability distribution function.  The pdf associated with the data often called the likelihood ($\mathcal{L}$), while the one corresponding the model error bars is the {\em posterior probability distribution}, $\Prob(M|D)$. They are related

\[
\Prob(M|D) = \frac{\mathcal{L}(D|M) \Prob(M)}{\Prob(D)}
\] 
by the factor $\frac{\Prob(M)}{\Prob(D)}$, the prior probability of the model $M$ (given past experiments) over the normalization factor, integrating over all models.  In general the posterior pdf depends on both the known relation between the model parameters and as well as correlations hidden within the data.

Direct calculation of the posterior is difficult, particularly the normalization factor, however there is a simple procedure for drawing samples from the posterior. In this paper we use a Markov Chain Monte Carlo sampler. Given any current location in parameter space, this algorithm draws a new set of parameters and computes the relative likelihood increase. If the probability difference is larger than a number drawn randomly from the set $(0:1]$, the jump is accepted ---a Metropolis-Hastings step. In the limit of an infinity of such steps, this process has been shown to converge on the true posterior distribution.  In practice it is run for a large number of steps until things appear to stabilize. The best fit model is the median of all the sampled parameter sets, while the volume containing a well defined fraction of samples sets the confidence limits.  The oft quoted ``1$\sigma$" probability level corresponding to a gaussian distribution contains 65\% of the samples. In practice the contours are not gaussian. Here we choose a slightly more conservative probability level of 76\%

In \S \ref{sec:fits} we fit a spectral power law to catalog values by sampling a (log) likelihood which assumes Gaussian measurement errors

\[
\logL = \sum_\nu{\frac{\left(S_\nu - S150\left(\frac{\nu}{150}\right)^\alpha\right)^2}{\Delta \textrm{SPAPER}_\nu}} \label{eq:catlogL}
\]

We estimate the confidence interval of the resulting parameters as the boundary enclosing 76\% of the samples. In the catalog we report both the upper and lower of these values for both parameters and plot the 2D contour to show the correlation of the two parameters. Many of these contours, the grey curves in Fig. \ref{fig:SI_contour_1}, are classic banana plots, displaying a non-linear correlation between the parameters.    In most cases the single contour adequately describes 2D posterior distribution.

\begin{figure}[htbp]
\includegraphics[width=0.49\textwidth]{plots/pic_trace_hist.png}
\includegraphics[width=0.49\textwidth]{plots/1556-466_trace_hist.png}
\caption{A more detailed view of the posterior probability distribution. On the left Pictor A, on the right 1556-466. Confidence contours range from 0.2 to 0.8. Compare with the contours for this source shown in Fig. \ref{fig:SI_contour_3}.  As above, grey for  the fit to catalog data, black for joint catalog and PAPER fit. }
\end{figure}

A single overall flux scale is computed in a similar way. However, here we add a single extra gain factor $g$ multiplying all PAPER measurements, and sum over several sources.

\begin{align}
\log\mathcal{L}_s &= \sum_{\nu}\frac{ (S_\textrm{cat}^{\nu}  - S_{150}  \left(\frac{\nu}{150}\right)^\alpha)^2}{2(\Delta S_\textrm{cat}^\nu)^2} +
\frac{ (g*S_\PAPER^{\nu}  - S_{150}\left(\frac{\nu}{150}\right)^\alpha)^2}{2(\Delta S_\PAPER^\nu)^2}\\
\log\mathcal{L} &= \sum_{s} \log\mathcal{L}_s
\end{align}
Another nice feature of the MCMC sampler is that each parameter sample is fully covariant with the others. To marginalize over the fitted flux and spectral index parameters and compute confidence limits on the gain parameter, we simply ignore them.

\begin{figure*}[htbp]
\begin{center}
\includegraphics[width=0.9\textwidth]{plots/srcfig_1.png}
\end{center}
\caption{PAPER spectra of 16 sources compared against existing data out of  \cite{Vollmer:2010p6422} between 40MHz and 2GHz, otherwise as described in Figure \ref{fig:pic_spectrum}.\label{fig:srcs1}. Sources used to bootstrap the flux calibration are noted with a *.}
\end{figure*}

\begin{figure*}[htbp]
\begin{center}
\includegraphics[width=0.9\textwidth]{plots/srcfig_2.png}
\caption{PAPER spectra of 16 sources compared against existing data out of  \cite{Vollmer:2010p6422} between 40MHz and 2GHz, otherwise as described in Figure \ref{fig:pic_spectrum}.\label{fig:srcs2} Sources used to bootstrap the flux calibration are noted with a *.}
\end{center}
\end{figure*}

\begin{figure*}[htbp]
\begin{center}
\includegraphics[width=0.9\textwidth]{plots/srcfig_3.png}
\caption{PAPER spectra of 16 sources compared against existing data out of  \cite{Vollmer:2010p6422} between 40MHz and 2GHz, otherwise as described in Figure \ref{fig:pic_spectrum}.\label{fig:srcs3} Sources used to bootstrap the flux calibration are noted with a *.}
\end{center}
\end{figure*}

%(PAPER_imaging)danny@keynes:plots$ python sort_SI_plots.py psa64_pic_stripe_perleycorr_SEDfits.txt
%BEGIN PASTE
%the best sources. High quality fit that improves on previous knowledge
\begin{figure*}[htbp]
\begin{center}
\includegraphics[width=2in]{plots/0003-428_SI_MCMC.png} %0.1064
\includegraphics[width=2in]{plots/0007-446_SI_MCMC.png} %0.1851
\includegraphics[width=2in]{plots/0039-445_SI_MCMC.png} %0.7325
\includegraphics[width=2in]{plots/0043-424_SI_MCMC.png} %0.2527
\includegraphics[width=2in]{plots/0048-447_SI_MCMC.png} %0.0596
\includegraphics[width=2in]{plots/0049-433_SI_MCMC.png} %0.2988
\includegraphics[width=2in]{plots/0103-453_SI_MCMC.png} %0.007
\includegraphics[width=2in]{plots/0201-440_SI_MCMC.png} %2.3481
\includegraphics[width=2in]{plots/0438-436_SI_MCMC.png} %0.0595
\includegraphics[width=2in]{plots/0511-484_SI_MCMC.png} %2.6709
\includegraphics[width=2in]{plots/0534-497_SI_MCMC.png} %2.6256
\includegraphics[width=2in]{plots/0546-445_SI_MCMC.png} %0.1024
\end{center}
\caption{Spectral model contours as described in Figure \ref{fig:pic_spectrum}. Sources marked with a
* were used to assess calibration error.
}\label{fig:SI_contour_1}
\end{figure*}
\clearpage
\begin{figure*}[htbp]2\begin{center}
\includegraphics[width=2in]{plots/0547-408_SI_MCMC.png} %0.1044
\includegraphics[width=2in]{plots/0647-475_SI_MCMC.png} %0.8893
\includegraphics[width=2in]{plots/0700-473_SI_MCMC.png} %1.709
\includegraphics[width=2in]{plots/0704-427_SI_MCMC.png} %0.0824
\includegraphics[width=2in]{plots/0748-440_SI_MCMC.png} %0.3377
\includegraphics[width=2in]{plots/0748-454_SI_MCMC.png} %0.0699
\includegraphics[width=2in]{plots/0809-492_SI_MCMC.png} %1.2296
\includegraphics[width=2in]{plots/0819-474_SI_MCMC.png} %1.5069
\includegraphics[width=2in]{plots/1017-421_SI_MCMC.png} %0.0031
\includegraphics[width=2in]{plots/1017-426_SI_MCMC.png} %0.0455
\includegraphics[width=2in]{plots/1046-409_SI_MCMC.png} %0.0055
\includegraphics[width=2in]{plots/1302-491_SI_MCMC.png} %0.0592
\end{center}
\caption{Spectral model contours as described in Figure \ref{fig:pic_spectrum}. Sources marked with a
* were used to assess calibration error.
}\label{fig:SI_contour_2}
\end{figure*}
\clearpage
\begin{figure*}[htbp]2\begin{center}
\includegraphics[width=2in]{plots/1358-493_SI_MCMC.png} %0.4795
\includegraphics[width=2in]{plots/1421-490_SI_MCMC.png} %0.891
\includegraphics[width=2in]{plots/1424-418_SI_MCMC.png} %0.0056
\includegraphics[width=2in]{plots/1445-468_SI_MCMC.png} %0.973
\includegraphics[width=2in]{plots/1526-423_SI_MCMC.png} %0.0961
\includegraphics[width=2in]{plots/1552-433_SI_MCMC.png} %0.9684
\includegraphics[width=2in]{plots/1556-466_SI_MCMC.png} %1.4713
\includegraphics[width=2in]{plots/1616-457_SI_MCMC.png} %0.0157
\includegraphics[width=2in]{plots/1618-430_SI_MCMC.png} %2.7782
\includegraphics[width=2in]{plots/1633-409_SI_MCMC.png} %0.2602
\includegraphics[width=2in]{plots/1839-487_SI_MCMC.png} %0.135
\includegraphics[width=2in]{plots/1840-404_SI_MCMC.png} %0.1159
\end{center}
\caption{Spectral model contours as described in Figure \ref{fig:pic_spectrum}. Sources marked with a
* were used to assess calibration error.
}\label{fig:SI_contour_3}
\end{figure*}
\clearpage
\begin{figure*}[htbp]2\begin{center}
\includegraphics[width=2in]{plots/1932-464_SI_MCMC.png} %0.0164
\includegraphics[width=2in]{plots/1940-406_SI_MCMC.png} %0.0524
\includegraphics[width=2in]{plots/1953-425_SI_MCMC.png} %0.0739
\includegraphics[width=2in]{plots/2140-434_SI_MCMC.png} %0.3123
\includegraphics[width=2in]{plots/2213-456_SI_MCMC.png} %0.1767
\includegraphics[width=2in]{plots/2226-411_SI_MCMC.png} %0.1166
\includegraphics[width=2in]{plots/2250-412_SI_MCMC.png} %0.2199
\includegraphics[width=2in]{plots/2323-407_SI_MCMC.png} %6.9237
\includegraphics[width=2in]{plots/2331-416_SI_MCMC.png} %0.2179
\end{center}
\caption{fits of the next 16 sources, as described in Figure \ref{fig:SI_contour_1}. Sources marked with a
* were used to assess calibration error.
}\label{fig:SI_contour_4}
\end{figure*}
%BEGIN PASTE
\begin{figure*}[htbp]
\begin{center}
%ok fit, but doesn't agree with past data, or actually increases model uncertainty
%contour length limit =  209.039667221
%Poor improvement:  1116-462 8.66,9.97,11.27 -0.72,-0.59,-0.47 8.56,9.82,11.15 -0.71,-0.58,-0.46 0.22 0.23 -0 0.6 -0.0018 164.0
\includegraphics[width=2in]{plots/1116-462_SI_MCMC.png} %-0.0018
%Poor improvement:  1143-483 13.47,15.46,17.58 -0.83,-0.7,-0.57 9.91,11.65,13.51 -0.7,-0.56,-0.44 0.34 0.37 -0.03 0.21 -0.0064 122.0
\includegraphics[width=2in]{plots/1143-483_SI_MCMC.png} %-0.0064
%Poor improvement:  1215-457 15.08,16.94,18.88 -0.59,-0.47,-0.36 11.28,12.93,14.57 -0.46,-0.33,-0.21 0.36 0.39 -0.03 0.15 -0.0042 122.0
\includegraphics[width=2in]{plots/1215-457_SI_MCMC.png} %-0.0042
%Poor improvement:  1221-423 9.46,11.52,13.87 -0.96,-0.78,-0.61 6.77,8.6,10.49 -0.78,-0.57,-0.39 0.45 0.53 -0.08 0.27 -0.022 116.0
\includegraphics[width=2in]{plots/1221-423_SI_MCMC.png} %-0.022
%Poor improvement:  1232-416 9.42,10.83,12.3 -0.88,-0.75,-0.63 9.2,10.57,11.96 -0.88,-0.74,-0.62 0.22 0.22 -0 0.57 -0.002 164.0
\includegraphics[width=2in]{plots/1232-416_SI_MCMC.png} %-0.002
%Poor improvement:  1407-425 13.6,15.19,16.86 -1.21,-1.09,-0.98 9.91,11.35,12.85 -1.07,-0.94,-0.82 0.36 0.41 -0.05 0.11 -0.0059 128.0
\includegraphics[width=2in]{plots/1407-425_SI_MCMC.png} %-0.0059
\end{center}
\caption{fits of the worst sources. Contours as described in Figure \ref{fig:SI_contour_1}. The fit either disagrees
with past data or does not offer any improvement (improvement index $\le 0$). All are near
the galactic plane and are likely dominated by sidelobes.
}\label{fig:SI_contour_bad}
\end{figure*}

\begin{figure*}[htbp]
\begin{center}
%zero overlap
\includegraphics[width=2in]{plots/1246-410_SI_MCMC.png} %-0
\includegraphics[width=2in]{plots/1320-446_SI_MCMC.png} %0.0
\includegraphics[width=2in]{plots/1355-416_SI_MCMC.png} %0.0
\includegraphics[width=2in]{plots/1416-493_SI_MCMC.png} %-0
\includegraphics[width=2in]{plots/1459-417_SI_MCMC.png} %0
\includegraphics[width=2in]{plots/cen_SI_MCMC.png} %0.0
\end{center}
\caption{These sources offer results at odds with previous measurements. These have small enough error bars to require a deviation from spectral index fit suggested by prior catalog measurements. All are near Centaurus A (see Figure \ref{fig:error_map}), a very bright, extended source, and are likely evidence for side lobe contamination.  Side lobes from distant sources manifest as ripples in the spectrum, increasing the error bars (e.g. the sources listed in Figure \ref{fig:SI_contour_bad}). However, the sources shown here are close enough to Centaurus A that the side-lobe oscillates on scales longer than 10MHz and does not fall into the rms, but rather into the mean. Thus these few points have anomalously high fluxes and small error bars. }
\label{fig:SI_contour_new}
\end{figure*}

%END PASTE

\begin{figure*}
\includegraphics[width=\textwidth]{plots/psa64_pic_strip_positions_annotated_cropped.png}
\caption{A map of the radio sky centered on the south pole \citep{deOliveiraCosta:2008p2242}.  x's mark measured locations and have size scaled by agreement with prior data (inverse ``improvement index", see \S\ref{sec:fits}). Black dots indicate sources with $\le0$ improvement score. For these the fit quality decreases with addition of PAPER data or the model revision disagrees completely with the prior estimate due to side lobes or spectral curvature.  We estimate that   \label{fig:error_map}}
\end{figure*}

%TODO catalog format, table for data points and a table for fit results

\begin{deluxetable}{lllllllllllll}
\tablecolumns{13}
\tablecaption{PAPER spectra for 59 MRC sources. Full table available online}
\tablehead{
\colhead{Name} &
\colhead{\parbox[c][3em]{2em}{Ra \unit{deg}}} & 
\colhead{\parbox[c][2em]{2em}{Dec \unit{deg}}} &
\colhead{\parbox[c][2em]{2em}{S125 \unit{Jy}}} &
\colhead{\parbox[c][2em]{2em}{rms \unit{Jy}}} &
\colhead{\parbox[c][2em]{2em}{S135 \unit{Jy}}} &
\colhead{\parbox[c][2em]{2em}{rms \unit{Jy}}} &
\colhead{\parbox[c][2em]{2em}{S145 \unit{Jy}}} &
\colhead{\parbox[c][2em]{2em}{rms \unit{Jy}}} &
\colhead{\parbox[c][2em]{2em}{S155 \unit{Jy}}} &
\colhead{\parbox[c][2em]{2em}{rms \unit{Jy}}} &
\colhead{\parbox[c][2em]{2em}{S165 \unit{Jy}}} &
\colhead{\parbox[c][2em]{2em}{rms \unit{Jy}}}
}
\startdata
Pictor A&	80.1&	-45.79&	459.23&	30.2&	416.59&	28.3&	397.17&	21.8&	375.14&	18.5&	359.72&	17.1 \\
0003-428&	1.67&	-42.5&	14.98&	2.0&	13.45&	1.2&	13.02&	1.8&	12.9&	1.6&	10.42&	1.2 \\
0007-446&	2.79&	-44.31&	23.51&	2.5&	21.18&	2.4&	20.24&	1.5&	18.74&	1.5&	17.61&	1.8 \\
0008-421&	2.88&	-41.81&	-0.94&	1.7&	-0.68&	1.7&	0.54&	1.8&	0.52&	1.4&	1.98&	1.8 \\
0039-445&	10.69&	-44.16&	31.95&	2.9&	30.29&	3.0&	28.54&	2.1&	26.0&	1.9&	24.06&	1.4 \\
0043-424&	11.72&	-42.05&	51.9&	4.2&	47.43&	3.5&	45.82&	2.6&	42.74&	3.0&	40.68&	2.6 \\
0048-447&	12.86&	-44.41&	17.86&	2.6&	16.02&	2.3&	15.15&	2.5&	14.51&	1.5&	12.51&	1.6 \\
0049-433&	13.21&	-43.03&	23.53&	2.4&	21.0&	1.5&	21.94&	2.4&	20.2&	1.9&	18.85&	2.1 \\
0103-453&	16.48&	-45.02&	35.5&	3.2&	32.61&	3.5&	30.86&	2.4&	28.21&	2.5&	27.2&	1.5 \\
0201-440&	31.05&	-43.77&	16.22&	4.4&	15.02&	1.7&	13.73&	1.7&	12.78&	1.2&	14.07&	1.7 \\
0438-436&	70.17&	-43.53&	8.44&	2.5&	6.26&	1.9&	8.05&	1.6&	5.74&	2.1&	9.0&	1.7 \\

\enddata
\label{tab:data}
\end{deluxetable}

%note: put at top of latex file \newcommand{\unit}[1]{\footnotesize \#1}
\begin{deluxetable}{ccccccccccc}
\tablecolumns{11}
\tablecaption{Spectral fits for 52 MRC sources with and without PAPER.}
\tablehead{
\multicolumn{3}{c}{ }&
\multicolumn{4}{c}{PAPER\tablenotemark{1} + Catalog}&
\multicolumn{4}{c}{Catalog\tablenotemark{2}}\\
\colhead{Name} &
\colhead{\parbox[c][3em]{2em}{Ra\\ \unit{deg}}}& 
\colhead{\parbox[c][3em]{2em}{Dec\\ \unit{deg}}} &
\colhead{\parbox[c][3em]{2em}{$S150$\\ \unit{Jy}}} &
\colhead{\parbox[c][3em]{2em}{$\Delta$S\\ \unit{Jy}}} &
\colhead{\parbox[c][3em]{2em}{$\alpha$\\ \unit{--}}} &
\colhead{\parbox[c][3em]{2em}{$\Delta\alpha$\\ \unit{--}}} &
\colhead{\parbox[c][3em]{2em}{$S150_p$\\ \unit{Jy}}} &
\colhead{\parbox[c][3em]{2em}{$\Delta S_p$\\ \unit{Jy}}} &
\colhead{\parbox[c][3em]{2em}{$\alpha_p$\\ \unit{--}}} &
\colhead{\parbox[c][3em]{2em}{$\Delta\alpha_p$\\ \unit{--}}}
}
\startdata
Pictor A&	80.09&	-45.79&	388.92&	9.35&	-0.77&	0.02&	392.08&	21.36&	-0.77&	0.04 \\
0003-428&	1.67&	-42.5&	11.61&	0.54&	-0.81&	0.03&	10.32&	0.76&	-0.73&	0.05 \\
0007-446&	2.79&	-44.31&	18.74&	0.69&	-1.0&	0.03&	16.98&	1.26&	-0.93&	0.05 \\
0039-445&	10.69&	-44.16&	26.77&	1.08&	-0.92&	0.11&	22.71&	5.1&	-0.79&	0.19 \\
0043-424&	11.72&	-42.05&	43.6&	1.46&	-0.79&	0.11&	36.16&	4.97&	-0.69&	0.13 \\
0048-447&	12.86&	-44.41&	13.21&	0.64&	-0.98&	0.04&	11.58&	0.88&	-0.89&	0.05 \\
0049-433&	13.21&	-43.03&	20.16&	0.77&	-0.97&	0.03&	20.54&	1.53&	-0.98&	0.05 \\
0103-453&	16.48&	-45.02&	28.9&	1.14&	-1.16&	0.11&	21.76&	2.93&	-1.04&	0.12 \\
0201-440&	31.05&	-43.77&	13.72&	0.9&	-0.71&	0.12&	10.31&	6.54&	-0.51&	0.42 \\
0438-436&	70.17&	-43.53&	8.08&	0.74&	-0.19&	0.09&	8.32&	1.09&	-0.21&	0.1 \\
0511-484&	78.3&	-48.39&	24.92&	1.59&	-1.14&	0.09&	17.3&	10.7&	-0.93&	0.39

\enddata
\label{tab:fits}
\tablenotetext{1}{Fits for the majority of sources (78\%) that agree with prior measurements are included here. 
The remainder (the 6 sources shown in Figure \ref{fig:SI_contour_new}) are likely contaminated by bright sources and are not included.   Full table available online.}

\tablenotetext{2}{MCMC fits to prior catalog data, before addition of PAPER measurements}
\end{deluxetable}

%\begin{deluxetable}{ccccccccrrr}
%%\begin{tabular}{ccccccccrrr}
%\tablecolumns{12}
%\tablecaption{Spectral fits for models shown in Figures \ref{fig:SI_contour_1} - \ref{fig:SI_contour_4}.
%\tablehead{
%\colhead{Ra} & \colhead{Dec} & \colhead{Name} & \colhead{S150} & 
%\colhead{e_S150} & \colhead{SI} & \colhead{e_SI}
%\startdata
%
%
%\enddata
%\tablecomments{}
%\label{tab:data}
%\end{deluxetable}

\bibliography{library}

\end{document}

### 2013-04-22 psa64_srcspec.tex
Commit from Danny's google drive

\documentclass[preprint]{aastex}
\shorttitle{PAPER 64-Station Results}
\shortauthors{Parsons, et al.}

\usepackage{amsmath}
\usepackage{graphicx}
\usepackage[figuresright]{rotating}
%\usepackage{rotating}
\usepackage{natbib}
%\usepackage{pdflscape}
\usepackage{lscape}
\citestyle{aa}

\begin{document}
\title{PAPER-64: Southern-Hemisphere Source Spectra}

\author{Aaron R. Parsons}

\begin{abstract}
\end{abstract}

\section{Introduction}

Numerous radio telescopes are now exploring the prospects for
using measurements of highly redshifted 21cm emission to inform our understanding
of cosmic reionization. 
These include telescopes aiming to measure the global temperature change of 
21cm emission during the Epoch of Reionization (EoR), such as
the Compact Reionization Experiment (CoRE) and
the Experiment to Detect the Global EoR Signature (EDGES; \citealt{bowman_rogers2010}),
and interferometers aiming to measure the power spectrum of 21-cm EoR emission, such as
the Giant Metre-wave Radio Telescope (GMRT;
\citealt{pen_et_al2009})\footnote{\url{http://gmrt.ncra.tifr.res.in/}},
the LOw Frequency ARray (LOFAR; \citealt{rottgering_et_al2006})\footnote{\url{http://www.lofar.org/}},
the Murchison Widefield Array (MWA; \citealt{lonsdale_et_al2009})\footnote{\url{http://www.mwatelescope.org/}}, 
and 
the Donald C. Backer Precision Array for Probing the Epoch of Reionization (PAPER;
\citealt{parsons_et_al2010})\footnote{\url{http://eor.berkeley.edu/}}.

As such, there has been a renewed interest in the spectral and spatial variation of 
foreground emission in the 100--200 MHz frequency band that covers
the $z=6$--13 redshift range expected to encompass reionization
\citep{furlanetto_et_al2006}.
In particular, the spectral properties of extra-galactic point-sources are important
both because they are valuable calibration references
and because they are strong foreground emitters that must be removed from 21-cm EoR measurements.
With the sparse availability of measured foreground properties in the
100--200-MHz frequency band over large areas of the sky \citep{deolivieracosta_et_al2008}, continued 
foreground characterization is a
vital step en route to any 21-cm EoR detection.

%Since the 
%first-generation radio telescopes 
%are strongly influenced by the estimated angular power-spectra and
%frequency-dependence of foregrounds \citep{wang_et_al2006,bowman_et_al2009,parsons_et_al2011}.

In this paper, we report source spectra derived from PAPER observations.
PAPER is a dedicated experiment 
that employs non-tracking, dual-polarization dipole antennas 
tuned for efficient operation over a 120--170-MHz band.
PAPER employs two distinct deployments. PAPER Green Bank, at the NRAO site 
near Green Bank, WV,
is used primarily for engineering investigations and field testing.  PAPER South Africa
(PSA) is used primarily for science observations, and is data from this deployment
on which this paper is based.  PSA is located in the Karoo desert
on the Square Kilometer Array
South Africa (SKA-SA) reserve, somewhat near the small town of Carnarvon.
The PSA array has grown from 16 elements deployed in early 2009 to the
64-element array currently in use.

This paper is structured as follows:
in \S\ref{sec:} we XXX...

with primary beams that illuminate
a large ($\sim$1 sr) field of view.

\section{Observations}
\label{sec:observations}

\begin{figure*}\centering
\includegraphics[width=0.85\columnwidth]{plots/antpos.png}
\caption{The 64-antenna, minimum-redundancy array configuration used by the PAPER deployment
in the Karoo Radio Observatory site in South Africa for these observations.
}\label{fig:antpos}
\end{figure*}

Measurements are derived from observations using only the east-west dipole arms of 64 PAPER antennas 
deployed in the Karoo Radio Observatory site in South Africa (see Figure \ref{fig:antpos}).  
A 100-MHz band from 100-200MHz was
correlated with 1024 frequency channels and integrated for 10.7 seconds before visibilities were stored.
Source spectra measured over the course of a 24-hour observing run on July 4, 2011, running
from JD2455747.15 to JD2455748.12.
Two antennas (\#40,\#55) were omitted owing to malfunctioning signal path, leaving 62 remaining antennas
used in the observations.

Quantization gain through the correlator was linearized \citep{parsons_et_al2008}.
Removed RFI by flagging samples in each frequency channel versus time that exceed the mean amplitude by 4-sigma
after performing a time derivative.  Also flagged samples in each integrated spectrum that exceeded the
mean amplitude across the spectrum by 6-sigma after performing a frequency derivative.  For efficiency, flagging
was derived using only the subset of baselines involving a fiducial antenna.
Frequencies below 120 MHz and above 180 MHz were also flagged, owing to roll-off of analog response.
After RFI flagging, frequency channel resolution was decreased by a factor of four by summing channels.
Finally, measurements of ambient temperature versus time near the balun amplifier of a fiducial antenna and near
receiver amplifiers were used to divide out the predicted gain variation versus temperature that these amplifiers
are known to exhibit.  A predicted gain profile was drived using coefficients characterized in 
laboratory measurements \citep{parashare_bradley2009} and
confirmed in field measurements \citep{pober_et_al2011} of $H_{\rm balun}=-0.024$ dB/K, $H_{\rm recvr}=-0.045$
dB/K, and $H_{\rm cable}=-0.018$ dB/K for 150m-long cables.  Because cable temperatures were not measured
during these observations, the cable temperature was assumed to be the same as the measured balun temperature.

\begin{figure*}\centering
\includegraphics[width=0.85\columnwidth]{plots/tempgain.png}
\caption{Upper panel: ambient temperatures measured near various components with temperature-dependent
gains in the PAPER analog signal chain versus time offset from JD2455747.0. Lower panel: the 
predicted multiplicative gain that is corrected for using the temperature curves and the gain coefficients
listed in \S\ref{sec:observations}.
}\label{fig:tempgain}
\end{figure*}

Phase calibration performed using the central components of Centaurus A, Fornax A, and Pictor A.
The overall gain and bandpass were calibrated to J2214-170 listed by Helmboldt et al. (2006).

As the sky drifts through the primary beam of PAPER antennas, widely
separated points will be observed with substantially different gains and
so will require different data weightings to optimize SNR.

Drift-scan observations of sources were divided by the calibrated beam response in the
direction of the source as a function of time.  Spectra were calculated by averaging over
time, weighting data at each time step by the square of the 150-MHz beam response in the source direction.
Since noise and systematics relating to source observations are expected to be approximately constant
versus time, while source amplitude is proportional to beam response, this weighting 
is an effective approximation of inverse-variance weighting \citep{pober_et_al2011}.

After measuring their spectra, point-source models of the brightest sources (Centaurus A, Fornax A, 
Pictor A, Sun, Virgo A,
and Cygnus A) were subtracted from visibilities, and bright sources at low altitudes (Sun, Virgo A,
and Cygnus A) where antenna response models are less reliable were further surpressed with DDR 
filters \citep{parsons_backer2009}.  Remaining source used these filtered/subtracted visibilities
for characterizing their spectra in order to reduce sidelobe contamination.

Finally, data from all baselines longer than 20 wavelengths were phased toward each source
and summed using natural weighting to produce a beam tracking that source, yielding a measured
source spectrum for each time integation.

\begin{figure*}\centering
%\includegraphics[width=0.85\columnwidth]{plots/skymap.png}
\caption{
}\label{fig:skymap}
\end{figure*}

\begin{figure*}\centering
%\includegraphics[width=0.85\columnwidth]{plots/skymap_eq.png}
\caption{
}\label{fig:skymap_eq}
\end{figure*}

\section{Target Selection}
\label{sec:target_selection}

A first set of source targets were selected from the Helmboldt \citep{helmboldt_et_al2008}, Culgoora \citep{slee1995}, and
Mauritius Radio Telescope \citep{golap_et_al1998} catalogs, restricted to sources with fluxes at 150 MHz 
exceeding 5 Jys and source declination 
falling within $\pm20^\circ$ of the -30:43 latitude
of the PAPER array.  Sources within $\pm10^\circ$ of the galactic plane were also excluded, as were
sources near Centaurus A ($\pm5^\circ$ in declination, $\pm2.5^\circ$ in right-ascension).

\section{Discussion}

\begin{figure*}\centering
\includegraphics[width=0.85\columnwidth]{plots/catcompare.png}
\caption{A comparison of catalogued flux-density extrapolated to 150 MHz (horizontal axis) versus 
measured flux-density (vertical axis) for various catalogs.
}\label{fig:catcompare}
\end{figure*}

A comparison of measured source fluxes at 150 MHz and catalog values extrapolate to that frequency
is illustrated in Figure \ref{fig:catcompare}.
Comparison with PSA32 catalog \citep{jacobs_et_al2011}.

\begin{figure*}\centering
\includegraphics[width=0.85\columnwidth]{plots/numcounts.png}
\caption{Number counts (vertical axis) versus flux-density at 150 MHz (horizontal axis), normalized
to the angular area of XXX sr surveyed for this catalog.  Source count statistics from this
catalog (black crosses) are compared with pixel statistics derived from imaging various regions:
the entire sky below $\delta=0^\circ$ (green), the galactic plane $\pm10^\circ$ latitude below
$\delta=0^\circ$ (magenta), the region surveyed for this catalog (black, as described 
in \S\ref{sec:target_selection}), and the region outside the galactic plane below $\delta=0^\circ$
that was not included in this survey (cyan).
}\label{fig:numcounts}
\end{figure*}

Source-count statistics versus flux density for this catalog are shown in 
Figure \ref{fig:numcounts}, along with comparisons to pixel-count statistics for an all-sky map
generated from the same data (see Figure \ref{fig:skymap}).  In addition to justifying the
selection of angular area described in \S\ref{sec:target_selection} for producing this 
catalog on the basis of disparate source-count statistics, Figure \ref{fig:numcounts} 
provides context for ruling out selection bias and target ambiguity arising from confusion.
The chosen selection threshold of 5 Jy lies a factor of five higher than the $\sim$1-Jy threshold
at which the number density of source fluxes departs from a power law.

\section{Conclusion}

This cataloging work is part of a broader initiative in foreground characterization 
in the 100-200MHz frequency band.  Future work in this area 
will include updating
and expanding previous source catalogs, measuring the effects of
ionospheric refraction on source removal, mapping galactic synchrotron
emission, using rotation measure synthesis to determine the frequency
dependence of synchrotron polarization structure, and directly
measuring the magnitude of emission and absorption from radio
recombination lines in galactic emission.  The global sky model
resulting from this work will be used to remove foreground emission
from 21cm EoR experiments, and to estimate residual systematic biases in power
spectrum measurements.

Meanwhile, work is underway to
expand PSA to 128 antennas in the near future.

The modest size of the ground-screen reflecting structure and the fact
that PAPER employs rugged above-ground cables to carry signals from the antenna
elements to a central location for correlation allow PAPER antennas to be
moved relativlty easily.
PAPER is in a unique position to use the mobility of its antennas to
explore different configurations.  Current PAPER observing activities aim to explore
the feasibility of tuning array sensitivity relative to foreground
brightness \citep{parsons_et_al2011}.

Research
activities in the near term will focus on improving the
characterization of the PAPER primary beam and mapping foreground
emission with the goal of establishing a global sky model for removing
foreground emission from PAPER data and estimating residual systematic
biases in power spectrum measurements.  Results from foreground
characterization will also be directly applicable to other
reionization efforts, providing a valuable point of contact with other
HERA progenitors and with the global reionization community.

An important step in route to obtaining a high-sensitivity power spectrum
measurement is to direct the sensitivity of the PAPER-128 array in a
low-redundancy configuration toward improving the global sky model.
The foreground model established in this stage of PAPER observing will
be generally useful for all reionization experiments operating at
these frequencies.  These observing activities will also be useful
within PAPER for re-establishing calibration parameters, verifying
instrumental performance, and removing foregrounds from power-spectrum
detection observations.

Results from this work will be disseminated as
source catalogs and all-sky maps in the HEALPix FITS format \citep{gorski_et_al2006} as a
resource for the global reionization community.

\section{Acknowledgment}

We would like to thank SKA-SA for the site infrastructure, maintanence, and observing support
that has made this work possible.

\begin{table}[ht]
\caption{Measured Source Parameters}
\begin{tabular}{l|lrrr||l|lrrr}
\hline
Name & RA & DEC & $f_{150}$ & $\alpha$ & Name & RA & DEC & $f_{150}$ & $\alpha$
\\
\hline
  0000-362 &  0:03 & -35:57 &   13.1 & -0.54 &   0057-180 &  1:00 & -17:49 &    7.0 & -0.29 \\
 J0003-173 &  0:03 & -17:27 &   24.1 & -0.86 &   0100-221 &  1:02 & -21:52 &   14.7 & -1.03 \\
MRTJ0003-3059 &  0:03 & -30:59 &    8.7 & +0.19 &   0100-278 &  1:02 & -27:32 &    9.9 & -0.45 \\
MRTJ0006-4234 &  0:06 & -42:34 &   21.2 & +0.16 &   0101-416 &  1:03 & -41:20 &    9.2 & +0.12 \\
MRTJ0009-4503 &  0:09 & -45:03 &    8.0 & +0.12 &   0102-384 &  1:05 & -38:10 &   12.6 & -0.38 \\
MRTJ0010-4339 &  0:10 & -43:39 &    9.2 & +0.19 &   0103-453 &  1:05 & -45:05 &   45.7 & -0.01 \\
MRTJ0010-4423 &  0:10 & -44:23 &   32.9 & +0.06 &  J0108-160 &  1:08 & -16:04 &   59.1 & -1.09 \\
MRTJ0012-3322 &  0:12 & -33:22 &   10.4 & +0.16 &   0112-445 &  1:14 & -44:18 &    8.9 & +0.27 \\
  0012-383 &  0:15 & -38:05 &   18.2 & -0.16 &   0114-476 &  1:16 & -47:24 &   38.1 & -0.26 \\
  0013-147 &  0:16 & -14:30 &    6.9 & -0.97 &   0114-211 &  1:16 & -20:52 &   15.5 & +0.17 \\
MRTJ0016-3827 &  0:16 & -38:27 &    8.5 & -0.30 &   0116-413 &  1:18 & -41:02 &    6.9 & -0.46 \\
 J0019-124 &  0:18 & -12:42 &   12.3 & -0.32 &  J0120-152 &  1:20 & -15:20 &   37.8 & -0.85 \\
MRTJ0020-4847 &  0:20 & -48:47 &    8.4 & +0.11 &   0119-377 &  1:22 & -37:30 &   15.2 & -0.27 \\
MRTJ0020-2015 &  0:20 & -20:15 &    5.5 & -0.48 &   0122-255 &  1:24 & -25:17 &    9.3 & -0.32 \\
MRTJ0021-1910 &  0:21 & -19:10 &    6.0 & -0.36 &   0124-409 &  1:26 & -40:41 &   12.9 & +0.68 \\
MRTJ0021-4657 &  0:21 & -46:57 &   11.1 & -0.54 &   0124-414 &  1:27 & -41:12 &   18.3 & +0.00 \\
  0020-253 &  0:23 & -25:02 &   12.0 & -0.10 &  J0128-140 &  1:27 & -14:02 &   29.2 & -1.23 \\
 J0025-293 &  0:24 & -29:28 &   32.4 & -0.20 &   0125-438 &  1:27 & -43:35 &    8.4 & +0.25 \\
  0023-333 &  0:25 & -33:03 &   14.0 & -0.20 &  J0130-261 &  1:30 & -26:10 &   27.8 & -0.81 \\
  0023-263 &  0:25 & -26:02 &   24.5 & +0.41 &   0131-450 &  1:33 & -44:44 &   20.6 & -0.01 \\
MRTJ0026-4918 &  0:26 & -49:18 &    7.3 & +0.79 &   0131-367 &  1:33 & -36:29 &   49.1 & -0.29 \\
  0024-372 &  0:26 & -36:56 &    7.0 & -0.38 &   0139-273 &  1:41 & -27:06 &   12.1 & -0.06 \\
MRTJ0028-4157 &  0:28 & -41:57 &    8.4 & +0.09 &  J0142-163 &  1:42 & -16:28 &   33.1 & -1.56 \\
MRTJ0030-5018 &  0:30 & -50:18 &   10.4 & +0.35 &   0141-439 &  1:43 & -43:42 &    6.1 & -0.88 \\
 J0035-200 &  0:35 & -20:03 &   23.7 & -0.54 &   0144-374 &  1:46 & -37:11 &    9.4 & +0.41 \\
MRTJ0036-4903 &  0:36 & -49:03 &    6.9 & -0.58 &   0148-297 &  1:50 & -29:32 &   25.4 & -0.50 \\
  0034-377 &  0:36 & -37:28 &    7.5 & -0.58 &   0149-394 &  1:51 & -39:10 &    7.2 & -0.03 \\
MRTJ0038-3859 &  0:38 & -39:00 &   23.8 & -0.35 &   0149-299 &  1:52 & -29:42 &   10.3 & -0.45 \\
  0039-445 &  0:42 & -44:14 &   44.2 & +0.18 &   0152-437 &  1:54 & -43:27 &   10.5 & -0.09 \\
  0042-357 &  0:44 & -35:30 &   14.9 & +0.30 &  J0200-305 &  2:00 & -30:53 &   35.8 & -0.22 \\
  0043-424 &  0:46 & -42:07 &   73.7 & +0.22 &   0159-117 &  2:01 & -11:32 &    4.2 & -2.30 \\
  0045-255 &  0:47 & -25:17 &   24.6 & -0.24 &   0201-441 &  2:03 & -43:51 &   21.4 & +0.69 \\
  0048-447 &  0:50 & -44:28 &   23.6 & +0.01 &   0202-182 &  2:05 & -18:01 &    6.8 & -0.83 \\
  0049-433 &  0:52 & -43:06 &   32.7 & +0.20 &   0204-378 &  2:06 & -37:38 &    8.5 & -0.46 \\
 J0059-170 &  0:59 & -17:00 &   30.5 & -1.26 &   0207-112 &  2:10 & -11:00 &    6.3 & -0.85 \\
\hline
\end{tabular}
\end{table}

\begin{table}[ht]
\caption{Measured Source Parameters}
\begin{tabular}{l|lrrr||l|lrrr}
\hline
Name & RA & DEC & $f_{150}$ & $\alpha$ & Name & RA & DEC & $f_{150}$ & $\alpha$
\\
\hline
  0211-344 &  2:13 & -34:13 &    9.6 & -0.33 &   0328-370 &  3:30 & -36:53 &   15.7 & -0.43 \\
 J0216-126 &  2:15 & -12:59 &   52.4 & -1.25 &   0332-391 &  3:33 & -38:58 &   16.4 & +0.47 \\
  0213-134 &  2:15 & -13:15 &    5.4 & -0.93 &   0335-415 &  3:37 & -41:22 &   18.0 & -0.16 \\
  0214-480 &  2:16 & -47:47 &   23.4 & +0.11 &   0336-355 &  3:38 & -35:23 &   16.8 & -1.32 \\
  0216-250 &  2:18 & -24:48 &   11.2 & -0.73 &   0338-404 &  3:39 & -40:18 &   18.6 & +0.11 \\
  0216-366 &  2:19 & -36:25 &   17.1 & -0.64 &   0340-372 &  3:42 & -37:02 &   12.4 & -0.79 \\
  0217-369 &  2:19 & -36:43 &    9.0 & +0.12 &   0344-345 &  3:46 & -34:22 &   26.3 & -0.09 \\
  0218-387 &  2:20 & -38:33 &   11.0 & -0.91 &  J0351-143 &  3:51 & -14:29 &   67.1 & -1.56 \\
  0220-422 &  2:22 & -41:59 &   16.1 & -0.20 &   0349-278 &  3:51 & -27:44 &   37.8 & -0.66 \\
  0221-285 &  2:23 & -28:19 &   12.5 & -0.64 &   0354-485 &  3:55 & -48:23 &   16.1 & +0.01 \\
  0222-234 &  2:25 & -23:12 &   11.8 & -0.68 &   0358-371 &  3:59 & -37:00 &   15.8 & -0.33 \\
  0225-308 &  2:27 & -30:38 &    9.0 & +0.18 &  J0400-161 &  4:00 & -16:10 &   39.4 & -1.75 \\
  0228-399 &  2:30 & -39:44 &   10.9 & -0.56 &   0403-132 &  4:05 & -13:08 &    7.2 & -2.01 \\
  0231-235 &  2:33 & -23:21 &   12.6 & +0.01 &  J0408-121 &  4:07 & -12:11 &   25.7 & -1.01 \\
 J0238-193 &  2:37 & -19:32 &   37.5 & -0.49 &   0406-311 &  4:08 & -31:01 &    6.1 & +0.06 \\
  0240-422 &  2:42 & -42:01 &   17.8 & +0.14 &  J0409-242 &  4:08 & -24:18 &   25.0 & -1.18 \\
  0244-452 &  2:45 & -44:59 &   12.6 & -0.46 &   0411-346 &  4:13 & -34:30 &   11.9 & -0.76 \\
  0245-297 &  2:47 & -29:30 &    6.6 & -0.25 &   0413-425 &  4:15 & -42:24 &    8.2 & -1.07 \\
  0252-418 &  2:53 & -41:41 &    8.1 & +0.35 &  J0415-293 &  4:15 & -29:29 &   13.3 & -0.09 \\
 J0256-232 &  2:56 & -23:24 &   25.6 & -1.12 &  J0416-206 &  4:16 & -20:56 &   18.4 & -0.25 \\
  0257-398 &  2:59 & -39:41 &    5.9 & -1.10 &   0418-399 &  4:19 & -39:50 &    9.8 & +0.81 \\
  0302-361 &  3:04 & -35:54 &    9.3 & +0.09 &   0420-264 &  4:22 & -26:17 &    8.3 & -1.15 \\
  0304-122 &  3:06 & -12:06 &    6.2 & +0.38 &   0421-341 &  4:23 & -34:02 &    8.8 & -0.69 \\
  0305-226 &  3:07 & -22:25 &   11.9 & -0.34 &   0427-366 &  4:29 & -36:30 &   28.0 & -0.25 \\
 J0313-145 &  3:12 & -14:49 &   19.9 & -0.91 &   0431-300 &  4:32 & -29:57 &   10.7 & -0.66 \\
  0313-271 &  3:16 & -26:58 &    8.4 & -1.47 &   0431-133 &  4:33 & -13:15 &    7.0 & -3.16 \\
  0314-440 &  3:16 & -43:51 &   10.2 & -1.44 &   0435-300 &  4:37 & -29:55 &    7.6 & +0.00 \\
  0315-146 &  3:17 & -14:30 &    5.1 & -2.44 &   0438-436 &  4:40 & -43:33 &   13.8 & +1.65 \\
  0316-444 &  3:17 & -44:14 &   12.6 & -0.57 &  J0445-281 &  4:44 & -28:09 &   73.5 & -0.41 \\
  0319-453 &  3:21 & -45:10 &   37.2 & +0.00 &   0446-206 &  4:48 & -20:32 &    8.0 & -1.79 \\
  0320-389 &  3:22 & -38:47 &    6.4 & +0.79 &  J0455-301 &  4:55 & -30:06 &   41.0 & -0.60 \\
       for &  3:22 & -37:12 &  250.1 & -2.29 &  J0455-203 &  4:55 & -20:34 &   27.0 & -0.45 \\
  0325-441 &  3:27 & -43:57 &   15.9 & -0.26 &   0454-463 &  4:55 & -46:15 &   13.1 & -0.66 \\
  0326-288 &  3:28 & -28:41 &   10.5 & +0.40 &   0454-220 &  4:56 & -21:59 &   10.2 & -0.60 \\
  0327-168 &  3:30 & -16:39 &    6.3 & -2.63 &   0455-405 &  4:57 & -40:25 &   10.4 & -0.29 \\
\hline
\end{tabular}
\end{table}

\begin{table}[ht]
\caption{Measured Source Parameters}
\begin{tabular}{l|lrrr||l|lrrr}
\hline
Name & RA & DEC & $f_{150}$ & $\alpha$ & Name & RA & DEC & $f_{150}$ & $\alpha$
\\
\hline
  0456-301 &  4:58 & -30:07 &   19.5 & -0.10 &   0703-451 &  7:05 & -45:15 &   10.5 & +0.10 \\
  0503-284 &  5:05 & -28:22 &    8.4 & +0.39 &   0704-427 &  7:05 & -42:49 &   20.0 & -0.02 \\
 J0511-184 &  5:10 & -18:38 &   43.2 & -1.08 &   0707-360 &  7:09 & -36:06 &   14.7 & -0.42 \\
  0508-221 &  5:11 & -22:02 &   11.1 & +0.32 &  J0712-204 &  7:11 & -20:43 &   15.9 & -0.22 \\
  0511-305 &  5:13 & -30:30 &   21.6 & -0.32 &   0715-362 &  7:17 & -36:21 &   20.2 & +0.17 \\
       pic &  5:19 & -45:46 &  655.6 & -0.04 &  J0717-250 &  7:17 & -25:04 &   24.2 & -0.27 \\
 J0522-205 &  5:21 & -20:47 &   27.8 & -0.89 &  J0722-185 &  7:22 & -18:48 &  302.1 & -5.50 \\
  0521-364 &  5:22 & -36:27 &   89.1 & -0.09 &  J0747-186 &  7:47 & -18:56 &   11.8 & -0.25 \\
  0521-329 &  5:23 & -32:51 &    9.5 & +0.20 &  J0748-192 &  7:47 & -19:17 &   33.4 & -0.46 \\
  0523-327 &  5:25 & -32:42 &    8.0 & -0.39 &  J0827-203 &  8:27 & -20:26 &   16.6 & +0.33 \\
 J0543-242 &  5:43 & -24:21 &    7.5 & +0.37 &   0834-196 &  8:37 & -19:52 &   10.6 & +0.44 \\
  0546-445 &  5:47 & -44:31 &   17.8 & -0.07 &   0837-120 &  8:39 & -12:14 &   10.9 & +1.70 \\
  0547-408 &  5:49 & -40:51 &   29.2 & -0.01 &  J0853-205 &  8:53 & -20:47 &   13.3 & +0.32 \\
  0554-323 &  5:56 & -32:23 &   10.7 & -0.97 &   0851-142 &  8:53 & -14:27 &    6.2 & -2.21 \\
  0559-398 &  6:01 & -39:51 &   19.3 & -3.24 &  J0902-256 &  9:01 & -25:55 &   66.0 & -0.57 \\
  0600-383 &  6:02 & -38:19 &   11.3 & -0.49 &  J0918-121 &  9:18 & -12:05 &  489.1 & -99.00 \\
  0600-131 &  6:03 & -13:10 &    3.8 & -2.86 &   0926-292 &  9:29 & -29:29 &    9.9 & -0.57 \\
  0601-344 &  6:03 & -34:27 &   13.8 & -0.11 &   0935-289 &  9:38 & -29:12 &   15.5 & -0.56 \\
  0602-319 &  6:04 & -31:56 &   12.0 & -0.13 &   0942-196 &  9:45 & -19:53 &    4.8 & -1.13 \\
  0604-352 &  6:05 & -35:18 &   10.0 & +0.55 &   0946-182 &  9:48 & -18:28 &    6.3 & -1.28 \\
 J0607-202 &  6:06 & -20:22 &   11.0 & +0.28 &  J0950-251 &  9:49 & -25:11 &   26.8 & -1.03 \\
  0612-474 &  6:13 & -47:26 &   19.6 & -0.62 &   0955-288 &  9:58 & -29:04 &   10.1 & -1.13 \\
  0614-349 &  6:16 & -34:56 &    7.8 & +0.34 &  J1005-214 & 10:05 & -21:44 &   33.8 & -0.80 \\
  0615-365 &  6:17 & -36:34 &   10.5 & -0.03 &   1002-216 & 10:05 & -21:52 &    3.1 & -0.37 \\
  0618-371 &  6:19 & -37:11 &   16.0 & -0.48 &   1003-415 & 10:05 & -41:49 &    8.2 & +2.23 \\
  0625-354 &  6:27 & -35:29 &   25.0 & -0.40 &   1006-286 & 10:09 & -28:55 &    6.7 & -0.85 \\
  0630-368 &  6:32 & -36:50 &    7.6 & +0.10 &   1011-316 & 10:13 & -31:55 &   10.2 & +0.21 \\
  0630-273 &  6:32 & -27:20 &    6.5 & -0.35 &   1015-315 & 10:18 & -31:45 &   15.7 & +0.32 \\
  0634-205 &  6:36 & -20:37 &   34.2 & -1.25 &   1017-421 & 10:19 & -42:24 &   20.7 & +0.79 \\
  0636-167 &  6:38 & -16:49 &    7.2 & +0.93 &   1017-426 & 10:20 & -42:51 &   46.8 & +0.13 \\
  0637-277 &  6:39 & -27:46 &   12.7 & +1.71 &   1017-325 & 10:20 & -32:46 &   11.6 & +0.41 \\
  0642-436 &  6:44 & -43:43 &   14.3 & +0.17 &   1024-414 & 10:26 & -41:43 &    6.3 & +0.43 \\
  0646-399 &  6:48 & -39:57 &   24.7 & -0.28 &   1025-405 & 10:27 & -40:50 &    9.8 & +0.32 \\
 J0659-242 &  6:58 & -24:17 &   38.8 & -0.24 &   1030-357 & 10:33 & -36:02 &    6.6 & +1.30 \\
  0700-473 &  7:02 & -47:26 &   26.2 & -0.42 &   1030-340 & 10:33 & -34:18 &   16.7 & -0.33 \\
\hline
\end{tabular}
\end{table}

\begin{table}[ht]
\caption{Measured Source Parameters}
\begin{tabular}{l|lrrr||l|lrrr}
\hline
Name & RA & DEC & $f_{150}$ & $\alpha$ & Name & RA & DEC & $f_{150}$ & $\alpha$
\\
\hline
  1031-408 & 10:33 & -41:09 &   16.1 & +0.06 &   1156-402 & 11:58 & -40:30 &    6.5 & +1.48 \\
  1033-413 & 10:35 & -41:39 &   12.1 & +0.68 &   1202-262 & 12:05 & -26:33 &    7.9 & +0.55 \\
  1042-409 & 10:45 & -41:14 &    8.0 & -1.63 &  J1208-170 & 12:07 & -17:03 &    8.6 & -0.68 \\
  1043-378 & 10:46 & -38:06 &    6.0 & +0.35 &  J1209-340 & 12:08 & -34:03 &    6.1 & +1.13 \\
  1044-357 & 10:46 & -36:01 &   12.6 & +0.07 &   1211-417 & 12:14 & -42:00 &   10.0 & +0.94 \\
  1046-409 & 10:48 & -41:14 &   16.8 & +0.44 &   1212-448 & 12:14 & -45:07 &    6.8 & -0.27 \\
  1049-201 & 10:51 & -20:24 &    5.5 & -0.95 &   1215-457 & 12:18 & -46:01 &   27.1 & +0.84 \\
  1052-340 & 10:55 & -34:20 &    9.4 & -0.19 &   1218-373 & 12:20 & -37:40 &    7.5 & +0.05 \\
  1053-282 & 10:55 & -28:31 &    6.9 & +0.42 &   1221-423 & 12:23 & -42:36 &   15.4 & +1.04 \\
  1054-370 & 10:57 & -37:18 &    9.4 & +0.97 &   1224-262 & 12:26 & -26:30 &    5.9 & +0.86 \\
  1056-360 & 10:58 & -36:19 &    9.3 & -0.09 &   1225-440 & 12:27 & -44:21 &   11.5 & +0.93 \\
 J1106-244 & 11:06 & -24:44 &   12.3 & -0.18 &   1232-331 & 12:35 & -33:22 &    7.3 & +1.75 \\
 J1106-211 & 11:06 & -21:09 &   18.7 & -0.71 &   1232-249 & 12:35 & -25:12 &   14.2 & +0.31 \\
  1105-440 & 11:07 & -44:21 &    7.5 & -0.40 &   1232-416 & 12:35 & -41:53 &   16.4 & +0.24 \\
  1107-227 & 11:09 & -23:02 &    7.3 & -1.49 &   1240-209 & 12:43 & -21:11 &    7.4 & +0.55 \\
  1109-402 & 11:11 & -40:31 &    8.7 & +0.90 &   1243-412 & 12:45 & -41:29 &   15.0 & +2.15 \\
  1116-463 & 11:18 & -46:34 &   20.5 & +0.70 &   1244-112 & 12:47 & -11:29 &    6.2 & +0.24 \\
  1123-351 & 11:25 & -35:23 &   17.3 & +0.73 &   1245-197 & 12:48 & -20:00 &    5.6 & +1.23 \\
 J1134-195 & 11:33 & -19:54 &   10.0 & +0.10 &   1246-410 & 12:48 & -41:19 &   45.3 & +0.64 \\
 J1134-173 & 11:34 & -17:27 &   20.6 & -1.17 &   1247-401 & 12:50 & -40:26 &   16.2 & -0.34 \\
  1135-390 & 11:38 & -39:22 &    7.4 & +1.47 &   1247-194 & 12:50 & -19:46 &    7.0 & +0.69 \\
 J1139-135 & 11:39 & -13:50 &   50.3 & -2.02 &   1251-184 & 12:54 & -18:45 &    4.6 & -1.43 \\
 J1139-322 & 11:39 & -32:22 &   18.1 & +0.09 &  J1255-123 & 12:54 & -12:33 &   79.4 & -0.82 \\
 J1141-263 & 11:40 & -26:29 &   20.2 & -0.60 &  J1255-291 & 12:54 & -29:13 &   26.0 & +0.16 \\
 J1142-285 & 11:41 & -28:50 &   27.4 & -0.44 &   1254-333 & 12:57 & -33:34 &    8.2 & +2.35 \\
 J1143-114 & 11:42 & -11:41 &   14.0 & -1.54 &   1254-300 & 12:57 & -30:21 &    9.6 & +0.46 \\
  1143-483 & 11:45 & -48:36 &   18.1 & +0.61 &   1257-230 & 13:00 & -23:18 &    8.2 & -1.65 \\
  1143-317 & 11:45 & -31:58 &   16.8 & +0.19 &   1258-321 & 13:00 & -32:26 &    5.3 & +1.01 \\
 J1146-316 & 11:46 & -31:57 &    1.4 & +1.61 &   1259-200 & 13:01 & -20:19 &    7.3 & -0.25 \\
  1143-332 & 11:46 & -33:31 &    9.0 & +0.70 &   1302-326 & 13:04 & -32:53 &    9.5 & +0.50 \\
  1144-409 & 11:47 & -41:11 &   10.1 & +0.01 &  J1312-222 & 13:11 & -22:16 &   40.7 & +0.18 \\
  1146-117 & 11:49 & -12:04 &    5.5 & -0.66 &  J1315-186 & 13:15 & -18:58 &    7.4 & +0.17 \\
  1148-353 & 11:51 & -35:36 &    9.1 & +0.55 &        cen & 13:25 & -43:01 & 2850.9 & +0.82 \\
  1151-348 & 11:54 & -35:05 &   14.7 & +1.62 &   1323-271 & 13:26 & -27:25 &    6.7 & +0.15 \\
  1155-423 & 11:57 & -42:39 &    8.1 & +0.67 &  J1330-214 & 13:30 & -21:42 &    9.3 & +0.06 \\
\hline
\end{tabular}
\end{table}

\begin{table}[ht]
\caption{Measured Source Parameters}
\begin{tabular}{l|lrrr||l|lrrr}
\hline
Name & RA & DEC & $f_{150}$ & $\alpha$ & Name & RA & DEC & $f_{150}$ & $\alpha$
\\
\hline
 J1331-256 & 13:31 & -25:59 &   21.8 & -0.45 &  J1456-111 & 14:55 & -11:08 &   14.5 & -0.53 \\
  1329-328 & 13:32 & -33:07 &   13.3 & +1.63 &   1459-419 & 15:02 & -42:08 &   28.1 & -0.19 \\
  1329-257 & 13:32 & -25:59 &    6.0 & -0.26 &   1514-165 & 15:17 & -16:41 &    6.6 & -0.03 \\
  1330-328 & 13:33 & -33:06 &    6.2 & -0.01 &   1518-295 & 15:21 & -29:43 &    7.4 & +1.58 \\
  1333-337 & 13:36 & -33:57 &   37.2 & -0.64 &   1526-423 & 15:30 & -42:31 &   77.0 & +0.76 \\
  1334-296 & 13:36 & -29:52 &   12.2 & +0.27 &   1528-293 & 15:31 & -29:30 &    7.9 & +0.78 \\
  1334-338 & 13:37 & -34:09 &   15.3 & +0.67 &   1530-334 & 15:33 & -33:36 &    8.1 & +1.55 \\
  1340-373 & 13:43 & -37:33 &   10.0 & +2.91 &   1540-337 & 15:44 & -33:53 &    8.7 & +0.76 \\
  1346-391 & 13:49 & -39:22 &   21.6 & +0.81 &   1545-321 & 15:48 & -32:16 &   10.7 & +0.46 \\
  1355-416 & 13:59 & -41:52 &   44.8 & +0.59 &   1556-215 & 15:59 & -21:40 &    9.6 & -0.20 \\
  1359-358 & 14:02 & -36:03 &   11.7 & +0.66 &  J1605-173 & 16:05 & -17:34 &    7.4 & -0.04 \\
  1400-338 & 14:03 & -34:02 &   39.7 & -0.51 &   1602-288 & 16:05 & -28:58 &   12.6 & -1.68 \\
  1401-296 & 14:04 & -29:52 &    6.8 & -0.04 &   1618-235 & 16:21 & -23:42 &    5.6 & +1.29 \\
  1402-367 & 14:05 & -36:56 &    9.3 & +0.55 &  J1624-114 & 16:23 & -11:40 &    7.3 & -0.08 \\
  1403-273 & 14:06 & -27:36 &    7.3 & +0.15 &   1621-260 & 16:24 & -26:12 &    6.3 & +0.66 \\
  1407-425 & 14:10 & -42:47 &   16.9 & -0.11 &   1622-310 & 16:25 & -31:08 &    9.5 & +0.07 \\
  1413-364 & 14:16 & -36:40 &   13.0 & -0.34 &   1628-268 & 16:31 & -26:56 &    8.8 & +0.62 \\
 J1417-215 & 14:16 & -21:46 &   16.5 & -0.18 &   1640-153 & 16:43 & -15:26 &    7.6 & +0.74 \\
  1415-379 & 14:18 & -38:10 &    4.1 & -0.96 &  J1646-223 & 16:46 & -22:28 &    7.5 & +0.40 \\
  1417-192 & 14:19 & -19:28 &    7.3 & -1.49 & MRTJ1802-4859 & 18:02 & -48:59 &    7.2 & +1.46 \\
  1416-493 & 14:20 & -49:36 &   17.8 & +0.67 & MRTJ1803-4331 & 18:03 & -43:31 &   10.2 & +1.12 \\
 J1423-273 & 14:22 & -27:27 &   21.9 & +0.02 & MRTJ1809-4552 & 18:09 & -45:52 &    7.7 & -0.23 \\
  1420-180 & 14:23 & -18:16 &    6.5 & +1.70 &   1817-391 & 18:20 & -39:09 &   22.6 & +0.03 \\
  1421-382 & 14:24 & -38:27 &   22.3 & +0.22 & MRTJ1830-3820 & 18:30 & -38:20 &    8.9 & +2.86 \\
 J1425-296 & 14:25 & -29:59 &   20.6 & +0.27 & MRTJ1830-3602 & 18:30 & -36:02 &   29.5 & +0.29 \\
 J1428-120 & 14:27 & -12:03 &   13.3 & -1.25 & MRTJ1832-3422 & 18:32 & -34:22 &    8.2 & +3.77 \\
  1424-418 & 14:27 & -42:06 &   15.7 & +0.31 & MRTJ1833-3940 & 18:33 & -39:40 &    5.2 & +1.33 \\
  1425-274 & 14:28 & -27:41 &    6.5 & -0.42 & MRTJ1834-4357 & 18:34 & -43:57 &    5.0 & +1.34 \\
  1425-397 & 14:28 & -39:59 &    8.3 & +0.87 &   1834-436 & 18:37 & -43:35 &   16.3 & +1.10 \\
  1436-167 & 14:39 & -16:59 &    7.0 & +0.69 & MRTJ1841-3629 & 18:41 & -36:29 &    7.4 & +1.23 \\
  1439-264 & 14:42 & -26:37 &    8.5 & +0.18 & MRTJ1843-4836 & 18:43 & -48:36 &   31.5 & +0.63 \\
  1445-468 & 14:48 & -47:01 &   14.2 & +0.72 & MRTJ1844-4022 & 18:44 & -40:22 &   28.3 & +0.94 \\
  1449-129 & 14:52 & -13:11 &    6.1 & -0.80 & MRTJ1848-5004 & 18:48 & -50:04 &   10.7 & +1.28 \\
  1451-364 & 14:54 & -36:40 &   26.8 & +0.27 &   1847-260 & 18:50 & -25:56 &    4.3 & -1.21 \\
  1452-421 & 14:55 & -42:18 &   16.3 & +0.92 & MRTJ1851-3345 & 18:51 & -33:45 &    7.3 & -0.34 \\
\hline
\end{tabular}
\end{table}

\begin{table}[ht]
\caption{Measured Source Parameters}
\begin{tabular}{l|lrrr||l|lrrr}
\hline
Name & RA & DEC & $f_{150}$ & $\alpha$ & Name & RA & DEC & $f_{150}$ & $\alpha$
\\
\hline
MRTJ1857-3019 & 18:57 & -30:19 &   11.3 & +0.05 & MRTJ2016-3035 & 20:16 & -30:35 &    6.6 & +0.84 \\
MRTJ1902-2705 & 19:02 & -27:05 &    9.5 & +0.65 & MRTJ2017-4516 & 20:17 & -45:16 &    8.7 & +0.18 \\
MRTJ1902-2329 & 19:02 & -23:29 &   22.1 & +0.15 &   2017-439 & 20:20 & -43:45 &    7.0 & +0.52 \\
MRTJ1914-2928 & 19:14 & -29:28 &    6.3 & +0.88 &   2018-224 & 20:21 & -22:14 &    5.0 & -1.18 \\
MRTJ1915-2653 & 19:15 & -26:53 &   17.2 & -0.01 & MRTJ2028-1521 & 20:28 & -15:21 &    8.2 & -0.58 \\
  1914-455 & 19:17 & -45:29 &   12.8 & +0.92 & MRTJ2029-4119 & 20:29 & -41:19 &   12.2 & -0.19 \\
  1916-300 & 19:19 & -29:57 &   10.2 & +0.46 & MRTJ2033-4540 & 20:33 & -45:40 &    5.9 & -0.61 \\
  1918-355 & 19:21 & -35:27 &    9.2 & +0.49 &   2030-230 & 20:33 & -22:53 &   13.0 & +0.01 \\
MRTJ1925-4257 & 19:25 & -42:57 &    8.1 & +0.90 & MRTJ2034-3548 & 20:34 & -35:48 &   11.6 & +0.53 \\
  1923-187 & 19:25 & -18:36 &    7.1 & +0.20 &   2032-350 & 20:35 & -34:54 &   37.7 & +0.41 \\
MRTJ1926-3242 & 19:26 & -32:42 &   13.1 & +0.36 & MRTJ2042-2855 & 20:42 & -28:55 &    7.5 & +0.11 \\
MRTJ1926-3918 & 19:26 & -39:18 &    7.0 & +3.51 &   2040-267 & 20:43 & -26:33 &   10.7 & -0.12 \\
MRTJ1928-2931 & 19:28 & -29:31 &    9.9 & +0.38 & MRTJ2050-2949 & 20:50 & -29:49 &    5.7 & -1.01 \\
MRTJ1929-3733 & 19:29 & -37:33 &    6.8 & +1.55 & MRTJ2052-3640 & 20:52 & -36:40 &   14.8 & +0.49 \\
MRTJ1930-1509 & 19:30 & -15:09 &    6.2 & -2.02 & MRTJ2053-4818 & 20:53 & -48:18 &    7.6 & -0.02 \\
MRTJ1931-3354 & 19:31 & -33:54 &   10.2 & +0.40 &   2053-201 & 20:56 & -19:57 &   12.0 & -0.03 \\
  1928-266 & 19:31 & -26:34 &    4.9 & -2.64 &   2052-474 & 20:56 & -47:15 &    8.0 & +0.09 \\
MRTJ1932-1931 & 19:32 & -19:31 &    7.8 & -0.32 & MRTJ2058-4905 & 20:58 & -49:05 &    8.5 & -0.10 \\
MRTJ1932-2754 & 19:32 & -27:54 &    7.2 & +0.11 &  J2100-175 & 21:00 & -17:45 &   23.5 & -1.57 \\
MRTJ1933-3940 & 19:33 & -39:40 &   16.2 & +0.46 &   2058-282 & 21:01 & -28:01 &   35.7 & -0.08 \\
MRTJ1933-2633 & 19:33 & -26:33 &    8.1 & -0.44 & MRTJ2102-3921 & 21:02 & -39:21 &    8.3 & -0.81 \\
  1932-464 & 19:35 & -46:20 &   91.6 & -0.75 & MRTJ2103-2749 & 21:03 & -27:49 &    5.9 & +0.74 \\
  1938-155 & 19:41 & -15:24 &   17.9 & -0.40 & MRTJ2105-4848 & 21:05 & -48:48 &    7.2 & +0.51 \\
MRTJ1943-4030 & 19:43 & -40:30 &   26.2 & +0.36 &  J2107-253 & 21:07 & -25:25 &   86.3 & -0.31 \\
MRTJ1945-2706 & 19:45 & -27:06 &    5.9 & -1.14 & MRTJ2110-3351 & 21:10 & -33:51 &    9.2 & +0.42 \\
MRTJ1951-2737 & 19:51 & -27:37 &    6.6 & +0.08 &   2110-352 & 21:14 & -35:02 &   10.0 & +0.54 \\
MRTJ1954-3054 & 19:54 & -30:54 &    5.4 & +0.05 &   2111-259 & 21:14 & -25:41 &    9.3 & +0.89 \\
MRTJ1955-5001 & 19:55 & -50:01 &   15.0 & +0.65 &  J2117-206 & 21:16 & -20:55 &   23.2 & -0.24 \\
  1953-425 & 19:57 & -42:22 &   32.8 & +0.77 &  J2118-302 & 21:18 & -30:19 &   13.2 & +0.31 \\
MRTJ1958-4657 & 19:58 & -46:57 &    9.3 & -0.04 &  J2123-163 & 21:23 & -16:27 &   24.0 & -0.89 \\
MRTJ1959-3534 & 19:59 & -35:34 &   13.0 & +0.28 & MRTJ2126-3941 & 21:26 & -39:41 &    7.1 & +0.55 \\
MRTJ2006-5011 & 20:06 & -50:11 &   12.2 & +0.34 & MRTJ2126-2901 & 21:26 & -29:01 &    9.6 & -0.14 \\
MRTJ2007-4750 & 20:07 & -47:50 &    7.3 & +0.58 &  J2131-204 & 21:31 & -20:36 &   19.9 & -0.51 \\
MRTJ2009-4249 & 20:09 & -42:49 &    7.4 & -0.22 &  J2131-312 & 21:31 & -31:21 &    8.9 & +0.26 \\
MRTJ2009-3407 & 20:09 & -34:07 &    6.5 & -0.89 &  J2138-143 & 21:37 & -14:32 &   27.0 & -0.49 \\
\hline
\end{tabular}
\end{table}

\begin{table}[ht]
\caption{Measured Source Parameters}
\begin{tabular}{l|lrrr||l|lrrr}
\hline
Name & RA & DEC & $f_{150}$ & $\alpha$ & Name & RA & DEC & $f_{150}$ & $\alpha$
\\
\hline
  2134-209 & 21:37 & -20:42 &   12.2 & +0.27 & MRTJ2229-4051 & 22:29 & -40:51 &   22.4 & +0.60 \\
MRTJ2138-1843 & 21:38 & -18:43 &    6.8 & +0.01 &   2226-386 & 22:29 & -38:23 &   20.6 & +0.83 \\
MRTJ2139-4213 & 21:39 & -42:13 &    8.1 & +1.01 &   2234-174 & 22:37 & -17:12 &    6.4 & -1.05 \\
MRTJ2139-2556 & 21:39 & -25:56 &    7.5 & -0.65 & MRTJ2237-1145 & 22:37 & -11:45 &    5.9 & -0.82 \\
MRTJ2140-4412 & 21:40 & -44:12 &    8.6 & +0.53 & MRTJ2238-1731 & 22:38 & -17:31 &    5.1 & -3.25 \\
  2140-434 & 21:43 & -43:12 &   37.0 & +0.27 & MRTJ2246-3044 & 22:46 & -30:44 &    8.7 & +0.34 \\
MRTJ2145-3441 & 21:45 & -34:41 &    5.6 & +0.03 &   2244-372 & 22:47 & -36:57 &    8.4 & -0.08 \\
  2149-200 & 21:51 & -19:46 &    8.9 & -0.24 & MRTJ2250-2301 & 22:50 & -23:01 &    6.6 & -0.08 \\
MRTJ2152-2828 & 21:52 & -28:28 &    9.5 & +0.31 & MRTJ2251-4258 & 22:51 & -42:58 &    7.6 & +0.19 \\
MRTJ2153-4638 & 21:53 & -46:38 &   14.8 & -0.06 &   2250-412 & 22:53 & -40:57 &   60.9 & +0.18 \\
  2150-202 & 21:53 & -20:01 &    5.3 & -0.60 &   2252-394 & 22:55 & -39:13 &   11.8 & +0.04 \\
MRTJ2154-4552 & 21:54 & -45:52 &    8.0 & +0.76 & MRTJ2256-4617 & 22:56 & -46:17 &   10.0 & +0.84 \\
MRTJ2156-4350 & 21:56 & -43:50 &    7.4 & -0.31 & MRTJ2302-3718 & 23:02 & -37:18 &   18.5 & +0.41 \\
MRTJ2156-1127 & 21:56 & -11:27 &    7.5 & -1.67 & MRTJ2303-4215 & 23:03 & -42:15 &   10.7 & +0.20 \\
 J2157-181 & 21:56 & -18:13 &   25.8 & -0.68 & MRTJ2304-3431 & 23:04 & -34:31 &    6.8 & +0.54 \\
MRTJ2201-3746 & 22:01 & -37:46 &   14.6 & -0.11 & MRTJ2306-2506 & 23:06 & -25:06 &    7.1 & -0.28 \\
MRTJ2201-3321 & 22:01 & -33:21 &    7.1 & -0.46 & MRTJ2307-4132 & 23:07 & -41:32 &   13.7 & +0.48 \\
MRTJ2206-1835 & 22:06 & -18:35 &   11.0 & -0.70 & MRTJ2310-2758 & 23:10 & -27:58 &    9.3 & -0.32 \\
  2204-203 & 22:07 & -20:04 &    6.0 & -1.15 & MRTJ2312-4127 & 23:12 & -41:27 &    9.3 & +1.39 \\
MRTJ2207-4541 & 22:07 & -45:41 &    8.0 & +0.20 & MRTJ2313-4243 & 23:13 & -42:43 &    7.5 & -0.12 \\
MRTJ2208-3132 & 22:08 & -31:32 &    6.2 & -0.18 & MRTJ2316-4729 & 23:16 & -47:29 &    9.2 & +0.54 \\
MRTJ2210-4542 & 22:10 & -45:42 &   15.6 & +0.53 &   2313-167 & 23:16 & -16:25 &    6.8 & -0.42 \\
  2210-404 & 22:13 & -40:12 &    8.7 & +0.45 & MRTJ2319-4206 & 23:19 & -42:06 &   11.1 & +0.17 \\
MRTJ2214-2456 & 22:14 & -24:57 &    7.2 & -0.02 & MRTJ2319-2204 & 23:19 & -22:04 &   11.3 & -0.55 \\
 J2214-170 & 22:14 & -17:01 &  173.8 & -1.05 &   2317-277 & 23:19 & -27:28 &   19.4 & -0.44 \\
MRTJ2216-2803 & 22:16 & -28:03 &    8.0 & -0.55 &   2317-341 & 23:20 & -33:53 &    7.8 & -0.40 \\
  2213-456 & 22:16 & -45:22 &   11.4 & +1.93 &  J2321-162 & 23:21 & -16:23 &   33.5 & -0.98 \\
MRTJ2217-4016 & 22:17 & -40:16 &    8.4 & -0.36 & MRTJ2321-2410 & 23:21 & -24:10 &    6.7 & -0.91 \\
MRTJ2218-3024 & 22:18 & -30:24 &    6.9 & -0.04 & MRTJ2325-4051 & 23:25 & -40:51 &    6.7 & +0.85 \\
  2216-281 & 22:19 & -27:56 &   13.4 & +0.08 &  J2325-121 & 23:25 & -12:07 &   37.3 & -1.44 \\
MRTJ2220-3732 & 22:20 & -37:32 &    5.7 & -0.12 & MRTJ2326-4027 & 23:26 & -40:27 &   28.1 & +0.24 \\
MRTJ2221-5018 & 22:21 & -50:18 &   16.3 & +0.40 &   2325-151 & 23:28 & -14:54 &    6.3 & -1.43 \\
MRTJ2222-4527 & 22:22 & -45:27 &    8.4 & +0.17 &   2325-214 & 23:28 & -21:07 &    6.7 & -1.52 \\
MRTJ2225-4020 & 22:25 & -40:20 &    8.3 & -0.08 &   2326-196 & 23:29 & -19:24 &    7.1 & -0.94 \\
MRTJ2227-3033 & 22:27 & -30:33 &    6.2 & +0.13 & MRTJ2331-2452 & 23:31 & -24:52 &    8.1 & -0.66 \\
\hline
\end{tabular}
\end{table}

\begin{table}[ht]
\caption{Measured Source Parameters}
\begin{tabular}{l|lrrr||l|lrrr}
\hline
Name & RA & DEC & $f_{150}$ & $\alpha$ & Name & RA & DEC & $f_{150}$ & $\alpha$
\\
\hline
MRTJ2333-3057 & 23:33 & -30:57 &    6.8 & +0.66 &   2345-284 & 23:47 & -28:07 &    7.8 & -0.96 \\
  2331-416 & 23:34 & -41:24 &   58.2 & +0.14 &   2345-426 & 23:47 & -42:20 &    7.3 & +0.72 \\
MRTJ2334-3345 & 23:34 & -33:45 &    6.2 & +0.63 & MRTJ2349-4638 & 23:49 & -46:38 &    7.5 & -0.15 \\
MRTJ2336-3443 & 23:36 & -34:43 &   14.5 & -0.74 &  J2351-246 & 23:50 & -24:57 &   19.3 & -0.34 \\
 J2341-162 & 23:41 & -16:20 &   31.8 & -1.45 &   2352-455 & 23:55 & -45:13 &   11.5 & +0.11 \\
  2339-353 & 23:41 & -35:06 &   16.5 & +0.26 &  J2357-345 & 23:57 & -34:45 &   56.6 & -0.42 \\
MRTJ2343-2141 & 23:43 & -21:41 &    5.8 & -0.66 & MRTJ2358-4208 & 23:58 & -42:08 &    7.5 & -0.61 \\
MRTJ2344-5040 & 23:44 & -50:40 &    7.1 & +0.03 & & & & & \\
\hline
\end{tabular}
\end{table}

\clearpage

\begin{figure*}\centering
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_0000-362.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_J0003-173.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_MRTJ0003-3059.png}\\
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_MRTJ0006-4234.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_MRTJ0009-4503.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_MRTJ0010-4339.png}\\
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_MRTJ0010-4423.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_MRTJ0012-3322.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_0012-383.png}\\
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_0013-147.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_MRTJ0016-3827.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_J0019-124.png}\\
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_MRTJ0020-4847.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_MRTJ0020-2015.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_MRTJ0021-1910.png}\\
\caption{Spectra of the next 15 sources, as described in Figure \ref{fig:src_spec1}.
}\label{fig:src_spec1}
\end{figure*}\clearpage

\begin{figure*}\centering
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_MRTJ0021-4657.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_0020-253.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_J0025-293.png}\\
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_0023-333.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_0023-263.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_MRTJ0026-4918.png}\\
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_0024-372.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_MRTJ0028-4157.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_MRTJ0030-5018.png}\\
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_J0035-200.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_MRTJ0036-4903.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_0034-377.png}\\
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_MRTJ0038-3859.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_0039-445.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_0042-357.png}\\
\caption{Spectra of the next 15 sources, as described in Figure \ref{fig:src_spec1}.
}\label{fig:src_spec2}
\end{figure*}\clearpage

\begin{figure*}\centering
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_0043-424.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_0045-255.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_0048-447.png}\\
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_0049-433.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_J0059-170.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_0057-180.png}\\
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_0100-221.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_0100-278.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_0101-416.png}\\
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_0102-384.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_0103-453.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_J0108-160.png}\\
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_0112-445.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_0114-476.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_0114-211.png}\\
\caption{Spectra of the next 15 sources, as described in Figure \ref{fig:src_spec1}.
}\label{fig:src_spec3}
\end{figure*}\clearpage

\begin{figure*}\centering
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_0116-413.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_J0120-152.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_0119-377.png}\\
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_0122-255.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_0124-409.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_0124-414.png}\\
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_J0128-140.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_0125-438.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_J0130-261.png}\\
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_0131-450.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_0131-367.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_0139-273.png}\\
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_J0142-163.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_0141-439.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_0144-374.png}\\
\caption{Spectra of the next 15 sources, as described in Figure \ref{fig:src_spec1}.
}\label{fig:src_spec4}
\end{figure*}\clearpage

\begin{figure*}\centering
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_0148-297.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_0149-394.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_0149-299.png}\\
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_0152-437.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_J0200-305.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_0159-117.png}\\
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_0201-441.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_0202-182.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_0204-378.png}\\
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_0207-112.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_0211-344.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_J0216-126.png}\\
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_0213-134.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_0214-480.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_0216-250.png}\\
\caption{Spectra of the next 15 sources, as described in Figure \ref{fig:src_spec1}.
}\label{fig:src_spec5}
\end{figure*}\clearpage

\begin{figure*}\centering
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_0216-366.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_0217-369.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_0218-387.png}\\
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_0220-422.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_0221-285.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_0222-234.png}\\
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_0225-308.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_0228-399.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_0231-235.png}\\
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_J0238-193.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_0240-422.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_0244-452.png}\\
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_0245-297.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_0252-418.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_J0256-232.png}\\
\caption{Spectra of the next 15 sources, as described in Figure \ref{fig:src_spec1}.
}\label{fig:src_spec6}
\end{figure*}\clearpage

\begin{figure*}\centering
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_0257-398.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_0302-361.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_0304-122.png}\\
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_0305-226.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_J0313-145.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_0313-271.png}\\
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_0314-440.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_0315-146.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_0316-444.png}\\
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_0319-453.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_0320-389.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_for.png}\\
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_0325-441.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_0326-288.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_0327-168.png}\\
\caption{Spectra of the next 15 sources, as described in Figure \ref{fig:src_spec1}.
}\label{fig:src_spec7}
\end{figure*}\clearpage

\begin{figure*}\centering
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_0328-370.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_0332-391.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_0335-415.png}\\
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_0336-355.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_0338-404.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_0340-372.png}\\
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_0344-345.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_J0351-143.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_0349-278.png}\\
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_0354-485.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_0358-371.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_J0400-161.png}\\
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_0403-132.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_J0408-121.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_0406-311.png}\\
\caption{Spectra of the next 15 sources, as described in Figure \ref{fig:src_spec1}.
}\label{fig:src_spec8}
\end{figure*}\clearpage

\begin{figure*}\centering
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_J0409-242.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_0411-346.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_0413-425.png}\\
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_J0415-293.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_J0416-206.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_0418-399.png}\\
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_0420-264.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_0421-341.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_0427-366.png}\\
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_0431-300.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_0431-133.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_0435-300.png}\\
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_0438-436.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_J0445-281.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_0446-206.png}\\
\caption{Spectra of the next 15 sources, as described in Figure \ref{fig:src_spec1}.
}\label{fig:src_spec9}
\end{figure*}\clearpage

\begin{figure*}\centering
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_J0455-301.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_J0455-203.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_0454-463.png}\\
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_0454-220.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_0455-405.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_0456-301.png}\\
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_0503-284.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_J0511-184.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_0508-221.png}\\
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_0511-305.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_pic.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_J0522-205.png}\\
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_0521-364.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_0521-329.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_0523-327.png}\\
\caption{Spectra of the next 15 sources, as described in Figure \ref{fig:src_spec1}.
}\label{fig:src_spec10}
\end{figure*}\clearpage

\begin{figure*}\centering
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_J0543-242.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_0546-445.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_0547-408.png}\\
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_0554-323.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_0559-398.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_0600-383.png}\\
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_0600-131.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_0601-344.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_0602-319.png}\\
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_0604-352.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_J0607-202.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_0612-474.png}\\
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_0614-349.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_0615-365.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_0618-371.png}\\
\caption{Spectra of the next 15 sources, as described in Figure \ref{fig:src_spec1}.
}\label{fig:src_spec11}
\end{figure*}\clearpage

\begin{figure*}\centering
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_0625-354.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_0630-368.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_0630-273.png}\\
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_0634-205.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_0636-167.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_0637-277.png}\\
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_0642-436.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_0646-399.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_J0659-242.png}\\
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_0700-473.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_0703-451.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_0704-427.png}\\
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_0707-360.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_J0712-204.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_0715-362.png}\\
\caption{Spectra of the next 15 sources, as described in Figure \ref{fig:src_spec1}.
}\label{fig:src_spec12}
\end{figure*}\clearpage

\begin{figure*}\centering
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_J0717-250.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_J0722-185.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_J0747-186.png}\\
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_J0748-192.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_J0827-203.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_0834-196.png}\\
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_0837-120.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_J0853-205.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_0851-142.png}\\
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_J0902-256.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_J0918-121.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_0926-292.png}\\
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_0935-289.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_0942-196.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_0946-182.png}\\
\caption{Spectra of the next 15 sources, as described in Figure \ref{fig:src_spec1}.
}\label{fig:src_spec13}
\end{figure*}\clearpage

\begin{figure*}\centering
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_J0950-251.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_0955-288.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_J1005-214.png}\\
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_1002-216.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_1003-415.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_1006-286.png}\\
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_1011-316.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_1015-315.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_1017-421.png}\\
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_1017-426.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_1017-325.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_1024-414.png}\\
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_1025-405.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_1030-357.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_1030-340.png}\\
\caption{Spectra of the next 15 sources, as described in Figure \ref{fig:src_spec1}.
}\label{fig:src_spec14}
\end{figure*}\clearpage

\begin{figure*}\centering
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_1031-408.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_1033-413.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_1042-409.png}\\
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_1043-378.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_1044-357.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_1046-409.png}\\
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_1049-201.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_1052-340.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_1053-282.png}\\
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_1054-370.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_1056-360.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_J1106-244.png}\\
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_J1106-211.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_1105-440.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_1107-227.png}\\
\caption{Spectra of the next 15 sources, as described in Figure \ref{fig:src_spec1}.
}\label{fig:src_spec15}
\end{figure*}\clearpage

\begin{figure*}\centering
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_1109-402.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_1116-463.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_1123-351.png}\\
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_J1134-195.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_J1134-173.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_1135-390.png}\\
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_J1139-135.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_J1139-322.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_J1141-263.png}\\
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_J1142-285.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_J1143-114.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_1143-483.png}\\
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_1143-317.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_J1146-316.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_1143-332.png}\\
\caption{Spectra of the next 15 sources, as described in Figure \ref{fig:src_spec1}.
}\label{fig:src_spec16}
\end{figure*}\clearpage

\begin{figure*}\centering
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_1144-409.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_1146-117.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_1148-353.png}\\
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_1151-348.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_1155-423.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_1156-402.png}\\
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_1202-262.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_J1208-170.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_J1209-340.png}\\
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_1211-417.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_1212-448.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_1215-457.png}\\
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_1218-373.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_1221-423.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_1224-262.png}\\
\caption{Spectra of the next 15 sources, as described in Figure \ref{fig:src_spec1}.
}\label{fig:src_spec17}
\end{figure*}\clearpage

\begin{figure*}\centering
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_1225-440.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_1232-331.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_1232-249.png}\\
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_1232-416.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_1240-209.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_1243-412.png}\\
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_1244-112.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_1245-197.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_1246-410.png}\\
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_1247-401.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_1247-194.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_1251-184.png}\\
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_J1255-123.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_J1255-291.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_1254-333.png}\\
\caption{Spectra of the next 15 sources, as described in Figure \ref{fig:src_spec1}.
}\label{fig:src_spec18}
\end{figure*}\clearpage

\begin{figure*}\centering
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_1254-300.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_1257-230.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_1258-321.png}\\
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_1259-200.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_1302-326.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_J1312-222.png}\\
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_J1315-186.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_cen.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_1323-271.png}\\
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_J1330-214.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_J1331-256.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_1329-328.png}\\
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_1329-257.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_1330-328.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_1333-337.png}\\
\caption{Spectra of the next 15 sources, as described in Figure \ref{fig:src_spec1}.
}\label{fig:src_spec19}
\end{figure*}\clearpage

\begin{figure*}\centering
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_1334-296.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_1334-338.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_1340-373.png}\\
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_1346-391.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_1355-416.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_1359-358.png}\\
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_1400-338.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_1401-296.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_1402-367.png}\\
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_1403-273.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_1407-425.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_1413-364.png}\\
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_J1417-215.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_1415-379.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_1417-192.png}\\
\caption{Spectra of the next 15 sources, as described in Figure \ref{fig:src_spec1}.
}\label{fig:src_spec20}
\end{figure*}\clearpage

\begin{figure*}\centering
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_1416-493.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_J1423-273.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_1420-180.png}\\
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_1421-382.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_J1425-296.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_J1428-120.png}\\
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_1424-418.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_1425-274.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_1425-397.png}\\
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_1436-167.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_1439-264.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_1445-468.png}\\
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_1449-129.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_1451-364.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_1452-421.png}\\
\caption{Spectra of the next 15 sources, as described in Figure \ref{fig:src_spec1}.
}\label{fig:src_spec21}
\end{figure*}\clearpage

\begin{figure*}\centering
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_J1456-111.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_1459-419.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_1514-165.png}\\
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_1518-295.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_1526-423.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_1528-293.png}\\
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_1530-334.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_1540-337.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_1545-321.png}\\
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_1556-215.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_J1605-173.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_1602-288.png}\\
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_1618-235.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_J1624-114.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_1621-260.png}\\
\caption{Spectra of the next 15 sources, as described in Figure \ref{fig:src_spec1}.
}\label{fig:src_spec22}
\end{figure*}\clearpage

\begin{figure*}\centering
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_1622-310.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_1628-268.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_1640-153.png}\\
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_J1646-223.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_MRTJ1802-4859.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_MRTJ1803-4331.png}\\
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_MRTJ1809-4552.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_1817-391.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_MRTJ1830-3820.png}\\
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_MRTJ1830-3602.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_MRTJ1832-3422.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_MRTJ1833-3940.png}\\
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_MRTJ1834-4357.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_1834-436.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_MRTJ1841-3629.png}\\
\caption{Spectra of the next 15 sources, as described in Figure \ref{fig:src_spec1}.
}\label{fig:src_spec23}
\end{figure*}\clearpage

\begin{figure*}\centering
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_MRTJ1843-4836.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_MRTJ1844-4022.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_MRTJ1848-5004.png}\\
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_1847-260.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_MRTJ1851-3345.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_MRTJ1857-3019.png}\\
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_MRTJ1902-2705.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_MRTJ1902-2329.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_MRTJ1914-2928.png}\\
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_MRTJ1915-2653.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_1914-455.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_1916-300.png}\\
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_1918-355.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_MRTJ1925-4257.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_1923-187.png}\\
\caption{Spectra of the next 15 sources, as described in Figure \ref{fig:src_spec1}.
}\label{fig:src_spec24}
\end{figure*}\clearpage

\begin{figure*}\centering
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_MRTJ1926-3242.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_MRTJ1926-3918.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_MRTJ1928-2931.png}\\
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_MRTJ1929-3733.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_MRTJ1930-1509.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_MRTJ1931-3354.png}\\
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_1928-266.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_MRTJ1932-1931.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_MRTJ1932-2754.png}\\
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_MRTJ1933-3940.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_MRTJ1933-2633.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_1932-464.png}\\
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_1938-155.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_MRTJ1943-4030.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_MRTJ1945-2706.png}\\
\caption{Spectra of the next 15 sources, as described in Figure \ref{fig:src_spec1}.
}\label{fig:src_spec25}
\end{figure*}\clearpage

\begin{figure*}\centering
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_MRTJ1951-2737.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_MRTJ1954-3054.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_MRTJ1955-5001.png}\\
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_1953-425.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_MRTJ1958-4657.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_MRTJ1959-3534.png}\\
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_MRTJ2006-5011.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_MRTJ2007-4750.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_MRTJ2009-4249.png}\\
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_MRTJ2009-3407.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_MRTJ2016-3035.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_MRTJ2017-4516.png}\\
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_2017-439.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_2018-224.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_MRTJ2028-1521.png}\\
\caption{Spectra of the next 15 sources, as described in Figure \ref{fig:src_spec1}.
}\label{fig:src_spec26}
\end{figure*}\clearpage

\begin{figure*}\centering
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_MRTJ2029-4119.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_MRTJ2033-4540.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_2030-230.png}\\
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_MRTJ2034-3548.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_2032-350.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_MRTJ2042-2855.png}\\
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_2040-267.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_MRTJ2050-2949.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_MRTJ2052-3640.png}\\
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_MRTJ2053-4818.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_2053-201.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_2052-474.png}\\
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_MRTJ2058-4905.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_J2100-175.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_2058-282.png}\\
\caption{Spectra of the next 15 sources, as described in Figure \ref{fig:src_spec1}.
}\label{fig:src_spec27}
\end{figure*}\clearpage

\begin{figure*}\centering
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_MRTJ2102-3921.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_MRTJ2103-2749.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_MRTJ2105-4848.png}\\
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_J2107-253.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_MRTJ2110-3351.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_2110-352.png}\\
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_2111-259.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_J2117-206.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_J2118-302.png}\\
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_J2123-163.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_MRTJ2126-3941.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_MRTJ2126-2901.png}\\
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_J2131-204.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_J2131-312.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_J2138-143.png}\\
\caption{Spectra of the next 15 sources, as described in Figure \ref{fig:src_spec1}.
}\label{fig:src_spec28}
\end{figure*}\clearpage

\begin{figure*}\centering
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_2134-209.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_MRTJ2138-1843.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_MRTJ2139-4213.png}\\
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_MRTJ2139-2556.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_MRTJ2140-4412.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_2140-434.png}\\
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_MRTJ2145-3441.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_2149-200.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_MRTJ2152-2828.png}\\
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_MRTJ2153-4638.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_2150-202.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_MRTJ2154-4552.png}\\
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_MRTJ2156-4350.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_MRTJ2156-1127.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_J2157-181.png}\\
\caption{Spectra of the next 15 sources, as described in Figure \ref{fig:src_spec1}.
}\label{fig:src_spec29}
\end{figure*}\clearpage

\begin{figure*}\centering
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_MRTJ2201-3746.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_MRTJ2201-3321.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_MRTJ2206-1835.png}\\
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_2204-203.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_MRTJ2207-4541.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_MRTJ2208-3132.png}\\
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_MRTJ2210-4542.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_2210-404.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_MRTJ2214-2456.png}\\
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_J2214-170.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_MRTJ2216-2803.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_2213-456.png}\\
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_MRTJ2217-4016.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_MRTJ2218-3024.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_2216-281.png}\\
\caption{Spectra of the next 15 sources, as described in Figure \ref{fig:src_spec1}.
}\label{fig:src_spec30}
\end{figure*}\clearpage

\begin{figure*}\centering
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_MRTJ2220-3732.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_MRTJ2221-5018.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_MRTJ2222-4527.png}\\
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_MRTJ2225-4020.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_MRTJ2227-3033.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_MRTJ2229-4051.png}\\
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_2226-386.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_2234-174.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_MRTJ2237-1145.png}\\
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_MRTJ2238-1731.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_MRTJ2246-3044.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_2244-372.png}\\
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_MRTJ2250-2301.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_MRTJ2251-4258.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_2250-412.png}\\
\caption{Spectra of the next 15 sources, as described in Figure \ref{fig:src_spec1}.
}\label{fig:src_spec31}
\end{figure*}\clearpage

\begin{figure*}\centering
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_2252-394.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_MRTJ2256-4617.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_MRTJ2302-3718.png}\\
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_MRTJ2303-4215.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_MRTJ2304-3431.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_MRTJ2306-2506.png}\\
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_MRTJ2307-4132.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_MRTJ2310-2758.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_MRTJ2312-4127.png}\\
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_MRTJ2313-4243.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_MRTJ2316-4729.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_2313-167.png}\\
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_MRTJ2319-4206.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_MRTJ2319-2204.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_2317-277.png}\\
\caption{Spectra of the next 15 sources, as described in Figure \ref{fig:src_spec1}.
}\label{fig:src_spec32}
\end{figure*}\clearpage

\begin{figure*}\centering
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_2317-341.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_J2321-162.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_MRTJ2321-2410.png}\\
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_MRTJ2325-4051.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_J2325-121.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_MRTJ2326-4027.png}\\
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_2325-151.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_2325-214.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_2326-196.png}\\
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_MRTJ2331-2452.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_MRTJ2333-3057.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_2331-416.png}\\
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_MRTJ2334-3345.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_MRTJ2336-3443.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_J2341-162.png}\\
\caption{Spectra of the next 15 sources, as described in Figure \ref{fig:src_spec1}.
}\label{fig:src_spec33}
\end{figure*}\clearpage

\begin{figure*}\centering
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_2339-353.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_MRTJ2343-2141.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_MRTJ2344-5040.png}\\
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_2345-284.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_2345-426.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_MRTJ2349-4638.png}\\
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_J2351-246.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_2352-455.png}
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_J2357-345.png}\\
\includegraphics[width=0.32\columnwidth]{plots/specs/spec_MRTJ2358-4208.png}
\caption{Spectra of the next 10 sources, as described in Figure \ref{fig:src_spec1}.
}\label{fig:src_spec34}
\end{figure*}

\bibliographystyle{apj}
\bibliography{biblio}
\end{document}

### 2013-04-22 nat2jour.pl

@@ -1,0 +1,374 @@
+#!/opt/local/bin/perl -- # -*-Perl-*-
+
+######################################################################
+#
+# nat2jour.pl
+#
+# Program for converting tex/bbl files generated using the natbib
+# (v5.3) BibTeX style into files which may be submitted electronically
+# to astronomy journals.
+#
+# Written by Jonathan Baker <jbaker@astro.berkeley.edu>
+# inspired by 2apj.pl code by Eddie Baron
+#
+# $Log: nat2jour.pl,v $
+# Revision 1.6  2000/04/21 17:48:02  jbaker
+# Changed addition of space before \cite's so that it only happens when
+# \cite is preceeded by a \... command (so that it doesn't happen with
+# ~\cite, for example, as suggested by Norman Gray).
+#
+# Revision 1.5  2000/04/20 22:16:26  jbaker
+# If using -references, insert a space before \cite in case it is
+# terminating a command (like \protect, for example).
+#
+# Revision 1.4  1999/09/01 02:45:19  jbaker
+# Added flag to generate `references' environment instead of `thebibliography'.
+#
+# Revision 1.3  1998/08/30 19:48:32  jbaker
+# Added RCS keywords.  Non-MNRAS lettering style changed from "1998a,b" to
+# "1998a, 1998b".
+#
+#
+######################################################################
+
+$MaxAuths = 8;
+$inline = 0;
+$refenv = 0; $bibenv = "thebibliography";
+$etal = "{et al.}";
+
+$usage = <<EOT;
+
+Usage: $0 [options] INPUT [OUTPUT]
+
+$Id: nat2jour.pl,v 1.6 2000/04/21 17:48:02 jbaker Exp $
+
+Convert BibTeX/Natbib tex/bbl files into files which may be submitted
+to astronomy journals.  Inlines citations adding \\markcite or
+\\nocite and formats \\bibitems and removes natbib package dependencies,
+stripping "%nat" comments.  Also implements astronomy 3-author citation
+style and truncates long author lists.
+
+Arguments:
+  INPUT        If this is "foo", input files are "foo.tex" and "foo.bbl"
+  OUTPUT       (optional) Same for output files; default appends "-aas".
+
+Options:
+  -inline      Inline the bibliography into a single LaTeX file
[…]

### 2013-04-22 plots/SED_fit_to_mrtprep.py

@@ -1,0 +1,170 @@
+#! /usr/bin/env python
+"""
+python script to parse output of avg_spectrum.py into input suitable for the MRT creator at
+http://authortools.aas.org/MRT/upload.html
+
+input a catalog using usual aipy convention for positions of the sources
+"""
+import numpy as n,sys,optparse,aipy as a,ephem
+from pylab import *
+
+
+o = optparse.OptionParser()
+o.set_usage('cat_to_mrt.py [options] psa64_pic_stripe.txt')
+o.set_description(__doc__)
+a.scripting.add_standard_options(o, cal=True, src=True)
+o.add_option('--filename',
+    help='output MRT file. Default=<input>_tomrt.txt')
+opts,args = o.parse_args(sys.argv[1:])
+
+if not opts.filename is None:
+    filename = opts.filename
+else:
+    filename = args[-1][:-4]+'_tomrt.txt'
+
+lines = open(args[-1]).readlines()
+lines = [line.split() for line in lines if not line.startswith('#')]
+srclist = [l[0] for l in lines]
+overlap = n.array([n.float(line[8]) for line in lines])
+
+#if not opts.cat is None:
+srclist,cutoff,catalogs = a.scripting.parse_srcs(','.join(srclist), opts.cat)
+if not opts.cal is None:
+    cat = a.cal.get_catalog(opts.cal, srclist, cutoff, catalogs)
+else:
+    cat = a.src.get_catalog(srclist, cutoff, catalogs)
+o = a.scripting.get_null_aa()
+cat.compute(o)
+
+def nrow(s,n):
+    return '\n'.join([s]*n)
+def l2a(l,delim=','):
+    #convert a delim list into a float array
+    return n.array(map(float,l.split(delim)))
+def p(f,d):
+    "print the input as a string with n digits"
+    return str(n.round(f,d))
+
+F = open(filename,'w')
+recs = []
+picrec = None
+total = 0
+for i,line in enumerate(lines):
+    rec = []
+    if overlap[i]==0: continue
+    if line[0] == 'pic':
+        rec.append('Pictor A')
+        picrec = total
+    elif line[0] == 'cen':
+        rec.append('Centaurus A')
+    elif line[0] == 'vela':
+        rec.append('Pup A')
+    else:
+        rec.append(line[0])
+
+    rec.append(str(n.round(cat[line[0]].ra*180/n.pi,2)))
[…]

### 2013-04-22 plots/cat_to_mrt.py

@@ -1,0 +1,110 @@
+#! /usr/bin/env python
+"""
+python script to parse output of avg_spectrum.py into input suitable for the MRT creator at
+http://authortools.aas.org/MRT/upload.html
+
+input a catalog using usual aipy convention for positions of the sources
+"""
+import numpy as n,sys,optparse,aipy as a,ephem
+from pylab import *
+
+
+o = optparse.OptionParser()
+o.set_usage('cat_to_mrt.py [options] psa64_pic_stripe.txt')
+o.set_description(__doc__)
+a.scripting.add_standard_options(o, cal=True, src=True)
+o.add_option('--filename',default='raw_table.txt',
+    help='output MRT file. Default=raw_table.txt')
+opts,args = o.parse_args(sys.argv[1:])
+
+lines = open(args[-1]).readlines()
+print 
+freqs = map(float,lines[0].split('=')[1].split(','))
+
+lines = [line.split() for line in lines if not line.startswith('#')]
+srclist = [l[0] for l in lines]
+
+#if not opts.cat is None:
+srclist,cutoff,catalogs = a.scripting.parse_srcs(','.join(srclist), opts.cat)
+if not opts.cal is None:
+    cat = a.cal.get_catalog(opts.cal, srclist, cutoff, catalogs)
+else:
+    cat = a.src.get_catalog(srclist, cutoff, catalogs)
+o = a.scripting.get_null_aa()
+cat.compute(o)
+
+#first output the MRT input table
+#MRTfilename = args[-1][:-4]+'_MRT.txt'
+            
+F = open(opts.filename,'w')
+recs = []
+picrec = None
+for i,line in enumerate(lines):
+    rec = []
+    if line[0] == 'pic':
+        rec.append('Pictor A')
+        picrec = i
+    elif line[0] == 'cen':
+        rec.append('Centaurus A')
+    elif line[0] == 'vela':
+        rec.append('Pup A')
+    else:
+        rec.append(line[0])
+    rec.append(str(n.round(cat[line[0]].ra*180/n.pi,2)))
+    rec.append(str(n.round(cat[line[0]].dec*180/n.pi,2)))
+    spec = line[1].split(',')
+    err = line[2].split(',')
+    for v,e in zip(spec,err):
+        rec.append(str(n.round(float(v),2)))
[…]

### 2013-04-22 plots/open_MCMC_files_in_FOMorder.sh

@@ -1,0 +1,39 @@
+#! /bin/bash
+#grep -v '^#' psa64_pic_stripe_SEDfit_wFOM.txt | sort  -t' ' -k 8 -g  > psa64_pic_stripe_SEDfit_FOMsorted.txt
+grep -v '^#' psa64_pic_stripe_perleycorr_SEDfits.txt | sort  -t' ' -k 10 -g  > \
+psa64_pic_stripe_perleycorr_SEDfits_Pcorrsorted.txt
+
+MYFILES=
+i=0
+for F in `cut -d' ' -f 1 psa64_pic_stripe_perleycorr_SEDfits_Pcorrsorted.txt`; 
+do 
+#print useful latex stuff
+if [ $i -eq 15 ]
+then
+i=0
+fi
+if [ $i -eq 0 ]
+then
+echo "\begin{figure*}[htbp]"
+echo "\begin{center}"
+fi
+
+MYFILES="${F}*MCMC.png $MYFILES"; 
+MYFILE=`ls ${F}*MCMC.png`
+echo "\includegraphics[width=2in]{plots/${MYFILE}}"   
+((i++)) 
+
+if [ $i -eq 15 ]
+then
+echo "\end{center}"
+echo "\caption{fits of the next 16 sources, as described in Figure \ref{fig:src_spec1}."
+echo "}\label{fig:src_spec1}"
+echo "\end{figure*}"
+echo "\clearpage"
+i=0
+fi
+done
+echo $MYFILES
+open $MYFILES
+
+

### 2013-04-22 plots/plot_FOM.py

@@ -1,0 +1,70 @@
+#! /usr/bin/env python
+"""
+Plot the ouput of beam_src_vs_ha along with other catalog data
+"""
+import matplotlib
+#matplotlib.use('Agg')
+import os,aipy as a, numpy as n#,atpy
+import optparse, sys#, scipy.optimize
+#import capo as C
+from pylab import *
+from scipy import optimize
+#import ipdb
+
+CAT=True
+o = optparse.OptionParser()
+a.scripting.add_standard_options(o, cal=True,src=True)
+o.set_description(__doc__)
+#o.add_option('--mcmc_recompute',action='store_true',
+#    help='Ignore saved traces and rerun mcmc fit, otherwise just move on to plotting.')
+#o.add_option('--plot',action='store_true',
+#    help='Do MCMC contour plots')
+opts,args = o.parse_args(sys.argv[1:])
+
+srcs,coff,cats = a.scripting.parse_srcs(opts.src,opts.cat)
+cat = a.cal.get_catalog(opts.cal,srcs,catalogs=cats)
+aa = a.scripting.get_null_aa()
+#use PAPER for the location
+aa.lat = '-30:43:17.5'
+aa.lon = '21:25:41.9'
+#aa.set_afreqs([0.15])
+cat.compute(aa)
+RAs = []
+DECs = []
+FOMs = []
+FLUX = []
+for F in args:
+    lines = open(F).readlines()
+    for line in lines:
+        if line.startswith('#'): continue
+        FOM_change = float(line.split()[-1])
+        srcname = line.split()[0]
+        FOMs.append(FOM_change)
+        RAs.append(cat[srcname].ra)
+        DECs.append(cat[srcname].dec)
+        FLUX.append(cat[srcname].get_jys())
+        if FOM_change>1:
+            print cat[srcname],FOM_change
+RAs = n.array(RAs)
+DECs = n.array(DECs)
+FLUX = n.array(FLUX)
+figure(figsize=(7,9))
+clf()
+subplot(311)
+plot(RAs*12/n.pi,FOMs,'.k')
+xlabel('RA [h]')
+ylabel('FOM improvement')
+subplot(312)
+plot(DECs*180/n.pi,FOMs,'.k')
+xlabel('DEC [d]')
+ylabel('FOM improvement')
+subplot(313)
+loglog(FLUX,FOMs,'.k')
+xlabel('flux [Jy]')
+ylabel('FOM improvement')
[…]

### 2013-04-22 plots/plot_psa64_beam_profile.py

@@ -1,0 +1,20 @@
+"""
+plot psa64_beam_profile.dat with nice interpolation
+"""
+from matplotlib import use
+use('Agg')
+from pylab import *
+import numpy as n
+from scipy.interpolate import InterpolatedUnivariateSpline,UnivariateSpline
+
+D = n.loadtxt('psa64_beam_profile.dat')
+figure()
+x = (D[:,0] - D[D[:,1].argmax(),0])*5
+semilogy(x,n.abs(D[:,1]),'k')
+xlabel('[arcmin]')
+ylabel('psf amplitude')
+subplots_adjust(bottom=0.13,left=0.13)
+#Y = InterpolatedUnivariateSpline(D[:,0],D[:,1],k=5)
+#x = n.linspace(D[:,0].min(),D[:,0].max())
+#plot(x,Y(x),'k')
+savefig('psa64_beam_profile.png')

### 2013-04-22 plots/plot_srcs_on_sky.py

@@ -1,0 +1,592 @@
+#!/usr/bin/env python
+"""
+Script for displaying a projection of a spherical (Healpix) data set stored
+in a *.fits file.
+
+Modified version of plot_map for showing stylized sky.
+Background is Angelica's GSM.  Sources are shown as log power radius circles.
+
+Modified further to grab source names and data from a text file
+Author: Aaron Parsons, Danny Jacobs
+"""
+
+import aipy as a, numpy as n, sys, os, ephem, optparse
+import matplotlib as mpl
+from pylab import *
+def imedian(x):
+    return n.sort(x)[len(x)/2]
+class Basemap:
+    """A placeholder class to give plot_map.py some functionality if
+    matplotlib-basemap is not installed."""
+    def __init__(self, projection, lat_0=0, lon_0=0, **kwargs):
+        if projection != 'cyl':
+            raise ValueError('Without matplotlib-basemap installed, only cyl projection is supported.')
+        self.lat_0, self.lon_0 = lat_0, lon_0
+    def __call__(self, lon, lat, inverse=False):
+        if inverse:
+            lon = lon.astype(n.float) * 90 - self.lon_0
+            lon = self.wrap(lon, -180, 180)
+            lat = lat.astype(n.float) * 90 - self.lat_0
+            lat = self.wrap(lat, -90, 90)
+            return lon,lat
+        else:
+            x = (lon + self.lon_0) / 90.
+            x = self.wrap(x, -2, 2)
+            y = (lat + self.lat_0) / 90.
+            y = self.wrap(y, -1, 1)
+            return x,y
+    def wrap(self, data, lo, hi):
+        data = n.where(data >= hi, lo + (data - hi), data)
+        data = n.where(data < lo, hi + (data - lo), data)
+        return data
+    def drawmapboundary(self): pass
+    def drawmeridians(self, locs, **kwargs):
+        x,y = self(locs, n.zeros_like(locs))
+        x = self.wrap(x, -2, 2)
+        p.xticks(x, visible=False)
+        p.grid(True)
+    def drawparallels(self, lats, **kwargs):
+        x,y = self(n.zeros_like(lats),lats)
+        y = self.wrap(y, -1, 1)
+        p.yticks(y, [str(L) for L in lats])
+        p.grid(True)
[…]

### 2013-04-22 plots/sort_SI_plots.py

@@ -1,0 +1,118 @@
+"""
+python script to sort out output from fit_SED.py
+"""
+import numpy as n,sys
+from pylab import *
+
+lines = open(sys.argv[-1]).readlines()
+lines = [line for line in lines if not line.startswith('#')]
+print [len(line.split()) for line in lines]
+improvement = n.array([n.float(line.split()[9]) for line in lines]) # (FOM change)*(fraction of PAPER overlapping previos)
+overlap = n.array([n.float(line.split()[8]) for line in lines])
+coastline = n.array([float(line.split()[10]) for line in lines]) # number of pixels on the 76% contour
+poor = []
+change = []
+j = 0
+coastmax = n.mean(coastline)+n.std(coastline)*3
+disagree = []
+imps = []
+goodlines = []
+shit = []
+for i in n.argsort(improvement)[::-1]:
+    if coastline[i]>coastmax: 
+        #what else could there be?  
+        print '%Bad fit: ',lines[i].strip()
+        print '%\t\t improvement = ',improvement[i],'\t coastline = ',coastline[i]
+        shit.append(line)
+        continue #throw out bad fits with bubbly contours (long "coastline")  As of 5 April 2013 there are none!
+    if improvement[i] >0 and overlap[i]>0.001:   
+        goodlines.append(lines[i]) 
+        #good safe fits have some overlap, positive improvement and not bubbly contours (coastline) #on April 5 there
+        #is just one of these! I'm probably going to just include it in the good fits.
+    elif improvement[i]<0 and overlap[i]>0.001:
+        poor.append(lines[i])
+        #actually negative improvement 
+    else:
+        #these should just be sources that disagree completely
+        disagree.append(lines[i])
+
+
+print  "\\begin{figure*}[htbp]"
+print  "\\begin{center}"
+print "%ok fit, but doesn't agree with past data, or actually increases model uncertainty"
+print "%contour length limit = ",coastmax
+for line in n.sort(poor):
+    print '%Poor improvement: ',line.strip()
+    print "\includegraphics[width=2in]{plots/%s_SI_MCMC.png} %%%s"%\
+    (line.split()[0],line.split()[9]) #
+    
+
+print """\\end{center}
[…]

### 2013-04-22 ms.tex
Just rewrap of text (no edits).

@@
 \begin{abstract}
-We present the first spectral measurements from the Precision Array for Probing the Epoch of Reionization (PAPER) in South Africa observed in July and September of 2011.
-The spectra are determined by calibrating directly to a nearby source, eliminating the error-prone primary beam correction.
-The global flux calibration, bootstrapped from catalog data of 5 bright sources, is estimated to be accurate to 3.2\%.
-Comparing with prior measurements, 45 out of 58 sources observed are found to confirm and refine a spectral index model.
-This includes Pictor A which provides a key flux reference for PAPER's EoR power spectrum.
-Combining catalog data at other frequencies with the PAPER data we are able to estimate the flux model parameters to an uncertainty of 2.4\%.
-This accuracy, which is ultimately limited by the uncertainty of the many prior measurements used to estimate the flux scale, is an order of magnitude improvement on previous estimates.
+We present the first spectral measurements from the Precision Array for Probing
+the Epoch of Reionization (PAPER) in South Africa observed in July and
+September of 2011.  The spectra are determined by calibrating directly to a
+nearby source, eliminating the error-prone primary beam correction.  The global
+flux calibration, bootstrapped from catalog data of 5 bright sources, is
+estimated to be accurate to 3.2\%.  Comparing with prior measurements, 45 out
+of 58 sources observed are found to confirm and refine a spectral index model.
+This includes Pictor A which provides a key flux reference for PAPER's EoR
+power spectrum. Combining catalog data at other frequencies with the PAPER data
+we are able to estimate the flux model parameters to an uncertainty of 2.4\%.
+This accuracy, which is ultimately limited by the uncertainty of the many prior
+measurements used to estimate the flux scale, is an order of magnitude
+improvement on previous estimates.  
 \end{abstract}
@@
 
-Numerous radio telescopes are now exploring the prospects for
-using measurements of highly redshifted 21cm emission to inform our understanding
-of cosmic reionization in the redshift range $6< z<12$, corresponding to radio frequencies below 200MHz (see reviews in  \citet{Furlanetto:2006p2267,Morales:2010p8093,Pritchard:2012p9555}) .  
-These include telescopes aiming to measure the global temperature change of 
-21cm emission during the Epoch of Reionization (EoR), such as
-the Compact Reionization Experiment (CoRE) and
-the Experiment to Detect the Global EoR Signature (EDGES; \citealt{Bowman:2010p8546}),
-and interferometers aiming to measure the power spectrum of 21-cm EoR emission, such as
-the Giant Metre-wave Radio Telescope (GMRT;
+Numerous radio telescopes are now exploring the prospects for using
+measurements of highly redshifted 21cm emission to inform our understanding of
+cosmic reionization in the redshift range $6< z<12$, corresponding to radio
+frequencies below 200MHz (see reviews in
+\citet{Furlanetto:2006p2267,Morales:2010p8093,Pritchard:2012p9555}) .  These
+include telescopes aiming to measure the global temperature change of 21cm
+emission during the Epoch of Reionization (EoR), such as the Compact
+Reionization Experiment (CoRE) and the Experiment to Detect the Global EoR
+Signature (EDGES; \citealt{Bowman:2010p8546}), and interferometers aiming to
+measure the power spectrum of 21-cm EoR emission, such as the Giant Metre-wave
+Radio Telescope (GMRT;
 \citealt{Paciga:2011p9470,Paciga:2013p9627})\footnote{\url{http://gmrt.ncra.tifr.res.in/}},
-the LOw Frequency ARray (LOFAR; \citealt{Yatawatta:2013p9699})\footnote{\url{http://www.lofar.org/}},
-the Murchison Widefield Array (MWA;  \citealt{Bowman:2012p9138}; \citealt{Tingay:2013p9022}))\footnote{\url{http://www.mwatelescope.org/}}, 
-and 
-the Donald C. Backer Precision Array for Probing the Epoch of Reionization (PAPER;
-\citealt{Parsons:2010p6757})\footnote{\url{http://eor.berkeley.edu/}}.
-Both PAPER and the MWA are located in the southern hemisphere at radio quiet reserves being prepared for the upcoming Square Kilometer Array.
-At these low frequencies the Southern sky is much less well known than the North, with the most extensive surveying work being conducted  by the EoR experiments themselves \citep{Jacobs:2011p8438,Williams:2012p8768}.
+the LOw Frequency ARray (LOFAR;
+\citealt{Yatawatta:2013p9699})\footnote{\url{http://www.lofar.org/}}, the
+Murchison Widefield Array (MWA;  \citealt{Bowman:2012p9138};
+\citealt{Tingay:2013p9022}))\footnote{\url{http://www.mwatelescope.org/}}, and
+the Donald C. Backer Precision Array for Probing the Epoch of Reionization
+(PAPER; \citealt{Parsons:2010p6757})\footnote{\url{http://eor.berkeley.edu/}}.
+Both PAPER and the MWA are located in the southern hemisphere at radio quiet
+reserves being prepared for the upcoming Square Kilometer Array.  At these low
+frequencies the Southern sky is much less well known than the North, with the
+most extensive surveying work being conducted  by the EoR experiments
+themselves \citep{Jacobs:2011p8438,Williams:2012p8768}.
 
-Neutral hydrogen is visible during reionization as $\sim$30mK excess surface brightness over the CMB punctuated both spectrally and spatially by regions of zero emission.
-This patchy signal is predicted to be visible everywhere on the sky at size scales up to degrees, or about $0.1$cMpc$^{-1}$.
-To increase the surface brightness sensitivity without building costly dishes, MWA, PAPER and LOFAR have chosen to use combinations of phased and/or correlated dipoles.
-By design also cover much wider fields of view ($>10$\arcdeg) and bandwidths ($\sim 100$\% fractional) than traditional dish telescopes.
-As the elements can not be physically pointed, the apparent flux scale varies across the sky.
-This direction dependent gain is currently uncertain to 20\% or higher \citep{Jacobs:2013p9713}.
-The ideal solution is to use a wide-grid of well-known calibrators to map the primary beam and set the flux scale.
+Neutral hydrogen is visible during reionization as $\sim$30mK excess surface
+brightness over the CMB punctuated both spectrally and spatially by regions of
+zero emission.  This patchy signal is predicted to be visible everywhere on the
+sky at size scales up to degrees, or about $0.1$cMpc$^{-1}$.   To increase the
+surface brightness sensitivity without building costly dishes, MWA, PAPER and
+LOFAR have chosen to use combinations of phased and/or correlated dipoles. By
+design also cover much wider fields of view ($>10$\arcdeg) and bandwidths
+($\sim 100$\% fractional) than traditional dish telescopes.   As the elements
+can not be physically pointed, the apparent flux scale varies across the sky.
+This direction dependent gain is currently uncertain to 20\% or higher
+\citep{Jacobs:2013p9713}.  The ideal solution is to use a wide-grid of
+well-known calibrators to map the primary beam and set the flux scale.
+
 %The position dependent gain varies for each instrument.
@@
 
-However, catalog source fluxes at 150MHz are also inaccurate to the 20\% level, particularly at southern declinations ($<-20$\arcdeg) .
-Historically, the best EoR band data were by \citet{Slee:1995p7541} with Culgoora Circular Array\footnote{Known during daylight hours as Culgoora Radio Heliograph} and various higher frequency measurements with Parkes.
-These data are typically uncertain to 10\% or higher and provide little coverage of the EoR band beyond a single narrow-band data point.
+However, catalog source fluxes at 150MHz are also inaccurate to the 20\% level,
+particularly at southern declinations ($<-20$\arcdeg) . Historically, the best
+EoR band data were by \citet{Slee:1995p7541} with Culgoora Circular
+Array\footnote{Known during daylight hours as Culgoora Radio Heliograph} and
+various higher frequency measurements with Parkes.  These data are typically
+uncertain to 10\% or higher and provide little coverage of the EoR band beyond
+a single narrow-band data point.
 
-PAPER, in its maximum redundancy configuration, has a very broad beam with large regular grating side-lobes and is therefor limited to using the few sources above $\sim$50 Jy for flux calibration.
-The best calibrator for most observations is Pictor A.
-For this source the current best EoR band measurement is uncertain to 12\% and appears to imply spectral flattening in the EoR band \citep{Perley:1997p9312}.
+PAPER, in its maximum redundancy configuration, has a very broad beam with
+large regular grating side-lobes and is therefor limited to using the few
+sources above $\sim$50 Jy for flux calibration. The best calibrator for most
+observations is Pictor A. For this source the current best EoR band measurement
+is uncertain to 12\% and appears to imply spectral flattening in the EoR band
+\citep{Perley:1997p9312}.
 
-More recent surveys include narrow-band surveys by the GMRT and Mauritius, a deep survey of the region near Hydra A by the 32 antenna MWA prototype \cite{Williams:2012p8768} and a wide field survey by PAPER, also with 32 elements \cite{Jacobs:2011p8438}.
-Several sub-channels were provided in the Williams catalog, though with 60-80\% error bars ---large compared to the 30\% uncertainty on their wide band measurements.
-The latter cover the band and spatial scales relevant to EoR measurements but are limited by the accuracy of the primary beam \citep{Jacobs:2013p9713}.
+More recent surveys include narrow-band surveys by the GMRT and Mauritius, a
+deep survey of the region near Hydra A by the 32 antenna MWA prototype
+\cite{Williams:2012p8768} and a wide field survey by PAPER, also with 32
+elements \cite{Jacobs:2011p8438}. Several sub-channels were provided in the
+Williams catalog, though with 60-80\% error bars ---large compared to the 30\%
+uncertainty on their wide band measurements.  The latter cover the band and
+spatial scales relevant to EoR measurements but are limited by the accuracy of
+the primary beam \citep{Jacobs:2013p9713}.
 
-A method for decoupling uncertain fluxes from the uncertain beam has been described by \citet{Pober:2012p8800}.
-In simulation the method was able to achieve 3 to 10\% accuracy in measuring the primary beam, depending on the number of antennae and other variables.
-The Pober method emphasized the need for many repeated measurements of each alt-az pointing.
-Further investigation is under way to improve and implement this method and would be greatly aided by the availability of precise flux measurements unaffected by primary beam uncertainty.
-This paper reports a set of flux measurements where a primary beam model has not been used to estimate the flux, but instead are directly calibrated to a single calibrator making the track through the beam.
+A method for decoupling uncertain fluxes from the uncertain beam has been
+described by \citet{Pober:2012p8800}. In simulation the method was able to
+achieve 3 to 10\% accuracy in measuring the primary beam, depending on the
+number of antennae and other variables. The Pober method emphasized the need
+for many repeated measurements of each alt-az pointing. Further investigation
+is under way to improve and implement this method and would be greatly aided by
+the availability of precise flux measurements unaffected by primary beam
+uncertainty. This paper reports a set of flux measurements where a primary beam
+model has not been used to estimate the flux, but instead are directly
+calibrated to a single calibrator making the track through the beam.
 
@@
 
-In this paper our primary goal is to provide a subset of accurate fluxes suitable for EoR power spectrum and catalog calibration.
-After recording the data used in this paper, PAPER was reconfigured into a redundant layout optimized to detect a small number of power spectrum bins at high precision, an arrangement which trades imaging dynamic range for power spectrum sensitivity.
-As such it is only able to easily distinguish the very brightest sources on the sky a step necessary for setting the overall flux scale.
-Of these, Pictor A is one of the most useful, being bright, minimally resolved and far from from confusing structure.
+In this paper our primary goal is to provide a subset of accurate fluxes
+suitable for EoR power spectrum and catalog calibration.  After recording the
+data used in this paper, PAPER was reconfigured into a redundant layout
+optimized to detect a small number of power spectrum bins at high precision, an
+arrangement which trades imaging dynamic range for power spectrum sensitivity.
+As such it is only able to easily distinguish the very brightest sources on the
+sky a step necessary for setting the overall flux scale. Of these, Pictor A is
+one of the most useful, being bright, minimally resolved and far from from
+confusing structure.
 
-The data  include new measurements of Pictor A that are uncertain to 3.5\%, close to the level of the most precise higher frequency measurements by \citet{Wills:1975p9314}.
-Using these new measurements we update the spectral calibration model to an accuracy of 2.5\%.
-As validation of this method, we also measure a selection of 58 additional sources at the same Declination.
-The primary beam is calibrated using a single common source (J2331-416), thus limiting the declination probed to $-45 \pm 5$\arcdeg.
-The flux scale is set by Monte Carlo fitting to a subset of sources, all of which are calibrated to the Baars et al scale.
-In \S\ref{sec:Observations} we describe the instrumental setup, observations and analysis method followed.
-In \S\ref{sec:fits} we compare the spectra with available data followed by conclusions in \S\ref{sec:Conclusion}.
+The data  include new measurements of Pictor A that are uncertain to 3.5\%,
+close to the level of the most precise higher frequency measurements by
+\citet{Wills:1975p9314}. Using these new measurements we update the spectral
+calibration model to an accuracy of 2.5\%. As validation of this method, we
+also measure a selection of 58 additional sources at the same Declination.  The
+primary beam is calibrated using a single common source (J2331-416), thus
+limiting the declination probed to $-45 \pm 5$\arcdeg.  The flux scale is set
+by Monte Carlo fitting to a subset of sources, all of which are calibrated to
+the Baars et al scale. In \S\ref{sec:Observations} we describe the instrumental
+setup, observations and analysis method followed. In \S\ref{sec:fits} we
+compare the spectra with available data followed by conclusions in
+\S\ref{sec:Conclusion}.
 
@@
  \label{sec:Observations}
- Measurements are derived from observations using  the east-west dipole arms of 64 PAPER antennas 
-deployed in the Karoo Radio Observatory site in South Africa (see Figure \ref{fig:antpos}).  
-A 100-MHz band from 100-200MHz was
-correlated with 2048 frequency channels and integrated for 10.7 seconds before visibilities were stored.
-Observations included here on  July 4, 2011, running
-from JD2455748.17 to JD2455748.72. and October 17, 2011 running from JD2455852.2 to JD2455852.6.
-In both seasons two antennas were omitted owing to malfunctioning signal path.
-This 20 hour long combined dataset provides observations provides complete hour angle coverage for the entire 24 hours of Right Ascension.
-The July portion of the dataset comes from the same observing campaign described by \cite{Pober:2013p9567} and \cite{Stefan:2012p9707}.
+
+ Measurements are derived from observations using  the east-west dipole arms of
+64 PAPER antennas deployed in the Karoo Radio Observatory site in South Africa
+(see Figure \ref{fig:antpos}).  A 100-MHz band from 100-200MHz was correlated
+with 2048 frequency channels and integrated for 10.7 seconds before
+visibilities were stored.  Observations included here on  July 4, 2011, running
+from JD2455748.17 to JD2455748.72. and October 17, 2011 running from
+JD2455852.2 to JD2455852.6.  In both seasons two antennas were omitted owing to
+malfunctioning signal path. This 20 hour long combined dataset provides
+observations provides complete hour angle coverage for the entire 24 hours of
+Right Ascension. The July portion of the dataset comes from the same observing
+campaign described by \cite{Pober:2013p9567} and \cite{Stefan:2012p9707}. 
 %July (\#40,\#55), September (\#7,\#28)
@@
 \textbf{Compression}\\
-In pre-processing, we use delay/delay-rate (DDR) filters \citep{Parsons:2009p7859} to identify
-radio-frequency interference (RFI) events, and as part of a data compression
-technique that reduces data volume by over a factor of 40.
-A more detailed description may be found in Appendix A of \cite{Parsons2013b}, which uses the same compression method on PAPER power spectrum observations.
-Here we summarize the process.
+
+In pre-processing, we use delay/delay-rate (DDR) filters
+\citep{Parsons:2009p7859} to identify radio-frequency interference (RFI)
+events, and as part of a data compression technique that reduces data volume by
+over a factor of 40.  A more detailed description may be found in Appendix A of
+\cite{Parsons2013b}, which uses the same compression method on PAPER power
+spectrum observations. Here we summarize the process.
 
 First, we remove known RFI transmission bands and analog filter edges, and then
- flag outliers at 6$\sigma$ to remove RFI events.
-Next, we suppress foreground emission by applying a DDR filter to remove delays and delay-rates 
-within the horizon limit of a 300-m baseline (the maximum length of any PAPER baseline).
-We derive a second set of RFI flags by masking 4$\sigma$ outliers in these residuals and apply these flags back
-to the unfiltered data.  Finally, we compress the data by applying a 
-DDR filter preserving emission within the horizon limit of a 300-m baseline, deconvolving to suppress 
-flagging artifacts, and down-sampling the result in time/frequency domain to the critical Nyquist rate of
-the DDR filter.
-The result is that the 2048 original frequency channels become 203, and the
-60 original time samples per 10-minute file become 14.
+flag outliers at 6$\sigma$ to remove RFI events.  Next, we suppress foreground
+emission by applying a DDR filter to remove delays and delay-rates within the
+horizon limit of a 300-m baseline (the maximum length of any PAPER baseline).
+We derive a second set of RFI flags by masking 4$\sigma$ outliers in these
+residuals and apply these flags back to the unfiltered data.  Finally, we
+compress the data by applying a DDR filter preserving emission within the
+horizon limit of a 300-m baseline, deconvolving to suppress flagging artifacts,
+and down-sampling the result in time/frequency domain to the critical Nyquist
+rate of the DDR filter.  The result is that the 2048 original frequency
+channels become 203, and the 60 original time samples per 10-minute file become
+14.
 
@@
 \textbf{Antenna calibration}\\
-Antennae delays and amplitudes were found by fitting a point source visibility model to Centaurus A, Pictor A, and Fornax A.
-Each source is imperfectly modeled by a single point-source, but the solution differences are minimized by averaging over the three independent solutions.
-These same calibration solutions have also been successfully applied in the power spectrum analysis by Pober (2013) and Centaurus A imaging by Stefan (2013).
+
+Antennae delays and amplitudes were found by fitting a point source visibility
+model to Centaurus A, Pictor A, and Fornax A.  Each source is imperfectly
+modeled by a single point-source, but the solution differences are minimized by
+averaging over the three independent solutions. These same calibration
+solutions have also been successfully applied in the power spectrum analysis by
+Pober (2013) and Centaurus A imaging by Stefan (2013).
 
@@
 
-To provide a basis for establishing the accuracy of the Pictor measurement we measured more sources.
-Specifically, we choose sources from the Molonglo Reference Catalog \cite[MRC]{Large:1981p7798} that are within 5\arcdeg in declination of a common calibrator (J2331-416) and have a flux extrapolated from 408MHz greater than 10Jy assuming a power law spectral index of -1.\footnote{Most radio
-  sources in this band have power law spectra $S(\nu) =
-  \left(\frac{\nu}{\nu_0}\right)^\alpha$.
-The 5\arcdeg distance between source and calibrator was chosen as a balance between number of sources included and the known smoothness of the beam.
-The average spectral index
-  for radio sources in this band is $-0.8$.} This selection contains 62 sources in a narrow stripe that passes through the majority of the southern EoR fields, much of the galaxy and Centaurus A.
+To provide a basis for establishing the accuracy of the Pictor measurement we
+measured more sources.  Specifically, we choose sources from the Molonglo
+Reference Catalog \cite[MRC]{Large:1981p7798} that are within 5\arcdeg in
+declination of a common calibrator (J2331-416) and have a flux extrapolated
+from 408MHz greater than 10Jy assuming a power law spectral index of
+-1.\footnote{Most radio sources in this band have power law spectra $S(\nu) =
+\left(\frac{\nu}{\nu_0}\right)^\alpha$.  The 5\arcdeg distance between source
+and calibrator was chosen as a balance between number of sources included and
+the known smoothness of the beam.   The average spectral index for radio
+sources in this band is $-0.8$.} This selection contains 62 sources in a narrow
+stripe that passes through the majority of the southern EoR fields, much of the
+galaxy and Centaurus A.
 
 \textbf{Beamforming}\\
-Spectral time-series are computed by beam-forming to the selected sky locations.
-A beam is formed by phasing baselines to the desired location and summing over baselines.
+
+Spectral time-series are computed by beam-forming to the selected sky
+locations. A beam is formed by phasing baselines to the desired location and
+summing over baselines.  
 %Samples were only included if there was a calibrator sample within 5\arcdeg in altitude/azimuth.
 By using both seasons of data we were able to match all measurements with calibrator measurements, making this cut moot.
- These complex spectra are then delay-delay rate filtered to remove spectrally smooth sources far from phase center \citep{Parsons:2009p7859} (cf the LOFAR de-mixing approach \cite{Offringa:2012p9691})  producing a time dependent spectrum.
-This is then averaged in time,  weighting by a model of the primary beam.
-This down-weighting, or multiplying by the primary beam, should be clearly distinguished from up-weighting, which we are at pains to avoid.
-Weighting by another factor of the primary beam is an effective approximation of inverse-variance weighting \citep{Pober:2012p8800} and reduces the contribution of noisy low elevation measurements.
-The result is equivalent to a very long earth rotation synthesis image with a single image pixel.
-When combined with the filtering it is a robust and simple method for measuring spectra of unresolved sources.
+
+ These complex spectra are then delay-delay rate filtered to remove spectrally
+smooth sources far from phase center \citep{Parsons:2009p7859} (cf the LOFAR
+de-mixing approach \cite{Offringa:2012p9691})  producing a time dependent
+spectrum. This is then averaged in time,  weighting by a model of the primary
+beam. This down-weighting, or multiplying by the primary beam, should be
+clearly distinguished from up-weighting, which we are at pains to avoid.
+Weighting by another factor of the primary beam is an effective approximation
+of inverse-variance weighting \citep{Pober:2012p8800} and reduces the
+contribution of noisy low elevation measurements.  The result is equivalent to
+a very long earth rotation synthesis image with a single image pixel. When
+combined with the filtering it is a robust and simple method for measuring
+spectra of unresolved sources.
+
 \begin{figure}
@@
 
-The beam-forming method assumes the target is a point source.
-Our primary target, Pictor A, is slightly resolved by PAPER, and merits closer attention.
-Pictor A is a double-lobed radio galaxy with a main lobe separation of 7\arcmin.
-As we see in Figure \ref{fig:pic_perley}, it is nearly unresolved by PAPER's 15\arcmin synthesized beam.
-However, given the high SNR of the observations, resolution effects are observers, in a slight decrease in flux on the longest ($\sim$300m) baselines.
-We account for this by weighting baselines in the beam form step according to a model of structure observed by \citet{Perley:1997p9312} at 330MHz, which they found to be consistent with their more limited 74MHz images as well as the detailed high frequency maps.
-The normalized image is Fourier transformed and sampled at the desired uv spacing by spline interpolation.
-These samples are used to weight each baseline contribution in the baseline sum.
-The result is an estimate of the total integrated flux for Pictor A.
-Where the resolution is highest, at the top of the band, the correction is 3\%.
-At the bottom of the band, where the resolution size has grown to 19\arcmin, the correction is only 0.6\%.
-The resulting spectrum is shown in Figure \ref{fig:pic_spectrum}a.
+The beam-forming method assumes the target is a point source. Our primary
+target, Pictor A, is slightly resolved by PAPER, and merits closer attention.
+Pictor A is a double-lobed radio galaxy with a main lobe separation of
+7\arcmin. As we see in Figure \ref{fig:pic_perley}, it is nearly unresolved by
+PAPER's 15\arcmin synthesized beam. However, given the high SNR of the
+observations, resolution effects are observers, in a slight decrease in flux on
+the longest ($\sim$300m) baselines. We account for this by weighting baselines
+in the beam form step according to a model of structure observed by
+\citet{Perley:1997p9312} at 330MHz, which they found to be consistent with
+their more limited 74MHz images as well as the detailed high frequency maps.
+The normalized image is Fourier transformed and sampled at the desired uv
+spacing by spline interpolation. These samples are used to weight each baseline
+contribution in the baseline sum. The result is an estimate of the total
+integrated flux for Pictor A. Where the resolution is highest, at the top of
+the band, the correction is 3\%. At the bottom of the band, where the
+resolution size has grown to 19\arcmin, the correction is only 0.6\%. The
+resulting spectrum is shown in Figure \ref{fig:pic_spectrum}a.
+
 \begin{figure}
 \includegraphics[width=0.96\textwidth]{plots/picA_Perley.png}
-\caption{Pictor A imaged at 330MHz by the VLA \citep{Perley:1997p9312}.
-Black circle indicates PAPER resolution at the 150MHz, dashed, the resolution at 185MHz.
-To correct for the small residual structure in the PAPER measurements we interpolated the PAPER baselines in the uv plane.
-At the highest frequency this led to a 3\% correction, at the lowest frequency, 0.6\%.
+\caption{
+Pictor A imaged at 330MHz by the VLA \citep{Perley:1997p9312}. Black circle
+indicates PAPER resolution at the 150MHz, dashed, the resolution at 185MHz.  To
+correct for the small residual structure in the PAPER measurements we
+interpolated the PAPER baselines in the uv plane. At the highest frequency this
+led to a 3\% correction, at the lowest frequency, 0.6\%.
 \label{fig:pic_perley}}
@@
 \label{sec:Calibration}
-The gain of each channel is the product of an overall instrumental passband and the spectral dependence of the primary beam in the direction of the source.
-Sources sharing the same track through the primary beam will have the same average spectral gain function resulting from frequency dependent primary beam attenuation.
-We matched each measured source spectrum time sample to the nearest sample (in altitude/azimuth) of a calibrator source (J2331-416)\footnote{This source was chosen for the amount of data found in the literature and the apparent smoothness of the spectrum.}.
-We then, average the two matched data streams in time.
-Since both tracks make the same slice through the primary beam, they will have the same average effective gain.
-Assuming a power law model for J2331-416 (33Jy $\alpha=-0.76$), we compute a bandpass gain.
-After calibrating the raw 203 channel spectra with this bandpass, we average into 10MHz sub-bands between 120 and 180 MHz, computing the standard deviation as an estimate of the error.
+
+The gain of each channel is the product of an overall instrumental passband and
+the spectral dependence of the primary beam in the direction of the source.
+Sources sharing the same track through the primary beam will have the same
+average spectral gain function resulting from frequency dependent primary beam
+attenuation.   We matched each measured source spectrum time sample to the
+nearest sample (in altitude/azimuth) of a calibrator source
+(J2331-416)\footnote{This source was chosen for the amount of data found in the
+literature and the apparent smoothness of the spectrum.}.  We then, average the
+two matched data streams in time.  Since both tracks make the same slice
+through the primary beam, they will have the same average effective gain.
+Assuming a power law model for J2331-416 (33Jy $\alpha=-0.76$), we compute a
+bandpass gain.  After calibrating the raw 203 channel spectra with this
+bandpass, we average into 10MHz sub-bands between 120 and 180 MHz, computing
+the standard deviation as an estimate of the error.
 
 \textbf{Catalogs}\\
-Data for prior comparison was pulled from two major sources.
-Catalog values for Pictor A, and the flux calibration sources were pulled directly from the NASA/IPAC Extragalactic Database (NED) \footnote{\url{http://ned.ipac.caltech.edu/}}.
-Cross-matching radio sources between bands is made difficult by changes in resolution, spectral curvature, and resolved multi-scale structure.
-For a small number of sources these problems can be ameliorated by inspection of the spectra, source names, coordinates,  and originating publications.
-However for a large sample of sources this becomes unwieldily and prone to error.
-Thus for the larger number of samples we make use of the Vollmer et al meta-catalog which takes pains to match multi-wavelength observations \citep{Vollmer:2010p6422}.% given the known source dimensions and spectral properties as well as telescope bandwidth and spatial resolutions.
+
+Data for prior comparison was pulled from two major sources. Catalog values for
+Pictor A, and the flux calibration sources were pulled directly from the
+NASA/IPAC Extragalactic Database (NED)
+\footnote{\url{http://ned.ipac.caltech.edu/}}. Cross-matching radio sources
+between bands is made difficult by changes in resolution, spectral curvature,
+and resolved multi-scale structure.  For a small number of sources these
+problems can be ameliorated by inspection of the spectra, source names,
+coordinates,  and originating publications. However for a large sample of
+sources this becomes unwieldily and prone to error. Thus for the larger number
+of samples we make use of the Vollmer et al meta-catalog which takes pains to
+match multi-wavelength observations \citep{Vollmer:2010p6422}.
+% given the known source dimensions and spectral properties as well as telescope bandwidth and spatial resolutions.
 
@@
 \label{sec:flux_scale}
-At this stage each source flux is tied to a model fit on the catalog values of J2331-416.
-The accuracy of this fit and the implied uncertainty in the flux scale limits the accuracy of the PAPER measurements..
-To refine the flux scale, we bootstrap a single global flux scale correction factor using 5 sources selected for their brightness, spectral linearity and data availability\footnote{Calibration sources: 2250-412,2331-416,2140-434,0007-446,0704-427}.
-To build a more complete spectral model we go beyond the data found in SPECFIND, using all spectral measurements below 2GHz found in the NED database.
-These catalog measurements are primarily by Parkes, and Molonglo with the best precision coming from the Wills fluxes at 538 and 634 MHz (when available).
-Where error bars are not given, we assume uncertainty of 25\%.
 
-As described in the Appendix, we fit spectral index models for all sources (using catalog data) simultaneously with a global PAPER flux scale factor (using the PAPER data).
-We fit the model using a Markov Chain Monte Carlo sampler to sample the posterior probability of PAPER data ($SPAPER_{\nu}$) and catalog values ($Scat_{\nu}$) given a spectral index model for each source and a global flux scale factor ($g$) ($S_\PAPER^\textrm{calibrated} = g S_\PAPER$).
-The resulting flux scale distribution function is shown in Figure \ref{fig:gain}.
-The 76\% confidence limit on this flux scale, relative to the J2331-413 calibration, is  $-0.01 ^{+0.11}_{-0.17}$ dB, or a 3.24\% multiplicative error on every calibrated PAPER measurement.
+At this stage each source flux is tied to a model fit on the catalog values of
+J2331-416. The accuracy of this fit and the implied uncertainty in the flux
+scale limits the accuracy of the PAPER measurements..  To refine the flux
+scale, we bootstrap a single global flux scale correction factor using 5
+sources selected for their brightness, spectral linearity and data
+availability\footnote{Calibration sources:
+2250-412,2331-416,2140-434,0007-446,0704-427}. To build a more complete
+spectral model we go beyond the data found in SPECFIND, using all spectral
+measurements below 2GHz found in the NED database.  These catalog measurements
+are primarily by Parkes, and Molonglo with the best precision coming from the
+Wills fluxes at 538 and 634 MHz (when available). Where error bars are not
+given, we assume uncertainty of 25\%.
 
-The calibrated spectra are plotted in Figures \ref{fig:srcs1},\ref{fig:srcs2}, \& \ref{fig:srcs3} and the data are listed in Table \ref{tab:data}.
-See the Appendix for details on this fitting procedure and definition of terms.
-The resulting Pictor A spectrum ranges in precision from 6.5\% at 125MHz to 4.7\% at 185MHz.
-At least half of this error is due to uncertainty in the flux scale.
+As described in the Appendix, we fit spectral index models for all sources
+(using catalog data) simultaneously with a global PAPER flux scale factor
+(using the PAPER data). We fit the model using a Markov Chain Monte Carlo
+sampler to sample the posterior probability of PAPER data ($SPAPER_{\nu}$) and
+catalog values ($Scat_{\nu}$) given a spectral index model for each source and
+a global flux scale factor ($g$) ($S_\PAPER^\textrm{calibrated} = g S_\PAPER$).
+The resulting flux scale distribution function is shown in Figure
+\ref{fig:gain}. The 76\% confidence limit on this flux scale, relative to the
+J2331-413 calibration, is  $-0.01 ^{+0.11}_{-0.17}$ dB, or a 3.24\%
+multiplicative error on every calibrated PAPER measurement.
+
+The calibrated spectra are plotted in Figures \ref{fig:srcs1},\ref{fig:srcs2},
+\& \ref{fig:srcs3} and the data are listed in Table \ref{tab:data}.  See the
+Appendix for details on this fitting procedure and definition of terms.  The
+resulting Pictor A spectrum ranges in precision from 6.5\% at 125MHz to 4.7\%
+at 185MHz. At least half of this error is due to uncertainty in the flux scale.  
 %\footnote{Of the 315 data points in this catalog, 7 fluxes points are negative.
@@
  \label{sec:fits}
-The primary purpose of this observation is to produce a high quality Pictor A spectrum.
-As a verification measure we have observed many other sources at the same declination for comparison against previous observations.
-Our comparison metric will be the degree to which the PAPER data are consistent with previous observations,given a model and, if consistent, they improve on the precision of our spectral model parameters.
 
-To compare with observations at other frequencies we must assume a spectral model.
-The prevailing spectral model for low frequency radio sources is a single power law due to synchrotron emission, though curvature or other deviation from a power-law is not-uncommon.
-To establish a baseline model, we fit a spectral model to prior catalog data from the spectrally and spatially cross-matched meta-catalog by \citet{Vollmer:2010p6422} using the MCMC method described in \S \ref{sec:flux_scale} and the Appendix.
-Confidence contours for these fits are shown in grey in Figs.
-\ref{fig:SI_contour_1} - \ref{fig:SI_contour_4}.
-In general these are lower limits on the possible precision, as the Vollmer catalog emphasizes minimization of cross-match error but at the cost of excluding data points.
-The fit is then performed again with both PAPER and catalog data, shown in black on the same Figures.
-The values are given in Table \ref{tab:fits}.
+The primary purpose of this observation is to produce a high quality Pictor A
+spectrum. As a verification measure we have observed many other sources at the
+same declination for comparison against previous observations.  Our comparison
+metric will be the degree to which the PAPER data are consistent with previous
+observations,given a model and, if consistent, they improve on the precision of
+our spectral model parameters.
+
+To compare with observations at other frequencies we must assume a spectral
+model. The prevailing spectral model for low frequency radio sources is a
+single power law due to synchrotron emission, though curvature or other
+deviation from a power-law is not-uncommon.   To establish a baseline model, we
+fit a spectral model to prior catalog data from the spectrally and spatially
+cross-matched meta-catalog by \citet{Vollmer:2010p6422} using the MCMC method
+described in \S \ref{sec:flux_scale} and the Appendix. Confidence contours for
+these fits are shown in grey in Figs. \ref{fig:SI_contour_1} -
+\ref{fig:SI_contour_4}.  In general these are lower limits on the possible
+precision, as the Vollmer catalog emphasizes minimization of cross-match error
+but at the cost of excluding data points.  The fit is then performed again with
+both PAPER and catalog data, shown in black on the same Figures. The values are
+given in Table \ref{tab:fits}.
 
@@
 %TODO round up the source counts
-In the 59 sources measured, four demonstrated poor convergence fitting a single spectral index to both the PAPER data and prior catalog data.
-In three cases\footnote{1243-412,1247-401,1315-460} %TODO update
-these sources are in the Centaurus A/galactic plane region.
-Though the beam forming method provides relatively high dynamic range of $\sim$100:1 it is unable to distinguish between these sources and the bright diffuse Centaurus and galactic structure.
-The last source, 0008-421, was not detected by previous PAPER observations and exhibits flattening at higher frequencies, most likely due to synchrotron self-absorption \citep{Jacobs:2011p8438} .
-The remaining 94\% MCMC chains arrived at a stable posterior distribution.
-The spectral index parameters for these chains are given in table \ref{tab:fits}.
 
-Inspecting the confidence contours we find that, for the vast majority ($\sim 75$\%), the PAPER measurements confirm the power law extrapolation from higher frequencies.
-The remaining 25\% either A) have large PAPER error bars and therefor provide no new information or B) do not agree with the spectral index model.
-To understand where most measurements fall on this spectrum we numerically quantify the overall model improvement derived from the addition of the PAPER data as
+In the 59 sources measured, four demonstrated poor convergence fitting a single
+spectral index to both the PAPER data and prior catalog data. In three
+cases\footnote{1243-412,1247-401,1315-460} %TODO update these sources are in
+the Centaurus A/galactic plane region. Though the beam forming method provides
+relatively high dynamic range of $\sim$100:1 it is unable to distinguish
+between these sources and the bright diffuse Centaurus and galactic structure.
+The last source, 0008-421, was not detected by previous PAPER observations and
+exhibits flattening at higher frequencies, most likely due to synchrotron
+self-absorption \citep{Jacobs:2011p8438} .  The remaining 94\% MCMC chains
+arrived at a stable posterior distribution. The spectral index parameters for
+these chains are given in table \ref{tab:fits}.
+
+Inspecting the confidence contours we find that, for the vast majority ($\sim
+75$\%), the PAPER measurements confirm the power law extrapolation from higher
+frequencies. The remaining 25\% either A) have large PAPER error bars and
+therefor provide no new information or B) do not agree with the spectral index
+model.  To understand where most measurements fall on this spectrum we
+numerically quantify the overall model improvement derived from the addition of
+the PAPER data as 
 \begin{align}
@@
 
-We quantify the fit {\em precision increase} as the change in the contour figure of merit, defined as the inverse area of the confidence contour.
-Meanwhile, {\em catalog agreement} is the fraction of the PAPER confidence interval that overlaps the catalog confidence interval.
-Thus, for example, in a PAPER fit that overlaps the catalog confidence contour by 41\% but increases in precision (confidence area shrinks) by a factor of 3, the resulting {\em improvement} will be 0.123.
+We quantify the fit {\em precision increase} as the change in the contour
+figure of merit, defined as the inverse area of the confidence contour.
+Meanwhile, {\em catalog agreement} is the fraction of the PAPER confidence
+interval that overlaps the catalog confidence interval.  Thus, for example, in
+a PAPER fit that overlaps the catalog confidence contour by 41\% but increases
+in precision (confidence area shrinks) by a factor of 3, the resulting {\em
+improvement} will be 0.123.
 
 In these sources, the improvement index ranges from a max of 6.9 to -0.022.
-10\% of sources showed negative improvement, suggesting that PAPER data have added to uncertainty (see Figure \ref{fig:SI_contour_bad}).
-12\% of sources have exactly zero improvement, which indicates that the PAPER data have pulled the fit far from the model preferred by the catalog data (see Fig.
-\ref{fig:SI_contour_new}).
-The spectral models of these sources have not been included in Table \ref{tab:fits}.
-The remainder of the spectral fits are included for completeness, but given the range of quality found, particularly near the Galactic plane and Centaurus A, should be used with utmost caution.
+10\% of sources showed negative improvement, suggesting that PAPER data have
+added to uncertainty (see Figure \ref{fig:SI_contour_bad}). 12\% of sources
+have exactly zero improvement, which indicates that the PAPER data have pulled
+the fit far from the model preferred by the catalog data (see Fig.
+\ref{fig:SI_contour_new}).  The spectral models of these sources have not been
+included in Table \ref{tab:fits}.  The remainder of the spectral fits are
+included for completeness, but given the range of quality found, particularly
+near the Galactic plane and Centaurus A, should be used with utmost caution.
 
-However, the majority of source 78\% have positive improvement index, indicating strong confirmation of the extrapolated spectrum (see Figures  \ref{fig:SI_contour_1} - \ref{fig:SI_contour_4}).
-Pictor A is in the middle of this group  with an improvement of 0.39 ---only 14 sources show stronger confirmation.
-The flux model is $S150=$388 $\pm$ 9.4Jy, $\alpha=-0.77\pm0.02$.
-The combination of several independent PAPER data points near 150MHz with previous catalog measurements results in this estimated uncertainty of 2.4\%.
-This uncertainty is dominated by agreement between the 2 Wills measurements near 600MHz which are accurate to 2\% and the five PAPER measurements, which are accurate to ~5\%.
+However, the majority of source 78\% have positive improvement index,
+indicating strong confirmation of the extrapolated spectrum (see Figures
+\ref{fig:SI_contour_1} - \ref{fig:SI_contour_4}).  Pictor A is in the middle of
+this group  with an improvement of 0.39 ---only 14 sources show stronger
+confirmation.  The flux model is $S150=$388 $\pm$ 9.4Jy, $\alpha=-0.77\pm0.02$.
+The combination of several independent PAPER data points near 150MHz with
+previous catalog measurements results in this estimated uncertainty of 2.4\%.
+This uncertainty is dominated by agreement between the 2 Wills measurements
+near 600MHz which are accurate to 2\% and the five PAPER measurements, which
+are accurate to ~5\%.
 
@@
 
-Direct measurements of the Pictor A spectrum are key to correctly setting the flux scale of PAPER and other EoR experiments.
-Existing EoR band measurements are accurate to 20\% implying a 40\% uncertainty in the absolute power spectrum level.
-Here we have provided new measurements of Pictor A that are accurate to 2.4\%;  388 $\pm$ 9.4Jy on the \citet{Baars:1977p9678} scale.
-The PAPER measurement has a precision of $<$1\%; the majority of the uncertainty comes in setting the absolute flux scale from prior data.
+Direct measurements of the Pictor A spectrum are key to correctly setting the
+flux scale of PAPER and other EoR experiments. Existing EoR band measurements
+are accurate to 20\% implying a 40\% uncertainty in the absolute power spectrum
+level.  Here we have provided new measurements of Pictor A that are accurate to
+2.4\%;  388 $\pm$ 9.4Jy on the \citet{Baars:1977p9678} scale. The PAPER
+measurement has a precision of $<$1\%; the majority of the uncertainty comes in
+setting the absolute flux scale from prior data.
 
-We also take advantage of multiple PAPER observations to measure the next  61 brightest, previously cataloged, sources.
-These sources are distributed over the full 24 hours of Right Ascension coverage but are within 5 degrees declination of Pictor A.
-Using a Bayesian analysis we conclude that most of these are consistent with previous measurements and provide useful new constraints.
-However, in the remainder, the simple spectral model fails to adequately describe the data.
-In most cases the proximity to bright or extended structures implies side lobe contamination.
-Therefore, though we include the model parameters, they are not meant to be definitive, but provide confidence that the reported PAPER flux values are on the correct global scale.
+We also take advantage of multiple PAPER observations to measure the next  61
+brightest, previously cataloged, sources. These sources are distributed over
+the full 24 hours of Right Ascension coverage but are within 5 degrees
+declination of Pictor A.  Using a Bayesian analysis we conclude that most of
+these are consistent with previous measurements and provide useful new
+constraints. However, in the remainder, the simple spectral model fails to
+adequately describe the data. In most cases the proximity to bright or extended
+structures implies side lobe contamination.  Therefore, though we include the
+model parameters, they are not meant to be definitive, but provide confidence
+that the reported PAPER flux values are on the correct global scale.
 
@@
 \includegraphics[width=0.9\textwidth]{plots/2250-412_2331-416_2140-434_0007-446_0704-427_gain_mcmc_chain_gain_conf.png}
-
-\caption{The marginalized PAPER flux scale factor posterior probability distribution function bootstrapped from the NED database listings for 2250-412,2331-416,2140-434,0007-446 and 0704-427 below 2GHz.
+\caption{
+The marginalized PAPER flux scale factor posterior probability distribution
+function bootstrapped from the NED database listings for
+2250-412,2331-416,2140-434,0007-446 and 0704-427 below 2GHz.
 \label{fig:gain}}
@@
 \includegraphics[width=0.49\textwidth]{plots/pic_SI_MCMC.png}
-\caption{Using new PAPER results to constrain the spectrum of Pictor A.
-On the left, the PAPER Pictor A spectrum with 2$\sigma$ error bars (x) and  MCMC fits (grey cloud).
-Inset allows comparison between the 10MHz averaged points with the 403kHz points (grey).
-The oscillations in the PAPER spectrum are residual side lobe contamination from other sources and are well represented by the error bars.
-The most reliable prior measurements (dots) are those by \cite{Wills:1975p9314} at 580MHz and 635MHz \citep{Perley:1997p9312}.
-The rest are from with Culgoora \cite{Slee:1995p7541} or Parkes  \cite{Otrupcek:1991p8780} and have been set to the (extrapolated) \citet{Baars:1977p9678} scale by  \cite{Kuehr:1981p9628}.
-A sub-sample of MCMC fits are shown in blue.
-On the right, the grey contour indicates the 76\% confidence interval for 150MHz flux and spectral index given the prior data.
+\caption{
+Using new PAPER results to constrain the spectrum of Pictor A.  On the left,
+the PAPER Pictor A spectrum with 2$\sigma$ error bars (x) and  MCMC fits (grey
+cloud). Inset allows comparison between the 10MHz averaged points with the
+403kHz points (grey). The oscillations in the PAPER spectrum are residual side
+lobe contamination from other sources and are well represented by the error
+bars.  The most reliable prior measurements (dots) are those by
+\cite{Wills:1975p9314} at 580MHz and 635MHz \citep{Perley:1997p9312}. The rest
+are from with Culgoora \cite{Slee:1995p7541} or Parkes
+\cite{Otrupcek:1991p8780} and have been set to the (extrapolated)
+\citet{Baars:1977p9678} scale by  \cite{Kuehr:1981p9628}. A sub-sample of MCMC
+fits are shown in blue. On the right, the grey contour indicates the 76\%
+confidence interval for 150MHz flux and spectral index given the prior data.
 Black folds in the PAPER data.
-}
-\label{fig:pic_spectrum}
+} \label{fig:pic_spectrum}
 \end{figure*}
@@
 \section*{Acknowledgements}
-The PAPER project is supported by the National Science Foundation (awards 0804508, 1129258, and 1125558), and a generous grant from the Mt. Cuba Astronomical Association.
 
-This work makes use of ]the ``MCMC Hammer"
-	emcee python library \citep[  \url{http://danfm.ca/emcee/}]{ForemanMackey:2012p8684}  and the NASA/IPAC Extragalactic Database (NED) which is operated by the Jet Propulsion Laboratory, California Institute of Technology, under contract with the National Aeronautics and Space Administration.
+The PAPER project is supported by the National Science Foundation (awards
+0804508, 1129258, and 1125558), and a generous grant from the Mt. Cuba
+Astronomical Association.
+
+This work makes use of ]the ``MCMC Hammer" emcee python library \citep[
+\url{http://danfm.ca/emcee/}]{ForemanMackey:2012p8684}  and the NASA/IPAC
+Extragalactic Database (NED) which is operated by the Jet Propulsion
+Laboratory, California Institute of Technology, under contract with the
+National Aeronautics and Space Administration.
 
 \section*{Appendix: Model Fitting}
-In this paper we estimate spectral model parameters and flux calibration in a Bayesian way by calculating and marginalizing the posterior probability of the data, past and present, given a spectral and instrumental model.
-This method offers improved repeatability by specifying a single objective function that represents the quality of the model fit and naturally defines the errors on the parameters \citep{Hogg:2010p8759}.
-See  \citet{Mackay:2003p9717}  or \citet{Sivia:2006p9736} for more on Bayesian analysis methods and an excellent astrophysical example by \cite{Press:1997p9783}.
 
-In general an experiment measures data $D$ and given some model of the statistics of the measurement one usually assigns an error bar defining the probability of getting that data, given a model $M$.
-Given all the new data, and prior data, there will be a new optimal set of model parameters $M$ with associated error bars.
-In general, these error bars are a parameterization of a probability distribution function.
-The pdf associated with the data often called the likelihood ($\mathcal{L}$), while the one corresponding the model error bars is the {\em posterior probability distribution}, $\Prob(M|D)$.
-They are related
+In this paper we estimate spectral model parameters and flux calibration in a
+Bayesian way by calculating and marginalizing the posterior probability of the
+data, past and present, given a spectral and instrumental model.   This method
+offers improved repeatability by specifying a single objective function that
+represents the quality of the model fit and naturally defines the errors on the
+parameters \citep{Hogg:2010p8759}.   See  \citet{Mackay:2003p9717}  or
+\citet{Sivia:2006p9736} for more on Bayesian analysis methods and an excellent
+astrophysical example by \cite{Press:1997p9783}.
+
+In general an experiment measures data $D$ and given some model of the
+statistics of the measurement one usually assigns an error bar defining the
+probability of getting that data, given a model $M$.  Given all the new data,
+and prior data, there will be a new optimal set of model parameters $M$ with
+associated error bars.  In general, these error bars are a parameterization of
+a probability distribution function.  The pdf associated with the data often
+called the likelihood ($\mathcal{L}$), while the one corresponding the model
+error bars is the {\em posterior probability distribution}, $\Prob(M|D)$. They
+are related
 
@@
 \] 
-by the factor $\frac{\Prob(M)}{\Prob(D)}$, the prior probability of the model $M$ (given past experiments) over the normalization factor, integrating over all models.
-In general the posterior pdf depends on both the known relation between the model parameters and as well as correlations hidden within the data.
+by the factor $\frac{\Prob(M)}{\Prob(D)}$, the prior probability of the model
+$M$ (given past experiments) over the normalization factor, integrating over
+all models.  In general the posterior pdf depends on both the known relation
+between the model parameters and as well as correlations hidden within the
+data.
 
-Direct calculation of the posterior is difficult, particularly the normalization factor, however there is a simple procedure for drawing samples from the posterior.
-In this paper we use a Markov Chain Monte Carlo sampler.
-Given any current location in parameter space, this algorithm draws a new set of parameters and computes the relative likelihood increase.
-If the probability difference is larger than a number drawn randomly from the set $(0:1]$, the jump is accepted ---a Metropolis-Hastings step.
-In the limit of an infinity of such steps, this process has been shown to converge on the true posterior distribution.
-In practice it is run for a large number of steps until things appear to stabilize.
-The best fit model is the median of all the sampled parameter sets, while the volume containing a well defined fraction of samples sets the confidence limits.
-The oft quoted ``1$\sigma$" probability level corresponding to a gaussian distribution contains 65\% of the samples.
-In practice the contours are not gaussian.
-Here we choose a slightly more conservative probability level of 76\%
+Direct calculation of the posterior is difficult, particularly the
+normalization factor, however there is a simple procedure for drawing samples
+from the posterior. In this paper we use a Markov Chain Monte Carlo sampler.
+Given any current location in parameter space, this algorithm draws a new set
+of parameters and computes the relative likelihood increase. If the probability
+difference is larger than a number drawn randomly from the set $(0:1]$, the
+jump is accepted ---a Metropolis-Hastings step. In the limit of an infinity of
+such steps, this process has been shown to converge on the true posterior
+distribution.  In practice it is run for a large number of steps until things
+appear to stabilize. The best fit model is the median of all the sampled
+parameter sets, while the volume containing a well defined fraction of samples
+sets the confidence limits.  The oft quoted ``1$\sigma$" probability level
+corresponding to a gaussian distribution contains 65\% of the samples. In
+practice the contours are not gaussian. Here we choose a slightly more
+conservative probability level of 76\%
 
-In \S \ref{sec:fits} we fit a spectral power law to catalog values by sampling a (log) likelihood which assumes Gaussian measurement errors
+In \S \ref{sec:fits} we fit a spectral power law to catalog values by sampling
+a (log) likelihood which assumes Gaussian measurement errors
 
@@
 
-We estimate the confidence interval of the resulting parameters as the boundary enclosing 76\% of the samples.
-In the catalog we report both the upper and lower of these values for both parameters and plot the 2D contour to show the correlation of the two parameters.
-Many of these contours, the grey curves in Fig.
-\ref{fig:SI_contour_1}, are classic banana plots, displaying a non-linear correlation between the parameters.
-In most cases the single contour adequately describes 2D posterior distribution.
+We estimate the confidence interval of the resulting parameters as the boundary
+enclosing 76\% of the samples. In the catalog we report both the upper and
+lower of these values for both parameters and plot the 2D contour to show the
+correlation of the two parameters. Many of these contours, the grey curves in
+Fig. \ref{fig:SI_contour_1}, are classic banana plots, displaying a non-linear
+correlation between the parameters.    In most cases the single contour
+adequately describes 2D posterior distribution.
 
@@
 \includegraphics[width=0.49\textwidth]{plots/1556-466_trace_hist.png}
-\caption{A more detailed view of the posterior probability distribution.
-On the left Pictor A, on the right 1556-466.
-Confidence contours range from 0.2 to 0.8.
-Compare with the contours for this source shown in Fig.
-\ref{fig:SI_contour_3}.
-As above, grey for  the fit to catalog data, black for joint catalog and PAPER fit.
+\caption{
+A more detailed view of the posterior probability distribution. On the left
+Pictor A, on the right 1556-466. Confidence contours range from 0.2 to 0.8.
+Compare with the contours for this source shown in Fig. \ref{fig:SI_contour_3}.
+As above, grey for  the fit to catalog data, black for joint catalog and PAPER
+fit.
 }
@@
 
-A single overall flux scale is computed in a similar way. However, here we add a single extra gain factor $g$ multiplying all PAPER measurements, and sum over several sources.
+A single overall flux scale is computed in a similar way. However, here we add
+a single extra gain factor $g$ multiplying all PAPER measurements, and sum over
+several sources.
 
@@
 \end{align}
-Another nice feature of the MCMC sampler is that each parameter sample is fully covariant with the others.
-To marginalize over the fitted flux and spectral index parameters and compute confidence limits on the gain parameter, we simply ignore them.
+Another nice feature of the MCMC sampler is that each parameter sample is fully
+covariant with the others. To marginalize over the fitted flux and spectral
+index parameters and compute confidence limits on the gain parameter, we simply
+ignore them.
 
@@
 \end{center}
-\caption{PAPER spectra of 16 sources compared against existing data out of  \cite{Vollmer:2010p6422} between 40MHz and 2GHz, otherwise as described in Figure \ref{fig:pic_spectrum}.\label{fig:srcs1}.
-Sources used to bootstrap the flux calibration are noted with a *.}
+\caption{
+PAPER spectra of 16 sources compared against existing data out of
+\cite{Vollmer:2010p6422} between 40MHz and 2GHz, otherwise as described in
+Figure \ref{fig:pic_spectrum}.\label{fig:srcs1}. Sources used to bootstrap the
+flux calibration are noted with a *.
+}
 \end{figure*}
@@
 \includegraphics[width=0.9\textwidth]{plots/srcfig_2.png}
-\caption{PAPER spectra of 16 sources compared against existing data out of  \cite{Vollmer:2010p6422} between 40MHz and 2GHz, otherwise as described in Figure \ref{fig:pic_spectrum}.\label{fig:srcs2} Sources used to bootstrap the flux calibration are noted with a *.}
+\caption{
+PAPER spectra of 16 sources compared against existing data out of
+\cite{Vollmer:2010p6422} between 40MHz and 2GHz, otherwise as described in
+Figure \ref{fig:pic_spectrum}.\label{fig:srcs2} Sources used to bootstrap the
+flux calibration are noted with a *.
+}
 \end{center}
@@
 \includegraphics[width=0.9\textwidth]{plots/srcfig_3.png}
-\caption{PAPER spectra of 16 sources compared against existing data out of  \cite{Vollmer:2010p6422} between 40MHz and 2GHz, otherwise as described in Figure \ref{fig:pic_spectrum}.\label{fig:srcs3} Sources used to bootstrap the flux calibration are noted with a *.}
+\caption{
+PAPER spectra of 16 sources compared against existing data out of
+\cite{Vollmer:2010p6422} between 40MHz and 2GHz, otherwise as described in
+Figure \ref{fig:pic_spectrum}.\label{fig:srcs3} Sources used to bootstrap the
+flux calibration are noted with a *.
+}
 \end{center}
@@
 \end{center}
-\caption{These sources offer results at odds with previous measurements.
-These have small enough error bars to require a deviation from spectral index fit suggested by prior catalog measurements.
-All are near Centaurus A (see Figure \ref{fig:error_map}), a very bright, extended source, and are likely evidence for side lobe contamination.
-Side lobes from distant sources manifest as ripples in the spectrum, increasing the error bars (e.g.
-the sources listed in Figure \ref{fig:SI_contour_bad}).
-However, the sources shown here are close enough to Centaurus A that the side-lobe oscillates on scales longer than 10MHz and does not fall into the rms, but rather into the mean.
-Thus these few points have anomalously high fluxes and small error bars.
-}
-\label{fig:SI_contour_new}
+\caption{
+These sources offer results at odds with previous measurements. These have
+small enough error bars to require a deviation from spectral index fit
+suggested by prior catalog measurements. All are near Centaurus A (see Figure
+\ref{fig:error_map}), a very bright, extended source, and are likely evidence
+for side lobe contamination.  Side lobes from distant sources manifest as
+ripples in the spectrum, increasing the error bars (e.g. the sources listed in
+Figure \ref{fig:SI_contour_bad}). However, the sources shown here are close
+enough to Centaurus A that the side-lobe oscillates on scales longer than 10MHz
+and does not fall into the rms, but rather into the mean. Thus these few points
+have anomalously high fluxes and small error bars. 
+} \label{fig:SI_contour_new}
 \end{figure*}
@@
 \includegraphics[width=\textwidth]{plots/psa64_pic_strip_positions_annotated_cropped.png}
-\caption{A map of the radio sky centered on the south pole \citep{deOliveiraCosta:2008p2242}.
-x's mark measured locations and have size scaled by agreement with prior data (inverse ``improvement index", see \S\ref{sec:fits}).
-Black dots indicate sources with $\le0$ improvement score.
-For these the fit quality decreases with addition of PAPER data or the model revision disagrees completely with the prior estimate due to side lobes or spectral curvature.
-We estimate that   \label{fig:error_map}}
+\caption{
+A map of the radio sky centered on the south pole
+\citep{deOliveiraCosta:2008p2242}.  x's mark measured locations and have size
+scaled by agreement with prior data (inverse ``improvement index", see
+\S\ref{sec:fits}). Black dots indicate sources with $\le0$ improvement score.
+For these the fit quality decreases with addition of PAPER data or the model
+revision disagrees completely with the prior estimate due to side lobes or
+spectral curvature.  We estimate that   \label{fig:error_map}
+}
 \end{figure*}

### 2013-04-23 ms.tex
Minor edits (except for substantial stuff in abstract), commented in areas to focus on and proposed changes.  Will proceed shortly with trying to execute these various changes.

@@
 
-\shorttitle{PSA64}
+\shorttitle{Southern Hemisphere Flux Scale}
 \shortauthors{Jacobs et al.}
@@
 %\title{The Reionization flux scale in the Southern Sky}
-\title{A southern hemisphere flux scale for 21cm epoch of reionization experiments}
+\title{A Flux Scale for Southern Hemisphere 21cm EoR Experiments}
 \author{
@@
 Chris L.  Carilli\altaffilmark{7},
-Dave DeBoer\altaffilmark{8},
-Matthew Dexter\altaffilmark{8},
+David R. DeBoer\altaffilmark{8},
+Matthew R. Dexter\altaffilmark{8},
 Nicole E. Gugliucci\altaffilmark{5},
-Dave MacMahon\altaffilmark{8},
-Jason Manley\altaffilmark{9},
+Pat Klima\altaffilmark{5},
+Dave H. E. MacMahon\altaffilmark{8},
+Jason R. Manley\altaffilmark{9},
 David F. Moore\altaffilmark{3},
@@
 \begin{abstract}
-We present the first spectral measurements from the Precision Array for Probing
+We present a first catalog of broad-band spectral measurements from the 
+Donald C. Backer Precision Array for Probing
+% XXX ARP: was irina "first"?  and maybe "catalog"
 the Epoch of Reionization (PAPER) in South Africa observed in July and
-September of 2011.  The spectra are determined by calibrating directly to a
-nearby source, eliminating the error-prone primary beam correction.  The global
-flux calibration, bootstrapped from catalog data of 5 bright sources, is
-estimated to be accurate to 3.2\%.  Comparing with prior measurements, 45 out
-of 58 sources observed are found to confirm and refine a spectral index model.
-This includes Pictor A which provides a key flux reference for PAPER's EoR
-power spectrum. Combining catalog data at other frequencies with the PAPER data
-we are able to estimate the flux model parameters to an uncertainty of 2.4\%.
-This accuracy, which is ultimately limited by the uncertainty of the many prior
-measurements used to estimate the flux scale, is an order of magnitude
-improvement on previous estimates.  
+September of 2011.  In order to reduce the impact of beam calibration, which proves to
+be a difficult endeavor for transit telescopes such as PAPER, on the determination
+of source spectra, we have focused on calibrating sources in a narrow declination range.
+Since each source follows a nearly identical path through the primary beam, this
+restriction allows beam calibration to be nearly eliminated as a source of error,
+yielding a dramatic improvement in the accuracy of source spectra measured in the 
+100--200-MHz band that is receiving renewed attention by experiments seeking to
+measure 21cm emission from the Epoch of Reionization (EoR).
+Based on the variation in our data and the estimated error in the absolute
+flux scale we bootstrap from multiple bright sources, we estimate PAPER measurements
+of sources above XXX Jy to be accurate to 3.2\%.
+When combined with catalog data at other frequencies, these data constrain parameters of
+a power-law model for flux density with an uncertainty of 2.4\%.
+% XXX ARP: this must again be dependent on source strength and location.
+This accuracy is limited by the uncertainty in the catalog measurements we use
+to estimate an absolute flux scale, and represents 
+an order of magnitude improvement over previous measurements in this band.  
+Comparing with prior measurements, 45 out
+of 58 sources observed are found to confirm and refine a power-law model for flux density.
+This includes Pictor A, which provides a key flux reference for PAPER's EoR
+power spectrum analysis.
 \end{abstract}
@@
 cosmic reionization in the redshift range $6< z<12$, corresponding to radio
-frequencies below 200MHz (see reviews in
-\citet{Furlanetto:2006p2267,Morales:2010p8093,Pritchard:2012p9555}) .  These
+frequencies below 200 MHz (see reviews in
+\citealt{Furlanetto:2006p2267,Morales:2010p8093,Pritchard:2012p9555}) .  These
 include telescopes aiming to measure the global temperature change of 21cm
@@
 the Donald C. Backer Precision Array for Probing the Epoch of Reionization
-(PAPER; \citealt{Parsons:2010p6757})\footnote{\url{http://eor.berkeley.edu/}}.
+(PAPER; \citealt{Parsons:2010p6757,Parsons2013b})\footnote{\url{http://eor.berkeley.edu/}}.
 Both PAPER and the MWA are located in the southern hemisphere at radio quiet
@@
 zero emission.  This patchy signal is predicted to be visible everywhere on the
+% XXX ARP: don't like description of EoR signal as "surface brightness"
 sky at size scales up to degrees, or about $0.1$cMpc$^{-1}$.   To increase the
@@
 ($\sim 100$\% fractional) than traditional dish telescopes.   As the elements
+% XXX what about GMRT?
 can not be physically pointed, the apparent flux scale varies across the sky.
@@
 well-known calibrators to map the primary beam and set the flux scale.  
+% XXX don't go to "ideal solution" just yet
+% XXX ARP: add importance of accurate flux vs. frequency (Parsons et al. 2012, etc.)
 
@@
 However, catalog source fluxes at 150MHz are also inaccurate to the 20\% level,
-particularly at southern declinations ($<-20$\arcdeg) . Historically, the best
+particularly at southern declinations ($\delta<-20$\arcdeg) . Historically, the best
 EoR band data were by \citet{Slee:1995p7541} with Culgoora Circular
@@
 PAPER, in its maximum redundancy configuration, has a very broad beam with
-large regular grating side-lobes and is therefor limited to using the few
+% XXX need background on minimum/maximum array configurations
+large regular grating side-lobes and is therefore limited to using the few
 sources above $\sim$50 Jy for flux calibration. The best calibrator for most
+% XXX qualify "best"
 observations is Pictor A. For this source the current best EoR band measurement
@@
 The PAPER array has grown from 16 elements deployed in early 2009 to a
-64-element imaging array in 2011 (see Figure \ref{fig:antpos}). Since November 2011 it has been arranged in a maximally redundant grid configuration to make deep power spectral integrations.  
+64-element imaging array in 2011 (see Figure \ref{fig:antpos}).
+Since November 2011 it has been arranged in a maximally redundant grid configuration to make deep power spectral integrations \citep{Parsons:2012a}.
 \begin{figure*}\centering
 \includegraphics[width=0.85\columnwidth]{plots/antpos.png}
-\caption{The 64-antenna, minimum-redundancy PAPER array at Karoo Radio Observatory site in South Africa used for these observations.
+\caption{Antenna position in the 64-antenna, minimum-redundancy PAPER array configuration at the Karoo Radio Observatory site in South Africa used for these observations.
+% XXX add brief summary of observations.
 }\label{fig:antpos}
@@
 As such it is only able to easily distinguish the very brightest sources on the
-sky a step necessary for setting the overall flux scale. Of these, Pictor A is
+sky a step necessary for setting the overall flux scale \citep{Parsons2013b}. Of these, Pictor A is
 one of the most useful, being bright, minimally resolved and far from from
@@
 %This declination limit removes the necessity of correcting for a primary beam model and allows us to calculate more precise fluxes that provide a reference standard for future work.
+
+\section{Approach}
+
+% XXX write this section
 
@@
 interpolated the PAPER baselines in the uv plane. At the highest frequency this
+% XXX "interpolated" needs to be clarified
 led to a 3\% correction, at the lowest frequency, 0.6\%.
@@
 The primary purpose of this observation is to produce a high quality Pictor A
+% XXX need to coordinate "primary purpose" here with abstract and intro motivation
 spectrum. As a verification measure we have observed many other sources at the
@@
 frequencies. The remaining 25\% either A) have large PAPER error bars and
-therefor provide no new information or B) do not agree with the spectral index
+therefore provide no new information or B) do not agree with the spectral index
 model.  To understand where most measurements fall on this spectrum we
@@
 \end{align}
+% XXX This equation is yucky
 
@@
 confirmation.  The flux model is $S150=$388 $\pm$ 9.4Jy, $\alpha=-0.77\pm0.02$.
+% XXX need more detail here.  This is the crux of what is done.
 The combination of several independent PAPER data points near 150MHz with
@@
 that the reported PAPER flux values are on the correct global scale.
+
+% XXX need more discussion
 
@@
 \section*{Appendix: Model Fitting}
+% XXX this should be in main body, not an appendix
 

### 2013-04-23 ms.tex
Pasted in unused text from psa32 power spectrum paper

@@
 (PAPER; \citealt{Parsons:2010p6757,Parsons2013b})\footnote{\url{http://eor.berkeley.edu/}}.
+
+As such, there has been a renewed interest in the spectral and spatial variation of
+foreground emission in the 100--200 MHz frequency band that covers
+the $z=6$--13 redshift range expected to encompass reionization
+\citep{furlanetto_et_al2006}.
+In particular, the spectral properties of extra-galactic point-sources are important
+both because they are valuable calibration references
+and because they are strong foreground emitters that must be removed from 21-cm EoR measurements.
+With the sparse availability of measured foreground properties in the
+100--200-MHz frequency band over large areas of the sky \citep{deolivieracosta_et_al2008}, continued
+foreground characterization is a
+vital step en route to any 21-cm EoR detection.
 Both PAPER and the MWA are located in the southern hemisphere at radio quiet
@@
 
+% XXX is the "eor science" part necessary?  this isn't a paper on eor
 Neutral hydrogen is visible during reionization as $\sim$30mK excess surface
@@
 
+% XXX incorporate
+%Given these shortcomings in the literature, we felt it prudent to examine-Pictor A directly.  We use data observed on JD2455747 
+%from a 64-antenna single-polarization deployment of the 
+%PAPER array in a minimum redundancy configuration that is more suited for imaging.  The details
+%of these observations and their calibration are given in \citet{pober_et_al2013}.  In order to ensure that 
+%errors in
+%the beam model did not skew our result, we chose a set of calibrator sources near in declination
+%to Pictor A that would follow nearly identical tracks through the primary beam.
+
+% XXX incorporate
+%To measure the spectrum of each source, we apply per-antenna phase and gain cal
+%brations established-via self-calibration and remove
+%the known dependence of amplifier gain and cable attenuation on ambient temperature was corrected
+%using measured temperature data and temperature coefficients that were characterized in
+%laboratory measurements \citep{parashare_bradley2009} and confirmed in field-measurements \citep{pober_et_al2012}.  For each source, we phase to the source 
+%osition
+%and sum over 
+%all baselines greater than 20 wavelengths in length.
+%A fringe-rate filter is applied to the resulting
+%beam to suppress beam sidelobes where sources introduce variations that deviate more than 
+%$\pm$0.1 mHz from the fringe rate of the source in question.
+
+% XXX incorporate
+%To derive a source spectrum from each drift-scan source profile, we compute a weighted average using
+%weights derived from a model of
+%PAPER's primary beam response as an effective approximation of inverse-variance weighting
+%\citep{pober_et_al2012}, and averaging over the time series for each source.  Each output source spectrum
+%represents a best estimate given the limitations of the beam model and flux calibration that were established
+%up to this point.  To further improve these estimates, we derive an additional frequency-dependent gain parameter,
+%smoothed on 10-MHz scales,
+%that brings the spectrum of J2331-416 into closest agreement with a power-law spectrum of
+%$S_{150}=31.9\ {\rm Jy}$, $\alpha=-0.69$ that represents the best fit to measurements below 1 GHz.
+%This additional gain factor was applied to all measured spectra, including that
+%of Pictor A.  The expectation is that, since all sources at similar declinations follow similar tracks 
+%through the PAPER beam, any errors present in the original measured spectra as a result of differences between
+%the simulated and actual beam response should be absent in the ratio between source spectra, and therefore
+%should be corrected by the applied gain factor.
+
+% XXX incorporate
+%Finally, because Pictor A is resolved at the 20\% level on the longest (300m) East-West PAPER baselines, we 
+%use per-baseline estimates of resolution weights to down-weight and correct for resolution effects.  To estimate
+%resolution weights, we use the 90cm map of Pictor A presented in \citet{perley_et_al1997}.  Averaged over all
+%the baselines in the array, the inclusion of resolution effects changed the measured flux by less than 5\%.
+
  \section{Observations and Data Reduction}
@@
 
+% XXX merge with below
+%Removed RFI by flagging samples in each frequency channel versus time that exceed the mean amplitude by 4-sigma
+%after performing a time derivative.  Also flagged samples in each integrated spectrum that exceeded the
+%mean amplitude across the spectrum by 6-sigma after performing a frequency derivative.  For efficiency, flagging
+%was derived using only the subset of baselines involving a fiducial antenna.
+%Frequencies below 120 MHz and above 180 MHz were also flagged, owing to roll-off of analog response.
+%After RFI flagging, frequency channel resolution was decreased by a factor of four by summing channels.
+
 %CALIBRATION
 \textbf{Antenna calibration}\\
+
+% XXX time-dependent calibration is critical.  modify paragraph below
+Quantization gain through the correlator was linearized \citep{parsons_et_al2008}.
+Finally, measurements of ambient temperature versus time near the balun amplifier of a fiducial antenna and near
+receiver amplifiers were used to divide out the predicted gain variation versus temperature that these amplifiers
+are known to exhibit.  A predicted gain profile was drived using coefficients characterized in
+laboratory measurements \citep{parashare_bradley2009} and
+confirmed in field measurements \citep{pober_et_al2011} of $H_{\rm balun}=-0.024$ dB/K, $H_{\rm recvr}=-0.045$
+dB/K, and $H_{\rm cable}=-0.018$ dB/K for 150m-long cables.  Because cable temperatures were not measured
+during these observations, the cable temperature was assumed to be the same as the measured balun temperature.
 
@@
 averaging over the three independent solutions. These same calibration
-solutions have also been successfully applied in the power spectrum analysis by
-Pober (2013) and Centaurus A imaging by Stefan (2013).
+solutions have been successfully applied in \citet{Pober:2013XXX} and \citet{Stefan:2013:XXX}.
+for power-spectrum analysis of foregrounds and imaging of Centaurus A, respectively.
+
+% XXX differentiate amp cal here from spectral cal that comes later.
 
@@
 \textbf{Source Selection}\\
+
+In order to ensure that errors in
+the beam model did not skew our result, we chose a set of sources near in declination
+to Pictor A that would follow nearly identical tracks through the primary beam.
+A list of these 
+sources is given in Table \ref{tab:src_spec}, with the spectra measure by PAPER
+illustrated in Figure \ref{fig:src_spec}.  These sources were chosen on the basis of brightness and
+proximity in declination to Pictor A.
+% XXX merge this with paragraph below
 
@@
 
+% XXX incorporate paragraph below
+%As the sky drifts through the primary beam of PAPER antennas, widely
+%separated points will be observed with substantially different gains and
+%so will require different data weightings to optimize SNR.
+%Drift-scan observations of sources were divided by the calibrated beam response in the
+%direction of the source as a function of time.  Spectra were calculated by averaging over
+%time, weighting data at each time step by the square of the 150-MHz beam response in the source direction.
+%Since noise and systematics relating to source observations are expected to be approximately constant
+%versus time, while source amplitude is proportional to beam response, this weighting
+%is an effective approximation of inverse-variance weighting \citep{pober_et_al2011}.
+
+% XXX exclusion of minimum uv spacing?
+
  These complex spectra are then delay-delay rate filtered to remove spectrally
@@
 
+% XXX incorporate paragraph below
+%To measure the spectrum of each source, we apply per-antenna phase and gain cal
+%via self-calibration and remove
+%the known dependence of amplifier gain and cable attenuation on ambient tempera
+%using measured temperature data and temperature coefficients that were characte
+%laboratory measurements \citep{parashare_bradley2009} and confirmed in field
+%measurements \citep{pober_et_al2012}.  For each source, we phase to the source 
+%and sum over 
+%all baselines greater than 20 wavelengths in length.
+%A fringe-rate filter is applied to the resulting
+%beam to suppress beam sidelobes where sources introduce variations that deviate
+%$\pm$0.1 mHz from the fringe rate of the source in question.
+
 \begin{figure}
@@
 \caption{The effective uv coverage, showing the relative contributions of each baseline when beam-forming on Pictor over a 9.6 hour synthesis in the October observing session. \label{fig:uv_coverage}}
+% XXX unclear whether amplitudes include our model of Pic A, or are even actual data vs. weights
 \end{figure}
@@
 
+% XXX selection of calibrator sources
+
 The gain of each channel is the product of an overall instrumental passband and
@@
 literature and the apparent smoothness of the spectrum.}.  We then, average the
+% XXX clarify why one source used here, and more sources later 
 two matched data streams in time.  Since both tracks make the same slice
@@
 the standard deviation as an estimate of the error.
+
+% XXX merge this with above
+%To further improve these estimates, we derive an additional frequency-dependent gain parameter,
+%smoothed on 10-MHz scales,
+%that brings the spectrum of J2331-416 into closest agreement with a power-law spectrum of
+%$S_{150}=31.9\ {\rm Jy}$, $\alpha=-0.69$ that represents the best fit to measurements below 1 GHz
+%\citep{slee1995,kuhr_et_al1981,large_et_al1981,burgess_hunstead2006}.
+%This additional gain factor was applied to all measured spectra, including that
+%of Pictor A.  The expectation is that, since all sources at similar declinations follow similar tracks 
+%through the PAPER beam, any errors present in the original measured spectra as a result of differences between
+%the simulated and actual beam response should be absent in the ratio between source spectra, and therefore
+%should be corrected by the applied gain factor
 

### 2013-04-23 ms.tex
Significant rewrite of S1.  S2 is a complete hodgepodge for now.

@@
 frequencies below 200 MHz (see reviews in
-\citealt{Furlanetto:2006p2267,Morales:2010p8093,Pritchard:2012p9555}) .  These
+\citealt{Furlanetto:2006p2267,Morales:2010p8093,Pritchard:2012p9555}).  These
 include telescopes aiming to measure the global temperature change of 21cm
@@
 vital step en route to any 21-cm EoR detection.
-Both PAPER and the MWA are located in the southern hemisphere at radio quiet
-reserves being prepared for the upcoming Square Kilometer Array.  At these low
-frequencies the Southern sky is much less well known than the North, with the
-most extensive surveying work being conducted  by the EoR experiments
+At these low
+frequencies the Southern sky is much less well known than the North, 
+with catalog source fluxes at 150MHz being inaccurate at the 20\% level
+at southern declinations ($\delta<-20$\arcdeg) (XXX cite).
+Both PAPER and the MWA are located in the southern hemisphere at radio-quiet
+reserves being prepared for the upcoming Square Kilometer Array, and hence,
+the
+most extensive surveying work is now being conducted by the EoR experiments
 themselves \citep{Jacobs:2011p8438,Williams:2012p8768}.
 
-% XXX is the "eor science" part necessary?  this isn't a paper on eor
-Neutral hydrogen is visible during reionization as $\sim$30mK excess surface
-brightness over the CMB punctuated both spectrally and spatially by regions of
-zero emission.  This patchy signal is predicted to be visible everywhere on the
-% XXX ARP: don't like description of EoR signal as "surface brightness"
-sky at size scales up to degrees, or about $0.1$cMpc$^{-1}$.   To increase the
-surface brightness sensitivity without building costly dishes, MWA, PAPER and
-LOFAR have chosen to use combinations of phased and/or correlated dipoles. By
-design also cover much wider fields of view ($>10$\arcdeg) and bandwidths
-($\sim 100$\% fractional) than traditional dish telescopes.   As the elements
-% XXX what about GMRT?
-can not be physically pointed, the apparent flux scale varies across the sky.
+One significant complication to improving the state of affairs in foreground characterization
+is that many 21cm EoR experiments, including LOFAR in the northern hemisphere, and
+PAPER and MWA in the southern hemisphere, are designed for drift-scan observations.
+This design decision has largely been driven by the simplicity and cost-effectiveness of
+phased and/or correlated dipoles for achieving the aggressive sensitivity requirements
+for measuring the 21cm power spectrum of reionization (XXX cite).
+Adding to the challenge, these telescopes 
+cover much wider fields of view ($>10$\arcdeg) and bandwidths
+($\sim 100$\% fractional) than traditional dish telescopes.
+Because they do not physically point, flux calibration for such arrays relies heavily
+on an accurate model of the primary beam response to correct for an
+the apparent flux scale that varies across the sky.
 This direction dependent gain is currently uncertain to 20\% or higher
-\citep{Jacobs:2013p9713}.  The ideal solution is to use a wide-grid of
-well-known calibrators to map the primary beam and set the flux scale.  
+% XXX 20% seems a bit grim.  Doesn't jonnie argue for 5 to 10% in his paper?
+\citep{Jacobs:2013p9713}, approximately matching the level of uncertainty in the catalogs.
+
+In this paper, we set out to significantly improve the accuracy of spectral measurements between 
+100--200 MHz for a set of bright sources in the declination range XXX to XXX that
+are of particular value for southern-hemisphere 21cm EoR experiments such as PAPER and the MWA.
+Using the fact that, for this restricted declination range,
+sources transit through a nearly identical primary beam response pattern, we are able to avoid one of the
+most debilitating source of error in these measurements: the primary beam.  
+% XXX document map
+In \S\ref{sec:analysis} we describe our approach for measuring source spectra with
+drift-scan observations and deriving an absolute flux scale from catalog data.  
+In \S\ref{sec:Observations} we detail the instrumental
+setup, observations and analysis method followed. In \S\ref{sec:fits} we
+compare the spectra with available data.  We conclude in 
+\S\ref{sec:Conclusion}.
+
+%The ideal solution is to use a wide-grid of
+%well-known calibrators to map the primary beam and set the flux scale.  
 % XXX don't go to "ideal solution" just yet
@@
 
+\section{Approach}
+
+% XXX write this section
+
 However, catalog source fluxes at 150MHz are also inaccurate to the 20\% level,
-particularly at southern declinations ($\delta<-20$\arcdeg) . Historically, the best
+particularly at southern declinations ($\delta<-20$\arcdeg).
+
+Historically, the best
 EoR band data were by \citet{Slee:1995p7541} with Culgoora Circular
@@
 by Monte Carlo fitting to a subset of sources, all of which are calibrated to
-the Baars et al scale. In \S\ref{sec:Observations} we describe the instrumental
-setup, observations and analysis method followed. In \S\ref{sec:fits} we
-compare the spectra with available data followed by conclusions in
-\S\ref{sec:Conclusion}.
-
+the Baars et al scale. 
 %This declination limit removes the necessity of correcting for a primary beam model and allows us to calculate more precise fluxes that provide a reference standard for future work.
-
-\section{Approach}
-
-% XXX write this section
 

### 2013-04-24 ms.tex
moved lots of text around to try to get a better organization

@@
 
+\section{Introduction}
+
 Numerous radio telescopes are now exploring the prospects for using
@@
 with catalog source fluxes at 150MHz being inaccurate at the 20\% level
-at southern declinations ($\delta<-20$\arcdeg) (XXX cite).
+for $\delta<-20$\arcdeg (XXX cite).
 Both PAPER and the MWA are located in the southern hemisphere at radio-quiet
@@
 % XXX 20% seems a bit grim.  Doesn't jonnie argue for 5 to 10% in his paper?
-\citep{Jacobs:2013p9713}, approximately matching the level of uncertainty in the catalogs.
+\citep{Jacobs:2013p9713}, approximately matching the current level of uncertainty in catalogs.
 
@@
 most debilitating source of error in these measurements: the primary beam.  
-% XXX document map
+% XXX update document map
 In \S\ref{sec:analysis} we describe our approach for measuring source spectra with
@@
 
-\section{Approach}
-
-% XXX write this section
-
-However, catalog source fluxes at 150MHz are also inaccurate to the 20\% level,
-particularly at southern declinations ($\delta<-20$\arcdeg).
+\section{Background}
+
+% XXX unsure about this section.  need someplace to give overviews of catalogs
 
@@
 a single narrow-band data point.
-
-PAPER, in its maximum redundancy configuration, has a very broad beam with
-% XXX need background on minimum/maximum array configurations
-large regular grating side-lobes and is therefore limited to using the few
-sources above $\sim$50 Jy for flux calibration. The best calibrator for most
-% XXX qualify "best"
-observations is Pictor A. For this source the current best EoR band measurement
-is uncertain to 12\% and appears to imply spectral flattening in the EoR band
-\citep{Perley:1997p9312}.
 
@@
 
+% XXX elaborate on:
+%However, catalog source fluxes at 150MHz are also inaccurate to the 20\% level,
+%particularly at southern declinations ($\delta<-20$\arcdeg).
+
+% XXX remove PAPER specificity from below?
+For power-spectrum measurements, PAPER uses an antenna layout
+optimized to detect a small number of Fourier modes at high precision.  This ``maximum-redundancy''
+array configuration trades imaging dynamic range for power spectrum sensitivity \citep{Parsons2012a}.
+As such it is only able to easily distinguish the very brightest sources on the
+sky for setting the overall flux scale \citep{Parsons2013b}. 
+Of these, Pictor A is
+one of the most useful, being bright, minimally resolved, and far from
+confusing structure. 
+For this source the current best EoR band measurement
+is uncertain to 12\% and appears to imply spectral flattening in the EoR band
+\citep{Perley:1997p9312}.
+% XXX more background on pictor A
+
+% XXX transition to the PAPER instrument
+Establishing an accurate spectrum for Pictor A is of particular importance for
+PAPER --- a dedicated EoR experiment 
+that employs drift-scanning, dual-polarization dipole antennas 
+tuned for efficient operation over a 120--170-MHz band.  PAPER is located in the South African Karoo desert
+on the Square Kilometer Array
+South Africa (SKA-SA) reserve, 100km north of the small town of Carnarvon.
+The PAPER array has grown from 16 elements deployed in early 2009 to a
+64-element imaging array in 2011 (see Figure \ref{fig:antpos}). 
+Since November 2011 it has been arranged in a maximally redundant grid 
+configuration to make deep power spectral integrations \citep{Parsons:2012a}.
+% XXX to calibrate these observations...
+
 A method for decoupling uncertain fluxes from the uncertain beam has been
@@
 the availability of precise flux measurements unaffected by primary beam
-uncertainty. This paper reports a set of flux measurements where a primary beam
+uncertainty.
+
+This paper reports a set of flux measurements where a primary beam
 model has not been used to estimate the flux, but instead are directly
@@
 
-The spectra were measured by PAPER, a dedicated EoR experiment 
-that employs drift-scanning, dual-polarization dipole antennas 
-tuned for efficient operation over a 120--170-MHz band located in the South African Karoo desert
-on the Square Kilometer Array
-South Africa (SKA-SA) reserve, 100km north of the small town of Carnarvon.
-The PAPER array has grown from 16 elements deployed in early 2009 to a
-64-element imaging array in 2011 (see Figure \ref{fig:antpos}).
-Since November 2011 it has been arranged in a maximally redundant grid configuration to make deep power spectral integrations \citep{Parsons:2012a}.
+\section{Approach}
+
+% XXX incorporate
+Given the shortcomings in the literature, and the necessity for PAPER power-spectrum analysis
+to use Pictor A for flux calibration, we felt it prudent to examine Pictor A directly.
+
+In order to ensure that 
+errors in
+the beam model did not skew our result, we chose a set of calibrator sources near in declination
+to Pictor A that would follow nearly identical tracks through the primary beam.
+This declination limit removes the necessity of correcting for a primary beam model and allows us to calculate more precise fluxes that provide a reference standard for future work.
+
+In order to ensure that errors in
+the beam model did not skew our result, we chose a set of sources near in declination
+to Pictor A that would follow nearly identical tracks through the primary beam.
+A list of these 
+sources is given in Table \ref{tab:src_spec}. 
+These sources were chosen on the basis of brightness and
+proximity in declination to Pictor A.
+% XXX specific declination range
+% XXX merge this with paragraph below
+
+To provide a basis for establishing the accuracy of the Pictor measurement we
+measured more sources.  Specifically, we choose sources from the Molonglo
+Reference Catalog \cite[MRC]{Large:1981p7798} that are within 5\arcdeg in
+declination of a common calibrator (J2331-416) and have a flux extrapolated
+from 408MHz greater than 10Jy assuming a power law spectral index of
+-1.\footnote{Most radio sources in this band have power law spectra $S(\nu) =
+\left(\frac{\nu}{\nu_0}\right)^\alpha$.  The 5\arcdeg distance between source
+and calibrator was chosen as a balance between number of sources included and
+the known smoothness of the beam.   The average spectral index for radio
+sources in this band is $-0.8$.} This selection contains 62 sources in a narrow
+stripe that passes through the majority of the southern EoR fields, much of the
+galaxy and Centaurus A.
+
+% XXX equation for time-dependent beam amplitude times source flux for perceived flux density
+
+To derive a source spectrum from each drift-scan source profile, we compute a weighted average using
+weights derived from a model of
+PAPER's primary beam response as an effective approximation of inverse-variance weighting
+\citep{pober_et_al2012}, and averaging over the time series for each source.  Each output source spectrum
+represents a best estimate given the limitations of the beam model and flux calibration that were established
+up to this point.  To further improve these estimates, we derive an additional frequency-dependent gain parameter,
+smoothed on 10-MHz scales,
+that brings the spectrum of J2331-416 into closest agreement with a power-law spectrum
+that represents the best fit to measurements below 1 GHz.
+This additional gain factor was applied to all measured spectra, including that
+of Pictor A.  The expectation is that, since all sources at similar declinations follow similar tracks 
+through the PAPER beam, any errors present in the original measured spectra as a result of differences between
+the simulated and actual beam response should be absent in the ratio between source spectra, and therefore
+should be corrected by the applied gain factor.
+
+Finally,
+the flux scale is set
+by Monte Carlo fitting to a subset of sources, all of which are calibrated to
+the Baars et al scale. 
+% XXX elaborate on this, more on Baars, less on MC
+
+ \section{Data Reduction}
+ \label{sec:Observations}
+
 \begin{figure*}\centering
@@
 
-In this paper our primary goal is to provide a subset of accurate fluxes
-suitable for EoR power spectrum and catalog calibration.  After recording the
-data used in this paper, PAPER was reconfigured into a redundant layout
-optimized to detect a small number of power spectrum bins at high precision, an
-arrangement which trades imaging dynamic range for power spectrum sensitivity.
-As such it is only able to easily distinguish the very brightest sources on the
-sky a step necessary for setting the overall flux scale \citep{Parsons2013b}. Of these, Pictor A is
-one of the most useful, being bright, minimally resolved and far from from
-confusing structure.
-
-The data  include new measurements of Pictor A that are uncertain to 3.5\%,
-close to the level of the most precise higher frequency measurements by
-\citet{Wills:1975p9314}. Using these new measurements we update the spectral
-calibration model to an accuracy of 2.5\%. As validation of this method, we
-also measure a selection of 58 additional sources at the same Declination.  The
-primary beam is calibrated using a single common source (J2331-416), thus
-limiting the declination probed to $-45 \pm 5$\arcdeg.  The flux scale is set
-by Monte Carlo fitting to a subset of sources, all of which are calibrated to
-the Baars et al scale. 
-%This declination limit removes the necessity of correcting for a primary beam model and allows us to calculate more precise fluxes that provide a reference standard for future work.
-
-% XXX incorporate
-%Given these shortcomings in the literature, we felt it prudent to examine-Pictor A directly.  We use data observed on JD2455747 
-%from a 64-antenna single-polarization deployment of the 
-%PAPER array in a minimum redundancy configuration that is more suited for imaging.  The details
-%of these observations and their calibration are given in \citet{pober_et_al2013}.  In order to ensure that 
-%errors in
-%the beam model did not skew our result, we chose a set of calibrator sources near in declination
-%to Pictor A that would follow nearly identical tracks through the primary beam.
-
-% XXX incorporate
-%To measure the spectrum of each source, we apply per-antenna phase and gain cal
-%brations established-via self-calibration and remove
-%the known dependence of amplifier gain and cable attenuation on ambient temperature was corrected
-%using measured temperature data and temperature coefficients that were characterized in
-%laboratory measurements \citep{parashare_bradley2009} and confirmed in field-measurements \citep{pober_et_al2012}.  For each source, we phase to the source 
-%osition
-%and sum over 
-%all baselines greater than 20 wavelengths in length.
-%A fringe-rate filter is applied to the resulting
-%beam to suppress beam sidelobes where sources introduce variations that deviate more than 
-%$\pm$0.1 mHz from the fringe rate of the source in question.
-
-% XXX incorporate
-%To derive a source spectrum from each drift-scan source profile, we compute a weighted average using
-%weights derived from a model of
-%PAPER's primary beam response as an effective approximation of inverse-variance weighting
-%\citep{pober_et_al2012}, and averaging over the time series for each source.  Each output source spectrum
-%represents a best estimate given the limitations of the beam model and flux calibration that were established
-%up to this point.  To further improve these estimates, we derive an additional frequency-dependent gain parameter,
-%smoothed on 10-MHz scales,
-%that brings the spectrum of J2331-416 into closest agreement with a power-law spectrum of
-%$S_{150}=31.9\ {\rm Jy}$, $\alpha=-0.69$ that represents the best fit to measurements below 1 GHz.
-%This additional gain factor was applied to all measured spectra, including that
-%of Pictor A.  The expectation is that, since all sources at similar declinations follow similar tracks 
-%through the PAPER beam, any errors present in the original measured spectra as a result of differences between
-%the simulated and actual beam response should be absent in the ratio between source spectra, and therefore
-%should be corrected by the applied gain factor.
-
-% XXX incorporate
-%Finally, because Pictor A is resolved at the 20\% level on the longest (300m) East-West PAPER baselines, we 
-%use per-baseline estimates of resolution weights to down-weight and correct for resolution effects.  To estimate
-%resolution weights, we use the 90cm map of Pictor A presented in \citet{perley_et_al1997}.  Averaged over all
-%the baselines in the array, the inclusion of resolution effects changed the measured flux by less than 5\%.
-
- \section{Observations and Data Reduction}
- \label{sec:Observations}
-
  Measurements are derived from observations using  the east-west dipole arms of
-64 PAPER antennas deployed in the Karoo Radio Observatory site in South Africa
-(see Figure \ref{fig:antpos}).  A 100-MHz band from 100-200MHz was correlated
+64 PAPER antennas deployed in a minimum-redundancy imaging configuration
+(see Figure \ref{fig:antpos})
+at the Karoo Radio Observatory site in South Africa.
+A 100-MHz band from 100-200MHz was correlated
 with 2048 frequency channels and integrated for 10.7 seconds before
@@
 %July (\#40,\#55), September (\#7,\#28)
+
+% XXX incorporate
+We use data observed on JD2455747 
+from a 64-antenna single-polarization deployment of the 
+PAPER array in a minimum redundancy configuration that is more suited for imaging.  The details
+of these observations and their calibration are given in \citet{pober_et_al2013}.
 
@@
 %CALIBRATION
-\textbf{Antenna calibration}\\
+\textbf{Per-Antenna Gain and Phase Calibration}\\
+
+% XXX differentiate amp cal here from spectral cal and absolute cal that comes later.
 
@@
 Quantization gain through the correlator was linearized \citep{parsons_et_al2008}.
-Finally, measurements of ambient temperature versus time near the balun amplifier of a fiducial antenna and near
+Measurements of ambient temperature versus time near the balun amplifier of a fiducial antenna and near
 receiver amplifiers were used to divide out the predicted gain variation versus temperature that these amplifiers
@@
 
-Antennae delays and amplitudes were found by fitting a point source visibility
+Antenna delays and amplitudes were found by fitting a point source visibility
 model to Centaurus A, Pictor A, and Fornax A.  Each source is imperfectly
@@
 
-% XXX differentiate amp cal here from spectral cal that comes later.
+% XXX incorporate
+To measure the spectrum of each source, we begin by applying per-antenna phase and gain
+calibrations established via self-calibration.  We next remove
+the known dependence of amplifier gain and cable attenuation on ambient temperature 
+using measured temperature data and temperature coefficients that were characterized in
+laboratory measurements \citep{parashare_bradley2009} and confirmed 
+in field-measurements \citep{pober_et_al2012}.  For each source, we phase to the source 
+osition
+and sum over 
+all baselines greater than 20 wavelengths in length.
+A fringe-rate filter (see \citet{parsons_backer2009} and Appendix A in \citet{Parsons2013b})
+is applied to the resulting
+beam to suppress beam sidelobes where sources introduce variations that deviate more than 
+$\pm$0.1 mHz from the fringe rate of the source in question.
 
 %BEAMFORMING,FILTERING, AVERAGING
-\textbf{Source Selection}\\
-
-In order to ensure that errors in
-the beam model did not skew our result, we chose a set of sources near in declination
-to Pictor A that would follow nearly identical tracks through the primary beam.
-A list of these 
-sources is given in Table \ref{tab:src_spec}, with the spectra measure by PAPER
-illustrated in Figure \ref{fig:src_spec}.  These sources were chosen on the basis of brightness and
-proximity in declination to Pictor A.
-% XXX merge this with paragraph below
-
-To provide a basis for establishing the accuracy of the Pictor measurement we
-measured more sources.  Specifically, we choose sources from the Molonglo
-Reference Catalog \cite[MRC]{Large:1981p7798} that are within 5\arcdeg in
-declination of a common calibrator (J2331-416) and have a flux extrapolated
-from 408MHz greater than 10Jy assuming a power law spectral index of
--1.\footnote{Most radio sources in this band have power law spectra $S(\nu) =
-\left(\frac{\nu}{\nu_0}\right)^\alpha$.  The 5\arcdeg distance between source
-and calibrator was chosen as a balance between number of sources included and
-the known smoothness of the beam.   The average spectral index for radio
-sources in this band is $-0.8$.} This selection contains 62 sources in a narrow
-stripe that passes through the majority of the southern EoR fields, much of the
-galaxy and Centaurus A.
 
@@
 
+% XXX specific discussion of baseline weights to compensate for resolution effects for Pictor A
+% XXX need to elaborate on correcting for resolution effects for PicA.
+% XXX check paragraph below for relavant phrases
+Because Pictor A is resolved at the 20\% level on the longest (300m) East-West PAPER baselines, we 
+use per-baseline estimates of resolution weights to down-weight and correct for resolution effects.  To estimate
+resolution weights, we use the 90cm map of Pictor A presented in \citet{perley_et_al1997}.  Averaged over all
+the baselines in the array, the inclusion of resolution effects changed the measured flux by less than 5\%.
+
 \begin{figure}
@@
 Assuming a power law model for J2331-416 (33Jy $\alpha=-0.76$), we compute a
+% XXX I got these parameters for 2331: $S_{150}=31.9\ {\rm Jy}$, $\alpha=-0.69$ 
 bandpass gain.  After calibrating the raw 203 channel spectra with this
@@
 both PAPER and catalog data, shown in black on the same Figures. The values are
-given in Table \ref{tab:fits}.
+given in Table \ref{tab:fits}, and
+illustrated in Figure \ref{fig:src_spec}.
 
@@
 that the reported PAPER flux values are on the correct global scale.
+
+The data  include new measurements of Pictor A that are uncertain to 3.5\%,
+close to the level of the most precise higher frequency measurements by
+\citet{Wills:1975p9314}. Using these new measurements we update the spectral
+calibration model to an accuracy of 2.5\%. As validation of this method, we
+also measure a selection of 58 additional sources at the same Declination.
 

### 2013-04-24 ms.tex
More organization.  created sections "results and discussion" and "conclusion" and divided existing text among these.

@@
 
-In order to ensure that errors in
-the beam model did not skew our result, we chose a set of sources near in declination
-to Pictor A that would follow nearly identical tracks through the primary beam.
-A list of these 
-sources is given in Table \ref{tab:src_spec}. 
-These sources were chosen on the basis of brightness and
-proximity in declination to Pictor A.
-% XXX specific declination range
-% XXX merge this with paragraph below
-
-To provide a basis for establishing the accuracy of the Pictor measurement we
-measured more sources.  Specifically, we choose sources from the Molonglo
+To begin, we choose sources from the Molonglo
 Reference Catalog \cite[MRC]{Large:1981p7798} that are within 5\arcdeg in
@@
 galaxy and Centaurus A.
-
-% XXX equation for time-dependent beam amplitude times source flux for perceived flux density
+A list of these 
+sources is given in Table \ref{tab:src_spec}.
+
+For these sources, spectral data measured below XXX GHz were compiled from 
+the NASA/IPAC Extragalactic Database (NED)
+\footnote{\url{http://ned.ipac.caltech.edu/}}. Cross-matching radio sources
+between bands is made difficult by changes in resolution, spectral curvature,
+and resolved multi-scale structure.  For a small number of sources these
+problems can be ameliorated by inspection of the spectra, source names,
+coordinates,  and originating publications. However for a large sample of
+sources this becomes unwieldily and prone to error. Thus for the larger number
+of samples we make use of the Vollmer et al meta-catalog which takes pains to
+match multi-wavelength observations \citep{Vollmer:2010p6422}.
+% given the known source dimensions and spectral properties as well as telescope bandwidth and spatial resolutions.
 
@@
 represents a best estimate given the limitations of the beam model and flux calibration that were established
-up to this point.  To further improve these estimates, we derive an additional frequency-dependent gain parameter,
+up to this point, according to the equation:
+% XXX equation for time-dependent beam amplitude times source flux for perceived flux density
+To further improve these estimates, we derive an additional frequency-dependent gain parameter,
 smoothed on 10-MHz scales,
@@
 Finally,
-the flux scale is set
+an absolute flux scale is set
 by Monte Carlo fitting to a subset of sources, all of which are calibrated to
@@
 \end{figure*}
+
+\subsection{Observations}
 
@@
 
-% XXX incorporate
-We use data observed on JD2455747 
-from a 64-antenna single-polarization deployment of the 
-PAPER array in a minimum redundancy configuration that is more suited for imaging.  The details
-of these observations and their calibration are given in \citet{pober_et_al2013}.
-
 %COMPRESSION
-\textbf{Compression}\\
+\subsection{Data Compression}
 
@@
 %CALIBRATION
-\textbf{Per-Antenna Gain and Phase Calibration}\\
+\subsection{Per-Antenna Gain and Phase Calibration}
 
@@
 
-\textbf{Beamforming}\\
+\subsection{Beamforming}
 
@@
 %BANDPASS CALIBRATION
-\textbf{Spectral calibration}\\
+\subsection{Bandpass Calibration}
 \label{sec:Calibration}
@@
 
-\textbf{Catalogs}\\
-
-Data for prior comparison was pulled from two major sources. Catalog values for
-Pictor A, and the flux calibration sources were pulled directly from the
-NASA/IPAC Extragalactic Database (NED)
-\footnote{\url{http://ned.ipac.caltech.edu/}}. Cross-matching radio sources
-between bands is made difficult by changes in resolution, spectral curvature,
-and resolved multi-scale structure.  For a small number of sources these
-problems can be ameliorated by inspection of the spectra, source names,
-coordinates,  and originating publications. However for a large sample of
-sources this becomes unwieldily and prone to error. Thus for the larger number
-of samples we make use of the Vollmer et al meta-catalog which takes pains to
-match multi-wavelength observations \citep{Vollmer:2010p6422}.
-% given the known source dimensions and spectral properties as well as telescope bandwidth and spatial resolutions.
-
-\textbf{Flux Scale}\\
+\subsection{Approximating an Absolute Flux Scale}
 \label{sec:flux_scale}
@@
 
- \section{Spectral Results}
- \label{sec:fits}
-
-The primary purpose of this observation is to produce a high quality Pictor A
-% XXX need to coordinate "primary purpose" here with abstract and intro motivation
-spectrum. As a verification measure we have observed many other sources at the
-same declination for comparison against previous observations.  Our comparison
-metric will be the degree to which the PAPER data are consistent with previous
-observations,given a model and, if consistent, they improve on the precision of
-our spectral model parameters.
+\subsection{Fitting a Power-Law Model to Spectra}
+
+% XXX write this
 
@@
 
+\section{Results and Discussion}
+\label{sec:fits}
+
 %0008-421#
@@
 
- \section{Discussion and Conclusions}
+% XXX comparison with previous in-band results (danny 2011, williams 2012)
+
+ \section{Conclusion}
  \label{sec:Conclusion}
+
+% XXX adapt this paragraph to be a summary of the broad goals attained in this paper
+The primary purpose of this observation is to produce a high quality Pictor A
+% XXX need to coordinate "primary purpose" here with abstract and intro motivation
+spectrum. As a verification measure we have observed many other sources at the
+same declination for comparison against previous observations.  Our comparison
+metric will be the degree to which the PAPER data are consistent with previous
+observations,given a model and, if consistent, they improve on the precision of
+our spectral model parameters.
 
@@
 
-% XXX need more discussion
+% XXX looking to the future, what next
 

### 2013-04-24 ms.tex
Moved appendix into text.  switched order of spectral fitting and absolute flux calibration subsections

@@
 
+% XXX remove references to appendix
+
 \section{Introduction}
@@
 to use Pictor A for flux calibration, we felt it prudent to examine Pictor A directly.
+In this section, we describe ... % XXX
 
@@
 
+% XXX in this section, we describe the details of data analysis used ...
+% XXX connect to Parsons2010,2013, pober2013, stefan2012, jacobs2011? for similar basic pipeline.
+
 \begin{figure*}\centering
@@
 %$\pm$0.1 mHz from the fringe rate of the source in question.
+
+\subsubsection{Compensation for Resolution Effects in Pictor A}
 
@@
 % XXX I got these parameters for 2331: $S_{150}=31.9\ {\rm Jy}$, $\alpha=-0.69$ 
+% XXX forward reference section on fitting spectra for how this was derived for 2331
 bandpass gain.  After calibrating the raw 203 channel spectra with this
@@
 %should be corrected by the applied gain factor
-
-\subsection{Approximating an Absolute Flux Scale}
-\label{sec:flux_scale}
-
-At this stage each source flux is tied to a model fit on the catalog values of
-J2331-416. The accuracy of this fit and the implied uncertainty in the flux
-scale limits the accuracy of the PAPER measurements..  To refine the flux
-scale, we bootstrap a single global flux scale correction factor using 5
-sources selected for their brightness, spectral linearity and data
-availability\footnote{Calibration sources:
-2250-412,2331-416,2140-434,0007-446,0704-427}. To build a more complete
-spectral model we go beyond the data found in SPECFIND, using all spectral
-measurements below 2GHz found in the NED database.  These catalog measurements
-are primarily by Parkes, and Molonglo with the best precision coming from the
-Wills fluxes at 538 and 634 MHz (when available). Where error bars are not
-given, we assume uncertainty of 25\%.
-
-As described in the Appendix, we fit spectral index models for all sources
-(using catalog data) simultaneously with a global PAPER flux scale factor
-(using the PAPER data). We fit the model using a Markov Chain Monte Carlo
-sampler to sample the posterior probability of PAPER data ($SPAPER_{\nu}$) and
-catalog values ($Scat_{\nu}$) given a spectral index model for each source and
-a global flux scale factor ($g$) ($S_\PAPER^\textrm{calibrated} = g S_\PAPER$).
-The resulting flux scale distribution function is shown in Figure
-\ref{fig:gain}. The 76\% confidence limit on this flux scale, relative to the
-J2331-413 calibration, is  $-0.01 ^{+0.11}_{-0.17}$ dB, or a 3.24\%
-multiplicative error on every calibrated PAPER measurement.
-
-The calibrated spectra are plotted in Figures \ref{fig:srcs1},\ref{fig:srcs2},
-\& \ref{fig:srcs3} and the data are listed in Table \ref{tab:data}.  See the
-Appendix for details on this fitting procedure and definition of terms.  The
-resulting Pictor A spectrum ranges in precision from 6.5\% at 125MHz to 4.7\%
-at 185MHz. At least half of this error is due to uncertainty in the flux scale.  
-%\footnote{Of the 315 data points in this catalog, 7 fluxes points are negative.
-All three occur quite close to Centaurus A, which has large structure on degree scales in this region and is the brightest sources in the sky.
-These sources have been flagged and removed from further analysis.}
-
-%The Pictor track is calibrated to 2331-416 ($S_{150}=33.8$Jy,$\alpha=-0.76$) and the Hydra A track to 0231-126 ($S_{150}=21$Jy,$\alpha=-0.7$).  
-%    cal['0213-132'] = 21 * (fq/.150)**-0.7  
-%    cal['1932-464'] = 93.7 * (fq/.150)**-0.82 
-%    #cal['2331-416'] = 31.9 * (fq/.150)**-0.69
-%    cal['2331-416'] = 33.9 * (fq/.150)**-0.76
-%COMPARISON WITH DATA
 
@@
 illustrated in Figure \ref{fig:src_spec}.
+
+In this paper we estimate spectral model parameters and flux calibration in a
+Bayesian way by calculating and marginalizing the posterior probability of the
+data, past and present, given a spectral and instrumental model.   This method
+offers improved repeatability by specifying a single objective function that
+represents the quality of the model fit and naturally defines the errors on the
+parameters \citep{Hogg:2010p8759}.   See  \citet{Mackay:2003p9717}  or
+\citet{Sivia:2006p9736} for more on Bayesian analysis methods and an excellent
+astrophysical example by \cite{Press:1997p9783}.
+
+% XXX paragraph too remedial. digest
+In general an experiment measures data $D$ and given some model of the
+statistics of the measurement one usually assigns an error bar defining the
+probability of getting that data, given a model $M$.  Given all the new data,
+and prior data, there will be a new optimal set of model parameters $M$ with
+associated error bars.  In general, these error bars are a parameterization of
+a probability distribution function.  The pdf associated with the data often
+called the likelihood ($\mathcal{L}$), while the one corresponding the model
+error bars is the {\em posterior probability distribution}, $\Prob(M|D)$. They
+are related
+
+\[
+\Prob(M|D) = \frac{\mathcal{L}(D|M) \Prob(M)}{\Prob(D)}
+\] 
+by the factor $\frac{\Prob(M)}{\Prob(D)}$, the prior probability of the model
+$M$ (given past experiments) over the normalization factor, integrating over
+all models.  In general the posterior pdf depends on both the known relation
+between the model parameters and as well as correlations hidden within the
+data.
+
+% XXX too remedial.  digest to 1 senetence
+Direct calculation of the posterior is difficult, particularly the
+normalization factor, however there is a simple procedure for drawing samples
+from the posterior. In this paper we use a Markov Chain Monte Carlo sampler.
+Given any current location in parameter space, this algorithm draws a new set
+of parameters and computes the relative likelihood increase. If the probability
+difference is larger than a number drawn randomly from the set $(0:1]$, the
+jump is accepted ---a Metropolis-Hastings step. In the limit of an infinity of
+such steps, this process has been shown to converge on the true posterior
+distribution.  In practice it is run for a large number of steps until things
+appear to stabilize. The best fit model is the median of all the sampled
+parameter sets, while the volume containing a well defined fraction of samples
+sets the confidence limits.  The oft quoted ``1$\sigma$" probability level
+corresponding to a gaussian distribution contains 65\% of the samples. In
+practice the contours are not gaussian. Here we choose a slightly more
+conservative probability level of 76\%
+
+We fit a spectral power law to catalog values by sampling
+a (log) likelihood which assumes Gaussian measurement errors
+
+\[
+\logL = \sum_\nu{\frac{\left(S_\nu - S150\left(\frac{\nu}{150}\right)^\alpha\right)^2}{\Delta \textrm{SPAPER}_\nu}} \label{eq:catlogL}
+\]
+
+We estimate the confidence interval of the resulting parameters as the boundary
+enclosing 76\% of the samples. In the catalog we report both the upper and
+lower of these values for both parameters and plot the 2D contour to show the
+correlation of the two parameters. Many of these contours, the grey curves in
+Fig. \ref{fig:SI_contour_1}, are classic banana plots, displaying a non-linear
+correlation between the parameters.    In most cases the single contour
+adequately describes 2D posterior distribution.
+
+\begin{figure}[htbp]
+\includegraphics[width=0.49\textwidth]{plots/pic_trace_hist.png}
+\includegraphics[width=0.49\textwidth]{plots/1556-466_trace_hist.png}
+\caption{
+A more detailed view of the posterior probability distribution. On the left
+Pictor A, on the right 1556-466. Confidence contours range from 0.2 to 0.8.
+Compare with the contours for this source shown in Fig. \ref{fig:SI_contour_3}.
+As above, grey for  the fit to catalog data, black for joint catalog and PAPER
+fit.
+}
+\end{figure}
+
+\subsection{Approximating an Absolute Flux Scale}
+\label{sec:flux_scale}
+
+At this stage each source flux is tied to a model fit on the catalog values of
+J2331-416. The accuracy of this fit and the implied uncertainty in the flux
+scale limits the accuracy of the PAPER measurements..  To refine the flux
+scale, we bootstrap a single global flux scale correction factor using 5
+sources selected for their brightness, spectral linearity and data
+availability\footnote{Calibration sources:
+2250-412,2331-416,2140-434,0007-446,0704-427}. To build a more complete
+spectral model we go beyond the data found in SPECFIND, using all spectral
+measurements below 2GHz found in the NED database.  These catalog measurements
+are primarily by Parkes, and Molonglo with the best precision coming from the
+Wills fluxes at 538 and 634 MHz (when available). Where error bars are not
+given, we assume uncertainty of 25\%.
+
+As described in the Appendix, we fit spectral index models for all sources
+(using catalog data) simultaneously with a global PAPER flux scale factor
+(using the PAPER data). We fit the model using a Markov Chain Monte Carlo
+sampler to sample the posterior probability of PAPER data ($SPAPER_{\nu}$) and
+catalog values ($Scat_{\nu}$) given a spectral index model for each source and
+a global flux scale factor ($g$) ($S_\PAPER^\textrm{calibrated} = g S_\PAPER$).
+The resulting flux scale distribution function is shown in Figure
+\ref{fig:gain}. The 76\% confidence limit on this flux scale, relative to the
+J2331-413 calibration, is  $-0.01 ^{+0.11}_{-0.17}$ dB, or a 3.24\%
+multiplicative error on every calibrated PAPER measurement.
+
+The calibrated spectra are plotted in Figures \ref{fig:srcs1},\ref{fig:srcs2},
+\& \ref{fig:srcs3} and the data are listed in Table \ref{tab:data}.  See the
+Appendix for details on this fitting procedure and definition of terms.  The
+resulting Pictor A spectrum ranges in precision from 6.5\% at 125MHz to 4.7\%
+at 185MHz. At least half of this error is due to uncertainty in the flux scale.  
+%\footnote{Of the 315 data points in this catalog, 7 fluxes points are negative.
+All three occur quite close to Centaurus A, which has large structure on degree scales in this region and is the brightest sources in the sky.
+These sources have been flagged and removed from further analysis.}
+
+%The Pictor track is calibrated to 2331-416 ($S_{150}=33.8$Jy,$\alpha=-0.76$) and the Hydra A track to 0231-126 ($S_{150}=21$Jy,$\alpha=-0.7$).  
+%    cal['0213-132'] = 21 * (fq/.150)**-0.7  
+%    cal['1932-464'] = 93.7 * (fq/.150)**-0.82 
+%    #cal['2331-416'] = 31.9 * (fq/.150)**-0.69
+%    cal['2331-416'] = 33.9 * (fq/.150)**-0.76
+%COMPARISON WITH DATA
+
+% XXX connect with text above
+A single overall flux scale is computed in a similar way. However, here we add
+a single extra gain factor $g$ multiplying all PAPER measurements, and sum over
+several sources.
+
+\begin{align}
+\log\mathcal{L}_s &= \sum_{\nu}\frac{ (S_\textrm{cat}^{\nu}  - S_{150}  \left(\frac{\nu}{150}\right)^\alpha)^2}{2(\Delta S_\textrm{cat}^\nu)^2} +
+\frac{ (g*S_\PAPER^{\nu}  - S_{150}\left(\frac{\nu}{150}\right)^\alpha)^2}{2(\Delta S_\PAPER^\nu)^2}\\
+\log\mathcal{L} &= \sum_{s} \log\mathcal{L}_s
+\end{align}
+Another nice feature of the MCMC sampler is that each parameter sample is fully
+covariant with the others. To marginalize over the fitted flux and spectral
+index parameters and compute confidence limits on the gain parameter, we simply
+ignore them.
 
@@
 National Aeronautics and Space Administration.
-
-\section*{Appendix: Model Fitting}
-% XXX this should be in main body, not an appendix
-
-In this paper we estimate spectral model parameters and flux calibration in a
-Bayesian way by calculating and marginalizing the posterior probability of the
-data, past and present, given a spectral and instrumental model.   This method
-offers improved repeatability by specifying a single objective function that
-represents the quality of the model fit and naturally defines the errors on the
-parameters \citep{Hogg:2010p8759}.   See  \citet{Mackay:2003p9717}  or
-\citet{Sivia:2006p9736} for more on Bayesian analysis methods and an excellent
-astrophysical example by \cite{Press:1997p9783}.
-
-In general an experiment measures data $D$ and given some model of the
-statistics of the measurement one usually assigns an error bar defining the
-probability of getting that data, given a model $M$.  Given all the new data,
-and prior data, there will be a new optimal set of model parameters $M$ with
-associated error bars.  In general, these error bars are a parameterization of
-a probability distribution function.  The pdf associated with the data often
-called the likelihood ($\mathcal{L}$), while the one corresponding the model
-error bars is the {\em posterior probability distribution}, $\Prob(M|D)$. They
-are related
-
-\[
-\Prob(M|D) = \frac{\mathcal{L}(D|M) \Prob(M)}{\Prob(D)}
-\] 
-by the factor $\frac{\Prob(M)}{\Prob(D)}$, the prior probability of the model
-$M$ (given past experiments) over the normalization factor, integrating over
-all models.  In general the posterior pdf depends on both the known relation
-between the model parameters and as well as correlations hidden within the
-data.
-
-Direct calculation of the posterior is difficult, particularly the
-normalization factor, however there is a simple procedure for drawing samples
-from the posterior. In this paper we use a Markov Chain Monte Carlo sampler.
-Given any current location in parameter space, this algorithm draws a new set
-of parameters and computes the relative likelihood increase. If the probability
-difference is larger than a number drawn randomly from the set $(0:1]$, the
-jump is accepted ---a Metropolis-Hastings step. In the limit of an infinity of
-such steps, this process has been shown to converge on the true posterior
-distribution.  In practice it is run for a large number of steps until things
-appear to stabilize. The best fit model is the median of all the sampled
-parameter sets, while the volume containing a well defined fraction of samples
-sets the confidence limits.  The oft quoted ``1$\sigma$" probability level
-corresponding to a gaussian distribution contains 65\% of the samples. In
-practice the contours are not gaussian. Here we choose a slightly more
-conservative probability level of 76\%
-
-In \S \ref{sec:fits} we fit a spectral power law to catalog values by sampling
-a (log) likelihood which assumes Gaussian measurement errors
-
-\[
-\logL = \sum_\nu{\frac{\left(S_\nu - S150\left(\frac{\nu}{150}\right)^\alpha\right)^2}{\Delta \textrm{SPAPER}_\nu}} \label{eq:catlogL}
-\]
-
-We estimate the confidence interval of the resulting parameters as the boundary
-enclosing 76\% of the samples. In the catalog we report both the upper and
-lower of these values for both parameters and plot the 2D contour to show the
-correlation of the two parameters. Many of these contours, the grey curves in
-Fig. \ref{fig:SI_contour_1}, are classic banana plots, displaying a non-linear
-correlation between the parameters.    In most cases the single contour
-adequately describes 2D posterior distribution.
-
-\begin{figure}[htbp]
-\includegraphics[width=0.49\textwidth]{plots/pic_trace_hist.png}
-\includegraphics[width=0.49\textwidth]{plots/1556-466_trace_hist.png}
-\caption{
-A more detailed view of the posterior probability distribution. On the left
-Pictor A, on the right 1556-466. Confidence contours range from 0.2 to 0.8.
-Compare with the contours for this source shown in Fig. \ref{fig:SI_contour_3}.
-As above, grey for  the fit to catalog data, black for joint catalog and PAPER
-fit.
-}
-\end{figure}
-
-A single overall flux scale is computed in a similar way. However, here we add
-a single extra gain factor $g$ multiplying all PAPER measurements, and sum over
-several sources.
-
-\begin{align}
-\log\mathcal{L}_s &= \sum_{\nu}\frac{ (S_\textrm{cat}^{\nu}  - S_{150}  \left(\frac{\nu}{150}\right)^\alpha)^2}{2(\Delta S_\textrm{cat}^\nu)^2} +
-\frac{ (g*S_\PAPER^{\nu}  - S_{150}\left(\frac{\nu}{150}\right)^\alpha)^2}{2(\Delta S_\PAPER^\nu)^2}\\
-\log\mathcal{L} &= \sum_{s} \log\mathcal{L}_s
-\end{align}
-Another nice feature of the MCMC sampler is that each parameter sample is fully
-covariant with the others. To marginalize over the fitted flux and spectral
-index parameters and compute confidence limits on the gain parameter, we simply
-ignore them.
 

### 2013-04-29 plots/beam_cal_sim.py
adding beam cal simulation

@@ -1,0 +1,117 @@
+#! /usr/bin/env python
+"""
+Simulate a source track with the cal file beam, then use the bradley beam to calibrate it
+What is the error?
+"""
+
+
+import aipy as a, numpy as n, sys, os, ephem, optparse
+import matplotlib as mpl
+from pylab import *
+from scipy.interpolate import interp2d
+def dB(x):
+    return 10*n.log10(x)
+def idB(x):
+    return 10**(x/10.)
+o = optparse.OptionParser()
+o.set_usage('slice_plot.py [options]')
+o.set_description(__doc__)
+a.scripting.add_standard_options(o, cal=True, src=True,pol=True)
+o.add_option('--calsrc',
+    help='choose a src from the list to divide out')
+#o.add_option('--beamfile',
+#    help='CST beam file')
+opts,args = o.parse_args(sys.argv[1:])
+dt = 10 /(24*60.)
+srclist,cutoff,catalogs = a.scripting.parse_srcs(opts.src, opts.cat)
+cat = a.cal.get_catalog(opts.cal, srclist, cutoff, catalogs)
+assert(len(cat)>0)#make sure the catalog got found
+print "loading beam files ",
+print args
+files = args
+B = []
+print "freqs"
+print [f.split('_')[-1][:-4] for f in files]
+freqs = [float(f.split('_')[-1][:-4]) for f in files] #grab the frequencies in MHz
+freqs = n.array(freqs)/1e3 #convert to GHz to match with the cal file option freqs
+plotfreq = n.median(range(len(freqs))).astype(int)
+nfreqs = len(files)
+for f in files:
+    B.append(n.loadtxt(f,skiprows=2))
+#reshape the datas
+B = n.array(B)
+THETA = B[:,:,0]
+THETA.shape = (nfreqs,360,181)
+PHI = B[:,:,1]
+PHI.shape = (nfreqs,360,181)
+BEAM = idB(B[:,:,2])**2 #put the beam into linear units and square
+BEAM.shape = (nfreqs,360,181)
+BEAM /= BEAM[plotfreq,0,0]
+def bradleybeam(src):
+    azalt = src.get_crds('top',ncrd=2)
+    theta = (n.pi/2 - azalt[1])*180/n.pi #theta is the polar coord, zero at pole
[…]

### 2013-04-29 plots/beam_cal_sim.py
making the bradley files optional

@@ -26,33 +26,34 @@ dt = 10 /(24*60.)
 srclist,cutoff,catalogs = a.scripting.parse_srcs(opts.src, opts.cat)
 cat = a.cal.get_catalog(opts.cal, srclist, cutoff, catalogs)
 assert(len(cat)>0)#make sure the catalog got found
-print "loading beam files ",
-print args
-files = args
-B = []
-print "freqs"
-print [f.split('_')[-1][:-4] for f in files]
-freqs = [float(f.split('_')[-1][:-4]) for f in files] #grab the frequencies in MHz
-freqs = n.array(freqs)/1e3 #convert to GHz to match with the cal file option freqs
-plotfreq = n.median(range(len(freqs))).astype(int)
-nfreqs = len(files)
-for f in files:
-    B.append(n.loadtxt(f,skiprows=2))
-#reshape the datas
-B = n.array(B)
-THETA = B[:,:,0]
-THETA.shape = (nfreqs,360,181)
-PHI = B[:,:,1]
-PHI.shape = (nfreqs,360,181)
-BEAM = idB(B[:,:,2])**2 #put the beam into linear units and square
-BEAM.shape = (nfreqs,360,181)
-BEAM /= BEAM[plotfreq,0,0]
-def bradleybeam(src):
-    azalt = src.get_crds('top',ncrd=2)
-    theta = (n.pi/2 - azalt[1])*180/n.pi #theta is the polar coord, zero at pole
-    phi = azalt[0]*180/n.pi #phi is longitude
-    if opts.pol.startswith('y'): phi -= 90
-    return BEAM[:,floor(phi),floor(theta)]
+if len(args)>0
+    print "loading beam files ",
+    print args
+    files = args
+    B = []
+    print "freqs"
+    print [f.split('_')[-1][:-4] for f in files]
+    freqs = [float(f.split('_')[-1][:-4]) for f in files] #grab the frequencies in MHz
+    freqs = n.array(freqs)/1e3 #convert to GHz to match with the cal file option freqs
+    plotfreq = n.median(range(len(freqs))).astype(int)
+    nfreqs = len(files)
+    for f in files:
+        B.append(n.loadtxt(f,skiprows=2))
+    #reshape the datas
+    B = n.array(B)
+    THETA = B[:,:,0]
+    THETA.shape = (nfreqs,360,181)
+    PHI = B[:,:,1]
+    PHI.shape = (nfreqs,360,181)
[…]

### 2013-05-01 plots/beam_cal_sim.py
adding calculation of simulated dec dep gain, code cleanup, makes images with labels

@@ -26,7 +26,7 @@ dt = 10 /(24*60.)
 srclist,cutoff,catalogs = a.scripting.parse_srcs(opts.src, opts.cat)
 cat = a.cal.get_catalog(opts.cal, srclist, cutoff, catalogs)
 assert(len(cat)>0)#make sure the catalog got found
-if len(args)>0
+if len(args)>0:
     print "loading beam files ",
     print args
     files = args
@@ -54,6 +54,14 @@ if len(args)>0
         phi = azalt[0]*180/n.pi #phi is longitude
         if opts.pol.startswith('y'): phi -= 90
         return BEAM[:,floor(phi),floor(theta)]
+    def rotbradleybeam(src):
+        azalt = src.get_crds('top',ncrd=2)
+        theta = (n.pi/2 - azalt[1])*180/n.pi #theta is the polar coord, zero at pole
+        phi = azalt[0]*180/n.pi #phi is longitude
+        if opts.pol.startswith('y'): phi -= 90
+        phi -= 90
+        return BEAM[:,floor(phi),floor(theta)]
+        
 def rotbeam(src):
     xyz = src.get_crds('top')
     if opts.pol.startswith('x'):pol = 'y'
@@ -62,8 +70,13 @@ def rotbeam(src):
 def calbeam(src):
     xyz = src.get_crds('top')
     return aa[0].bm_response(xyz,pol=opts.pol[0]).squeeze()**2
-
-plotfreq = n.median(range(len(freqs))).astype(int)
+def ModelBeam(src):
+    return bradleybeam(src)
+def TrueBeam(src):
+    return rotbradleybeam(src)
+#    return calbeam(src)
+nfreqs = len(freqs)
+plotfreq = int(nfreqs/2)
 print "loading cal file"
 aa = a.cal.get_aa(opts.cal,freqs)
 cat.compute(aa)
@@ -73,46 +86,145 @@ subplot(211)
 pos = {}
 Abeam = {}
 Bbeam = {}
-figure(1)
+
+print "Beam model amplitudes at meridian"
 for src in cat:
-    pos[src] = []
-    Abeam[src] = []
-    Bbeam[src] = []
-    aa.date = aa.next_rising(cat[src])
+    aa.date = aa.next_transit(cat[src])
+    cat.compute(aa)
+    print "beamfreq=",aa.get_afreqs()[3]
+    print src,cat[src].get_crds('top',ncrd=2),
[…]

### 2013-05-01 plots/psa64_CSTbeam.py
adding cal file

@@ -1,0 +1,263 @@
+''' This is a calibration file for data collected at PAPER in Karoo, South Africa
+on JD 2455742 '''
+
+import aipy as a, numpy as n,glob,ephem
+import bm_prms as bm
+import generic_catalog
+import logging
+loglevel = logging.CRITICAL
+logging.basicConfig(level=loglevel)
+log = logging.getLogger('psa_null')
+log.setLevel(loglevel)
+
+prms = {
+    'loc': ('-30:43:17.5', '21:25:41.9'), # KAT, SA (GPS)
+    'antpos':{
+        0:[147.659407413, 336.269469733, 264.566180759],
+        1:[-120.566931266, -270.142735412, -201.208899961],
+        2:[175.483874,-282.046474,309.593714],
+        3:[-24.5939776529, -369.022493234, -35.9049669793],
+        #--------------------------------------------------------
+        4:[-135.977107,-65.373043,-223.715356],
+        5:[-184.222167454,  60.9256169154, -307.675312464],
+        7:[84.568610,-397.906007,151.703088],
+        6:[60.9037241018, 422.222408268, 116.124879563],
+        #--------------------------------------------------------
+        8:[148.405177,-231.475974,263.305593],
+        9:[-151.30695,-328.29684,-185.60087],
+        10:[-28.800063,-420.849441,-43.564604],
+        #11:[-180.112865,-190.297251,-301.062917],
+        11:[-178.169736505,-185.482180584,-315.619611243],
+        #--------------------------------------------------------
+        12:[161.032208592, 207.530151484, 286.703007713],
+        13:[-79.830818,266.416356,-122.828467],
+        14:[90.491568,406.666552,171.303074],
+        15:[136.833937217,-349.10409, 256.16691],
+        #========================================================
+	    16:[75.008275,-366.663944,135.807286],
+        17:[-170.082246,113.392564,-280.090332],
+        18:[-173.308984588, -52.5844630491, -289.495946419],
+        19:[35.6156894023, -76.4247822222, 68.8003235664],
+        #-------------------------------------------------------
+        20:[ 223.405495506, -111.371927382, 391.352958368],
[…]

### 2013-05-01 plots/beam_cal_sim.py
now calibrating to -44 declination

@@ -3,7 +3,7 @@
 Simulate a source track with the cal file beam, then use the bradley beam to calibrate it
 What is the error?
 """
-
+#./beam_cal_sim.py -C psa64_CSTbeam -s pic,2331-416,zen -pyy --cat=southern_sky_v3 --calsrc=2331-416 /Users/danny/Work/radio_astronomy/2010_beam/sdipole_05e_eg_ffx_*.txt
 
 import aipy as a, numpy as n, sys, os, ephem, optparse
 import matplotlib as mpl
@@ -94,6 +94,8 @@ for src in cat:
     print "beamfreq=",aa.get_afreqs()[3]
     print src,cat[src].get_crds('top',ncrd=2),
     print ModelBeam(cat[src])[3],TrueBeam(cat[src])[3]
+
+#old stuff
 if False:
     figure(1)
     for src in cat:
@@ -174,7 +176,6 @@ for i,src in enumerate(n.sort(cat.keys())[::-1]):
         cat.compute(aa)        
         src_xyz = cat[src].get_crds('top')
         if src_xyz[2]<0:break
-        #print src_xyz
         crds[src].append(src_xyz)
         g[:,i] += ModelBeam(cat[src]) * TrueBeam(cat[src])
         w[:,i] += ModelBeam(cat[src]) * ModelBeam(cat[src])
@@ -184,26 +185,21 @@ for i,src in enumerate(n.sort(cat.keys())[::-1]):
         times[src].append(t)
 
 g /= w
-#TODO add a pane to the weighted plot showing the un-weighted tracks
 figure()
 clf()
-print n.max(A['0_-40']),n.argmax(A['0_-40']),len(crds['0_-40'])#crds['0_-40'][n.argmax(A['0_-40'])]
-print n.max(A['0_-50']),n.argmax(A['0_-50']),len(crds['0_-50'])##crds['0_-50'][n.argmax(A['0_-50'])]
-
+caldec = 15
+print "calibrating to declination %d"%decs[caldec]
 for src in ['0_-40','0_-50']:
     t = n.array(times[src])
     t -= n.median(t)
     t *= 24
-    B_A = n.array(A[src]).copy()
-    B_M = n.array(B[src]).copy()
+    B_A = n.array(A[src])
+    B_M = n.array(B[src])
[…]

### 2013-05-01 plots/beam_cal_sim.py
added Jonnies beam

@@ -8,7 +8,7 @@ What is the error?
 import aipy as a, numpy as n, sys, os, ephem, optparse
 import matplotlib as mpl
 from pylab import *
-from scipy.interpolate import interp2d
+from glob import glob
 def dB(x):
     return 10*n.log10(x)
 def idB(x):
@@ -26,42 +26,45 @@ dt = 10 /(24*60.)
 srclist,cutoff,catalogs = a.scripting.parse_srcs(opts.src, opts.cat)
 cat = a.cal.get_catalog(opts.cal, srclist, cutoff, catalogs)
 assert(len(cat)>0)#make sure the catalog got found
-if len(args)>0:
-    print "loading beam files ",
-    print args
-    files = args
-    B = []
-    print "freqs"
-    print [f.split('_')[-1][:-4] for f in files]
-    freqs = [float(f.split('_')[-1][:-4]) for f in files] #grab the frequencies in MHz
-    freqs = n.array(freqs)/1e3 #convert to GHz to match with the cal file option freqs
-    plotfreq = n.median(range(len(freqs))).astype(int)
-    nfreqs = len(files)
-    for f in files:
-        B.append(n.loadtxt(f,skiprows=2))
-    #reshape the datas
-    B = n.array(B)
-    THETA = B[:,:,0]
-    THETA.shape = (nfreqs,360,181)
-    PHI = B[:,:,1]
-    PHI.shape = (nfreqs,360,181)
-    BEAM = idB(B[:,:,2])**2 #put the beam into linear units and square
-    BEAM.shape = (nfreqs,360,181)
-    BEAM /= BEAM[plotfreq,0,0]
-    def bradleybeam(src):
-        azalt = src.get_crds('top',ncrd=2)
-        theta = (n.pi/2 - azalt[1])*180/n.pi #theta is the polar coord, zero at pole
-        phi = azalt[0]*180/n.pi #phi is longitude
-        if opts.pol.startswith('y'): phi -= 90
-        return BEAM[:,floor(phi),floor(theta)]
-    def rotbradleybeam(src):
-        azalt = src.get_crds('top',ncrd=2)
-        theta = (n.pi/2 - azalt[1])*180/n.pi #theta is the polar coord, zero at pole
-        phi = azalt[0]*180/n.pi #phi is longitude
-        if opts.pol.startswith('y'): phi -= 90
[…]

### 2013-05-01 plots/beam_cal_sim.py
removing some old code

@@ -19,8 +19,6 @@ o.set_description(__doc__)
 a.scripting.add_standard_options(o, cal=True, src=True,pol=True)
 o.add_option('--calsrc',
     help='choose a src from the list to divide out')
-#o.add_option('--beamfile',
-#    help='CST beam file')
 opts,args = o.parse_args(sys.argv[1:])
 dt = 10 /(24*60.)
 srclist,cutoff,catalogs = a.scripting.parse_srcs(opts.src, opts.cat)
@@ -74,7 +72,7 @@ def calbeam(src):
     xyz = src.get_crds('top')
     return aa[0].bm_response(xyz,pol=opts.pol[0]).squeeze()**2
 def ModelBeam(src):
-    return bradleybeam(src)
+    return calbeam(src)
 def TrueBeam(src):
 #    return rotbradleybeam(src)
 #    return calbeam(src)
@@ -98,59 +96,6 @@ for src in cat:
     print "beamfreq=",aa.get_afreqs()[0]
     print src,cat[src].get_crds('top',ncrd=2),
     print ModelBeam(cat[src])[0],TrueBeam(cat[src])[0]
-
-#old stuff
-if False:
-    figure(1)
-    for src in cat:
-        pos[src] = []
-        Abeam[src] = []
-        Bbeam[src] = []
-        times = []
-        risetime = aa.next_rising(cat[src])
-        aa.date = risetime
-        print src
-        while(True):
-            t = aa.date
-            aa.set_ephemtime(t+dt)
-            cat.compute(aa)
-            src_xyz = cat[src].get_crds('top')
-            if src_xyz[2]<0:break
-            times.append(t-risetime)
-            src_angle = cat[src].get_crds('top',ncrd=2)
-            #print src_angle,bradleybeam(cat[src])[plotfreq],calbeam(cat[src])[plotfreq]
-            pos[src].append(src_angle)
-    #        Abeam[src].append(calbeam(cat[src]))
-    #        Bbeam[src].append(rotbeam(cat[src]))    
-            Abeam[src].append(bradleybeam(cat[src]))
-            Bbeam[src].append(rotbradleybeam(cat[src]))
-    
-    
-        pos[src] = n.array(pos[src])
-        Abeam[src] = n.array(Abeam[src])
-        Bbeam[src] = n.array(Bbeam[src])
-        times = n.array(times)*24 #time in hours
-        if src=='zen': color = '0.5'
[…]

### 2013-05-02 ms.tex
Edits about the beam gain with an incorrect conclusion about the error.

@@
 \begin{abstract}
-We present a first catalog of broad-band spectral measurements from the 
+We present a catalog of broad-band spectral measurements from the 
 Donald C. Backer Precision Array for Probing
@@
 of sources above XXX Jy to be accurate to 3.2\%.
+% DCJ 3.2% is just for Pictor A, and certainly not all PAPER measurements of sources above XXX Jy
 When combined with catalog data at other frequencies, these data constrain parameters of
@@
 the apparent flux scale that varies across the sky.
-This direction dependent gain is currently uncertain to 20\% or higher
+This direction dependent gain is currently uncertain to 10\% or higher
 % XXX 20% seems a bit grim.  Doesn't jonnie argue for 5 to 10% in his paper?
-\citep{Jacobs:2013p9713}, approximately matching the current level of uncertainty in catalogs.
+%XXX 20\% comes from the overall uncertainty between MWA and PAPER, part of which is also side lobes. 
+%	Jonnie's fluxes are dominated by the side lobes in the pgb16 data, the fluxes have a range of errors around 15 to 20%
+\citep{Pober:2012p8800}, and comprises a large fraction of the 20\% difference between current telescopes \citep{Jacobs:2013p9713}.
 
@@
 various higher frequency measurements with Parkes.  These data are typically
-uncertain to 10\% or higher and provide little coverage of the EoR band beyond
+uncertain to 20\% or higher and provide little coverage of the EoR band beyond
 a single narrow-band data point.
@@
 
+A method for decoupling uncertain fluxes from the uncertain beam has been
+described by \citet{Pober:2012p8800}. In simulation the method was able to
+achieve 3 to 10\% accuracy in measuring the primary beam, depending on the
+number of antennae and other variables. The Pober method emphasized the need
+for many repeated measurements of each alt-az pointing. Further investigation
+is under way to improve and implement this method and would be greatly aided by
+the availability of precise flux measurements unaffected by primary beam
+uncertainty.
+
+This paper reports a set of flux measurements where a primary beam
+model has not been used to estimate the flux, but instead are directly
+calibrated to a single calibrator making the track through the beam.
+
 % XXX elaborate on:
@@
 %particularly at southern declinations ($\delta<-20$\arcdeg). 
+% not sure where this went. -dcj
 
 % XXX remove PAPER specificity from below?
-For power-spectrum measurements, PAPER uses an antenna layout
-optimized to detect a small number of Fourier modes at high precision.  This ``maximum-redundancy''
-array configuration trades imaging dynamic range for power spectrum sensitivity \citep{Parsons2012a}.
-As such it is only able to easily distinguish the very brightest sources on the
-sky for setting the overall flux scale \citep{Parsons2013b}. 
-Of these, Pictor A is
-one of the most useful, being bright, minimally resolved, and far from
-confusing structure. 
-For this source the current best EoR band measurement
+EoR measurements in the southern sky have focused on the coldest regions where
+galactic foregrounds are minimal. With the majority of possible observing time falling on 
+RA=4h,Dec=-30. The brightest and least-resolved calibrator in this region is Pictor A 
+(5h19m49.1 -45d46m45.0). Pictor A is a nearby FR-II type radio galaxy 
+ similar to Cygnus A.  At $\sim$400Jy Pictor is bright and sufficiently distant from other 
+bright sources to make it eminently suitable as both a phase and flux calibrator. Its apparent
+size of $\sim$8\arcmin is smaller than the scales being probed by current EoR instruments , 
+making resolution effects, making it suitable for precision calibration.  However, 
+like most other sources, precise flux measurements in the EoR band are not available.
+The current best EoR band measurement
 is uncertain to 12\% and appears to imply spectral flattening in the EoR band
 \citep{Perley:1997p9312}.
+
 % XXX more background on pictor A
-
+%  added dcj
+%0518-458	 PKS, Pictor A	G	 25.93	 24.01	1		W	 0.0342	 23.63	 176.
 % XXX transition to the PAPER instrument
@@
 configuration to make deep power spectral integrations \citep{Parsons:2012a}.
+Though highly sensitive as a power spectrum instrument, the maximally redundant
+has a broad point spread function and is able to measure only the brightest sources,
+like Pictor A, for flux calibration purposes.  
 % XXX to calibrate these observations...
-
-A method for decoupling uncertain fluxes from the uncertain beam has been
-described by \citet{Pober:2012p8800}. In simulation the method was able to
-achieve 3 to 10\% accuracy in measuring the primary beam, depending on the
-number of antennae and other variables. The Pober method emphasized the need
-for many repeated measurements of each alt-az pointing. Further investigation
-is under way to improve and implement this method and would be greatly aided by
-the availability of precise flux measurements unaffected by primary beam
-uncertainty.
-
-This paper reports a set of flux measurements where a primary beam
-model has not been used to estimate the flux, but instead are directly
-calibrated to a single calibrator making the track through the beam.
+% added dcj
 
@@
 % XXX incorporate
-Given the shortcomings in the literature, and the necessity for PAPER power-spectrum analysis
+Given the large uncertainties in the literature, and the necessity for PAPER power-spectrum analysis
 to use Pictor A for flux calibration, we felt it prudent to examine Pictor A directly.
-In this section, we describe ... % XXX
-
-In order to ensure that 
-errors in
-the beam model did not skew our result, we chose a set of calibrator sources near in declination
-to Pictor A that would follow nearly identical tracks through the primary beam.
-This declination limit removes the necessity of correcting for a primary beam model and allows us to calculate more precise fluxes that provide a reference standard for future work.
-
-To begin, we choose sources from the Molonglo
+In this section, we describe how we use PAPER in its imaging configuration
+to measure Pictor A and a selection of known, bright sources in a 5\arcdeg strip centered
+on -45\arcdeg. % XXX
+
+As we've seen above, any one point in the primary beam might be uncertain to 10\% or more. However
+this is partially a function of the imaging mode. In \citet{Jacobs:2013p9837} several limitations were identified that
+exasperated the primary beam uncertainty.  First, in imaging each source flux is measured at just a few 
+points in the primary beam. As errors tend to vary across the beam, the uncertainty will tend to vary between sources.
+Here we have averaged over all possible positions making the uncertainty a function of the net uncertainty in the beam,
+and stabilizing the source-to-source variations in error bars. The second limitation identified also identified in \citet{Williams:2012p8768}
+was the increase of uncertainty towards the edge of the beam. To minimize our sensitivity to both beam and noise
+uncertainty, we weight the source track by an additional factor of the primary beam model.
+
+Algebraically, the apparent flux at alittude-azimuth position $\theta-\phi$,
+ is the true flux multiplied by the actual primary beam
+
+\[
+S_\textrm{apparent}(\theta,\phi) = B_A(\theta,\phi)  S
+\]
+
+Integrating over the full source track and weighting by our model primary beam, we estimate the spectrum
+
+\begin{align}
+S_\textrm{estimate} &=& \sum_t   \frac{\sum_\phi B_M(\theta,\phi) S_\textrm{apparent}(\theta,\phi) }{ \sum_\phi B^2_M(\theta,\phi)}
+S_\texrm{estimate} & =&  \frac{\sum_\phi B_M(\theta,\phi) B_A(\theta,\phi)}{ \sum_\phi B^2_M(\theta,\phi)} S
+\end{align}
+In the fully general case, an incompletely sampled track will have its own unique weight. In this case, where each track is fully sampled,
+ the only remaining independent variable is the source declination.
+\[
+g(\delta) = \frac{\sum_\phi B_M(\theta,\phi) B_A(\theta,\phi)}{ \sum_\phi B^2_M(\theta,\phi)}
+\label{eq:g}
+\]
+
+ \begin{figure}[htbp]
+\begin{center}
+\includgraphics[width=0.9\textwidth]{plots/model_weighted_beam_sim_track.png}
+\caption{\label{fig:beam_track_sim} Simulated model weighted beam track. }
+\label{default}
+\end{center}
+\end{figure}
+
+  \begin{figure}[htbp]
+\begin{center}
+\includgraphics[width=0.9\textwidth]{plots/model_weighted_beam_sim_track.png}
+\caption{\label{fig:beam_track_sim} Simulated model weighted beam track. }
+\label{default}
+\end{center}
+\end{figure}
+ We may simulate this integral by calculating $g$ for 
+similar, but not identical models. For example, consider the case where the true beam is the model beam 
+but rotated by 90 degrees ('y' instead of 'x').  As shown in Figure \ref{XXX}
+ tracks separated by 10\arcdeg declination differ by as much as 25\%. 
+However, looking at the weighted tracks, the portion inside the sum in Eq \ref{eq:g} (Figure \ref{fig:beam_track_sim}), 
+we see that  we see that over a good portion of the beam, these tracks are very similar.  Thus
+  the sum displays very little declination dependance (Figure \ref{XXX}), varying by a maximum of 0.7\% over 
+  the declination range -30 to -60. 
+   However this conclusion is limited by the accuracy of the simulation. To limit our susceptibility to possibly larger errors we limit our use of this
+  technique to with $\pm5$\arcdeg of Pictor A.
+
+Another implication of this simulation is that there will be a net bandpass common to each source. 
+We estimate this bandpass by nominating one source as a bandpass calibrator, dividing its integrated spectrum by a 
+spectral model, and applying these calibration coefficients to the rest of the sources. Note that this  
+only puts the measurements on a common flux scale within the PAPER band given the flux model
+chosen for the calibrator.  A flux scale extrapolated from many catalog values is calculated separately in \S \ref{sec:flux_scale}.
+
+%This limitation in declination allows us to use a single source to calibrate all the measurements without 
+%needing to transfer gain solutions across the sky using a beam model. By insisting that the tracks of all sources
+% overlap entirely with a common calibrator we are able to directly calibrate out the effective passband of
+% the primary beam. 
+%This allows us to make a more precise flux measurement that provides a reference standard for future work.
+
+We choose sources from the Molonglo
 Reference Catalog \cite[MRC]{Large:1981p7798} that are within 5\arcdeg in
@@
 -1.\footnote{Most radio sources in this band have power law spectra $S(\nu) =
-\left(\frac{\nu}{\nu_0}\right)^\alpha$.  The 5\arcdeg distance between source
-and calibrator was chosen as a balance between number of sources included and
-the known smoothness of the beam.   The average spectral index for radio
-sources in this band is $-0.8$.} This selection contains 62 sources in a narrow
+\left(\frac{\nu}{\nu_0}\right)^\alpha$. } This selection contains 62 sources in a narrow
 stripe that passes through the majority of the southern EoR fields, much of the
-galaxy and Centaurus A.
+galaxy and Centaurus A. This stripe in the broader context of the galactic plane
+is shown in Figure \ref{fig:error_map}.
 A list of these 
@@
 
-For these sources, spectral data measured below XXX GHz were compiled from 
+For these sources, spectral data measured below 2 GHz were compiled from 
 the NASA/IPAC Extragalactic Database (NED)
@@
 % given the known source dimensions and spectral properties as well as telescope bandwidth and spatial resolutions.
+
+The spectra reported here are measured by beam-forming, phasing the visibilities to
+the target location, and summing to produce a dynamic spectrum. The spectrum is then isolated
+from neighboring sources by filtering and averaged in the time domain.  Though we do not rely on
+the primary beam model to estimate flux, we do employ it here to down weight low SNR measurements.
+Each source track is paired with samples of a calibrator to build a calibrator spectrum with the same weighting
+and the same track through the primary beam.  This calibrator observation provides a spectral bandpass unique 
+to that particular cut through the beam.
+The expectation is that, since all sources at similar declinations follow similar tracks 
+through the PAPER beam, any errors present in the original measured spectra as a result of differences between
+the simulated and actual beam response should be absent in the ratio between source spectra, and therefore
+should be corrected by the applied gain factor.
 
@@
 This additional gain factor was applied to all measured spectra, including that
-of Pictor A.  The expectation is that, since all sources at similar declinations follow similar tracks 
-through the PAPER beam, any errors present in the original measured spectra as a result of differences between
-the simulated and actual beam response should be absent in the ratio between source spectra, and therefore
-should be corrected by the applied gain factor.
+of Pictor A.
 

### 2013-05-03 ms.tex
incremental: everything from Approach to (but not including) Results

@@
 \section{Approach}
-
+\label{sec:approach}
 % XXX incorporate
@@
 to measure Pictor A and a selection of known, bright sources in a 5\arcdeg strip centered
-on -45\arcdeg. % XXX
-
-As we've seen above, any one point in the primary beam might be uncertain to 10\% or more. However
-this is partially a function of the imaging mode. In \citet{Jacobs:2013p9837} several limitations were identified that
+on -45\arcdeg.
+
+ In \citet{Jacobs:2013p9837} several limitations were identified that
 exasperated the primary beam uncertainty.  First, in imaging each source flux is measured at just a few 
@@
 Here we have averaged over all possible positions making the uncertainty a function of the net uncertainty in the beam,
-and stabilizing the source-to-source variations in error bars. The second limitation identified also identified in \citet{Williams:2012p8768}
+and stabilizing the source-to-source variations in error bars. The second limitation, identified in \citet{Williams:2012p8768},
 was the increase of uncertainty towards the edge of the beam. To minimize our sensitivity to both beam and noise
@@
 
-Algebraically, the apparent flux at alittude-azimuth position $\theta-\phi$,
- is the true flux multiplied by the actual primary beam
+As PAPER is a drift scan instrument, each declination $\delta$ describes a distinct cut through the primary beam. Each source track
+provides a detailed measurement of the primary beam relative to the peak of the measured flux. However,
+a model $g(\delta)$ is still required to calibrate between declinations. This model will be effective over a range of declinations, but will diverge at
+some rate depending on the accuracy of the slope of the beam model, limiting our declination range ($\Delta \delta$).
+
+EQUATION FOR BEAM ERROR %XXX
+% \[
+% g(\alpha,\delta) = \frac{d B(\theta,\phi)}{d\delta} \Delta \delta 
+% \]
+Using our source tracks, we can measure the slope of the beam and compare with models over a range of angles
+
+EQUATION FOR BEAM ERROR ALONG SOURCE TRACK %XXX
+
+As we see in Figure XXX the model beam is able to predict the measured beam slope across a 5\arcdeg
+distance to within XXX\%.
 
 \[
-S_\textrm{apparent}(\theta,\phi) = B_A(\theta,\phi)  S
+B_M = B_M(\theta(t),\phi(t))\\
+\sim 0.02\\
+\Delta B /B_M= \Delta (S_p)/B^2_M \sim \Delta B_M \\
+(\Delta B - \Delta B_M)/B_M < 0.01
 \]
-
-Integrating over the full source track and weighting by our model primary beam, we estimate the spectrum
-
-\begin{align}
-S_\textrm{estimate} &=& \sum_t   \frac{\sum_\phi B_M(\theta,\phi) S_\textrm{apparent}(\theta,\phi) }{ \sum_\phi B^2_M(\theta,\phi)}
-S_\texrm{estimate} & =&  \frac{\sum_\phi B_M(\theta,\phi) B_A(\theta,\phi)}{ \sum_\phi B^2_M(\theta,\phi)} S
-\end{align}
-In the fully general case, an incompletely sampled track will have its own unique weight. In this case, where each track is fully sampled,
- the only remaining independent variable is the source declination.
-\[
-g(\delta) = \frac{\sum_\phi B_M(\theta,\phi) B_A(\theta,\phi)}{ \sum_\phi B^2_M(\theta,\phi)}
-\label{eq:g}
-\]
-
- \begin{figure}[htbp]
-\begin{center}
-\includgraphics[width=0.9\textwidth]{plots/model_weighted_beam_sim_track.png}
-\caption{\label{fig:beam_track_sim} Simulated model weighted beam track. }
-\label{default}
-\end{center}
-\end{figure}
-
-  \begin{figure}[htbp]
-\begin{center}
-\includgraphics[width=0.9\textwidth]{plots/model_weighted_beam_sim_track.png}
-\caption{\label{fig:beam_track_sim} Simulated model weighted beam track. }
-\label{default}
-\end{center}
-\end{figure}
- We may simulate this integral by calculating $g$ for 
-similar, but not identical models. For example, consider the case where the true beam is the model beam 
-but rotated by 90 degrees ('y' instead of 'x').  As shown in Figure \ref{XXX}
- tracks separated by 10\arcdeg declination differ by as much as 25\%. 
-However, looking at the weighted tracks, the portion inside the sum in Eq \ref{eq:g} (Figure \ref{fig:beam_track_sim}), 
-we see that  we see that over a good portion of the beam, these tracks are very similar.  Thus
-  the sum displays very little declination dependance (Figure \ref{XXX}), varying by a maximum of 0.7\% over 
-  the declination range -30 to -60. 
-   However this conclusion is limited by the accuracy of the simulation. To limit our susceptibility to possibly larger errors we limit our use of this
-  technique to with $\pm5$\arcdeg of Pictor A.
-
-Another implication of this simulation is that there will be a net bandpass common to each source. 
-We estimate this bandpass by nominating one source as a bandpass calibrator, dividing its integrated spectrum by a 
-spectral model, and applying these calibration coefficients to the rest of the sources. Note that this  
-only puts the measurements on a common flux scale within the PAPER band given the flux model
-chosen for the calibrator.  A flux scale extrapolated from many catalog values is calculated separately in \S \ref{sec:flux_scale}.
-
-%This limitation in declination allows us to use a single source to calibrate all the measurements without 
-%needing to transfer gain solutions across the sky using a beam model. By insisting that the tracks of all sources
-% overlap entirely with a common calibrator we are able to directly calibrate out the effective passband of
-% the primary beam. 
-%This allows us to make a more precise flux measurement that provides a reference standard for future work.
 
@@
 the target location, and summing to produce a dynamic spectrum. The spectrum is then isolated
-from neighboring sources by filtering and averaged in the time domain.  Though we do not rely on
-the primary beam model to estimate flux, we do employ it here to down weight low SNR measurements.
-Each source track is paired with samples of a calibrator to build a calibrator spectrum with the same weighting
-and the same track through the primary beam.  This calibrator observation provides a spectral bandpass unique 
-to that particular cut through the beam.
-The expectation is that, since all sources at similar declinations follow similar tracks 
-through the PAPER beam, any errors present in the original measured spectra as a result of differences between
-the simulated and actual beam response should be absent in the ratio between source spectra, and therefore
-should be corrected by the applied gain factor.
-
-To derive a source spectrum from each drift-scan source profile, we compute a weighted average using
-weights derived from a model of
-PAPER's primary beam response as an effective approximation of inverse-variance weighting
-\citep{pober_et_al2012}, and averaging over the time series for each source.  Each output source spectrum
-represents a best estimate given the limitations of the beam model and flux calibration that were established
-up to this point, according to the equation:
-% XXX equation for time-dependent beam amplitude times source flux for perceived flux density
-To further improve these estimates, we derive an additional frequency-dependent gain parameter,
-smoothed on 10-MHz scales,
-that brings the spectrum of J2331-416 into closest agreement with a power-law spectrum
-that represents the best fit to measurements below 1 GHz.
-This additional gain factor was applied to all measured spectra, including that
-of Pictor A.
-
-Finally,
-an absolute flux scale is set
-by Monte Carlo fitting to a subset of sources, all of which are calibrated to
-the Baars et al scale. 
-% XXX elaborate on this, more on Baars, less on MC
+from neighboring sources by filtering and averaged in the time domain.  This time average is 
+weighted by an additional factor of the PAPER's primary beam response 
+\citep{pober_et_al2012}.  
+\begin{align}
+S_\textrm{est} &= \frac{\sum_t B_M S_p}{\sum_t B^2_M}\\
+&= \frac{\sum_t B_M B}{\sum_t B^2_M} S\\ \label{eq:g}
+\end{align}
+
+which is an effective approximation of inverse-variance weighting. The pre factor in Eq \ref{eq:g} is identical for 
+sources at the same declination, and as we found above, diverges slowly from the model in the 10\arcdeg declination stripe.
+We estimate this spectral dependent gain for a calibrator (J2331-416) fitting a spectral index model to the
+ well-defined data points below 2GHz. This removes an overall offset.
+
+ Finally we average the spectra from a resolution of 400kHz to 10MHz bins, taking the standard deviation within these bins
+ for an estimate of the uncertainty.
+
+At this point we have a set of spectra that have been calibrated relative to each other to the best of our ability. Now 
+they must be put on a global flux scale. We also have only a limited estimate of our error from our intra-channel
+rms.  To address both points we fit for a global flux scale that incorporates data from many catalogs. These catalogs
+have all been set, as best as possible, to the Baars et al scale.  Using a Bayesian analysis we compute the 
+variation in the flux scale implied by comparing many sources to prior catalog. By including sources from across
+the declination range,the variation in this flux scale fit estimates the overall uncertainty in flux resulting from primary beam 
+or prior catalog uncertainty.  So though the final scale is calibrated to the Baars scale as extrapolated beyond its
+defined band, the error on the flux scale fully encapsulates the error resulting from this extrapolation.
 
@@
 \caption{Antenna position in the 64-antenna, minimum-redundancy PAPER array configuration at the Karoo Radio Observatory site in South Africa used for these observations.
-% XXX add brief summary of observations.
+Data was captured during July and October of 2011 on a single 'x' polarization over a band between 120 and 180 MHz.
 }\label{fig:antpos}
@@
 
+%I'm Confused.  These are describing a different ordering of steps. Must re-read compression script.
+
 %CALIBRATION
@@
 % XXX time-dependent calibration is critical.  modify paragraph below
-Quantization gain through the correlator was linearized \citep{parsons_et_al2008}.
+
 Measurements of ambient temperature versus time near the balun amplifier of a fiducial antenna and near
 receiver amplifiers were used to divide out the predicted gain variation versus temperature that these amplifiers
-are known to exhibit.  A predicted gain profile was drived using coefficients characterized in
+are known to exhibit.  A predicted gain profile was derived using coefficients characterized in
 laboratory measurements \citep{parashare_bradley2009} and
@@
 % XXX incorporate
-To measure the spectrum of each source, we begin by applying per-antenna phase and gain
-calibrations established via self-calibration.  We next remove
-the known dependence of amplifier gain and cable attenuation on ambient temperature 
-using measured temperature data and temperature coefficients that were characterized in
-laboratory measurements \citep{parashare_bradley2009} and confirmed 
-in field-measurements \citep{pober_et_al2012}.  For each source, we phase to the source 
-osition
-and sum over 
-all baselines greater than 20 wavelengths in length.
-A fringe-rate filter (see \citet{parsons_backer2009} and Appendix A in \citet{Parsons2013b})
-is applied to the resulting
-beam to suppress beam sidelobes where sources introduce variations that deviate more than 
-$\pm$0.1 mHz from the fringe rate of the source in question.
+%To measure the spectrum of each source, we begin by applying per-antenna phase and gain
+%calibrations established via self-calibration.  We next remove
+%the known dependence of amplifier gain and cable attenuation on ambient temperature 
+%using measured temperature data and temperature coefficients that were characterized in
+%laboratory measurements \citep{parashare_bradley2009} and confirmed 
+%in field-measurements \citep{pober_et_al2012}.  For each source, we phase to the source 
+%osition
+%and sum over 
+%all baselines greater than 20 wavelengths in length.
+%A fringe-rate filter (see \citet{parsons_backer2009} and Appendix A in \citet{Parsons2013b})
+%is applied to the resulting
+%beam to suppress beam sidelobes where sources introduce variations that deviate more than 
+%$\pm$0.1 mHz from the fringe rate of the source in question.
 
@@
 locations. A beam is formed by phasing baselines to the desired location and
-summing over baselines.  
+summing over baselines longer than 20 wavelengths.
 %Samples were only included if there was a calibrator sample within 5\arcdeg in altitude/azimuth.
@@
 
- These complex spectra are then delay-delay rate filtered to remove spectrally
-smooth sources far from phase center \citep{Parsons:2009p7859} (cf the LOFAR
+ These complex spectra are then fringe rate filtered to remove spectrally
+smooth sources that deviate more than $\pm$0.1mHz from the fringe rate of the source in question
+ \citep{Parsons:2009p7859} (cf the LOFAR
 de-mixing approach \cite{Offringa:2012p9691})  producing a time dependent
-spectrum. This is then averaged in time,  weighting by a model of the primary
-beam. This down-weighting, or multiplying by the primary beam, should be
-clearly distinguished from up-weighting, which we are at pains to avoid.
-Weighting by another factor of the primary beam is an effective approximation
-of inverse-variance weighting \citep{Pober:2012p8800} and reduces the
-contribution of noisy low elevation measurements.  The result is equivalent to
-a very long earth rotation synthesis image with a single image pixel. When
+spectrum with minimal side lobes. This is then averaged in time,  weighting by a model of the primary
+beam as discussed above.
+The result is equivalent to
+a very long earth rotation synthesis image with a single image pixel. The weighted
+contributions from each baseline are shown in Figure \ref{fig:uv_coverage}.When
 combined with the filtering it is a robust and simple method for measuring
@@
 \includegraphics[width=0.9\textwidth]{plots/PicA_Oct2011_uv_coverage.png}
-\caption{The effective uv coverage, showing the relative contributions of each baseline when beam-forming on Pictor over a 9.6 hour synthesis in the October observing session. \label{fig:uv_coverage}}
-% XXX unclear whether amplitudes include our model of Pic A, or are even actual data vs. weights
+\caption{The effective uv coverage of a 10MHz-wide spectrum bin, showing the relative contributions of each baseline when beam-forming on Pictor over a 9.6 hour synthesis in the October observing session.
+\label{fig:uv_coverage}}
+Not shown here are the weights interpolated from the Perley et al 330MHz map (Fig.
+\ref{fig:pic_perley}) used to recover the total integrated flux of Pic  which represent a few \% change on the longest baselines.
 \end{figure}
@@
 PAPER's 15\arcmin synthesized beam. However, given the high SNR of the
-observations, resolution effects are observers, in a slight decrease in flux on
-the longest ($\sim$300m) baselines. We account for this by weighting baselines
-in the beam form step according to a model of structure observed by
+observations, we see a 20\% drop in flux on the longest ($\sim$300m) baselines. 
+We account for this by weighting baselines
+in the beamform step according to a model of structure observed by
 \citet{Perley:1997p9312} at 330MHz, which they found to be consistent with
@@
 
-% XXX specific discussion of baseline weights to compensate for resolution effects for Pictor A
-% XXX need to elaborate on correcting for resolution effects for PicA.
-% XXX check paragraph below for relavant phrases
-Because Pictor A is resolved at the 20\% level on the longest (300m) East-West PAPER baselines, we 
-use per-baseline estimates of resolution weights to down-weight and correct for resolution effects.  To estimate
-resolution weights, we use the 90cm map of Pictor A presented in \citet{perley_et_al1997}.  Averaged over all
-the baselines in the array, the inclusion of resolution effects changed the measured flux by less than 5\%.
-
 \begin{figure}
@@
 indicates PAPER resolution at the 150MHz, dashed, the resolution at 185MHz.  To
-correct for the small residual structure in the PAPER measurements we
-interpolated the PAPER baselines in the uv plane. At the highest frequency this
-% XXX "interpolated" needs to be clarified
+correct for the small residual structure in the PAPER measurements we resampled
+the Perley image to the PAPER resolution and estimated the relative contribution
+ to each PAPER baseline.  At the highest frequency this
 led to a 3\% correction, at the lowest frequency, 0.6\%.
@@
 
-% XXX selection of calibrator sources
-
-The gain of each channel is the product of an overall instrumental passband and
-the spectral dependence of the primary beam in the direction of the source.
-Sources sharing the same track through the primary beam will have the same
-average spectral gain function resulting from frequency dependent primary beam
-attenuation.   We matched each measured source spectrum time sample to the
-nearest sample (in altitude/azimuth) of a calibrator source
-(J2331-416)\footnote{This source was chosen for the amount of data found in the
-literature and the apparent smoothness of the spectrum.}.  We then, average the
-% XXX clarify why one source used here, and more sources later 
-two matched data streams in time.  Since both tracks make the same slice
-through the primary beam, they will have the same average effective gain.
-Assuming a power law model for J2331-416 (33Jy $\alpha=-0.76$), we compute a
-% XXX I got these parameters for 2331: $S_{150}=31.9\ {\rm Jy}$, $\alpha=-0.69$ 
-% XXX forward reference section on fitting spectra for how this was derived for 2331
-bandpass gain.  After calibrating the raw 203 channel spectra with this
-bandpass, we average into 10MHz sub-bands between 120 and 180 MHz, computing
-the standard deviation as an estimate of the error.
+The resulting set of spectra were then calibrated to a model of J2331-416 to remove 
+the residual bandpass due to the net effect of the primary beam as discussed in \S \ref{sec:approach}. J2331-416 
+\footnote{Here we set the spectrum to $S_{150}=33$Jy, $\alpha=-0.76$} fit to measurements beolow 1GHz \citep{slee1995,kuhr_et_al1981,large_et_al1981,burgess_hunstead2006}.}
+was selected for its relatively high brightness, spectral smoothness and large quantity
+ of available catalog data. Each source track has a slightly different sample profile
+ resulting from different amounts of flagged data at each time and channel. To account
+ for these differences in the bandpass calibration we build a set of calibration tracks 
+ that match the tracks for each source. Calibration of each source then proceeds with
+ an optimally matched calibration spectrum.
+
+%The gain of each channel is the product of an overall instrumental passband and
+%the spectral dependence of the primary beam in the direction of the source.
+%Sources sharing the same track through the primary beam will have the same
+%average spectral gain function resulting from frequency dependent primary beam
+%attenuation.   We matched each measured source spectrum time sample to the
+%nearest sample (in altitude/azimuth) of a calibrator source
+%(J2331-416)\footnote{This source was chosen for the amount of data found in the
+%literature and the apparent smoothness of the spectrum.}.  We then, average the
+%% XXX clarify why one source used here, and more sources later 
+%two matched data streams in time.  Since both tracks make the same slice
+%through the primary beam, they will have the same average effective gain.
+%Assuming a power law model for J2331-416 (33Jy $\alpha=-0.76$), we compute a
+%% XXX I got these parameters for 2331: $S_{150}=31.9\ {\rm Jy}$, $\alpha=-0.69$ 
+%% XXX forward reference section on fitting spectra for how this was derived for 2331
+%bandpass gain.  After calibrating the raw 203 channel spectra with this
+%bandpass, we average into 10MHz sub-bands between 120 and 180 MHz, computing
+%the standard deviation as an estimate of the error.
 
@@
 
-% XXX write this
-
-To compare with observations at other frequencies we must assume a spectral
-model. The prevailing spectral model for low frequency radio sources is a
-single power law due to synchrotron emission, though curvature or other
-deviation from a power-law is not-uncommon.   To establish a baseline model, we
-fit a spectral model to prior catalog data from the spectrally and spatially
-cross-matched meta-catalog by \citet{Vollmer:2010p6422} using the MCMC method
-described in \S \ref{sec:flux_scale} and the Appendix. Confidence contours for
-these fits are shown in grey in Figs. \ref{fig:SI_contour_1} -
-\ref{fig:SI_contour_4}.  In general these are lower limits on the possible
-precision, as the Vollmer catalog emphasizes minimization of cross-match error
-but at the cost of excluding data points.  The fit is then performed again with
-both PAPER and catalog data, shown in black on the same Figures. The values are
-given in Table \ref{tab:fits}, and
-illustrated in Figure \ref{fig:src_spec}.
-
-In this paper we estimate spectral model parameters and flux calibration in a
+There is a variety of prior data at multiple wavelengths to which we want to calibrate
+and then compare our measurements.  Our method for doing both of these steps
+is to assume a basic spectral model relating the different catalog data points and
+fit for spectral model and gain parameters.
+
+We estimate spectral model parameters and flux calibration in a
 Bayesian way by calculating and marginalizing the posterior probability of the
-data, past and present, given a spectral and instrumental model.   This method
+catalog and new PAPER data.   This method
 offers improved repeatability by specifying a single objective function that
@@
 \citet{Sivia:2006p9736} for more on Bayesian analysis methods and an excellent
-astrophysical example by \cite{Press:1997p9783}.
-
-% XXX paragraph too remedial. digest
-In general an experiment measures data $D$ and given some model of the
-statistics of the measurement one usually assigns an error bar defining the
-probability of getting that data, given a model $M$.  Given all the new data,
-and prior data, there will be a new optimal set of model parameters $M$ with
-associated error bars.  In general, these error bars are a parameterization of
-a probability distribution function.  The pdf associated with the data often
-called the likelihood ($\mathcal{L}$), while the one corresponding the model
-error bars is the {\em posterior probability distribution}, $\Prob(M|D)$. They
-are related
-
-\[
-\Prob(M|D) = \frac{\mathcal{L}(D|M) \Prob(M)}{\Prob(D)}
-\] 
-by the factor $\frac{\Prob(M)}{\Prob(D)}$, the prior probability of the model
-$M$ (given past experiments) over the normalization factor, integrating over
-all models.  In general the posterior pdf depends on both the known relation
-between the model parameters and as well as correlations hidden within the
-data.
-
-% XXX too remedial.  digest to 1 senetence
-Direct calculation of the posterior is difficult, particularly the
-normalization factor, however there is a simple procedure for drawing samples
-from the posterior. In this paper we use a Markov Chain Monte Carlo sampler.
-Given any current location in parameter space, this algorithm draws a new set
-of parameters and computes the relative likelihood increase. If the probability
-difference is larger than a number drawn randomly from the set $(0:1]$, the
-jump is accepted ---a Metropolis-Hastings step. In the limit of an infinity of
-such steps, this process has been shown to converge on the true posterior
-distribution.  In practice it is run for a large number of steps until things
-appear to stabilize. The best fit model is the median of all the sampled
+astrophysical example by \cite{Press:1997p9783}. In brief, measurement errors
+are related to parameter model errors via the likelihood, which we can calculate, 
+and the posterior, which we cannot.  However, the posterior is theoretically
+well sampled by a Markov Chain Monte Carlo sampler, which selects parameter
+values at random, computes the likelihood of the model given the data and noise model,
+and accepts or rejects the step based on an outside decision factor unrelated to the data.
+
+Here we use the emcee sampler by \citet{Mackay:2003p9717} et al to generate chains of
+parameter values. The best fit model is the median of all the sampled
 parameter sets, while the volume containing a well defined fraction of samples
@@
 
-We fit a spectral power law to catalog values by sampling
-a (log) likelihood which assumes Gaussian measurement errors
+To model the relationship between different wavelengths we assume a single spectral index
+which is the prevailing spectral energy distribution at low frequencies, 
+though curvature or other
+deviation from a power-law is not-uncommon.
+
+When fitting models to the full catalog, we use the Vollmer et al
+catalog which has been optimally cross-matched at the expense of excluding more data points.
+Meanwhile, the gain fit used a small sample of
+sources with spectra which meet our calibration criteria: more precision data available,
+brighter than most sources in the sample and far from any possibly confusing areas of
+the sky. 
+By limiting ourselves to a small number of sources we are able to go include catalog points by hand,
+to avoid making the error of falsely including erroneously matched 
+data points but benefiting from some measurements not included.
+
+\subsection{Approximating an Absolute Flux Scale}
+\label{sec:flux_scale}
+
+At the output of the beam forming and bandpass calibration step, the flux scale
+ is tied to a model fit tp the catalog values of
+J2331-416. The accuracy of this fit, and the implied uncertainty in the flux
+scale, limits the accuracy of the PAPER measurements..  To refine the flux
+scale and estimate our flux scale uncertainty, we bootstrap a single global flux scale 
+correction factor using 5
+sources selected for their brightness, spectral linearity and data
+availability\footnote{Calibration sources:
+2250-412,2331-416,2140-434,0007-446,0704-427}. To build a more complete
+spectral model we go beyond the data found in Vollmer et al, including all spectral
+measurements below 2GHz found in the NED database \footnote{\url{ned.ipac.caltech.edu}: Accessed 1 April 2013}.  These catalog measurements
+are primarily by Parkes, and Molonglo with the best precision coming from the
+Wills fluxes at 538 and 634 MHz (when available). Where error bars are not
+given, we assume uncertainty of 25\%.
+
+Using the MCMC method we fit spectral index models to the catalog fluxes
+ simultaneously with a global PAPER flux scale factor using  an MCMC chain to calculate the log likelihood
+
+\begin{align}
+\log\mathcal{L}_s &= \sum_{\nu}\frac{ (S_\textrm{cat}^{\nu}  - S_{150}  \left(\frac{\nu}{150}\right)^\alpha)^2}{2(\Delta S_\textrm{cat}^\nu)^2} +
+\frac{ (g*S_\PAPER^{\nu}  - S_{150}\left(\frac{\nu}{150}\right)^\alpha)^2}{2(\Delta S_\PAPER^\nu)^2}\\
+\log\mathcal{L} &= \sum_{s} \log\mathcal{L}_s
+\end{align}
+
+which samples the posterior probability of PAPER data ($SPAPER_{\nu}$) and
+catalog values ($Scat_{\nu}$) given a spectral index model for each source and
+a global flux scale factor ($g$) ($S_\PAPER^\textrm{calibrated} = g S_\PAPER$).
+Marginalizing over the fitted flux scales, we find the resulting flux scale distribution function which is shown in Figure
+\ref{fig:gain}. The 76\% confidence limit on this flux scale, relative to the
+J2331-413 calibration, is  $-0.01 ^{+0.11}_{-0.17}$ dB, or a 3.24\%
+multiplicative error on every calibrated PAPER measurement.  These errors are added, in quadrature,
+to the errors in the PAPER spectra.
+
+These calibrated spectra are plotted in Figures \ref{fig:srcs1},\ref{fig:srcs2},
+\& \ref{fig:srcs3} and the data are listed in Table \ref{tab:data}.  The
+resulting Pictor A spectrum ranges in precision from 6.5\% at 125MHz to 4.7\%
+at 185MHz. At least half of this error is due to uncertainty in the flux scale.
+
+%The Pictor track is calibrated to 2331-416 ($S_{150}=33.8$Jy,$\alpha=-0.76$) and the Hydra A track to 0231-126 ($S_{150}=21$Jy,$\alpha=-0.7$).  
+%    cal['0213-132'] = 21 * (fq/.150)**-0.7  
+%    cal['1932-464'] = 93.7 * (fq/.150)**-0.82 
+%    #cal['2331-416'] = 31.9 * (fq/.150)**-0.69
+%    cal['2331-416'] = 33.9 * (fq/.150)**-0.76
+%COMPARISON WITH DATA
+
+\subsection{Fitting Spectral Models}
+\label{sec:fitting_models}
+
+Finally we compare all of our  calibrated spectra to catalog measurements. Our method
+will be to first establish a best fit model to existing data, then add the PAPER data
+to the fit, and assess the degree to which the PAPER data is supported by prior measurements, or the reverse
+the degree to which PAPER offers an improvement in our knowledge of the spectrum.
+
+ To establish the baseline model, we
+fit a spectral model to catalog data from the spectrally and spatially
+cross-matched meta-catalog by \citet{Vollmer:2010p6422} using the
+ (log) likelihood which assumes Gaussian measurement errors
 
 \[
-\logL = \sum_\nu{\frac{\left(S_\nu - S150\left(\frac{\nu}{150}\right)^\alpha\right)^2}{\Delta \textrm{SPAPER}_\nu}} \label{eq:catlogL}
+\logL = \sum_\nu{\frac{\left(S_\nu - S_{150}\left(\frac{\nu}{150}\right)^\alpha\right)^2}{\Delta S_\nu} \label{eq:catlogL}
 \]
@@
 adequately describes 2D posterior distribution.
+
+Confidence contours for
+the complete set are shown in grey in Figs. \ref{fig:SI_contour_1} -
+\ref{fig:SI_contour_4}.  In general these are lower limits on the possible
+precision, as the Vollmer catalog emphasizes minimization of cross-match error
+but at the cost of excluding data points.  The fit is then performed again with
+both PAPER and catalog data, shown in black on the same Figures. The values are
+given in Table \ref{tab:fits}, and
+illustrated in Figure \ref{fig:src_spec}.
 
@@
 \end{figure}
-
-\subsection{Approximating an Absolute Flux Scale}
-\label{sec:flux_scale}
-
-At this stage each source flux is tied to a model fit on the catalog values of
-J2331-416. The accuracy of this fit and the implied uncertainty in the flux
-scale limits the accuracy of the PAPER measurements..  To refine the flux
-scale, we bootstrap a single global flux scale correction factor using 5
-sources selected for their brightness, spectral linearity and data
-availability\footnote{Calibration sources:
-2250-412,2331-416,2140-434,0007-446,0704-427}. To build a more complete
-spectral model we go beyond the data found in SPECFIND, using all spectral
-measurements below 2GHz found in the NED database.  These catalog measurements
-are primarily by Parkes, and Molonglo with the best precision coming from the
-Wills fluxes at 538 and 634 MHz (when available). Where error bars are not
-given, we assume uncertainty of 25\%.
-
-As described in the Appendix, we fit spectral index models for all sources
-(using catalog data) simultaneously with a global PAPER flux scale factor
-(using the PAPER data). We fit the model using a Markov Chain Monte Carlo
-sampler to sample the posterior probability of PAPER data ($SPAPER_{\nu}$) and
-catalog values ($Scat_{\nu}$) given a spectral index model for each source and
-a global flux scale factor ($g$) ($S_\PAPER^\textrm{calibrated} = g S_\PAPER$).
-The resulting flux scale distribution function is shown in Figure
-\ref{fig:gain}. The 76\% confidence limit on this flux scale, relative to the
-J2331-413 calibration, is  $-0.01 ^{+0.11}_{-0.17}$ dB, or a 3.24\%
-multiplicative error on every calibrated PAPER measurement.
-
-The calibrated spectra are plotted in Figures \ref{fig:srcs1},\ref{fig:srcs2},
-\& \ref{fig:srcs3} and the data are listed in Table \ref{tab:data}.  See the
-Appendix for details on this fitting procedure and definition of terms.  The
-resulting Pictor A spectrum ranges in precision from 6.5\% at 125MHz to 4.7\%
-at 185MHz. At least half of this error is due to uncertainty in the flux scale.  
-%\footnote{Of the 315 data points in this catalog, 7 fluxes points are negative.
-All three occur quite close to Centaurus A, which has large structure on degree scales in this region and is the brightest sources in the sky.
-These sources have been flagged and removed from further analysis.}
-
-%The Pictor track is calibrated to 2331-416 ($S_{150}=33.8$Jy,$\alpha=-0.76$) and the Hydra A track to 0231-126 ($S_{150}=21$Jy,$\alpha=-0.7$).  
-%    cal['0213-132'] = 21 * (fq/.150)**-0.7  
-%    cal['1932-464'] = 93.7 * (fq/.150)**-0.82 
-%    #cal['2331-416'] = 31.9 * (fq/.150)**-0.69
-%    cal['2331-416'] = 33.9 * (fq/.150)**-0.76
-%COMPARISON WITH DATA
-
-% XXX connect with text above
-A single overall flux scale is computed in a similar way. However, here we add
-a single extra gain factor $g$ multiplying all PAPER measurements, and sum over
-several sources.
-
-\begin{align}
-\log\mathcal{L}_s &= \sum_{\nu}\frac{ (S_\textrm{cat}^{\nu}  - S_{150}  \left(\frac{\nu}{150}\right)^\alpha)^2}{2(\Delta S_\textrm{cat}^\nu)^2} +
-\frac{ (g*S_\PAPER^{\nu}  - S_{150}\left(\frac{\nu}{150}\right)^\alpha)^2}{2(\Delta S_\PAPER^\nu)^2}\\
-\log\mathcal{L} &= \sum_{s} \log\mathcal{L}_s
-\end{align}
-Another nice feature of the MCMC sampler is that each parameter sample is fully
-covariant with the others. To marginalize over the fitted flux and spectral
-index parameters and compute confidence limits on the gain parameter, we simply
-ignore them.
+% XXX paragraph too remedial. digest
+%In general an experiment measures data $D$ and given some model of the
+%statistics of the measurement one usually assigns an error bar defining the
+%probability of getting that data, given a model $M$.  Given all the new data,
+%and prior data, there will be a new optimal set of model parameters $M$ with
+%associated error bars.  In general, these error bars are a parameterization of
+%a probability distribution function.  The pdf associated with the data often
+%called the likelihood ($\mathcal{L}$), while the one corresponding the model
+%error bars is the {\em posterior probability distribution}, $\Prob(M|D)$. They
+%are related
+%
+%\[
+%\Prob(M|D) = \frac{\mathcal{L}(D|M) \Prob(M)}{\Prob(D)}
+%\] 
+%by the factor $\frac{\Prob(M)}{\Prob(D)}$, the prior probability of the model
+%$M$ (given past experiments) over the normalization factor, integrating over
+%all models.  In general the posterior pdf depends on both the known relation
+%between the model parameters and as well as correlations hidden within the
+%data.  
+%
+%% XXX too remedial.  digest to 1 senetence
+%Direct calculation of the posterior is difficult, particularly the
+%normalization factor, however there is a simple procedure for drawing samples
+%from the posterior. In this paper we use a Markov Chain Monte Carlo sampler.
+%Given any current location in parameter space, this algorithm draws a new set
+%of parameters and computes the relative likelihood increase. If the probability
+%difference is larger than a number drawn randomly from the set $(0:1]$, the
+%jump is accepted ---a Metropolis-Hastings step. In the limit of an infinity of
+%such steps, this process has been shown to converge on the true posterior
+%distribution.  In practice it is run for a large number of steps until things
+%appear to stabilize.
 

### 2013-05-06 ms.tex
Rounding out text edits in Discussion and Conclusions

@@
 %CALIBRATION
-\subsection{Per-Antenna Gain and Phase Calibration}
+\subsection{Per-Antenna Gain Calibration}
 
@@
 
-% XXX time-dependent calibration is critical.  modify paragraph below
-
+Small gain variations between antennae and over time introduce significant systematic effects which degrade 
+instrument performance. Temporal variations are dominated by changes in ambient temperature. 
 Measurements of ambient temperature versus time near the balun amplifier of a fiducial antenna and near
@@
 
-Antenna delays and amplitudes were found by fitting a point source visibility
+Matching of relative gains and phases between antenna was done by fitting a per-antenna complex gain to portions
+of data which have easily modeled sky. 
+This calibration is only relative between antennae, absolute flux calibration
+comes after time and frequency averaging in  \S \ref{sec:flux_scale}.   
+The antenna delays and amplitudes were found by fitting a point source visibility
 model to Centaurus A, Pictor A, and Fornax A.  Each source is imperfectly
@@
 %is an effective approximation of inverse-variance weighting \citep{pober_et_al2011}.
-
-% XXX exclusion of minimum uv spacing?
 
@@
 the residual bandpass due to the net effect of the primary beam as discussed in \S \ref{sec:approach}. J2331-416 
-\footnote{Here we set the spectrum to $S_{150}=33$Jy, $\alpha=-0.76$} fit to measurements beolow 1GHz \citep{slee1995,kuhr_et_al1981,large_et_al1981,burgess_hunstead2006}.}
+\footnote{Here we set the spectrum to $S_{150}=33$Jy, $\alpha=-0.76$} fit to measurements beolow 1GHz \citep{slee1995,kuhr_et_al1981,large_et_al1981,burgess_hunstead2006}.
 was selected for its relatively high brightness, spectral smoothness and large quantity
@@
 
-\[
-\logL = \sum_\nu{\frac{\left(S_\nu - S_{150}\left(\frac{\nu}{150}\right)^\alpha\right)^2}{\Delta S_\nu} \label{eq:catlogL}
-\]
+\begin{equation}
+\logL = \sum_\nu{\frac{\left(S_\nu - S_{150}\left(\frac{\nu}{150}\right)^\alpha\right)^2}{\Delta S_\nu} }
+%\label{eq:catlogL}
+\end{equation}
 
@@
 \end{figure}
-% XXX paragraph too remedial. digest
-%In general an experiment measures data $D$ and given some model of the
-%statistics of the measurement one usually assigns an error bar defining the
-%probability of getting that data, given a model $M$.  Given all the new data,
-%and prior data, there will be a new optimal set of model parameters $M$ with
-%associated error bars.  In general, these error bars are a parameterization of
-%a probability distribution function.  The pdf associated with the data often
-%called the likelihood ($\mathcal{L}$), while the one corresponding the model
-%error bars is the {\em posterior probability distribution}, $\Prob(M|D)$. They
-%are related
-%
-%\[
-%\Prob(M|D) = \frac{\mathcal{L}(D|M) \Prob(M)}{\Prob(D)}
-%\] 
-%by the factor $\frac{\Prob(M)}{\Prob(D)}$, the prior probability of the model
-%$M$ (given past experiments) over the normalization factor, integrating over
-%all models.  In general the posterior pdf depends on both the known relation
-%between the model parameters and as well as correlations hidden within the
-%data.  
-%
-%% XXX too remedial.  digest to 1 senetence
-%Direct calculation of the posterior is difficult, particularly the
-%normalization factor, however there is a simple procedure for drawing samples
-%from the posterior. In this paper we use a Markov Chain Monte Carlo sampler.
-%Given any current location in parameter space, this algorithm draws a new set
-%of parameters and computes the relative likelihood increase. If the probability
-%difference is larger than a number drawn randomly from the set $(0:1]$, the
-%jump is accepted ---a Metropolis-Hastings step. In the limit of an infinity of
-%such steps, this process has been shown to converge on the true posterior
-%distribution.  In practice it is run for a large number of steps until things
-%appear to stabilize.
 
@@
 \end{align}
-% XXX This equation is yucky
 
@@
 confirmation.  The flux model is $S150=$388 $\pm$ 9.4Jy, $\alpha=-0.77\pm0.02$.
-% XXX need more detail here.  This is the crux of what is done.
 The combination of several independent PAPER data points near 150MHz with
@@
 near 600MHz which are accurate to 2\% and the five PAPER measurements, which
-are accurate to ~5\%.
+are accurate to ~5\%.  This error estimate includes an estimate of accuracy of the overall flux scale,
+as well as the source-source variation due to primary beam errors.
 
 % XXX comparison with previous in-band results (danny 2011, williams 2012)
+% work TODO
 
@@
 
-% XXX adapt this paragraph to be a summary of the broad goals attained in this paper
-The primary purpose of this observation is to produce a high quality Pictor A
-% XXX need to coordinate "primary purpose" here with abstract and intro motivation
-spectrum. As a verification measure we have observed many other sources at the
-same declination for comparison against previous observations.  Our comparison
-metric will be the degree to which the PAPER data are consistent with previous
-observations,given a model and, if consistent, they improve on the precision of
-our spectral model parameters.
-
-Direct measurements of the Pictor A spectrum are key to correctly setting the
-flux scale of PAPER and other EoR experiments. Existing EoR band measurements
+Here we have provided a measurement of Pictor A with enough precision to confirm
+a highly linear spectral index between 150 and 600MHz. We then used the same
+filtered beam form method to measure the spectra of bright sources with similar
+primary beam response. This primary beam limit is based on our measurements 
+of the primary beam along slices of constant declination.
+
+The measurements provided
+here are the first, calibrated, broad-band spectra to cover the EoR band. Existing EoR band measurements
 are accurate to 20\% implying a 40\% uncertainty in the absolute power spectrum
-level.  Here we have provided new measurements of Pictor A that are accurate to
-2.4\%;  388 $\pm$ 9.4Jy on the \citet{Baars:1977p9678} scale. The PAPER
-measurement has a precision of $<$1\%; the majority of the uncertainty comes in
-setting the absolute flux scale from prior data.
-
-We also take advantage of multiple PAPER observations to measure the next  61
-brightest, previously cataloged, sources. These sources are distributed over
-the full 24 hours of Right Ascension coverage but are within 5 degrees
+level.  The Pictor A spectrum here is shown to be accurate to 
+$\sim$5\%, a factor of 5 improvement over previous measurements.
+
+This uncertainty includes the 
+variation in each PAPER measurement ($\sim$1\%), variation between sources and the errors resulting
+from extrapolating the \citet{Baars:1977p9678} scale beyond its original range. These last
+two are found simultaneously by fitting the spectral extrapolations of several flux calibrators
+at once and account for the the majority of the error. Though past measurements suggested the possibility
+of spectral curvature below 200MHz we have found no evidence for this.  With these measurements we are able 
+to confirm single spectral index model for Pictor between 120MHz and 600MHz.
+
+A set of  61 verification sources were selected to be bright, previously cataloged
+and  distributed over
+the full 24 hours of Right Ascension coverage but only within 5 degrees
 declination of Pictor A.  Using a Bayesian analysis we conclude that most of
 these are consistent with previous measurements and provide useful new
-constraints. However, in the remainder, the simple spectral model fails to
+constraints. However, in a small remainder, the simple spectral model fails to
 adequately describe the data. In most cases the proximity to bright or extended
@@
 
-The data  include new measurements of Pictor A that are uncertain to 3.5\%,
-close to the level of the most precise higher frequency measurements by
-\citet{Wills:1975p9314}. Using these new measurements we update the spectral
-calibration model to an accuracy of 2.5\%. As validation of this method, we
-also measure a selection of 58 additional sources at the same Declination.
-
-% XXX looking to the future, what next
+Direct measurements of the Pictor A spectrum are key to correctly setting the
+flux scale of PAPER, MWA and future EoR experiments like the Hydrogen Epoch of Reionization Array (HERA).
+These spectra provide tighter constraints on many of the EoR band fluxes, while
+limiting the pernicious affect of primary beam uncertainty.  Future work will use these
+fluxes to further  refine the primary beam models of these experiments which is crucial to properly reconstructing
+both image and power spectrum flux.
 

### 2013-05-13 ms.tex
updating to latest cal

@@
 Pat Klima\altaffilmark{5},
-Dave H. E. MacMahon\altaffilmark{8},
+Dave H. E. MacMahon\altaffilmark{8}
 Jason R. Manley\altaffilmark{9},
@@
 
-% XXX elaborate on:
-%However, catalog source fluxes at 150MHz are also inaccurate to the 20\% level,
-%particularly at southern declinations ($\delta<-20$\arcdeg). 
-% not sure where this went. -dcj
-
-% XXX remove PAPER specificity from below?
 EoR measurements in the southern sky have focused on the coldest regions where
@@
 
-% XXX more background on pictor A
-%  added dcj
 %0518-458	 PKS, Pictor A	G	 25.93	 24.01	1		W	 0.0342	 23.63	 176.
@@
 configuration to make deep power spectral integrations \citep{Parsons:2012a}.
-Though highly sensitive as a power spectrum instrument, the maximally redundant
-has a broad point spread function and is able to measure only the brightest sources,
-like Pictor A, for flux calibration purposes.  
-% XXX to calibrate these observations...
-% added dcj
+Though highly sensitive as a power spectrum instrument, the maximally redundant array 
+has a broad point spread function in the image domain. This severely limits the number 
+of sources which may be used for flux calibration. Drift scanning across the sky with a 45\arcdeg FWHM
+primary beam there are very few unresolved, bright sources which are far from the galactic plane. 
+Pictor A is bright and well enough separated from other emission to dominate the visibilities for a good fraction of
+the EoR observing season, making it an ideal flux calibrator.
 
@@
 \label{sec:approach}
-% XXX incorporate
 Given the large uncertainties in the literature, and the necessity for PAPER power-spectrum analysis
@@
 
-As PAPER is a drift scan instrument, each declination $\delta$ describes a distinct cut through the primary beam. Each source track
-provides a detailed measurement of the primary beam relative to the peak of the measured flux. However,
+As PAPER is a drift scan instrument, each declination $\delta$ describes a distinct cut through the primary beam. These cuts
+provide a detailed measurement of the primary beam relative to the peak of the trace, however,
 a model $g(\delta)$ is still required to calibrate between declinations. This model will be effective over a range of declinations, but will diverge at
-some rate depending on the accuracy of the slope of the beam model, limiting our declination range ($\Delta \delta$).
-
-EQUATION FOR BEAM ERROR %XXX
-% \[
-% g(\alpha,\delta) = \frac{d B(\theta,\phi)}{d\delta} \Delta \delta 
-% \]
-Using our source tracks, we can measure the slope of the beam and compare with models over a range of angles
-
-EQUATION FOR BEAM ERROR ALONG SOURCE TRACK %XXX
-
-As we see in Figure XXX the model beam is able to predict the measured beam slope across a 5\arcdeg
-distance to within XXX\%.
+some rate depending on the accuracy with which the model describes the slope.  As an estimate of the extrapolated 
+beam amplitude we fit the slope of our Pictor A source track and compute the amplitude extrapolated over our fiducial
+stripe width of 5\arcdeg.
 
 \[
-B_M = B_M(\theta(t),\phi(t))\\
-\sim 0.02\\
-\Delta B /B_M= \Delta (S_p)/B^2_M \sim \Delta B_M \\
-(\Delta B - \Delta B_M)/B_M < 0.01
+B = dB/dt dt/\theta \Delta \theta
 \]
+
+Comparing this with the simulation in Figure \ref{fig:beam_extrapolation}, we find that the model predicts the 5\arcdeg extrapolation to better
+than 2\% even into the more uncertain areas far from zenith. The RMS difference for the central 15\arcdeg of the track
+is 1.5\%. From this we conclude that, as long as we constrain our extrapolations to $\pm5$\arcdeg around Pictor A,
+we will have negligible beam area.
+
+\begin{figure*}
+\includegraphics[width=.9\textwidth]{plots/beam_slope_compare.png}
+\caption{The beam is well along a declination cut but beam formed source tracks. Here we measure the beam, 
+as extrapolated by fitting a slope (dotted), and compare with the beam model (solid). The difference (circles) is never larger
+than $\sim$1\%.  Thus we conclude that the beam slope is locally well modeled and our beam model is suitable 
+for extrapolation over $\sim$5\arcdeg scales.
+  \label{fig:beam_extrapolation}}
+\end{figure*}
 
@@
 \centering
-\includegraphics[width=0.9\textwidth]{plots/2250-412_2331-416_2140-434_0007-446_0704-427_gain_mcmc_chain_gain_conf.png}
+\includegraphics[width=0.9\textwidth]{plots/1526-423_2250-412_2331-416_1932-464_1421-490_gain_mcmc_chain_gain_conf.png}
 \caption{
@@
 %(PAPER_imaging)danny@keynes:plots$ python sort_SI_plots.py psa64_pic_stripe_perleycorr_SEDfits.txt
-%BEGIN PASTE
+%TOP OF MAIN CONFIDENCE PLOT SECTION
 %the best sources. High quality fit that improves on previous knowledge
@@
 \begin{center}
-\includegraphics[width=2in]{plots/0003-428_SI_MCMC.png} %0.1064
-\includegraphics[width=2in]{plots/0007-446_SI_MCMC.png} %0.1851
-\includegraphics[width=2in]{plots/0039-445_SI_MCMC.png} %0.7325
-\includegraphics[width=2in]{plots/0043-424_SI_MCMC.png} %0.2527
-\includegraphics[width=2in]{plots/0048-447_SI_MCMC.png} %0.0596
-\includegraphics[width=2in]{plots/0049-433_SI_MCMC.png} %0.2988
-\includegraphics[width=2in]{plots/0103-453_SI_MCMC.png} %0.007
-\includegraphics[width=2in]{plots/0201-440_SI_MCMC.png} %2.3481
-\includegraphics[width=2in]{plots/0438-436_SI_MCMC.png} %0.0595
-\includegraphics[width=2in]{plots/0511-484_SI_MCMC.png} %2.6709
-\includegraphics[width=2in]{plots/0534-497_SI_MCMC.png} %2.6256
-\includegraphics[width=2in]{plots/0546-445_SI_MCMC.png} %0.1024
+\includegraphics[width=2in]{plots/0003-428_SI_MCMC.png} %0.9878
+\includegraphics[width=2in]{plots/0007-446_SI_MCMC.png} %1.0085
+\includegraphics[width=2in]{plots/0039-445_SI_MCMC.png} %1.3403
+\includegraphics[width=2in]{plots/0043-424_SI_MCMC.png} %0.5959
+\includegraphics[width=2in]{plots/0048-447_SI_MCMC.png} %0.6165
+\includegraphics[width=2in]{plots/0049-433_SI_MCMC.png} %1.0632
+\includegraphics[width=2in]{plots/0103-453_SI_MCMC.png} %0.1456
+\includegraphics[width=2in]{plots/0201-440_SI_MCMC.png} %3.0727
+\includegraphics[width=2in]{plots/0438-436_SI_MCMC.png} %0.0991
+\includegraphics[width=2in]{plots/0511-484_SI_MCMC.png} %3.3967
+\includegraphics[width=2in]{plots/0534-497_SI_MCMC.png} %3.4118
+\includegraphics[width=2in]{plots/0546-445_SI_MCMC.png} %0.1647
 \end{center}
@@
 \begin{figure*}[htbp]2\begin{center}
-\includegraphics[width=2in]{plots/0547-408_SI_MCMC.png} %0.1044
-\includegraphics[width=2in]{plots/0647-475_SI_MCMC.png} %0.8893
-\includegraphics[width=2in]{plots/0700-473_SI_MCMC.png} %1.709
-\includegraphics[width=2in]{plots/0704-427_SI_MCMC.png} %0.0824
-\includegraphics[width=2in]{plots/0748-440_SI_MCMC.png} %0.3377
-\includegraphics[width=2in]{plots/0748-454_SI_MCMC.png} %0.0699
-\includegraphics[width=2in]{plots/0809-492_SI_MCMC.png} %1.2296
-\includegraphics[width=2in]{plots/0819-474_SI_MCMC.png} %1.5069
-\includegraphics[width=2in]{plots/1017-421_SI_MCMC.png} %0.0031
-\includegraphics[width=2in]{plots/1017-426_SI_MCMC.png} %0.0455
-\includegraphics[width=2in]{plots/1046-409_SI_MCMC.png} %0.0055
-\includegraphics[width=2in]{plots/1302-491_SI_MCMC.png} %0.0592
+\includegraphics[width=2in]{plots/0547-408_SI_MCMC.png} %0.1506
+\includegraphics[width=2in]{plots/0647-475_SI_MCMC.png} %0.8384
+\includegraphics[width=2in]{plots/0700-473_SI_MCMC.png} %1.9848
+\includegraphics[width=2in]{plots/0704-427_SI_MCMC.png} %0.0785
+\includegraphics[width=2in]{plots/0748-440_SI_MCMC.png} %0.2942
+\includegraphics[width=2in]{plots/0748-454_SI_MCMC.png} %0.0742
+\includegraphics[width=2in]{plots/0809-492_SI_MCMC.png} %0.6265
+\includegraphics[width=2in]{plots/0819-474_SI_MCMC.png} %0.9749
+\includegraphics[width=2in]{plots/1017-421_SI_MCMC.png} %0.0034
+\includegraphics[width=2in]{plots/1017-426_SI_MCMC.png} %0.0195
+\includegraphics[width=2in]{plots/1046-409_SI_MCMC.png} %0.0012
+\includegraphics[width=2in]{plots/1116-462_SI_MCMC.png} %0.0062
 \end{center}
@@
 \begin{figure*}[htbp]2\begin{center}
-\includegraphics[width=2in]{plots/1358-493_SI_MCMC.png} %0.4795
-\includegraphics[width=2in]{plots/1421-490_SI_MCMC.png} %0.891
-\includegraphics[width=2in]{plots/1424-418_SI_MCMC.png} %0.0056
-\includegraphics[width=2in]{plots/1445-468_SI_MCMC.png} %0.973
-\includegraphics[width=2in]{plots/1526-423_SI_MCMC.png} %0.0961
-\includegraphics[width=2in]{plots/1552-433_SI_MCMC.png} %0.9684
-\includegraphics[width=2in]{plots/1556-466_SI_MCMC.png} %1.4713
-\includegraphics[width=2in]{plots/1616-457_SI_MCMC.png} %0.0157
-\includegraphics[width=2in]{plots/1618-430_SI_MCMC.png} %2.7782
-\includegraphics[width=2in]{plots/1633-409_SI_MCMC.png} %0.2602
-\includegraphics[width=2in]{plots/1839-487_SI_MCMC.png} %0.135
-\includegraphics[width=2in]{plots/1840-404_SI_MCMC.png} %0.1159
+\includegraphics[width=2in]{plots/1143-483_SI_MCMC.png} %0.004
+\includegraphics[width=2in]{plots/1215-457_SI_MCMC.png} %0.0163
+\includegraphics[width=2in]{plots/1232-416_SI_MCMC.png} %0.0227
+\includegraphics[width=2in]{plots/1243-412_SI_MCMC.png} %0.0076
+\includegraphics[width=2in]{plots/1246-410_SI_MCMC.png} %0.06
+\includegraphics[width=2in]{plots/1247-401_SI_MCMC.png} %0.1161
+\includegraphics[width=2in]{plots/1302-491_SI_MCMC.png} %0.5328
+\includegraphics[width=2in]{plots/1355-416_SI_MCMC.png} %0.1959
+\includegraphics[width=2in]{plots/1358-493_SI_MCMC.png} %0.7284
+\includegraphics[width=2in]{plots/1421-490_SI_MCMC.png} %1.3529
+\includegraphics[width=2in]{plots/1424-418_SI_MCMC.png} %0.0218
+\includegraphics[width=2in]{plots/1445-468_SI_MCMC.png} %1.8104
 \end{center}
@@
 \begin{figure*}[htbp]2\begin{center}
-\includegraphics[width=2in]{plots/1932-464_SI_MCMC.png} %0.0164
-\includegraphics[width=2in]{plots/1940-406_SI_MCMC.png} %0.0524
-\includegraphics[width=2in]{plots/1953-425_SI_MCMC.png} %0.0739
-\includegraphics[width=2in]{plots/2140-434_SI_MCMC.png} %0.3123
-\includegraphics[width=2in]{plots/2213-456_SI_MCMC.png} %0.1767
-\includegraphics[width=2in]{plots/2226-411_SI_MCMC.png} %0.1166
-\includegraphics[width=2in]{plots/2250-412_SI_MCMC.png} %0.2199
-\includegraphics[width=2in]{plots/2323-407_SI_MCMC.png} %6.9237
-\includegraphics[width=2in]{plots/2331-416_SI_MCMC.png} %0.2179
+\includegraphics[width=2in]{plots/1526-423_SI_MCMC.png} %0.1985
+\includegraphics[width=2in]{plots/1552-433_SI_MCMC.png} %1.3211
+\includegraphics[width=2in]{plots/1556-466_SI_MCMC.png} %2.5579
+\includegraphics[width=2in]{plots/1616-457_SI_MCMC.png} %0.0507
+\includegraphics[width=2in]{plots/1618-430_SI_MCMC.png} %3.821
+\includegraphics[width=2in]{plots/1633-409_SI_MCMC.png} %1.3843
+\includegraphics[width=2in]{plots/1839-487_SI_MCMC.png} %0.1766
+\includegraphics[width=2in]{plots/1840-404_SI_MCMC.png} %0.1658
+\includegraphics[width=2in]{plots/1932-464_SI_MCMC.png} %0.4321
+\includegraphics[width=2in]{plots/1940-406_SI_MCMC.png} %0.0325
+\includegraphics[width=2in]{plots/1953-425_SI_MCMC.png} %0.1181
+\includegraphics[width=2in]{plots/2140-434_SI_MCMC.png} %0.2976
 \end{center}
-\caption{fits of the next 16 sources, as described in Figure \ref{fig:SI_contour_1}. Sources marked with a
+\caption{Spectral model contours as described in Figure \ref{fig:pic_spectrum}. Sources marked with a
 * were used to assess calibration error.
@@
 \end{figure*}
+\clearpage
+\begin{figure*}[htbp]2\begin{center}
+\includegraphics[width=2in]{plots/2213-456_SI_MCMC.png} %0.2146
+\includegraphics[width=2in]{plots/2226-411_SI_MCMC.png} %0.3157
+\includegraphics[width=2in]{plots/2250-412_SI_MCMC.png} %0.5585
+\includegraphics[width=2in]{plots/2323-407_SI_MCMC.png} %4.9008
+\includegraphics[width=2in]{plots/2331-416_SI_MCMC.png} %0.8134
+\end{center}
+\caption{fits of the last 5 sources, as described in Figure \ref{fig:SI_contour_1}. Sources marked with a
+* were used to assess calibration error.
+}\label{fig:SI_contour_5}
+\end{figure*}%BOTTOM OF MAIN CONFIDENCE PLOT SECTION
+%%%%%%%%%%%%%%%%%%%%
+
 %BEGIN PASTE
@@
 %ok fit, but doesn't agree with past data, or actually increases model uncertainty
-%contour length limit =  209.039667221
-%Poor improvement:  1116-462 8.66,9.97,11.27 -0.72,-0.59,-0.47 8.56,9.82,11.15 -0.71,-0.58,-0.46 0.22 0.23 -0 0.6 -0.0018 164.0
-\includegraphics[width=2in]{plots/1116-462_SI_MCMC.png} %-0.0018
-%Poor improvement:  1143-483 13.47,15.46,17.58 -0.83,-0.7,-0.57 9.91,11.65,13.51 -0.7,-0.56,-0.44 0.34 0.37 -0.03 0.21 -0.0064 122.0
-\includegraphics[width=2in]{plots/1143-483_SI_MCMC.png} %-0.0064
-%Poor improvement:  1215-457 15.08,16.94,18.88 -0.59,-0.47,-0.36 11.28,12.93,14.57 -0.46,-0.33,-0.21 0.36 0.39 -0.03 0.15 -0.0042 122.0
-\includegraphics[width=2in]{plots/1215-457_SI_MCMC.png} %-0.0042
-%Poor improvement:  1221-423 9.46,11.52,13.87 -0.96,-0.78,-0.61 6.77,8.6,10.49 -0.78,-0.57,-0.39 0.45 0.53 -0.08 0.27 -0.022 116.0
-\includegraphics[width=2in]{plots/1221-423_SI_MCMC.png} %-0.022
-%Poor improvement:  1232-416 9.42,10.83,12.3 -0.88,-0.75,-0.63 9.2,10.57,11.96 -0.88,-0.74,-0.62 0.22 0.22 -0 0.57 -0.002 164.0
-\includegraphics[width=2in]{plots/1232-416_SI_MCMC.png} %-0.002
-%Poor improvement:  1407-425 13.6,15.19,16.86 -1.21,-1.09,-0.98 9.91,11.35,12.85 -1.07,-0.94,-0.82 0.36 0.41 -0.05 0.11 -0.0059 128.0
-\includegraphics[width=2in]{plots/1407-425_SI_MCMC.png} %-0.0059
+%contour length limit =  223.105907705
+%Poor improvement:  1407-425 14.03,15.48,16.92 -1.23,-1.11,-0.99 9.88,11.36,12.93 -1.08,-0.95,-0.82 0.4 0.41 -0.01 0.07 -0.0006 118.0
+\includegraphics[width=2in]{plots/1407-425_SI_MCMC.png} %-0.0006
+\caption{Contours of spectral fit as described in Figure \ref{fig:SI_contour_1}. This source displays negative 
+improvement. The addition of the PAPER data actually slightly increases the uncertainty.
+\label{fig:SI_contour_bad}}
 \end{center}
-\caption{fits of the worst sources. Contours as described in Figure \ref{fig:SI_contour_1}. The fit either disagrees
-with past data or does not offer any improvement (improvement index $\le 0$). All are near
-the galactic plane and are likely dominated by sidelobes.
-}\label{fig:SI_contour_bad}
 \end{figure*}
@@
 %zero overlap
-\includegraphics[width=2in]{plots/1246-410_SI_MCMC.png} %-0
+\includegraphics[width=2in]{plots/1221-423_SI_MCMC.png} %0.0
+\includegraphics[width=2in]{plots/1315-460_SI_MCMC.png} %0.0
 \includegraphics[width=2in]{plots/1320-446_SI_MCMC.png} %0.0
-\includegraphics[width=2in]{plots/1355-416_SI_MCMC.png} %0.0
-\includegraphics[width=2in]{plots/1416-493_SI_MCMC.png} %-0
+\includegraphics[width=2in]{plots/1416-493_SI_MCMC.png} %0.0
 \includegraphics[width=2in]{plots/1459-417_SI_MCMC.png} %0
@@
 \caption{
-These sources offer results at odds with previous measurements. These have
-small enough error bars to require a deviation from spectral index fit
-suggested by prior catalog measurements. All are near Centaurus A (see Figure
-\ref{fig:error_map}), a very bright, extended source, and are likely evidence
-for side lobe contamination.  Side lobes from distant sources manifest as
-ripples in the spectrum, increasing the error bars (e.g. the sources listed in
-Figure \ref{fig:SI_contour_bad}). However, the sources shown here are close
+These sources are at odds with previous measurements.
+Two simply do not have enough
+prior catalog data to fit a spectral model, while the rest have
+suggest a deviation from the catalog spectral index fit.
+All are near Centaurus A (see Figure
+\ref{fig:error_map}), a very bright, extended source, as well as the galactic plane.
+Side lobes manifest as
+ripples in the beam formed spectra which increases the error bars. See for example the 
+Pictor A spectrum \ref{fig:pic_spectrum_detail}. However, the sources shown here are close
 enough to Centaurus A that the side-lobe oscillates on scales longer than 10MHz
@@
 \begin{figure*}
-\includegraphics[width=\textwidth]{plots/psa64_pic_strip_positions_annotated_cropped.png}
+\includegraphics[width=\textwidth]{plots/psa64_pic_strip_positions_annotated_cropped.pdf}
 \caption{
@@
 \citep{deOliveiraCosta:2008p2242}.  x's mark measured locations and have size
-scaled by agreement with prior data (inverse ``improvement index", see
-\S\ref{sec:fits}). Black dots indicate sources with $\le0$ improvement score.
-For these the fit quality decreases with addition of PAPER data or the model
-revision disagrees completely with the prior estimate due to side lobes or
-spectral curvature.  We estimate that   \label{fig:error_map}
+scaled by dis-agreement with prior data (inverse ``improvement index" from 
+\S\ref{sec:fits}). Smaller indicates better agreement with past data.  Black dots indicate sources with $\le0$ improvement score;
+agreement decreases with addition of PAPER data (see Figures \ref{fig:SI_contour_bad} and \ref{fig:SI_contour_new}). 
+This is most likely due to galactic, and Centaurus A, side lobes.    \label{fig:error_map}
 }

### 2013-05-22 ms.tex
Updated description of source selection vis beam error.

@@
 Donald C. Backer Precision Array for Probing
-% XXX ARP: was irina "first"?  and maybe "catalog"
 the Epoch of Reionization (PAPER) in South Africa observed in July and
@@
 Since each source follows a nearly identical path through the primary beam, this
-restriction allows beam calibration to be nearly eliminated as a source of error,
+restriction allows beam calibration to be greatly reduced as a source of error,
 yielding a dramatic improvement in the accuracy of source spectra measured in the 
-100--200-MHz band that is receiving renewed attention by experiments seeking to
-measure 21cm emission from the Epoch of Reionization (EoR).
-Based on the variation in our data and the estimated error in the absolute
-flux scale we bootstrap from multiple bright sources, we estimate PAPER measurements
-of sources above XXX Jy to be accurate to 3.2\%.
-% DCJ 3.2% is just for Pictor A, and certainly not all PAPER measurements of sources above XXX Jy
-When combined with catalog data at other frequencies, these data constrain parameters of
-a power-law model for flux density with an uncertainty of 2.4\%.
-% XXX ARP: this must again be dependent on source strength and location.
+100--200-MHz band which is receiving renewed attention by experiments seeking to
+measure 21cm emission from the Epoch of Reionization (EoR). Using beam forming
+and fringe-rate filtering we measure spectra for Pictor A, which provides a key flux reference for PAPER's EoR
+power spectrum analysis, 
+as well as 60 other sources at nearby declinations. Extrapolating from higher frequency
+catalogs we set the flux scale in a monte-carlo fit across multiple sources. This fit 
+propagates uncertainty from both catalog and measurement errors. Fitting new spectral 
+models to both catalog and the new PAPER data we find a Pictor A flux model accurate to
+2.4\%.
 This accuracy is limited by the uncertainty in the catalog measurements we use
@@
 of 58 sources observed are found to confirm and refine a power-law model for flux density.
-This includes Pictor A, which provides a key flux reference for PAPER's EoR
-power spectrum analysis.
+
 \end{abstract}
@@
 spatial scales relevant to EoR measurements but are limited by the accuracy of
-the primary beam \citep{Jacobs:2013p9713}.
+the primary beam \citep{Jacobs:2013p9713}. The accuracy of the absolute flux calibrators in the southern hemisphere
+is similarly limited.
+
+The response of the primary beam is of critical importance to EoR measurements.
+Differences between the polarization responses cause leakage of polarized
+signals into the total intensity measurement possibly corrupting the 
+EoR power spectrum \cite{Moore:2013p9621}.  The primary beam 
+shape is also critical to measuring and subtracting foregrounds 
+\cite{Bernardi:2012p9020} a process which, to be affective, must be done to better than 1\%
+precision for the brightest sources \citet{Liu:2009p4762,Bowman:2009p7816} .
 
@@
 
-This paper reports a set of flux measurements where a primary beam
-model has not been used to estimate the flux, but instead are directly
-calibrated to a single calibrator making the track through the beam.
-
+In this paper we provide a set of detailed total flux measurements aimed at providing
+an absolute flux calibration for southern hemisphere EoR studies as well as a
+small set of verification fluxes suitable for constraining future primary beam studies.
+
+\subsection{The sources and instrument}
 EoR measurements in the southern sky have focused on the coldest regions where
@@
 \label{sec:approach}
-Given the large uncertainties in the literature, and the necessity for PAPER power-spectrum analysis
-to use Pictor A for flux calibration, we felt it prudent to examine Pictor A directly.
 In this section, we describe how we use PAPER in its imaging configuration
-to measure Pictor A and a selection of known, bright sources in a 5\arcdeg strip centered
-on -45\arcdeg.
+to measure Pictor A and a selection of known, bright sources suitable for confirming the accuracy of the measurement
+and extrapolated flux scale.
 
  In \citet{Jacobs:2013p9837} several limitations were identified that
-exasperated the primary beam uncertainty.  First, in imaging each source flux is measured at just a few 
+exasperated the primary beam uncertainty.  First, under most imaging schemes, each source flux is measured at just a few 
 points in the primary beam. As errors tend to vary across the beam, the uncertainty will tend to vary between sources.
-Here we have averaged over all possible positions making the uncertainty a function of the net uncertainty in the beam,
-and stabilizing the source-to-source variations in error bars. The second limitation, identified in \citet{Williams:2012p8768},
+Here we have averaged over long tracks through the primary beam. Using the drift scan-beamforming technique, each 
+source is measured hundreds of times at a variety of different pointings. The variation between these measurements is then
+used to calculate measurement uncertainty. Second, the flux scale was found to vary substantially over the 
+sky, due to the dual uncertainties of primary beam response and prior catalog. As a hedge against beam uncertainty 
+we limit our selection to source with similar primary beam responses. A third limitation, identified in \citet{Williams:2012p8768},
 was the increase of uncertainty towards the edge of the beam. To minimize our sensitivity to both beam and noise
@@
 
-As PAPER is a drift scan instrument, each declination $\delta$ describes a distinct cut through the primary beam. These cuts
-provide a detailed measurement of the primary beam relative to the peak of the trace, however,
-a model $g(\delta)$ is still required to calibrate between declinations. This model will be effective over a range of declinations, but will diverge at
-some rate depending on the accuracy with which the model describes the slope.  As an estimate of the extrapolated 
-beam amplitude we fit the slope of our Pictor A source track and compute the amplitude extrapolated over our fiducial
-stripe width of 5\arcdeg.
-
-\[
-B = dB/dt dt/\theta \Delta \theta
-\]
-
-Comparing this with the simulation in Figure \ref{fig:beam_extrapolation}, we find that the model predicts the 5\arcdeg extrapolation to better
-than 2\% even into the more uncertain areas far from zenith. The RMS difference for the central 15\arcdeg of the track
-is 1.5\%. From this we conclude that, as long as we constrain our extrapolations to $\pm5$\arcdeg around Pictor A,
-we will have negligible beam area.
-
-\begin{figure*}
-\includegraphics[width=.9\textwidth]{plots/beam_slope_compare.png}
-\caption{The beam is well along a declination cut but beam formed source tracks. Here we measure the beam, 
-as extrapolated by fitting a slope (dotted), and compare with the beam model (solid). The difference (circles) is never larger
-than $\sim$1\%.  Thus we conclude that the beam slope is locally well modeled and our beam model is suitable 
-for extrapolation over $\sim$5\arcdeg scales.
-  \label{fig:beam_extrapolation}}
-\end{figure*}
+\subsection{Selection of confirmation sources}
+As PAPER is a drift scan instrument, each declination describes a distinct path through the primary beam. These paths
+provide a detailed sample of the primary beam relative to the peak of the trace, however,
+a model is still required to calibrate between declinations and the accuracy of the trace is sometimes contaminated by
+sidelobes. In section XXX we will compare the beam response as measured by the PicA trace with the model 
+used to estimate flux. We will see that, on average, the primary beam is not the limiting factor in estimating the flux and that
+limiting ourselves to a declination range of 10\arcdeg around Pictor A for flux verification is a good compromise.
+%
+%
+%
+%This model will be effective over a range of declinations, but will diverge at
+%some rate depending on the accuracy with which the model describes the slope.  As an estimate of the extrapolated 
+%beam amplitude we fit the slope of our Pictor A source track and compute the amplitude extrapolated over our fiducial
+%stripe width of 5\arcdeg.
+%
+%\[
+%B = dB/dt dt/\theta \Delta \theta
+%\]
+%
+%Comparing this with the simulation in Figure \ref{fig:beam_extrapolation}, we find that the model predicts the 5\arcdeg extrapolation to better
+%than 2\% even into the more uncertain areas far from zenith. The RMS difference for the central 15\arcdeg of the track
+%is 1.5\%. From this we conclude that, as long as we constrain our extrapolations to $\pm5$\arcdeg around Pictor A,
+%we will have negligible beam area. 
+%
+%\begin{figure*}
+%\includegraphics[width=.9\textwidth]{plots/beam_slope_compare.png}
+%\caption{The beam is well along a declination cut but beam formed source tracks. Here we measure the beam, 
+%as extrapolated by fitting a slope (dotted), and compare with the beam model (solid). The difference (circles) is never larger
+%than $\sim$1\%.  Thus we conclude that the beam slope is locally well modeled and our beam model is suitable 
+%for extrapolation over $\sim$5\arcdeg scales.
+%  \label{fig:beam_extrapolation}}
+%\end{figure*}
 
@@
 \label{sec:fits}
-
-%0008-421#
-%1243-412#
-%1247-401#
-%1315-460
-%TODO round up the source counts
-
 In the 59 sources measured, four demonstrated poor convergence fitting a single

### 2013-06-08 plots/beam_cal_sim.py
step one of a massive cleanup. Some files are deleted by moving out of tree.

@@ -70,7 +70,9 @@ def rotbeam(src):
     return aa[0].bm_response(xyz,pol=pol).squeeze()**2
 def calbeam(src):
     xyz = src.get_crds('top')
-    return aa[0].bm_response(xyz,pol=opts.pol[0]).squeeze()**2
+    bm = aa[0].bm_response(xyz,pol=opts.pol[0]).squeeze()**2
+    if type(bm)!=n.ndarray: bm = n.array([bm])
+    return bm
 def ModelBeam(src):
     return calbeam(src)
 def TrueBeam(src):
@@ -108,6 +110,7 @@ g = n.zeros((nfreqs,len(cat)))
 w = n.zeros((nfreqs,len(cat)))
 A = {}
 B = {}
+A2 = {}
 W = {}
 crds = {}
 times = {}
@@ -116,6 +119,7 @@ for i,src in enumerate(n.sort(cat.keys())[::-1]):
     aa.date = aa.next_rising(cat[src])
     A[src] = []
     B[src] = []
+    A2[src] = []
     crds[src] = []
     W[src] = n.zeros(nfreqs)
     times[src] = []
@@ -124,14 +128,21 @@ for i,src in enumerate(n.sort(cat.keys())[::-1]):
         aa.set_ephemtime(t+dt)
         cat.compute(aa)        
         src_xyz = cat[src].get_crds('top')
+        src_ang = cat[src].get_crds('top',ncrd=2)
         if src_xyz[2]<0:break
+        if n.abs(src_ang[1]-n.pi)<(10*n.pi/180): break
+        print src_ang
         crds[src].append(src_xyz)
         g[:,i] += ModelBeam(cat[src]) * TrueBeam(cat[src])
         w[:,i] += ModelBeam(cat[src]) * ModelBeam(cat[src])
         A[src].append(ModelBeam(cat[src]))
         B[src].append(TrueBeam(cat[src]))
+        A2[src].append(bradleybeam(cat[src]))
         W[src] += ModelBeam(cat[src]) * ModelBeam(cat[src])
         times[src].append(t)
+    A[src] = n.array(A[src])
+    B[src] = n.array(B[src])
+    A2[src] = n.array(A2[src])
 
 g /= w
 figure()
@@ -156,14 +167,20 @@ print "Model weighted, simulated beam"
 savefig('model_weighted_beam_sim_track.png')
[…]

### 2013-06-08 plots/plot_srcs_on_sky.py

@@ -471,7 +471,9 @@ for i,file in enumerate(args):
 
                 if sd!=0:
                     #size = n.log10(n.abs((1./sd - 0.99/srcdatamax)*srcdatamin+1))*10+20
-                    size = n.abs((1.001/sd - 0.99/srcdatamax)*srcdatamin)*10+20
+                    size = n.abs((1.001/sd - 0.99/srcdatamax)*srcdatamin)*500+20
+                    print sd,srcdatamin,srcdatamax,
+                    #size = (sd-srcdatamin)/srcdatamax*20
                     print size
                     sizes[size] = name
                     if not opts.highquality is None:
@@ -481,12 +483,12 @@ for i,file in enumerate(args):
                     #else:
                     #    size =1./n.abs((sd - srcdatamin)/srcdatamax)+5
 #                    else:
-                    map.scatter(xpt,ypt,marker=marker,color='k',s=size)    
+                    map.scatter(xpt,ypt,marker=marker,color='w',s=size)    
                 else:
                     marker = 'o'
                     if not opts.highquality is None: size= 10*opts.highquality
                     else: size = 10
-                    map.scatter(xpt,ypt,marker=marker,color='k',s=size)
+                    map.scatter(xpt,ypt,marker=marker,color='w',s=size)
 
             else:
                 map.scatter(xpt,ypt,marker='o',color='k',s=s)

### 2013-06-08 plots/sort_SI_plots.py

@@ -5,7 +5,7 @@ import numpy as n,sys
 from pylab import *
 
 lines = open(sys.argv[-1]).readlines()
-lines = [line for line in lines if not line.startswith('#')]
+lines = [line for line in lines if not (line.startswith('#') or len(line)<3)]
 print [len(line.split()) for line in lines]
 improvement = n.array([n.float(line.split()[9]) for line in lines]) # (FOM change)*(fraction of PAPER overlapping previos)
 overlap = n.array([n.float(line.split()[8]) for line in lines])

### 2013-06-08 plots/plot_srcs_on_sky.py
changed markers to white, background to black for plotting on PSA64 data

@@ -144,6 +144,9 @@ if not opts.srcfile is None:
     lines = [l.split() for l in open(opts.srcfile).readlines() if not l.startswith('#') and not len(l)==0]
     opts.src = ','.join([l[0] for l in lines])
     srcdata = dict(zip([l[0] for l in lines],[l[opts.datacol] for l in lines]))
+    cals = [l[0] for l in lines if int(l[-1])]
+    print "found %d cals"%len(cals)
+    nocatdata= [l[0] for l in lines if l[3].startswith('-1')]
     for src in n.sort(srcdata.keys()):
         print src,srcdata[src]
     srcdatamin,srcdatamax = n.array(map(float,srcdata.values())).min()*1.001,n.array(map(float,srcdata.values())).max()
@@ -483,13 +486,18 @@ for i,file in enumerate(args):
                     #else:
                     #    size =1./n.abs((sd - srcdatamin)/srcdatamax)+5
 #                    else:
-                    map.scatter(xpt,ypt,marker=marker,color='w',s=size)    
+                    #map.scatter(xpt,ypt,marker=marker,color='w',s=size)    
+                elif name in nocatdata:
+                    marker='x'
+                    if not opts.highquality is None: size= 10*opts.highquality
+                    else: size = 10                   
                 else:
                     marker = 'o'
                     if not opts.highquality is None: size= 10*opts.highquality
                     else: size = 10
-                    map.scatter(xpt,ypt,marker=marker,color='w',s=size)
-
+                map.scatter(xpt,ypt,marker=marker,color='w',s=size)
+                if name in cals:
+                    map.scatter(xpt,ypt,marker='o',color='w',s=size*2,facecolor='None')
             else:
                 map.scatter(xpt,ypt,marker='o',color='k',s=s)
             if flx < 10: flx = 10

### 2013-06-10 ms.tex
Fixing nits from Monday datacon

@@
 \bibliographystyle{apj_w_etal}
+
+\newcommand{\Nconf}{31}
+\newcommand{\Nsrc}{32}
 
@@
 power spectrum analysis, 
-as well as 60 other sources at nearby declinations. Extrapolating from higher frequency
+as well as \Nconf other sources at nearby declinations. Extrapolating from higher frequency
 catalogs we set the flux scale in a monte-carlo fit across multiple sources. This fit 
@@
 an order of magnitude improvement over previous measurements in this band.  
-Comparing with prior measurements, 45 out
-of 58 sources observed are found to confirm and refine a power-law model for flux density.
+Comparing with prior measurements, 90\% are found to confirm and refine a power-law model for flux density.
 
@@
 most extensive surveying work is now being conducted by the EoR experiments
-themselves \citep{Jacobs:2011p8438,Williams:2012p8768}.
+themselves \citep{Jacobs:2011p8438,Williams:2012p8768,Bernardi:2013p9859}.
 
@@
 In this paper, we set out to significantly improve the accuracy of spectral measurements between 
-100--200 MHz for a set of bright sources in the declination range XXX to XXX that
+100--200 MHz for a set of bright sources in the declination range -46\arcdeg to -40\arcdeg that
 are of particular value for southern-hemisphere 21cm EoR experiments such as PAPER and the MWA.
@@
 In this section, we describe how we use PAPER in its imaging configuration
-to measure Pictor A and a selection of known, bright sources suitable for confirming the accuracy of the measurement
-and extrapolated flux scale.
-
- In \citet{Jacobs:2013p9837} several limitations were identified that
-exasperated the primary beam uncertainty.  First, under most imaging schemes, each source flux is measured at just a few 
-points in the primary beam. As errors tend to vary across the beam, the uncertainty will tend to vary between sources.
-Here we have averaged over long tracks through the primary beam. Using the drift scan-beamforming technique, each 
-source is measured hundreds of times at a variety of different pointings. The variation between these measurements is then
-used to calculate measurement uncertainty. Second, the flux scale was found to vary substantially over the 
-sky, due to the dual uncertainties of primary beam response and prior catalog. As a hedge against beam uncertainty 
-we limit our selection to source with similar primary beam responses. A third limitation, identified in \citet{Williams:2012p8768},
+to measure Pictor A and confirm our results by measuring a  selection of known, bright sources. The fluxes are obtained
+by forming beams towards known sources as they drift through the primary beam, calibrating to a single source making a similar track.
+These long tracks provide allow us to sidestep primary beam uncertainty to measure accurately calibrated fluxes.
+
+ In \citet{Jacobs:2013p9837} several errors were identified as originating in primary beam uncertainty.
+  First, under most imaging schemes, each source flux is measured at just a few 
+points in the primary beam. As errors tend to vary across the beam, the uncertainty will tend to vary between sources making
+it difficult to decouple flux uncertainty from beam uncertainty.
+ Using the drift scan-beamforming technique, each 
+source is measured hundreds of times at a variety of different pointings to provide a complete sample of the
+flux variance due to primary beam variation.  Second, the flux calibration was found to vary over the 
+sky due to the dual uncertainties of primary beam response and prior catalog. To limit our exposure to flux calibration
+variation we limit our observations to sources passing within 5\arcdeg of locations which we can directly calibrate
+from a single reference source.
+ A third limitation, identified in \citet{Williams:2012p8768},
 was the increase of uncertainty towards the edge of the beam. To minimize our sensitivity to both beam and noise
@@
 used to estimate flux. We will see that, on average, the primary beam is not the limiting factor in estimating the flux and that
-limiting ourselves to a declination range of 10\arcdeg around Pictor A for flux verification is a good compromise.
+limiting ourselves to a declination range of 5\arcdeg around calibrator 2331-416 for flux verification is a good compromise.
 %
@@
 
-The spectra reported here are measured by beam-forming, phasing the visibilities to
-the target location, and summing to produce a dynamic spectrum. The spectrum is then isolated
+\subsection*{Data Processing Overview}
+\label{sec:data_overview}
+The spectra reported here are measured by beam-forming ---phasing the visibilities to
+the target location and summing to produce a dynamic spectrum. The spectrum is then isolated
 from neighboring sources by filtering and averaged in the time domain.  This time average is 
-weighted by an additional factor of the PAPER's primary beam response 
+weighted by an additional factor of PAPER's primary beam response 
 \citep{pober_et_al2012}.  
 \begin{align}
-S_\textrm{est} &= \frac{\sum_t B_M S_p}{\sum_t B^2_M}\\
-&= \frac{\sum_t B_M B}{\sum_t B^2_M} S\\ \label{eq:g}
+S_\textrm{est} &= \frac{\sum_t B_M S_p}{\sum_t B^2_M} \nonumber \\ 
+&= \frac{\sum_t B_M B}{\sum_t B^2_M} S  \nonumber \\
+&= g(\delta) S  \label{eq:g}
 \end{align}
@@
 which is an effective approximation of inverse-variance weighting. The pre factor in Eq \ref{eq:g} is identical for 
-sources at the same declination, and as we found above, diverges slowly from the model in the 10\arcdeg declination stripe.
-We estimate this spectral dependent gain for a calibrator (J2331-416) fitting a spectral index model to the
- well-defined data points below 2GHz. This removes an overall offset.
+sources at the same declination.  In simulation we multiplied an early attempt to map the beam \cite{Pober:2012p8800}
+by electromagnetic simulations of the PAPER beam and find that it 
+diverges slowly with declination, with a maximum of 10\% over 5\arcdeg of declination range.
+We estimate this spectral dependent gain at a reference declination of 41\arcdeg36\arcmin using (J2331-416) fitting a spectral index model to the
+ well-defined data points below 2GHz.
 
@@
 At the output of the beam forming and bandpass calibration step, the flux scale
- is tied to a model fit tp the catalog values of
+ is tied to a model fit of the catalog values of
 J2331-416. The accuracy of this fit, and the implied uncertainty in the flux
@@
 \begin{align}
-\log\mathcal{L}_s &= \sum_{\nu}\frac{ (S_\textrm{cat}^{\nu}  - S_{150}  \left(\frac{\nu}{150}\right)^\alpha)^2}{2(\Delta S_\textrm{cat}^\nu)^2} +
-\frac{ (g*S_\PAPER^{\nu}  - S_{150}\left(\frac{\nu}{150}\right)^\alpha)^2}{2(\Delta S_\PAPER^\nu)^2}\\
+\log\mathcal{L}_s &= \sum_{\nu}\frac{ \left[S_\textrm{cat}^{\nu}  - S_{150}  \left(\frac{\nu}{150}\right)^\alpha\right]^2}{2(\Delta S_\textrm{cat}^\nu)^2} +
+\frac{ (g S_\PAPER^{\nu}  - S_{150}\left(\frac{\nu}{150}\right)^\alpha)^2}{2(\Delta S_\PAPER^\nu)^2} \nonumber \\
 \log\mathcal{L} &= \sum_{s} \log\mathcal{L}_s
@@
 
-which samples the posterior probability of PAPER data ($SPAPER_{\nu}$) and
-catalog values ($Scat_{\nu}$) given a spectral index model for each source and
-a global flux scale factor ($g$) ($S_\PAPER^\textrm{calibrated} = g S_\PAPER$).
+which samples the posterior probability of PAPER data ($S_\PAPER^{\nu}$) and
+catalog values ($S_\textrm{cat}^{\nu}$) given a spectral index model for each source and
+a global flux scale factor ($g$).
 Marginalizing over the fitted flux scales, we find the resulting flux scale distribution function which is shown in Figure
 \ref{fig:gain}. The 76\% confidence limit on this flux scale, relative to the
-J2331-413 calibration, is  $-0.01 ^{+0.11}_{-0.17}$ dB, or a 3.24\%
-multiplicative error on every calibrated PAPER measurement.  These errors are added, in quadrature,
-to the errors in the PAPER spectra.
-
+J2331-413 calibration, is  $+0.11 ^{+0.05}_{-0.08}$ dB, or a 1.54\%
+multiplicative error on every calibrated PAPER measurement.  This flux scale is applied to the PAPER spectra
+with the errors added in quadrature.
+%gain [dB] 0.03,0.11,0.16
+
+%TODO UPDATE this par
 These calibrated spectra are plotted in Figures \ref{fig:srcs1},\ref{fig:srcs2},
@@
 \begin{equation}
-\logL = \sum_\nu{\frac{\left(S_\nu - S_{150}\left(\frac{\nu}{150}\right)^\alpha\right)^2}{\Delta S_\nu} }
+\logL = \sum_\nu{\frac{\left[S_\nu - S_{150}\left(\frac{\nu}{150}\right)^\alpha\right]^2}{\Delta S_\nu} }
 %\label{eq:catlogL}
@@
 \includegraphics[width=0.49\textwidth]{plots/pic_trace_hist.png}
-\includegraphics[width=0.49\textwidth]{plots/1556-466_trace_hist.png}
+\includegraphics[width=0.49\textwidth]{plots/2323-407_trace_hist.png}
 \caption{
 A more detailed view of the posterior probability distribution. On the left
-Pictor A, on the right 1556-466. Confidence contours range from 0.2 to 0.8.
-Compare with the contours for this source shown in Fig. \ref{fig:SI_contour_3}.
-As above, grey for  the fit to catalog data, black for joint catalog and PAPER
-fit.
+Pictor A, on the right 2323-407. Confidence contours range from 0.2 to 0.8. The MCMC
+chain reveals the distinctive ``banana'' shape of the posterior
+due to correlation between the model parameters.
+Compare with the contours for this source shown in Fig. \ref{fig:SI_contour_2}.
+Grey plots the fit to catalog data, black for joint catalog and PAPER.
 }
@@
 \label{sec:fits}
+%TODO Revise all the numbers in this session.
+%now we have 32 sources (counting pic)
+% 25 have >0 improvement
+% 0 have negative
+% 6 have 0 overlap
 In the 59 sources measured, four demonstrated poor convergence fitting a single
@@
 \textrm{Improvement} &= \left(\textrm{Precision increase}\right) \left(\textrm{Catalog agreement}\right)\\
-&= \left(\frac{1}{Area(\textrm{PAPER})} - \frac{1}{Area(\textrm{Cat})}\right) \left( Area(\PAPER \cap \textrm{Cat}) \right)
+&= \left(\frac{1}{\textrm{Area}(\textrm{PAPER})} - \frac{1}{\textrm{Area}(\textrm{Cat})}\right) \left( \textrm{Area}(\PAPER \cap \textrm{Cat}) \right)
 \end{align}
+where the area is defined as the number of samples having posterior probability above 76\%.
 
@@
 \centering
-\includegraphics[width=0.9\textwidth]{plots/1526-423_2250-412_2331-416_1932-464_1421-490_gain_mcmc_chain_gain_conf.png}
+\includegraphics[width=0.9\textwidth]{plots/2250-412_2331-416_1932-464_0103-453_0547-408_0043-424_gain_mcmc_chain_gain_conf.png}
 \caption{
@@
 function bootstrapped from the NED database listings for
-2250-412,2331-416,2140-434,0007-446 and 0704-427 below 2GHz.
+2250-412,2331-416,1932-464,0103-453,0547-408,0043-424 below 2GHz.
 \label{fig:gain}}
@@
 \citet{Baars:1977p9678} scale by  \cite{Kuehr:1981p9628}. A sub-sample of MCMC
-fits are shown in blue. On the right, the grey contour indicates the 76\%
+fits are shown in grey. On the right, the grey contour indicates the 76\%
 confidence interval for 150MHz flux and spectral index given the prior data.
@@
 
-\begin{figure*}[htbp]
-\begin{center}
-\includegraphics[width=0.9\textwidth]{plots/srcfig_3.png}
-\caption{
-PAPER spectra of 16 sources compared against existing data out of
-\cite{Vollmer:2010p6422} between 40MHz and 2GHz, otherwise as described in
-Figure \ref{fig:pic_spectrum}.\label{fig:srcs3} Sources used to bootstrap the
-flux calibration are noted with a *.
-}
-\end{center}
-\end{figure*}
-
 %(PAPER_imaging)danny@keynes:plots$ python sort_SI_plots.py psa64_pic_stripe_perleycorr_SEDfits.txt
@@
 \begin{center}
-\includegraphics[width=2in]{plots/0003-428_SI_MCMC.png} %0.9878
-\includegraphics[width=2in]{plots/0007-446_SI_MCMC.png} %1.0085
-\includegraphics[width=2in]{plots/0039-445_SI_MCMC.png} %1.3403
-\includegraphics[width=2in]{plots/0043-424_SI_MCMC.png} %0.5959
-\includegraphics[width=2in]{plots/0048-447_SI_MCMC.png} %0.6165
-\includegraphics[width=2in]{plots/0049-433_SI_MCMC.png} %1.0632
-\includegraphics[width=2in]{plots/0103-453_SI_MCMC.png} %0.1456
-\includegraphics[width=2in]{plots/0201-440_SI_MCMC.png} %3.0727
-\includegraphics[width=2in]{plots/0438-436_SI_MCMC.png} %0.0991
-\includegraphics[width=2in]{plots/0511-484_SI_MCMC.png} %3.3967
-\includegraphics[width=2in]{plots/0534-497_SI_MCMC.png} %3.4118
-\includegraphics[width=2in]{plots/0546-445_SI_MCMC.png} %0.1647
+\includegraphics[width=2in]{plots/0003-428_SI_MCMC.png} %0.6363
+\includegraphics[width=2in]{plots/0007-446_SI_MCMC.png} %0.7038
+\includegraphics[width=2in]{plots/0008-421_SI_MCMC.png} %0.3103
+\includegraphics[width=2in]{plots/0039-445_SI_MCMC.png} %0.8007
+\includegraphics[width=2in]{plots/0043-424_SI_MCMC.png} %0.3398
+\includegraphics[width=2in]{plots/0048-447_SI_MCMC.png} %0.6566
+\includegraphics[width=2in]{plots/0049-433_SI_MCMC.png} %0.7536
+\includegraphics[width=2in]{plots/0103-453_SI_MCMC.png} %0.1772
+\includegraphics[width=2in]{plots/0201-440_SI_MCMC.png} %2.8054
+\includegraphics[width=2in]{plots/0438-436_SI_MCMC.png} %0.3053
+\includegraphics[width=2in]{plots/0546-445_SI_MCMC.png} %0.1881
+\includegraphics[width=2in]{plots/0547-408_SI_MCMC.png} %0.3435
+
 \end{center}
@@
 \begin{figure*}[htbp]2\begin{center}
-\includegraphics[width=2in]{plots/0547-408_SI_MCMC.png} %0.1506
-\includegraphics[width=2in]{plots/0647-475_SI_MCMC.png} %0.8384
-\includegraphics[width=2in]{plots/0700-473_SI_MCMC.png} %1.9848
-\includegraphics[width=2in]{plots/0704-427_SI_MCMC.png} %0.0785
-\includegraphics[width=2in]{plots/0748-440_SI_MCMC.png} %0.2942
-\includegraphics[width=2in]{plots/0748-454_SI_MCMC.png} %0.0742
-\includegraphics[width=2in]{plots/0809-492_SI_MCMC.png} %0.6265
-\includegraphics[width=2in]{plots/0819-474_SI_MCMC.png} %0.9749
-\includegraphics[width=2in]{plots/1017-421_SI_MCMC.png} %0.0034
-\includegraphics[width=2in]{plots/1017-426_SI_MCMC.png} %0.0195
-\includegraphics[width=2in]{plots/1046-409_SI_MCMC.png} %0.0012
-\includegraphics[width=2in]{plots/1116-462_SI_MCMC.png} %0.0062
+\includegraphics[width=2in]{plots/0704-427_SI_MCMC.png} %0.2743
+\includegraphics[width=2in]{plots/1017-426_SI_MCMC.png} %0.0266
+\includegraphics[width=2in]{plots/1046-409_SI_MCMC.png} %0.014
+\includegraphics[width=2in]{plots/1215-457_SI_MCMC.png} %0.0514
+\includegraphics[width=2in]{plots/1221-423_SI_MCMC.png} %0.0429
+\includegraphics[width=2in]{plots/1840-404_SI_MCMC.png} %0.2905
+\includegraphics[width=2in]{plots/1932-464_SI_MCMC.png} %0.6859
+\includegraphics[width=2in]{plots/1940-406_SI_MCMC.png} %0.0504
+\includegraphics[width=2in]{plots/1953-425_SI_MCMC.png} %0.3409
+\includegraphics[width=2in]{plots/2140-434_SI_MCMC.png} %0.2824
+\includegraphics[width=2in]{plots/2213-456_SI_MCMC.png} %0.2937
+\includegraphics[width=2in]{plots/2226-411_SI_MCMC.png} %0.2383
+
 \end{center}
@@
 \begin{figure*}[htbp]2\begin{center}
-\includegraphics[width=2in]{plots/1143-483_SI_MCMC.png} %0.004
-\includegraphics[width=2in]{plots/1215-457_SI_MCMC.png} %0.0163
-\includegraphics[width=2in]{plots/1232-416_SI_MCMC.png} %0.0227
-\includegraphics[width=2in]{plots/1243-412_SI_MCMC.png} %0.0076
-\includegraphics[width=2in]{plots/1246-410_SI_MCMC.png} %0.06
-\includegraphics[width=2in]{plots/1247-401_SI_MCMC.png} %0.1161
-\includegraphics[width=2in]{plots/1302-491_SI_MCMC.png} %0.5328
-\includegraphics[width=2in]{plots/1355-416_SI_MCMC.png} %0.1959
-\includegraphics[width=2in]{plots/1358-493_SI_MCMC.png} %0.7284
-\includegraphics[width=2in]{plots/1421-490_SI_MCMC.png} %1.3529
-\includegraphics[width=2in]{plots/1424-418_SI_MCMC.png} %0.0218
-\includegraphics[width=2in]{plots/1445-468_SI_MCMC.png} %1.8104
+\includegraphics[width=2in]{plots/2250-412_SI_MCMC.png} %0.3487
+\includegraphics[width=2in]{plots/2323-407_SI_MCMC.png} %7.8431
+\includegraphics[width=2in]{plots/2331-416_SI_MCMC.png} %0.3356
 \end{center}
-\caption{Spectral model contours as described in Figure \ref{fig:pic_spectrum}. Sources marked with a
+\caption{fits of the next 16 sources, as described in Figure \ref{fig:SI_contour_1}. Sources marked with a
 * were used to assess calibration error.
@@
 \end{figure*}
-\clearpage
-\begin{figure*}[htbp]2\begin{center}
-\includegraphics[width=2in]{plots/1526-423_SI_MCMC.png} %0.1985
-\includegraphics[width=2in]{plots/1552-433_SI_MCMC.png} %1.3211
-\includegraphics[width=2in]{plots/1556-466_SI_MCMC.png} %2.5579
-\includegraphics[width=2in]{plots/1616-457_SI_MCMC.png} %0.0507
-\includegraphics[width=2in]{plots/1618-430_SI_MCMC.png} %3.821
-\includegraphics[width=2in]{plots/1633-409_SI_MCMC.png} %1.3843
-\includegraphics[width=2in]{plots/1839-487_SI_MCMC.png} %0.1766
-\includegraphics[width=2in]{plots/1840-404_SI_MCMC.png} %0.1658
-\includegraphics[width=2in]{plots/1932-464_SI_MCMC.png} %0.4321
-\includegraphics[width=2in]{plots/1940-406_SI_MCMC.png} %0.0325
-\includegraphics[width=2in]{plots/1953-425_SI_MCMC.png} %0.1181
-\includegraphics[width=2in]{plots/2140-434_SI_MCMC.png} %0.2976
+%BOTTOM OF MAIN CONFIDENCE PLOT SECTION
+%%%%%%%%%%%%%%%%%%%%
+
+%BEGIN PASTE
+
+\begin{figure*}[htbp]
+\begin{center}
+%zero overlap
+\includegraphics[width=2in]{plots/1424-418_SI_MCMC.png} %0.0
+\includegraphics[width=2in]{plots/1526-423_SI_MCMC.png} %0.0
+
 \end{center}
-\caption{Spectral model contours as described in Figure \ref{fig:pic_spectrum}. Sources marked with a
-* were used to assess calibration error.
-}\label{fig:SI_contour_4}
+\caption{
+These fits are somehow at odds with other measurements.
+The 1526-42 spectrum is visibly curved (see Fig.
+\ref{fig:srcs1), which explains the large disagreement in spectral index but not flux.
+1424-418 is an optically polarized quasar with a flat and variable radio spectrum which might imply co-aligned jet viewing and high intrinsic variability.
+} \label{fig:SI_contour_new}
 \end{figure*}
-\clearpage
-\begin{figure*}[htbp]2\begin{center}
-\includegraphics[width=2in]{plots/2213-456_SI_MCMC.png} %0.2146
-\includegraphics[width=2in]{plots/2226-411_SI_MCMC.png} %0.3157
-\includegraphics[width=2in]{plots/2250-412_SI_MCMC.png} %0.5585
-\includegraphics[width=2in]{plots/2323-407_SI_MCMC.png} %4.9008
-\includegraphics[width=2in]{plots/2331-416_SI_MCMC.png} %0.8134
-\end{center}
-\caption{fits of the last 5 sources, as described in Figure \ref{fig:SI_contour_1}. Sources marked with a
-* were used to assess calibration error.
-}\label{fig:SI_contour_5}
-\end{figure*}%BOTTOM OF MAIN CONFIDENCE PLOT SECTION
-%%%%%%%%%%%%%%%%%%%%
-
-%BEGIN PASTE
+
 \begin{figure*}[htbp]
@@
 %ok fit, but doesn't agree with past data, or actually increases model uncertainty
-%contour length limit =  223.105907705
-%Poor improvement:  1407-425 14.03,15.48,16.92 -1.23,-1.11,-0.99 9.88,11.36,12.93 -1.08,-0.95,-0.82 0.4 0.41 -0.01 0.07 -0.0006 118.0
-\includegraphics[width=2in]{plots/1407-425_SI_MCMC.png} %-0.0006
-\caption{Contours of spectral fit as described in Figure \ref{fig:SI_contour_1}. This source displays negative 
-improvement. The addition of the PAPER data actually slightly increases the uncertainty.
-\label{fig:SI_contour_bad}}
+%contour length limit =  196.42253912
+%Poor improvement:  1017-421 11.88,13.56,15.22 -1.2,-1.08,-0.96 12.03,13.82,15.68 -1.22,-1.09,-0.96 0.25 0.25 -0 0.6 -0.0011 172.0 0
+\includegraphics[width=2in]{plots/1017-421_SI_MCMC.png} %-0.0011
 \end{center}
+\caption{A source with a slightly negative improvement index (-0.0011).  Here the PAPER data represents a large fraction of the available data
+but due to the large error bars slightly increases the uncertainty.
+}\label{fig:SI_contour_bad}
 \end{figure*}
 
-\begin{figure*}[htbp]
-\begin{center}
-%zero overlap
-\includegraphics[width=2in]{plots/1221-423_SI_MCMC.png} %0.0
-\includegraphics[width=2in]{plots/1315-460_SI_MCMC.png} %0.0
-\includegraphics[width=2in]{plots/1320-446_SI_MCMC.png} %0.0
-\includegraphics[width=2in]{plots/1416-493_SI_MCMC.png} %0.0
-\includegraphics[width=2in]{plots/1459-417_SI_MCMC.png} %0
-\includegraphics[width=2in]{plots/cen_SI_MCMC.png} %0.0
-\end{center}
+%END PASTE
+
+\begin{figure*}
+\includegraphics[width=\textwidth]{plots/psa64_pic_strip_positions_psa747_v2_annotated_cropped.png}
 \caption{
-These sources are at odds with previous measurements.
-Two simply do not have enough
-prior catalog data to fit a spectral model, while the rest have
-suggest a deviation from the catalog spectral index fit.
-All are near Centaurus A (see Figure
-\ref{fig:error_map}), a very bright, extended source, as well as the galactic plane.
-Side lobes manifest as
-ripples in the beam formed spectra which increases the error bars. See for example the 
-Pictor A spectrum \ref{fig:pic_spectrum_detail}. However, the sources shown here are close
-enough to Centaurus A that the side-lobe oscillates on scales longer than 10MHz
-and does not fall into the rms, but rather into the mean. Thus these few points
-have anomalously high fluxes and small error bars. 
-} \label{fig:SI_contour_new}
-\end{figure*}
-
-%END PASTE
-
-\begin{figure*}
-\includegraphics[width=\textwidth]{plots/psa64_pic_strip_positions_annotated_cropped.pdf}
-\caption{
-A map of the radio sky centered on the south pole
-\citep{deOliveiraCosta:2008p2242}.  x's mark measured locations and have size
+A PAPER map of the radio sky centered on the south pole showing relative positions of targeted sources. The map was made using the July half of the
+data used in this catalog using the procedure described in \citet{Jacobs:2011p8438} to produce a lightly CLEANed map.
+The circular artifact around the south Celestial pole is due to residual instrumental cross-talk and appears to be highly localized below declinations of 75\arcdeg where PAPER's sensitivity is small.
+x's mark measured source locations and have size
 scaled by dis-agreement with prior data (inverse ``improvement index" from 
-\S\ref{sec:fits}). Smaller indicates better agreement with past data.  Black dots indicate sources with $\le0$ improvement score;
-agreement decreases with addition of PAPER data (see Figures \ref{fig:SI_contour_bad} and \ref{fig:SI_contour_new}). 
-This is most likely due to galactic, and Centaurus A, side lobes.    \label{fig:error_map}
+\S\ref{sec:fits}). Smaller indicates better agreement with past data.  Orange dots indicate sources with no model overlap at 76\% \ref{fig:SI_contour_new}. 
+\label{fig:error_map}
 }
@@
 \tablecolumns{13}
-\tablecaption{PAPER spectra for 59 MRC sources. Full table available online}
+\tablecaption{PAPER spectra for 32 MRC sources}
 \tablehead{
@@
 \startdata
-Pictor A&	80.1&	-45.79&	459.23&	30.2&	416.59&	28.3&	397.17&	21.8&	375.14&	18.5&	359.72&	17.1 \\
-0003-428&	1.67&	-42.5&	14.98&	2.0&	13.45&	1.2&	13.02&	1.8&	12.9&	1.6&	10.42&	1.2 \\
-0007-446&	2.79&	-44.31&	23.51&	2.5&	21.18&	2.4&	20.24&	1.5&	18.74&	1.5&	17.61&	1.8 \\
-0008-421&	2.88&	-41.81&	-0.94&	1.7&	-0.68&	1.7&	0.54&	1.8&	0.52&	1.4&	1.98&	1.8 \\
-0039-445&	10.69&	-44.16&	31.95&	2.9&	30.29&	3.0&	28.54&	2.1&	26.0&	1.9&	24.06&	1.4 \\
-0043-424&	11.72&	-42.05&	51.9&	4.2&	47.43&	3.5&	45.82&	2.6&	42.74&	3.0&	40.68&	2.6 \\
-0048-447&	12.86&	-44.41&	17.86&	2.6&	16.02&	2.3&	15.15&	2.5&	14.51&	1.5&	12.51&	1.6 \\
-0049-433&	13.21&	-43.03&	23.53&	2.4&	21.0&	1.5&	21.94&	2.4&	20.2&	1.9&	18.85&	2.1 \\
-0103-453&	16.48&	-45.02&	35.5&	3.2&	32.61&	3.5&	30.86&	2.4&	28.21&	2.5&	27.2&	1.5 \\
-0201-440&	31.05&	-43.77&	16.22&	4.4&	15.02&	1.7&	13.73&	1.7&	12.78&	1.2&	14.07&	1.7 \\
-0438-436&	70.17&	-43.53&	8.44&	2.5&	6.26&	1.9&	8.05&	1.6&	5.74&	2.1&	9.0&	1.7 \\
+Pictor A&	80.09&	-45.78&	455.3&	13.3&	409.6&	15.8&	389.2&	12.4&	363.5&	11.1&	350.6&	9.1 \\
+0003-428&	1.68&	-42.5&	14.5&	1.7&	13.1&	1.4&	12.8&	1.2&	12.6&	1.1&	10.3&	1.0 \\
+0007-446&	2.8&	-44.3&	23.2&	2.2&	21.1&	2.2&	20.2&	1.7&	18.6&	1.4&	17.2&	1.6 \\
+0008-421&	2.89&	-41.81&	-0.2&	0.8&	-0.3&	1.0&	0.9&	0.9&	0.7&	0.9&	1.3&	1.0 \\
+0039-445&	10.7&	-44.16&	29.2&	3.0&	27.6&	2.2&	26.4&	2.2&	24.0&	1.6&	22.2&	1.5 \\
+0043-424&	11.73&	-42.05&	48.6&	4.2&	45.2&	3.5&	43.9&	2.3&	40.8&	2.2&	38.4&	2.4 \\
+0048-447&	12.87&	-44.4&	16.2&	1.7&	14.6&	1.3&	13.7&	1.6&	13.3&	1.3&	11.3&	1.2 \\
+0049-433&	13.22&	-43.03&	20.9&	2.5&	19.0&	2.2&	20.8&	2.2&	19.0&	1.5&	17.4&	1.2 \\
+0103-453&	16.48&	-45.02&	31.3&	3.0&	29.0&	2.7&	27.1&	2.9&	25.4&	1.8&	24.3&	2.0 \\
+0201-440&	31.05&	-43.76&	13.6&	2.2&	12.6&	1.5&	11.7&	1.0&	11.0&	1.0&	12.0&	1.2 \\
+0438-436&	70.17&	-43.53&	9.5&	1.4&	6.0&	0.7&	6.6&	0.6&	5.8&	0.7&	10.5&	1.0 \\
 
@@
 %note: put at top of latex file \newcommand{\unit}[1]{\footnotesize \#1}
-\begin{deluxetable}{ccccccccccc}
-\tablecolumns{11}
-\tablecaption{Spectral fits for 52 MRC sources with and without PAPER.}
+\begin{deluxetable}{cccccccccccc}
+\tablecolumns{12}
+\tablecaption{Spectral fits for 31\tablenotemark{1} MRC sources. Before and after the addition of PAPER data. 90\% agree well with prior
+measurements and demonstrate increased precision over previous measurements. Full table available online.}
 \tablehead{
 \multicolumn{3}{c}{ }&
-\multicolumn{4}{c}{PAPER\tablenotemark{1} + Catalog}&
-\multicolumn{4}{c}{Catalog\tablenotemark{2}}\\
+\multicolumn{4}{c}{PAPER + Catalog}&
+\multicolumn{4}{c}{Catalog\tablenotemark{2}}&\\
 \colhead{Name} &
@@
 \colhead{\parbox[c][3em]{2em}{$\alpha_p$\\ \unit{--}}} &
-\colhead{\parbox[c][3em]{2em}{$\Delta\alpha_p$\\ \unit{--}}}
+\colhead{\parbox[c][3em]{2em}{$\Delta\alpha_p$\\ \unit{--}}} &
+\colhead{\parbox[c][3em]{2em}{Imp.\tablenotemark{3}\\ \unit{--}}}
 }
 \startdata
-Pictor A&	80.09&	-45.79&	388.92&	9.35&	-0.77&	0.02&	392.08&	21.36&	-0.77&	0.04 \\
-0003-428&	1.67&	-42.5&	11.61&	0.54&	-0.81&	0.03&	10.32&	0.76&	-0.73&	0.05 \\
-0007-446&	2.79&	-44.31&	18.74&	0.69&	-1.0&	0.03&	16.98&	1.26&	-0.93&	0.05 \\
-0039-445&	10.69&	-44.16&	26.77&	1.08&	-0.92&	0.11&	22.71&	5.1&	-0.79&	0.19 \\
-0043-424&	11.72&	-42.05&	43.6&	1.46&	-0.79&	0.11&	36.16&	4.97&	-0.69&	0.13 \\
-0048-447&	12.86&	-44.41&	13.21&	0.64&	-0.98&	0.04&	11.58&	0.88&	-0.89&	0.05 \\
-0049-433&	13.21&	-43.03&	20.16&	0.77&	-0.97&	0.03&	20.54&	1.53&	-0.98&	0.05 \\
-0103-453&	16.48&	-45.02&	28.9&	1.14&	-1.16&	0.11&	21.76&	2.93&	-1.04&	0.12 \\
-0201-440&	31.05&	-43.77&	13.72&	0.9&	-0.71&	0.12&	10.31&	6.54&	-0.51&	0.42 \\
-0438-436&	70.17&	-43.53&	8.08&	0.74&	-0.19&	0.09&	8.32&	1.09&	-0.21&	0.1 \\
-0511-484&	78.3&	-48.39&	24.92&	1.59&	-1.14&	0.09&	17.3&	10.7&	-0.93&	0.39
+Pictor A&	80.09&	-45.78&	381.88&	5.36&	-0.76&	0.01&	392.63&	21.18&	-0.77&	0.04&	0.942 \\
+0003-428&	1.68&	-42.5&	12.24&	0.61&	-0.86&	0.11&	12.42&	2.75&	-0.86&	0.19&	0.636 \\
+0007-446&	2.8&	-44.3&	19.17&	0.82&	-1.02&	0.11&	18.08&	4.0&	-0.98&	0.19&	0.704 \\
+0008-421&	2.89&	-41.81&	5.68&	2.13&	-0.03&	0.22&	9.67&	4.11&	-0.32&	0.24&	0.31 \\
+0039-445&	10.7&	-44.16&	24.78&	0.91&	-0.86&	0.12&	22.6&	4.96&	-0.78&	0.19&	0.801 \\
+0043-424&	11.72&	-42.05&	41.69&	1.27&	-0.77&	0.1&	36.14&	4.93&	-0.69&	0.12&	0.34 \\
+0048-447&	12.87&	-44.4&	13.24&	0.64&	-0.99&	0.12&	13.37&	2.81&	-0.99&	0.19&	0.657 \\
+0049-433&	13.22&	-43.03&	18.99&	0.84&	-0.91&	0.11&	21.2&	4.58&	-1.01&	0.2&	0.754 \\
+0103-453&	16.48&	-45.02&	25.73&	1.07&	-1.11&	0.1&	21.75&	2.85&	-1.04&	0.12&	0.177 \\
+0201-440&	31.05&	-43.76&	11.71&	0.66&	-0.6&	0.12&	10.19&	6.72&	-0.5&	0.44&	2.805 \\
+0438-436&	70.17&	-43.53&	7.51&	0.38&	-0.14&	0.08&	8.35&	1.13&	-0.21&	0.1&	0.305 \\
 
@@
 \label{tab:fits}
-\tablenotetext{1}{Fits for the majority of sources (78\%) that agree with prior measurements are included here. 
-The remainder (the 6 sources shown in Figure \ref{fig:SI_contour_new}) are likely contaminated by bright sources and are not included.   Full table available online.}
-
+\tablenotetext{1}{0008-421 is self-absorbed at 150MHz and is not listed here, while 1 did not have sufficient catalog data
+for a spectral fit and was also excluded}
 \tablenotetext{2}{MCMC fits to prior catalog data, before addition of PAPER measurements}
+\tablenotetext{3}{SED figure of merit change times confidence overlap, a measure of accuracy and precision.  Higher
+value indicates an increase in both model fit precision and accuracy.}
 \end{deluxetable}

### 2013-06-10 plots/cat_to_mrt.py
tweaking captions on cat_to_mrt

@@ -55,7 +55,7 @@ for i,line in enumerate(lines):
     spec = line[1].split(',')
     err = line[2].split(',')
     for v,e in zip(spec,err):
-        rec.append(str(n.round(float(v),2)))
+        rec.append(str(n.round(float(v),1)))
         rec.append(str(n.round(float(e),1)))
     if i==0:
         print "UNITS:"

### 2013-06-10 plots/SED_fit_to_mrtprep.py
adding Improvement to table/tab2 on SED_fit_to_mrtprep

@@ -24,9 +24,13 @@ else:
 
 lines = open(args[-1]).readlines()
 lines = [line.split() for line in lines if not line.startswith('#')]
+#exclude sources with no catalog fit
+nocatfits = [l for l in lines if l[3].startswith('-1')]
+lines = [l for l in lines if not l[3].startswith('-1')]
 srclist = [l[0] for l in lines]
 overlap = n.array([n.float(line[8]) for line in lines])
-
+improvement = n.array([n.float(line[9]) for line in lines])
+print "found %d sources, %d with zero overlap"%(len(srclist),n.sum(overlap==0))
 #if not opts.cat is None:
 srclist,cutoff,catalogs = a.scripting.parse_srcs(','.join(srclist), opts.cat)
 if not opts.cal is None:
@@ -51,7 +55,7 @@ picrec = None
 total = 0
 for i,line in enumerate(lines):
     rec = []
-    if overlap[i]==0: continue
+    #if overlap[i]==0: continue
     if line[0] == 'pic':
         rec.append('Pictor A')
         picrec = total
@@ -69,18 +73,20 @@ for i,line in enumerate(lines):
 #    rec.append(line[3]) #catalpha
 #    rec.append(line[4])
     S0 = l2a(line[1])
-    rec.append(p(S0[1],2))
+    rec.append(p(S0[1],1))
     rec.append(p(n.abs((S0[-1]-S0[0]))/2,2))
     alpha = l2a(line[2])
     rec.append(p(alpha[1],2))
     rec.append(p(n.abs(alpha[-1] - alpha[0])/2,2))
     catS0 = l2a(line[3])
-    rec.append(p(catS0[1],2))
+    rec.append(p(catS0[1],1))
     rec.append(p(n.abs(catS0[-1]-catS0[0])/2,2))
     catalpha = l2a(line[4])
     rec.append(p(catalpha[1],2))
     rec.append(p(n.abs(catalpha[-1] - catalpha[0])/2,2))
-    
+    rec.append(p(improvement[i],3))
+    #if overlap[i]==0: rec.append('1')
+    #else:rec.append('0')
     if i==0:
         print "UNITS:"
         print '--'
@@ -94,6 +100,7 @@ for i,line in enumerate(lines):
         print 'Jy' #catalog S150 +/- 76% conf
         print '--' #catalog alpha
         print '--' #catalog alpha +/- 76% conf
+        print '--' #improvement
 
         #column names
[…]

### 2013-06-12 ms.tex
All citations work. Partway through updating text.

@@
 \usepackage{amsmath}
+\usepackage{xcolor}
 %\usepackage{graphicx}
@@
 \newcommand{\Nsrc}{32}
+\definecolor{orange}{RGB}{255,127,0}
 
@@
 as well as \Nconf other sources at nearby declinations. Extrapolating from higher frequency
-catalogs we set the flux scale in a monte-carlo fit across multiple sources. This fit 
+catalogs we set the flux scale in a Monte-C`arlo fit across multiple sources. This fit 
 propagates uncertainty from both catalog and measurement errors. Fitting new spectral 
@@
 emission during the Epoch of Reionization (EoR), such as the Compact
-Reionization Experiment (CoRE) and the Experiment to Detect the Global EoR
+Reionization Experiment (CoRE), the Zero-spacing Interferometer \citep{Raghunathan:2011}  and the Experiment to Detect the Global EoR
 Signature (EDGES; \citealt{Bowman:2010p8546}), and interferometers aiming to
@@
 the Donald C. Backer Precision Array for Probing the Epoch of Reionization
-(PAPER; \citealt{Parsons:2010p6757,Parsons2013b})\footnote{\url{http://eor.berkeley.edu/}}.
+(PAPER; \citealt{Parsons:2010p6757,Pober:2013p9567})\footnote{\url{http://eor.berkeley.edu/}}.
 
@@
 the $z=6$--13 redshift range expected to encompass reionization
-\citep{furlanetto_et_al2006}.
+\citep{Furlanetto:2006p2267}.
 In particular, the spectral properties of extra-galactic point-sources are important
@@
 With the sparse availability of measured foreground properties in the
-100--200-MHz frequency band over large areas of the sky \citep{deolivieracosta_et_al2008}, continued
+100--200-MHz frequency band over large areas of the sky \citep{deOliveiraCosta:2008p2242}, continued
 foreground characterization is a
@@
 with catalog source fluxes at 150MHz being inaccurate at the 20\% level
-for $\delta<-20$\arcdeg (XXX cite).
+for $\delta<-20$\arcdeg \citep{Slee:1995p7541,Vollmer:2005p6425}.
 Both PAPER and the MWA are located in the southern hemisphere at radio-quiet
@@
 is that many 21cm EoR experiments, including LOFAR in the northern hemisphere, and
-PAPER and MWA in the southern hemisphere, are designed for drift-scan observations.
+PAPER and MWA in the southern hemisphere, are designed for drift-scan observations or steered via phased array.
 This design decision has largely been driven by the simplicity and cost-effectiveness of
-phased and/or correlated dipoles for achieving the aggressive sensitivity requirements
-for measuring the 21cm power spectrum of reionization (XXX cite).
+phased and/or correlated dipoles to achieve the aggressive sensitivity requirements
+for measuring the 21cm power spectrum of reionization.
+%TODO ARP wanted a cite for the above.  I really don't know of a good one. Its it a bit of a broad statement
 Adding to the challenge, these telescopes 
@@
 This direction dependent gain is currently uncertain to 10\% or higher
-% XXX 20% seems a bit grim.  Doesn't jonnie argue for 5 to 10% in his paper?
-%XXX 20\% comes from the overall uncertainty between MWA and PAPER, part of which is also side lobes. 
-%	Jonnie's fluxes are dominated by the side lobes in the pgb16 data, the fluxes have a range of errors around 15 to 20%
 \citep{Pober:2012p8800}, and comprises a large fraction of the 20\% difference between current telescopes \citep{Jacobs:2013p9713}.
@@
 % XXX update document map
-In \S\ref{sec:analysis} we describe our approach for measuring source spectra with
+In section \ref{sec:background} we provide some background on uncertainty in early EoR-band catalogs,
+and explain our choice of calibrator. Section \ref{sec:approach} gives an overview 
+of our approach to making the measurement and motivates our data processing steps, which 
+are described in detail in section \ref{sec:Observations}. In section
+
+In section \ref{sec:approach} we describe our approach for measuring source spectra with
 drift-scan observations and deriving an absolute flux scale from catalog data.  
 In \S\ref{sec:Observations} we detail the instrumental 
-setup, observations and analysis method followed. In \S\ref{sec:fits} we
-compare the spectra with available data.  We conclude in 
-\S\ref{sec:Conclusion}.
+setup, observations and analysis method followed. Sections \ref{sec:mcmc} through
+\ref{fig:gain} detail our approach for fitting a global flux scale and spectral models for each source.
+We use these fits in section \ref{sec:results} to understand how well PAPER data agree
+with previous measurements and conclude in \ref{sec:Conclusion}.
 
@@
 \section{Background}
-
+\label{sec:background}
 % XXX unsure about this section.  need someplace to give overviews of catalogs
@@
 Since November 2011 it has been arranged in a maximally redundant grid 
-configuration to make deep power spectral integrations \citep{Parsons:2012a}.
+configuration to make deep power spectral integrations \citep{Parsons:2012p9028}.
 Though highly sensitive as a power spectrum instrument, the maximally redundant array 
@@
 weighted by an additional factor of PAPER's primary beam response 
-\citep{pober_et_al2012}.  
+\citep{Pober:2012p8800}.  
 \begin{align}
@@
 which is an effective approximation of inverse-variance weighting. The pre factor in Eq \ref{eq:g} is identical for 
-sources at the same declination.  In simulation we multiplied an early attempt to map the beam \cite{Pober:2012p8800}
-by electromagnetic simulations of the PAPER beam and find that it 
+sources at the same declination.  In simulation we multiplied an early holographic beam map \cite{Pober:2012p8800}
+by electromagnetic simulations and find that it 
 diverges slowly with declination, with a maximum of 10\% over 5\arcdeg of declination range.
@@
 
- Finally we average the spectra from a resolution of 400kHz to 10MHz bins, taking the standard deviation within these bins
- for an estimate of the uncertainty.
+ Finally we average the spectra from a resolution of 400kHz to 10MHz bins, adding the individual errors in quadrature
+ as our uncertainty.
 
 At this point we have a set of spectra that have been calibrated relative to each other to the best of our ability. Now 
-they must be put on a global flux scale. We also have only a limited estimate of our error from our intra-channel
-rms.  To address both points we fit for a global flux scale that incorporates data from many catalogs. These catalogs
+they must be put on a global flux scale. Meanwhile, our error estimate does not include an estimate of the 
+flux calibration error.  To address both points we fit for a global flux scale that incorporates data from many catalogs. These catalogs
 have all been set, as best as possible, to the Baars et al scale.  Using a Bayesian analysis we compute the 
-variation in the flux scale implied by comparing many sources to prior catalog. By including sources from across
+variation in the flux scale implied by comparing many sources to prior catalog models. By including sources from across
 the declination range,the variation in this flux scale fit estimates the overall uncertainty in flux resulting from primary beam 
-or prior catalog uncertainty.  So though the final scale is calibrated to the Baars scale as extrapolated beyond its
-defined band, the error on the flux scale fully encapsulates the error resulting from this extrapolation.
+or prior catalog uncertainty.  Though the final scale is calibrated to the Baars scale, as extrapolated beyond its
+lower limit of 300 MHz, the flux scale error derived by this method fully describes the error resulting from this extrapolation.
 
@@
 over a factor of 40.  A more detailed description may be found in Appendix A of
-\cite{Parsons2013b}, which uses the same compression method on PAPER power
+\cite{Parsons:2013p9876}, which uses the same compression method on PAPER power
 spectrum observations. Here we summarize the process.
@@
 
-% XXX merge with below
-%Removed RFI by flagging samples in each frequency channel versus time that exceed the mean amplitude by 4-sigma
-%after performing a time derivative.  Also flagged samples in each integrated spectrum that exceeded the
-%mean amplitude across the spectrum by 6-sigma after performing a frequency derivative.  For efficiency, flagging
-%was derived using only the subset of baselines involving a fiducial antenna.
-%Frequencies below 120 MHz and above 180 MHz were also flagged, owing to roll-off of analog response.
-%After RFI flagging, frequency channel resolution was decreased by a factor of four by summing channels.
-
-%I'm Confused.  These are describing a different ordering of steps. Must re-read compression script.
-
 %CALIBRATION
@@
 receiver amplifiers were used to divide out the predicted gain variation versus temperature that these amplifiers
-are known to exhibit.  A predicted gain profile was derived using coefficients characterized in
-laboratory measurements \citep{parashare_bradley2009} and
-confirmed in field measurements \citep{pober_et_al2011} of $H_{\rm balun}=-0.024$ dB/K, $H_{\rm recvr}=-0.045$
-dB/K, and $H_{\rm cable}=-0.018$ dB/K for 150m-long cables.  Because cable temperatures were not measured
-during these observations, the cable temperature was assumed to be the same as the measured balun temperature.
+are known to exhibit.  Inspecting the auto correlations we find that the net temperature gain coefficient (-0.042 dB/C) found in previous laboratory \cite{Parashare:2011p9872} and early field 
+measurements  \cite{Pober:2012p8800} did not appear to remove all temperature variation (black curve in Figure \ref{fig:auto_compare}).  To
+revise the temperature coefficient we use the October observations, when the temperatures remained nearly constant, as a reference.
+
+Comparing the average ratio between the July and October autocorrelations to their temperature difference (Figure \ref{fig:autos_tempcorr}) we find that the two are highly correlated  with 
+a best fit temperature coefficient of (-0.058 dB/C). As we see in the Figure \ref{fig:auto_compare}, this removes a significant amount of disagreement between the two nights, 
+with the peak difference decreasing from 18\% to 3\%.
+\begin{figure}
+\includegraphics[width=0.9\textwidth]{plots/auto_tempcorr.png}
+\caption{Calibrating the temperature coefficient by comparing the two nights.
+Here we plot the ratio of auto-correlations (averaged over frequency and antenna) against the temperature difference between the two data sets.
+The very linear middle region has a slope of  -0.055 dB/C while the full, more complex, range is fit by -0.06dB/C (black line).
+We compromise by choosing -0.058dB/C.
+\label{fig:autos_tempcorr}}
+\end{figure}
+\begin{figure}
+\includegraphics[width=0.9\textwidth]{plots/auto_balance.png}
+\caption{Gain differences between the July and October nights are dominated by temperature variation. Here we see the affect on 
+the average auto correlation before ({\color{orange} orange}) and after (black) application of the temperature dependent gain. \label{fig:auto_compare}}
+\end{figure}
 
@@
 averaging over the three independent solutions. These same calibration
-solutions have been successfully applied in \citet{Pober:2013XXX} and \citet{Stefan:2013:XXX}.
+solutions have been successfully applied in \citet{Pober:2013p9567} and \citet{Stefan:2012p9707}.
 for power-spectrum analysis of foregrounds and imaging of Centaurus A, respectively.
@@
 the residual bandpass due to the net effect of the primary beam as discussed in \S \ref{sec:approach}. J2331-416 
-\footnote{Here we set the spectrum to $S_{150}=33$Jy, $\alpha=-0.76$} fit to measurements beolow 1GHz \citep{slee1995,kuhr_et_al1981,large_et_al1981,burgess_hunstead2006}.
+\footnote{Here we set the spectrum to $S_{150}=33$Jy, $\alpha=-0.76$} a somewhat arbitrary 
+fit to measurements below 1GHz \citep{Slee:1995p7541,Kuehr:1981p9628,Large:1981p7798,Burgess:2006p7814}.
 was selected for its relatively high brightness, spectral smoothness and large quantity
@@
 \subsection{Fitting a Power-Law Model to Spectra}
+\label{sec:mcmc}
 
@@
 
-Here we use the emcee sampler by \citet{Mackay:2003p9717} et al to generate chains of
+Here we use the \emph{emcee} sampler by \citet{Mackay:2003p9717} et al to generate chains of
 parameter values. The best fit model is the median of all the sampled
@@
 the complete set are shown in grey in Figs. \ref{fig:SI_contour_1} -
-\ref{fig:SI_contour_4}.  In general these are lower limits on the possible
+\ref{fig:SI_contour_2}.  In general these are lower limits on the possible
 precision, as the Vollmer catalog emphasizes minimization of cross-match error
@@
 \section{Results and Discussion}
-\label{sec:fits}
+\label{sec:results}
 %TODO Revise all the numbers in this session.
 %now we have 32 sources (counting pic)
-% 25 have >0 improvement
-% 0 have negative
-% 6 have 0 overlap
-In the 59 sources measured, four demonstrated poor convergence fitting a single
-spectral index to both the PAPER data and prior catalog data. In three
-cases\footnote{1243-412,1247-401,1315-460} %TODO update these sources are in
-the Centaurus A/galactic plane region. Though the beam forming method provides
-relatively high dynamic range of $\sim$100:1 it is unable to distinguish
-between these sources and the bright diffuse Centaurus and galactic structure.
-The last source, 0008-421, was not detected by previous PAPER observations and
+%%>0 improvement: 27
+%%<0 improvement: 1
+%%=0 improvement: 3
+%total 31
+The majority of the \Nsrc models fit using the new PAPER data were found to agree with
+models fit to past data and all but two are suitable for comparison.  
+0008-421 was not detected by previous PAPER observations and
 exhibits flattening at higher frequencies, most likely due to synchrotron
-self-absorption \citep{Jacobs:2011p8438} .  The remaining 94\% MCMC chains
-arrived at a stable posterior distribution. The spectral index parameters for
-these chains are given in table \ref{tab:fits}.
-
-Inspecting the confidence contours we find that, for the vast majority ($\sim
-75$\%), the PAPER measurements confirm the power law extrapolation from higher
-frequencies. The remaining 25\% either A) have large PAPER error bars and
+self-absorption \citep{Jacobs:2011p8438}. While 1459-417 does not have enough 
+measurements in the Vollmet et al catalog on which to build a model for comparison. We exclude these 
+two from further analysis.
+
+Inspecting the remaining 29 confidence contours we find that, for the vast majority ($\sim
+90$\%), the PAPER measurements confirm the power law extrapolation from higher
+frequencies. The remaining 10\% either A) have large PAPER error bars and
 therefore provide no new information or B) do not agree with the spectral index
@@
 in precision (confidence area shrinks) by a factor of 3, the resulting {\em
-improvement} will be 0.123.
-
-In these sources, the improvement index ranges from a max of 6.9 to -0.022.
-10\% of sources showed negative improvement, suggesting that PAPER data have
-added to uncertainty (see Figure \ref{fig:SI_contour_bad}). 12\% of sources
+improvement} will be 0.123.  This Improvement Index is included in the table
+of fit parameters (Table \ref{tab:fits}).
+
+In these sources, the improvement index ranges from a maximum of 7.84  to -0.001.
+One source (1017-421) shows a slightly negative improvement, suggesting that PAPER data have
+added to uncertainty (see Figure \ref{fig:SI_contour_bad}), while two sources
 have exactly zero improvement, which indicates that the PAPER data have pulled
 the fit far from the model preferred by the catalog data (see Fig.
-\ref{fig:SI_contour_new}).  The spectral models of these sources have not been
-included in Table \ref{tab:fits}.  The remainder of the spectral fits are
-included for completeness, but given the range of quality found, particularly
-near the Galactic plane and Centaurus A, should be used with utmost caution.
-
-However, the majority of source 78\% have positive improvement index,
+\ref{fig:SI_contour_new}).
+
+However, the vast majority of sources (90\%) have positive improvement index,
 indicating strong confirmation of the extrapolated spectrum (see Figures
-\ref{fig:SI_contour_1} - \ref{fig:SI_contour_4}).  Pictor A is in the middle of
-this group  with an improvement of 0.39 ---only 14 sources show stronger
-confirmation.  The flux model is $S150=$388 $\pm$ 9.4Jy, $\alpha=-0.77\pm0.02$.
+\ref{fig:SI_contour_1} - \ref{fig:SI_contour_3}).  Pictor A is in the middle of
+this group  with an improvement of 0.942 ---only two sources show stronger
+confirmation.  The flux model is $S150=$381 $\pm$ 5.36Jy, $\alpha=-0.76\pm0.01$.
 The combination of several independent PAPER data points near 150MHz with
-previous catalog measurements results in this estimated uncertainty of 2.4\%.
-This uncertainty is dominated by agreement between the 2 Wills measurements
-near 600MHz which are accurate to 2\% and the five PAPER measurements, which
-are accurate to ~5\%.  This error estimate includes an estimate of accuracy of the overall flux scale,
-as well as the source-source variation due to primary beam errors.
+previous catalog measurements results in this estimated uncertainty of 1.4\%.
+This uncertainty is quite small, but is not surprising when we consider that we have
+used 7 precise data points (5 PAPER, 2 Wills), all accurate to 3\% to measure what appears to
+be an extremely linear power law spectrum. If the errors were completely guassian
+the net error would be $3/\sqrt(7) = 1.14$\%.
 
@@
 \caption{
-The marginalized PAPER flux scale factor posterior probability distribution
-function bootstrapped from the NED database listings for
-2250-412,2331-416,1932-464,0103-453,0547-408,0043-424 below 2GHz.
+The marginalized posterior of the PAPER flux scale factor relative to 2331-416. Given a joint fit to all the
+ NED database listings for
+2250-412,2331-416,1932-464,0103-453,0547-408,0043-424 below 2GHz and the corresponding PAPER values. The 76\% confidence 
+interval on this distribution is used to set the overall flux scale. While the width is an additional fractional error to be added quadratically to the per-source uncertainty.  
+By averaging over many sources and and Baars calibrated data points, this uncertainty encapsulates error due to both primary beam model inaccuracy 
+as well as the average flux scale uncertainty due to extrapolating many absolutely calibrated measurements.
 \label{fig:gain}}
@@
 Figure \ref{fig:pic_spectrum}.\label{fig:srcs1}. Sources used to bootstrap the
-flux calibration are noted with a *.
+flux calibration are noted with a * and are shown with the additional calibration data
+found in NED. Pictor A is shown separately in Figure \ref{fig:pic_spectrum}.
 }
-\end{figure*}
-
-\begin{figure*}[htbp]
-\begin{center}
-\includegraphics[width=0.9\textwidth]{plots/srcfig_2.png}
-\caption{
-PAPER spectra of 16 sources compared against existing data out of
-\cite{Vollmer:2010p6422} between 40MHz and 2GHz, otherwise as described in
-Figure \ref{fig:pic_spectrum}.\label{fig:srcs2} Sources used to bootstrap the
-flux calibration are noted with a *.
-}
-\end{center}
 \end{figure*}
@@
 The 1526-42 spectrum is visibly curved (see Fig.
-\ref{fig:srcs1), which explains the large disagreement in spectral index but not flux.
+\ref{fig:srcs1}), which explains the large disagreement in spectral index but not flux.
 1424-418 is an optically polarized quasar with a flat and variable radio spectrum which might imply co-aligned jet viewing and high intrinsic variability.

### 2013-06-13 ms.tex
finished updating text to final numbers

@@
 Zaki Ali\altaffilmark{2},
+Judd Bowman\altaffilmark{1},
 Richard F. Bradley\altaffilmark{4,5,6},
@@
 power spectrum analysis, 
-as well as \Nconf other sources at nearby declinations. Extrapolating from higher frequency
-catalogs we set the flux scale in a Monte-C`arlo fit across multiple sources. This fit 
+as well as \Nconf{} other sources at nearby declinations. Extrapolating from higher frequency
+catalogs we set the flux scale in a Monte-Carlo fit across multiple sources. This fit 
 propagates uncertainty from both catalog and measurement errors. Fitting new spectral 
 models to both catalog and the new PAPER data we find a Pictor A flux model accurate to
-2.4\%.
+1.4\%, confirming that Pictor A is a linear power law through the EoR band, and is an excellent calibrator. 
 This accuracy is limited by the uncertainty in the catalog measurements we use
@@
 \keywords{dark ages, reionization, first stars --- catalogs --- instrumentation: interferometers}
-
-% XXX remove references to appendix
 
@@
 with catalog source fluxes at 150MHz being inaccurate at the 20\% level
-for $\delta<-20$\arcdeg \citep{Slee:1995p7541,Vollmer:2005p6425}.
+for $\delta<-20$\arcdeg{} \citep{Slee:1995p7541,Vollmer:2005p6425}.
 Both PAPER and the MWA are located in the southern hemisphere at radio-quiet
@@
 This direction dependent gain is currently uncertain to 10\% or higher
-\citep{Pober:2012p8800}, and comprises a large fraction of the 20\% difference between current telescopes \citep{Jacobs:2013p9713}.
+\citep{Pober:2012p8800}, and comprises a large fraction of the 20\% difference between current telescopes \citep{Jacobs:2013p9908}.
 
 In this paper, we set out to significantly improve the accuracy of spectral measurements between 
-100--200 MHz for a set of bright sources in the declination range -46\arcdeg to -40\arcdeg that
+100--200 MHz for a set of bright sources in the declination range -46\arcdeg{} to -40\arcdeg{} that
 are of particular value for southern-hemisphere 21cm EoR experiments such as PAPER and the MWA.
@@
 most debilitating source of error in these measurements: the primary beam.
-% XXX update document map
+
 In section \ref{sec:background} we provide some background on uncertainty in early EoR-band catalogs,
@@
 
-%The ideal solution is to use a wide-grid of
-%well-known calibrators to map the primary beam and set the flux scale.  
-% XXX don't go to "ideal solution" just yet
-% XXX ARP: add importance of accurate flux vs. frequency (Parsons et al. 2012, etc.)
-
-%The position dependent gain varies for each instrument.
-LOFAR and MWA have a range of electrically steerable beams each with a different shape.
-For MWA and LOFAR, the number of high quality calibration sources is more important.
-PAPER has a single broad, 45\arcdeg wide, primary beam; sources at nearby declinations sample the same primary beam many times.
-% This will in turn provide a wide base to assess the accuracy of the primary calibrator which sets the overall amplitude of the EoR power spectrum.
-
-\section{Background}
-\label{sec:background}
-% XXX unsure about this section.  need someplace to give overviews of catalogs
-
-Historically, the best
-EoR band data were by \citet{Slee:1995p7541} with Culgoora Circular
-Array\footnote{Known during daylight hours as Culgoora Radio Heliograph} and
-various higher frequency measurements with Parkes.  These data are typically
-uncertain to 20\% or higher and provide little coverage of the EoR band beyond
-a single narrow-band data point.
-
-More recent surveys include narrow-band surveys by the GMRT and Mauritius, a
-deep survey of the region near Hydra A by the 32 antenna MWA prototype
-\cite{Williams:2012p8768} and a wide field survey by PAPER, also with 32
-elements \cite{Jacobs:2011p8438}. Several sub-channels were provided in the
-Williams catalog, though with 60-80\% error bars ---large compared to the 30\%
-uncertainty on their wide band measurements.  The latter cover the band and
-spatial scales relevant to EoR measurements but are limited by the accuracy of
-the primary beam \citep{Jacobs:2013p9713}. The accuracy of the absolute flux calibrators in the southern hemisphere
-is similarly limited.
-
-The response of the primary beam is of critical importance to EoR measurements.
-Differences between the polarization responses cause leakage of polarized
-signals into the total intensity measurement possibly corrupting the 
-EoR power spectrum \cite{Moore:2013p9621}.  The primary beam 
-shape is also critical to measuring and subtracting foregrounds 
-\cite{Bernardi:2012p9020} a process which, to be affective, must be done to better than 1\%
-precision for the brightest sources \citet{Liu:2009p4762,Bowman:2009p7816} .
-
-A method for decoupling uncertain fluxes from the uncertain beam has been
-described by \citet{Pober:2012p8800}. In simulation the method was able to
-achieve 3 to 10\% accuracy in measuring the primary beam, depending on the
-number of antennae and other variables. The Pober method emphasized the need
-for many repeated measurements of each alt-az pointing. Further investigation
-is under way to improve and implement this method and would be greatly aided by
-the availability of precise flux measurements unaffected by primary beam
-uncertainty.
-
-In this paper we provide a set of detailed total flux measurements aimed at providing
-an absolute flux calibration for southern hemisphere EoR studies as well as a
-small set of verification fluxes suitable for constraining future primary beam studies.
-
 \subsection{The sources and instrument}
@@
 bright sources to make it eminently suitable as both a phase and flux calibrator. Its apparent
-size of $\sim$8\arcmin is smaller than the scales being probed by current EoR instruments , 
+size of $\sim$8\arcmin{} is smaller than the scales being probed by current EoR instruments , 
 making resolution effects, making it suitable for precision calibration.  However, 
@@
 %0518-458	 PKS, Pictor A	G	 25.93	 24.01	1		W	 0.0342	 23.63	 176.
-% XXX transition to the PAPER instrument
+
 Establishing an accurate spectrum for Pictor A is of particular importance for
@@
 has a broad point spread function in the image domain. This severely limits the number 
-of sources which may be used for flux calibration. Drift scanning across the sky with a 45\arcdeg FWHM
+of sources which may be used for flux calibration. Drift scanning across the sky with a 45\arcdeg{} FWHM
 primary beam there are very few unresolved, bright sources which are far from the galactic plane. 
@@
 
+\subsection{Primary beam}
+\label{sec:background}
+
+Historically, the best Southern Hemisphere 
+EoR band data were by \citet{Slee:1995p7541} with Culgoora Circular
+Array\footnote{Known during daylight hours as Culgoora Radio Heliograph} and
+various higher frequency measurements with Parkes.  These data are typically
+uncertain to 20\% or higher and provide little coverage of the EoR band beyond
+a single narrow-band data point.
+
+More recent surveys include narrow-band surveys by the GMRT \footnote{\url{http://tgss.ncra.tifr.res.in/}} and Mauritius \citep{Pandey:2005p8687}, a
+deep survey of the region near Hydra A by the 32 antenna MWA prototype
+\cite{Williams:2012p8768} and a wide field survey by PAPER, also with 32
+elements \cite{Jacobs:2011p8438}. Several sub-channels were provided in the
+Williams catalog, though with 60-80\% error bars ---large compared to the 30\%
+uncertainty on their wide band measurements.  The latter cover the band and
+spatial scales relevant to EoR measurements but are limited by the accuracy of
+the primary beam \citep{Jacobs:2013p9908} as well as the lack of precise in-band flux calibrators.
+
+The response of the primary beam is of critical importance to EoR measurements.
+Differences between the polarization responses cause leakage of polarized
+signals into the total intensity measurement possibly corrupting the 
+EoR power spectrum \citep{Moore:2013p9621}.  The primary beam 
+shape is also critical to measuring and subtracting foregrounds 
+\cite{Bernardi:2012p9020,Sullivan:2012p9457,Morales:2012p8790} a process which, to be affective, must be done to better than 1\%
+precision for the brightest sources \citet{Liu:2009p4762,Bowman:2009p7816} .
+
+A method for decoupling uncertain fluxes from the uncertain beam has been
+described by \citet{Pober:2012p8800}. In simulation the method was able to
+achieve 3 to 10\% accuracy in measuring the primary beam, depending on the
+number of antennae and other variables. The Pober method emphasized the need
+for many repeated measurements of each alt-az pointing. Further investigation
+is under way to improve and implement this method and would be greatly aided by
+the availability of precise flux measurements unaffected by primary beam
+uncertainty.
+
+In this paper we provide a set of detailed total flux measurements aimed at providing
+an absolute flux calibration for southern hemisphere EoR studies as well as a
+small set of verification fluxes suitable for constraining future primary beam studies.
+
 \section{Approach}
@@
 In this section, we describe how we use PAPER in its imaging configuration
-to measure Pictor A and confirm our results by measuring a  selection of known, bright sources. The fluxes are obtained
+to measure Pictor A and a  selection of known, bright sources. The fluxes are obtained
 by forming beams towards known sources as they drift through the primary beam, calibrating to a single source making a similar track.
-These long tracks provide allow us to sidestep primary beam uncertainty to measure accurately calibrated fluxes.
-
- In \citet{Jacobs:2013p9837} several errors were identified as originating in primary beam uncertainty.
+These long tracks allow us to sidestep primary beam uncertainty and measure accurately calibrated fluxes.
+
+ In \citet{Jacobs:2013p9908} several errors were identified as originating in primary beam uncertainty.
   First, under most imaging schemes, each source flux is measured at just a few 
-points in the primary beam. As errors tend to vary across the beam, the uncertainty will tend to vary between sources making
-it difficult to decouple flux uncertainty from beam uncertainty.
+points in the primary beam. As errors tend to vary across the beam it is often
+ difficult to decouple flux uncertainty from beam uncertainty.
  Using the drift scan-beamforming technique, each 
-source is measured hundreds of times at a variety of different pointings to provide a complete sample of the
+source is measured thousands of times at a variety of different primay beam values to provide a complete sample of the
 flux variance due to primary beam variation.  Second, the flux calibration was found to vary over the 
-sky due to the dual uncertainties of primary beam response and prior catalog. To limit our exposure to flux calibration
-variation we limit our observations to sources passing within 5\arcdeg of locations which we can directly calibrate
-from a single reference source.
+sky due to the dual uncertainties of primary beam response and prior catalog. To reduce our exposure to flux calibration
+variation, we limit our observations to sources passing within 5\arcdeg{}  of pointings which we can directly calibrate
+to a single reference source.
  A third limitation, identified in \citet{Williams:2012p8768},
@@
 \subsection{Selection of confirmation sources}
-As PAPER is a drift scan instrument, each declination describes a distinct path through the primary beam. These paths
-provide a detailed sample of the primary beam relative to the peak of the trace, however,
-a model is still required to calibrate between declinations and the accuracy of the trace is sometimes contaminated by
-sidelobes. In section XXX we will compare the beam response as measured by the PicA trace with the model 
-used to estimate flux. We will see that, on average, the primary beam is not the limiting factor in estimating the flux and that
-limiting ourselves to a declination range of 5\arcdeg around calibrator 2331-416 for flux verification is a good compromise.
+As PAPER is a drift scan instrument, each declination describes a distinct path through the primary beam. The flux time seres of a beamform
+ provides a detailed sample of the primary beam relative to the peak of the trace, however,
+a model is still required to calibrate between declinations. Below we argue that be averaging over long tracks, we minimize our 
+susceptibility to localized primary beam error and find that limiting our source selection range to within 
+a declination range of 5\arcdeg{} around a calibrator is a good compromise. In section\ref{fig:gain}
+we estimate the error resulting from this limited scope application of the primary beam model.
+
+\begin{figure*}
+\includegraphics[width=\textwidth]{plots/psa64_pic_strip_positions_psa747_v2_annotated_cropped.png}
+\caption{
+A PAPER map of the radio sky centered on the south pole showing relative positions of targeted sources. The map was made using the July half of the
+data used in this catalog using the procedure described in \citet{Jacobs:2011p8438} to produce a lightly CLEANed map.
+The circular artifact around the south Celestial pole is due to residual instrumental cross-talk and appears to be highly localized below declinations of 75\arcdeg{} where PAPER's sensitivity is small.
+x's mark measured source locations and have size
+scaled by dis-agreement with prior data (inverse ``improvement index" from 
+\S\ref{sec:results}). Smaller indicates better agreement with past data.  Orange dots indicate sources with no model overlap at 76\% \ref{fig:SI_contour_new}. 
+\label{fig:error_map}
+}
+\end{figure*}
 %
@@
 %
-%Comparing this with the simulation in Figure \ref{fig:beam_extrapolation}, we find that the model predicts the 5\arcdeg extrapolation to better
-%than 2\% even into the more uncertain areas far from zenith. The RMS difference for the central 15\arcdeg of the track
-%is 1.5\%. From this we conclude that, as long as we constrain our extrapolations to $\pm5$\arcdeg around Pictor A,
+%Comparing this with the simulation in Figure \ref{fig:beam_extrapolation}, we find that the model predicts the 5\arcdeg{} extrapolation to better
+%than 2\% even into the more uncertain areas far from zenith. The RMS difference for the central 15\arcdeg{} of the track
+%is 1.5\%. From this we conclude that, as long as we constrain our extrapolations to $\pm5$\arcdeg{} around Pictor A,
 %we will have negligible beam area. 
@@
 %than $\sim$1\%.  Thus we conclude that the beam slope is locally well modeled and our beam model is suitable 
-%for extrapolation over $\sim$5\arcdeg scales.
+%for extrapolation over $\sim$5\arcdeg{} scales.
 %  \label{fig:beam_extrapolation}}
@@
 We choose sources from the Molonglo
-Reference Catalog \cite[MRC]{Large:1981p7798} that are within 5\arcdeg in
-declination of a common calibrator (J2331-416) and have a flux extrapolated
-from 408MHz greater than 10Jy assuming a power law spectral index of
+Reference Catalog \cite[MRC]{Large:1981p7798} that are within 5\arcdeg{}  in
+declination of a common calibrator (J2331-416), and more than 10\arcdeg{} from the galactic plane and
+Centaurus A. We limit the flux extrapolated
+from 408MHz to be greater than 10Jy, assuming a power law spectral index of
 -1.\footnote{Most radio sources in this band have power law spectra $S(\nu) =
-\left(\frac{\nu}{\nu_0}\right)^\alpha$. } This selection contains 62 sources in a narrow
-stripe that passes through the majority of the southern EoR fields, much of the
-galaxy and Centaurus A. This stripe in the broader context of the galactic plane
-is shown in Figure \ref{fig:error_map}.
-A list of these 
-sources is given in Table \ref{tab:src_spec}.
-
-For these sources, spectral data measured below 2 GHz were compiled from 
-the NASA/IPAC Extragalactic Database (NED)
-\footnote{\url{http://ned.ipac.caltech.edu/}}. Cross-matching radio sources
-between bands is made difficult by changes in resolution, spectral curvature,
-and resolved multi-scale structure.  For a small number of sources these
-problems can be ameliorated by inspection of the spectra, source names,
-coordinates,  and originating publications. However for a large sample of
-sources this becomes unwieldily and prone to error. Thus for the larger number
-of samples we make use of the Vollmer et al meta-catalog which takes pains to
-match multi-wavelength observations \citep{Vollmer:2010p6422}.
+\left(\frac{\nu}{\nu_0}\right)^\alpha$ and a typical spectral index of $\alpha = -1$. } This selection contains 32 sources in a narrow
+stripe that passes through the majority of the southern EoR fields. See Figure \ref{fig:error_map} 
+for a map of the sources relative to the galactic plane and other structure as mapped by PAPER using the 
+same observations presented here
+and Table \ref{tab:data} for a complete listing of names and positions.
+
+%For these sources, spectral data measured below 2 GHz were compiled from 
+%the NASA/IPAC Extragalactic Database (NED)
+%\footnote{\url{http://ned.ipac.caltech.edu/}}. Cross-matching radio sources
+%between bands is made difficult by changes in resolution, spectral curvature,
+%and resolved multi-scale structure.  For a small number of sources these
+%problems can be ameliorated by inspection of the spectra, source names,
+%coordinates,  and originating publications. However for a large sample of
+%sources this becomes unwieldily and prone to error. Thus for the larger number
+%of samples we make use of the Vollmer et al meta-catalog which takes pains to
+%match multi-wavelength observations \citep{Vollmer:2010p6422}.
 % given the known source dimensions and spectral properties as well as telescope bandwidth and spatial resolutions.
@@
 The spectra reported here are measured by beam-forming ---phasing the visibilities to
-the target location and summing to produce a dynamic spectrum. The spectrum is then isolated
+the target location and summing to produce a spectral time series of perceived flux $S_p$. The spectrum is then isolated
 from neighboring sources by filtering and averaged in the time domain.  This time average is 
-weighted by an additional factor of PAPER's primary beam response 
-\citep{Pober:2012p8800}.  
+weighted by a model of PAPER's primary beam response ($B$).  
 \begin{align}
@@
 
-which is an effective approximation of inverse-variance weighting. The pre factor in Eq \ref{eq:g} is identical for 
-sources at the same declination.  In simulation we multiplied an early holographic beam map \cite{Pober:2012p8800}
+As the perceived flux is already weighted once by the true beam $B$ this weighted sum is an effective approximation of inverse-variance weighting \citep{Pober:2012p8800}.
+
+The pre factor in Eq \ref{eq:g} has been integrated in time over the full azimuthal sweep across the sky and therefor depends only on declination. The rate at which this factor
+changes with declination defines maximum declination distance we can observe from our calibrator. 
+In simulation we multiplied an early holographic beam map \cite{Pober:2012p8800}
 by electromagnetic simulations and find that it 
-diverges slowly with declination, with a maximum of 10\% over 5\arcdeg of declination range.
-We estimate this spectral dependent gain at a reference declination of 41\arcdeg36\arcmin using (J2331-416) fitting a spectral index model to the
- well-defined data points below 2GHz.
+diverges slowly with declination, with a maximum of 10\% over 5\arcdeg{} of declination range, though most are less. 
+We estimate this spectral dependent gain at a reference declination of 41\arcdeg{}36\arcmin{}   using (J2331-416) fitting a spectral index model to the
+ catalog data points below 2GHz.
 
  Finally we average the spectra from a resolution of 400kHz to 10MHz bins, adding the individual errors in quadrature
- as our uncertainty.
+ for our uncertainty.
 
@@
 they must be put on a global flux scale. Meanwhile, our error estimate does not include an estimate of the 
-flux calibration error.  To address both points we fit for a global flux scale that incorporates data from many catalogs. These catalogs
-have all been set, as best as possible, to the Baars et al scale.  Using a Bayesian analysis we compute the 
+flux calibration error.  To address both points we fit for a global flux scale that incorporates the best available
+catalog data. These catalogs
+have all been set, as best as possible, to the Baars et al scale to which all other points are tied \citep{Baars:1977p9678}. Using a Bayesian analysis we compute the 
 variation in the flux scale implied by comparing many sources to prior catalog models. By including sources from across
-the declination range,the variation in this flux scale fit estimates the overall uncertainty in flux resulting from primary beam 
-or prior catalog uncertainty.  Though the final scale is calibrated to the Baars scale, as extrapolated beyond its
-lower limit of 300 MHz, the flux scale error derived by this method fully describes the error resulting from this extrapolation.
+the RA/Dec range, the variation in this flux scale fit estimates the overall uncertainty in flux resulting from primary beam 
+or prior catalog uncertainty.  This folds in the error due to extrapolation beyond the frequency range of the Baars scale which is
+technically limited to 300MHz and above.
 
@@
  \label{sec:Observations}
-
-% XXX in this section, we describe the details of data analysis used ...
-% XXX connect to Parsons2010,2013, pober2013, stefan2012, jacobs2011? for similar basic pipeline.
 
@@
 at the Karoo Radio Observatory site in South Africa.
-A 100-MHz band from 100-200MHz was correlated
+A100-200MHz band was correlated
 with 2048 frequency channels and integrated for 10.7 seconds before
@@
 malfunctioning signal path. This 20 hour long combined dataset provides
-observations provides complete hour angle coverage for the entire 24 hours of
+observations provides near complete hour angle coverage for the entire 24 hours of
 Right Ascension. The July portion of the dataset comes from the same observing
@@
 First, we remove known RFI transmission bands and analog filter edges, and then
-flag outliers at 6$\sigma$ to remove RFI events.  Next, we suppress foreground
+flag outliers at 6$\sigma$ to remove RFI events.  Next, we suppress sky-like
 emission by applying a DDR filter to remove delays and delay-rates within the
@@
 
-% XXX differentiate amp cal here from spectral cal and absolute cal that comes later.
-
 Small gain variations between antennae and over time introduce significant systematic effects which degrade 
 instrument performance. Temporal variations are dominated by changes in ambient temperature. 
-Measurements of ambient temperature versus time near the balun amplifier of a fiducial antenna and near
+Measurements of ambient temperature versus time on the balun amplifier of a fiducial antenna and near
 receiver amplifiers were used to divide out the predicted gain variation versus temperature that these amplifiers
-are known to exhibit.  Inspecting the auto correlations we find that the net temperature gain coefficient (-0.042 dB/C) found in previous laboratory \cite{Parashare:2011p9872} and early field 
-measurements  \cite{Pober:2012p8800} did not appear to remove all temperature variation (black curve in Figure \ref{fig:auto_compare}).  To
+are known to exhibit.
+Inspecting the auto correlations we find that the net antenna temperature gain coefficient (-0.042 dB/C) found in previous laboratory \citep{Parashare:2011p9872} and early field
+measurements  \citep{Pober:2012p8800} did not appear to remove all temperature variation.  To
 revise the temperature coefficient we use the October observations, when the temperatures remained nearly constant, as a reference.
@@
 Comparing the average ratio between the July and October autocorrelations to their temperature difference (Figure \ref{fig:autos_tempcorr}) we find that the two are highly correlated  with 
-a best fit temperature coefficient of (-0.058 dB/C). As we see in the Figure \ref{fig:auto_compare}, this removes a significant amount of disagreement between the two nights, 
+a best fit temperature coefficient of (-0.058 dB/C). As we see in Figure \ref{fig:auto_compare}, this removes a significant amount of disagreement between the two nights, 
 with the peak difference decreasing from 18\% to 3\%.
+
 \begin{figure}
 \includegraphics[width=0.9\textwidth]{plots/auto_tempcorr.png}
-\caption{Calibrating the temperature coefficient by comparing the two nights.
-Here we plot the ratio of auto-correlations (averaged over frequency and antenna) against the temperature difference between the two data sets.
+\caption{Calibrating the temperature coefficient  between the July and October observing runs.
+Here we plot the ratio of auto-correlations (averaged over frequency and antenna) against the temperature difference between the two nights.
 The very linear middle region has a slope of  -0.055 dB/C while the full, more complex, range is fit by -0.06dB/C (black line).
-We compromise by choosing -0.058dB/C.
+We compromise by choosing -0.058dB/C
+which was found to significantly improve the agreement (see Figure \ref{fig:auto_compare}).
 \label{fig:autos_tempcorr}}
 \end{figure}
+
 \begin{figure}
@@
 of data which have easily modeled sky. 
-This calibration is only relative between antennae, absolute flux calibration
-comes after time and frequency averaging in  \S \ref{sec:flux_scale}.   
+This calibration is only relative between antennae, bandpass and absolute flux calibration
+comes after time and frequency averaging in sections \ref{sec:Calibration} \ref{sec:flux_scale}.   
 The antenna delays and amplitudes were found by fitting a point source visibility
@@
 
-% XXX incorporate
-%To measure the spectrum of each source, we begin by applying per-antenna phase and gain
-%calibrations established via self-calibration.  We next remove
-%the known dependence of amplifier gain and cable attenuation on ambient temperature 
-%using measured temperature data and temperature coefficients that were characterized in
-%laboratory measurements \citep{parashare_bradley2009} and confirmed 
-%in field-measurements \citep{pober_et_al2012}.  For each source, we phase to the source 
-%osition
-%and sum over 
-%all baselines greater than 20 wavelengths in length.
-%A fringe-rate filter (see \citet{parsons_backer2009} and Appendix A in \citet{Parsons2013b})
-%is applied to the resulting
-%beam to suppress beam sidelobes where sources introduce variations that deviate more than 
-%$\pm$0.1 mHz from the fringe rate of the source in question.
+The October per-antenna gains were found by computing the average ratio of the auto correlations
+against the July data. Delays were help constant as in \citet{Jacobs:2011p8438}.
 
@@
 summing over baselines longer than 20 wavelengths.
-%Samples were only included if there was a calibrator sample within 5\arcdeg in altitude/azimuth.
-By using both seasons of data we were able to match all measurements with calibrator measurements, making this cut moot.
-
-% XXX incorporate paragraph below
-%As the sky drifts through the primary beam of PAPER antennas, widely
-%separated points will be observed with substantially different gains and
-%so will require different data weightings to optimize SNR.
-%Drift-scan observations of sources were divided by the calibrated beam response in the
-%direction of the source as a function of time.  Spectra were calculated by averaging over
-%time, weighting data at each time step by the square of the 150-MHz beam response in the source direction.
-%Since noise and systematics relating to source observations are expected to be approximately constant
-%versus time, while source amplitude is proportional to beam response, this weighting
-%is an effective approximation of inverse-variance weighting \citep{pober_et_al2011}.
 
@@
  \citep{Parsons:2009p7859} (cf the LOFAR
-de-mixing approach \cite{Offringa:2012p9691})  producing a time dependent
+de-mixing approach \citep{Offringa:2012p9691})  producing a time dependent
 spectrum with minimal side lobes. This is then averaged in time,  weighting by a model of the primary
@@
 a very long earth rotation synthesis image with a single image pixel. The weighted
-contributions from each baseline are shown in Figure \ref{fig:uv_coverage}.When
+contributions from each baseline (the uv coverage) are shown in Figure \ref{fig:uv_coverage}.  When
 combined with the filtering it is a robust and simple method for measuring
@@
 
-% XXX incorporate paragraph below
-%To measure the spectrum of each source, we apply per-antenna phase and gain cal
-%via self-calibration and remove
-%the known dependence of amplifier gain and cable attenuation on ambient tempera
-%using measured temperature data and temperature coefficients that were characte
-%laboratory measurements \citep{parashare_bradley2009} and confirmed in field
-%measurements \citep{pober_et_al2012}.  For each source, we phase to the source 
-%and sum over 
-%all baselines greater than 20 wavelengths in length.
-%A fringe-rate filter is applied to the resulting
-%beam to suppress beam sidelobes where sources introduce variations that deviate
-%$\pm$0.1 mHz from the fringe rate of the source in question.
-
-\subsubsection{Compensation for Resolution Effects in Pictor A}
+\subsection{Compensation for Resolution Effects in Pictor A}
 
@@
 Pictor A is a double-lobed radio galaxy with a main lobe separation of
-7\arcmin. As we see in Figure \ref{fig:pic_perley}, it is nearly unresolved by
-PAPER's 15\arcmin synthesized beam. However, given the high SNR of the
+7\arcmin{}. As we see in Figure \ref{fig:pic_perley}, it is nearly unresolved by
+PAPER's 15\arcmin{}  synthesized beam. However, given the high SNR of the
 observations, we see a 20\% drop in flux on the longest ($\sim$300m) baselines. 
@@
 integrated flux for Pictor A. Where the resolution is highest, at the top of
-the band, the correction is 3\%. At the bottom of the band, where the
-resolution size has grown to 19\arcmin, the correction is only 0.6\%. The
+the band, the net correction is 3\%. At the bottom of the band, where the
+resolution size has grown to 19\arcmin{}, the correction is only 0.6\%. The
 resulting spectrum is shown in Figure \ref{fig:pic_spectrum}a.
@@
 correct for the small residual structure in the PAPER measurements we resampled 
+(via spline interpolation in the Fourier plane)
 the Perley image to the PAPER resolution and estimated the relative contribution
@@
 
-The resulting set of spectra were then calibrated to a model of J2331-416 to remove 
-the residual bandpass due to the net effect of the primary beam as discussed in \S \ref{sec:approach}. J2331-416 
-\footnote{Here we set the spectrum to $S_{150}=33$Jy, $\alpha=-0.76$} a somewhat arbitrary 
-fit to measurements below 1GHz \citep{Slee:1995p7541,Kuehr:1981p9628,Large:1981p7798,Burgess:2006p7814}.
+The resulting set of spectra were then calibrated to a model of J2331-416
+\footnote{Here we set the spectrum to $S_{150}=33$Jy, $\alpha=-0.76$, derived by a linear least squares fit to
+catalog measurements below 1GHz \citep{Slee:1995p7541,Kuehr:1981p9628,Large:1981p7798,Burgess:2006p7814}.  Further calibration on top of this somewhat arbitrary calibration model
+is explored in detail below. }
+ to remove 
+the residual bandpass due to the net effect of the primary beam as discussed in section \ref{sec:approach}. 
+This source
 was selected for its relatively high brightness, spectral smoothness and large quantity
@@
  an optimally matched calibration spectrum.
-
-%The gain of each channel is the product of an overall instrumental passband and
-%the spectral dependence of the primary beam in the direction of the source.
-%Sources sharing the same track through the primary beam will have the same
-%average spectral gain function resulting from frequency dependent primary beam
-%attenuation.   We matched each measured source spectrum time sample to the
-%nearest sample (in altitude/azimuth) of a calibrator source
-%(J2331-416)\footnote{This source was chosen for the amount of data found in the
-%literature and the apparent smoothness of the spectrum.}.  We then, average the
-%% XXX clarify why one source used here, and more sources later 
-%two matched data streams in time.  Since both tracks make the same slice
-%through the primary beam, they will have the same average effective gain.
-%Assuming a power law model for J2331-416 (33Jy $\alpha=-0.76$), we compute a
-%% XXX I got these parameters for 2331: $S_{150}=31.9\ {\rm Jy}$, $\alpha=-0.69$ 
-%% XXX forward reference section on fitting spectra for how this was derived for 2331
-%bandpass gain.  After calibrating the raw 203 channel spectra with this
-%bandpass, we average into 10MHz sub-bands between 120 and 180 MHz, computing
-%the standard deviation as an estimate of the error.
-
-% XXX merge this with above
-%To further improve these estimates, we derive an additional frequency-dependent gain parameter,
-%smoothed on 10-MHz scales,
-%that brings the spectrum of J2331-416 into closest agreement with a power-law spectrum of
-%$S_{150}=31.9\ {\rm Jy}$, $\alpha=-0.69$ that represents the best fit to measurements below 1 GHz
-%\citep{slee1995,kuhr_et_al1981,large_et_al1981,burgess_hunstead2006}.
-%This additional gain factor was applied to all measured spectra, including that
-%of Pictor A.  The expectation is that, since all sources at similar declinations follow similar tracks 
-%through the PAPER beam, any errors present in the original measured spectra as a result of differences between
-%the simulated and actual beam response should be absent in the ratio between source spectra, and therefore
-%should be corrected by the applied gain factor
 
@@
 and the posterior, which we cannot.  However, the posterior is theoretically
-well sampled by a Markov Chain Monte Carlo sampler, which selects parameter
+well sampled by a Markov Chain Monte Carlo (MCMC) sampler, which selects parameter
 values at random, computes the likelihood of the model given the data and noise model,
@@
 
-\subsection{Approximating an Absolute Flux Scale}
+\subsection{Approximating the Absolute Flux Scale}
 \label{sec:flux_scale}
@@
 scale and estimate our flux scale uncertainty, we bootstrap a single global flux scale 
-correction factor using 5
+correction factor using 6
 sources selected for their brightness, spectral linearity and data
 availability\footnote{Calibration sources:
-2250-412,2331-416,2140-434,0007-446,0704-427}. To build a more complete
-spectral model we go beyond the data found in Vollmer et al, including all spectral
-measurements below 2GHz found in the NED database \footnote{\url{ned.ipac.caltech.edu}: Accessed 1 April 2013}.  These catalog measurements
-are primarily by Parkes, and Molonglo with the best precision coming from the
-Wills fluxes at 538 and 634 MHz (when available). Where error bars are not
+2250-412,2331-416,1932-464,0103-453,0547-408,0043-424}. To build a more complete
+spectral model we go beyond the data found in Vollmer et al to include all spectral
+measurements below 2GHz found in the NED database \footnote{\url{ned.ipac.caltech.edu}: Accessed 1 April 2013}.  These additional
+ catalog measurements are primarily by Parkes, and Molonglo  \citep{Kuehr:1981p9323} with the best precision coming from the
+Wills fluxes at 538 and 634 MHz \citep{Wills:1975p9314}. Where error bars are not
 given, we assume uncertainty of 25\%.
@@
 \log\mathcal{L}_s &= \sum_{\nu}\frac{ \left[S_\textrm{cat}^{\nu}  - S_{150}  \left(\frac{\nu}{150}\right)^\alpha\right]^2}{2(\Delta S_\textrm{cat}^\nu)^2} +
-\frac{ (g S_\PAPER^{\nu}  - S_{150}\left(\frac{\nu}{150}\right)^\alpha)^2}{2(\Delta S_\PAPER^\nu)^2} \nonumber \\
+\frac{ \left[g S_\PAPER^{\nu}  - S_{150}\left(\frac{\nu}{150}\right)^\alpha\right]^2}{2(\Delta S_\PAPER^\nu)^2} \nonumber \\
 \log\mathcal{L} &= \sum_{s} \log\mathcal{L}_s
@@
 %gain [dB] 0.03,0.11,0.16
-
-%TODO UPDATE this par
-These calibrated spectra are plotted in Figures \ref{fig:srcs1},\ref{fig:srcs2},
-\& \ref{fig:srcs3} and the data are listed in Table \ref{tab:data}.  The
-resulting Pictor A spectrum ranges in precision from 6.5\% at 125MHz to 4.7\%
-at 185MHz. At least half of this error is due to uncertainty in the flux scale.
-
-%The Pictor track is calibrated to 2331-416 ($S_{150}=33.8$Jy,$\alpha=-0.76$) and the Hydra A track to 0231-126 ($S_{150}=21$Jy,$\alpha=-0.7$).  
-%    cal['0213-132'] = 21 * (fq/.150)**-0.7  
-%    cal['1932-464'] = 93.7 * (fq/.150)**-0.82 
-%    #cal['2331-416'] = 31.9 * (fq/.150)**-0.69
-%    cal['2331-416'] = 33.9 * (fq/.150)**-0.76
-%COMPARISON WITH DATA
+\begin{figure*}
+\centering
+\includegraphics[width=0.9\textwidth]{plots/2250-412_2331-416_1932-464_0103-453_0547-408_0043-424_gain_mcmc_chain_gain_conf.png}
+\caption{
+The marginalized posterior of the PAPER flux scale factor relative to 2331-416. Given a joint fit to all the
+ NED database listings for
+2250-412,2331-416,1932-464,0103-453,0547-408,0043-424 below 2GHz and the corresponding PAPER values. The peak of the distribution sets the overall flux scale,
+while the 76\% width is an additional
+ fractional error to be added quadratically to the per-source uncertainty.  
+By averaging over many sources and and Baars calibrated data points, this uncertainty encapsulates error due to both primary beam model inaccuracy 
+as well as the average flux scale uncertainty due to extrapolating many absolutely calibrated measurements.
+\label{fig:gain}}
+\end{figure*}
+
+These calibrated spectra are plotted in Figure \ref{fig:srcs1} and are listed in Table \ref{tab:data}.  The
+resulting Pictor A spectrum ranges in precision from 3.8\% at 135MHz to 2.6\%
+at 165MHz. About half of this error is due to uncertainty in the flux scale.
 
@@
 will be to first establish a best fit model to existing data, then add the PAPER data
-to the fit, and assess the degree to which the PAPER data is supported by prior measurements, or the reverse
-the degree to which PAPER offers an improvement in our knowledge of the spectrum.
-
- To establish the baseline model, we
-fit a spectral model to catalog data from the spectrally and spatially
+to the fit, and assess the degree to which the PAPER data is supported by prior measurements (accuracy), and the reverse,
+the degree to which PAPER offers an improvement in our knowledge of the spectrum (precision).
+
+ To establish a baseline model, we
+fit a spectral model to prior catalog data from the spectrally and spatially
 cross-matched meta-catalog by \citet{Vollmer:2010p6422} using the
- (log) likelihood which assumes Gaussian measurement errors
+ MCMC chain to sample the (log) likelihood which assumes Gaussian measurement errors
 
@@
 
-We estimate the confidence interval of the resulting parameters as the boundary
-enclosing 76\% of the samples. In the catalog we report both the upper and
-lower of these values for both parameters and plot the 2D contour to show the
-correlation of the two parameters. Many of these contours, the grey curves in
-Fig. \ref{fig:SI_contour_1}, are classic banana plots, displaying a non-linear
-correlation between the parameters.    In most cases the single contour
-adequately describes 2D posterior distribution.
-
-Confidence contours for
-the complete set are shown in grey in Figs. \ref{fig:SI_contour_1} -
-\ref{fig:SI_contour_2}.  In general these are lower limits on the possible
-precision, as the Vollmer catalog emphasizes minimization of cross-match error
-but at the cost of excluding data points.  The fit is then performed again with
-both PAPER and catalog data, shown in black on the same Figures. The values are
-given in Table \ref{tab:fits}, and
-illustrated in Figure \ref{fig:src_spec}.
+As when fitting the flux scale, 
+we estimate the confidence interval of the resulting parameters as the boundary
+enclosing 76\% of the samples. A detailed view of the resulting posterior is shown in grey on Figure 
+\ref{fig:posteriors}. Most of the posteriors are characterized by steep sided, symmetric 
+distributions. While many appear to have linearly correlated parameters, several display
+the classic banana shape associated with a non-linear correlation between parameters.
+For the rest of the sources we focus on the 76\% confidence levels, plotting the 2D distributions
+in Figures \ref{fig:SI_contour_1} - \ref{fig:SI_contour_bad}, and listing the marginalized 
+values in Table \ref{tab:fits}.
+
+The fit is then performed again with
+both PAPER and catalog data, shown in black on the same Figures.
 
@@
 \caption{
-A more detailed view of the posterior probability distribution. On the left
-Pictor A, on the right 2323-407. Confidence contours range from 0.2 to 0.8. The MCMC
+A detailed view of the posterior probability distribution as described in section \ref{sec:fitting_models}. On the left
+Pictor A, on the right 2323-407. Confidence contours range from 0.2 to 0.8, curves top and right 
+are the marginalized distributions. Grey plots the fit to catalog data, black for joint catalog and PAPER.
+ The MCMC
 chain reveals the distinctive ``banana'' shape of the posterior
 due to correlation between the model parameters.
-Compare with the contours for this source shown in Fig. \ref{fig:SI_contour_2}.
-Grey plots the fit to catalog data, black for joint catalog and PAPER.
+Compare with the contours for this source shown in Fig. \ref{fig:SI_contour_2}. Fit parameters listed in
+Table \ref{tab:fits} are the locations where the marginalized curve crosses 0.76.
+\label{fig:posteriors}
 }
@@
 %total 31
-The majority of the \Nsrc models fit using the new PAPER data were found to agree with
+The majority of the \Nsrc{} models fit using the new PAPER data were found to agree with
 models fit to past data and all but two are suitable for comparison.  
@@
 exhibits flattening at higher frequencies, most likely due to synchrotron
-self-absorption \citep{Jacobs:2011p8438}. While 1459-417 does not have enough 
-measurements in the Vollmet et al catalog on which to build a model for comparison. We exclude these 
+self-absorption \citep{Jacobs:2011p8438}. Meanwhile, 1459-417 does not have enough 
+measurements in the SPECFIND catalog on which to build a model for comparison. We exclude these 
 two from further analysis.
 
-Inspecting the remaining 29 confidence contours we find that, for the vast majority ($\sim
+Inspecting the remaining 30 confidence contours we find that, for the vast majority ($
 90$\%), the PAPER measurements confirm the power law extrapolation from higher
@@
 improvement} will be 0.123.  This Improvement Index is included in the table
-of fit parameters (Table \ref{tab:fits}).
+of fit parameters (Table \ref{tab:fits}) and is used as the size scale on the 
+map in Figure \ref{fig:error_map}.
 
@@
 the fit far from the model preferred by the catalog data (see Fig.
-\ref{fig:SI_contour_new}).
+\ref{fig:SI_contour_new} for details on these).
 
@@
 indicating strong confirmation of the extrapolated spectrum (see Figures
-\ref{fig:SI_contour_1} - \ref{fig:SI_contour_3}).  Pictor A is in the middle of
+\ref{fig:SI_contour_1} - \ref{fig:SI_contour_3}).  Pictor A is close to the top of
 this group  with an improvement of 0.942 ---only two sources show stronger
-confirmation.  The flux model is $S150=$381 $\pm$ 5.36Jy, $\alpha=-0.76\pm0.01$.
-The combination of several independent PAPER data points near 150MHz with
-previous catalog measurements results in this estimated uncertainty of 1.4\%.
-This uncertainty is quite small, but is not surprising when we consider that we have
-used 7 precise data points (5 PAPER, 2 Wills), all accurate to 3\% to measure what appears to
-be an extremely linear power law spectrum. If the errors were completely guassian
-the net error would be $3/\sqrt(7) = 1.14$\%.
-
-% XXX comparison with previous in-band results (danny 2011, williams 2012)
-% work TODO
+confirmation.  The flux model is $S150=$381 $\pm$ 5.36Jy, $\alpha=-0.76\pm0.01$
+ a fractional error of 1.4\%.
+
+This represents an order of magnitude improvement in the accuracy of this primary 
+flux calibrator. In fact the uncertainty is so small that it pays to consider its reasonableness.
+First consider that we have fit the model to many data points, including  7 measurements
+(5 PAPER, 2 Wills) accurate to 3\%. If the errors were completely Guassian
+the net error would be $3\%/\sqrt(7) = 1.14$\%. Consider also that, where most surveys
+might include on the order of ten independent measures of a bright source from different facets to arrive at 
+a 5 to 20\% uncertainty,  we have included thousands of independent measurements
+over the full horizon to horizon transit, while carefully controlling for systematic variation and resolution affects.
 
@@
 filtered beam form method to measure the spectra of bright sources with similar
-primary beam response. This primary beam limit is based on our measurements 
-of the primary beam along slices of constant declination.
+primary beam response.
 
@@
 are accurate to 20\% implying a 40\% uncertainty in the absolute power spectrum
-level.  The Pictor A spectrum here is shown to be accurate to 
-$\sim$5\%, a factor of 5 improvement over previous measurements.
+level.  The PAPER Pictor A spectrum is found to be accurate to 
+$\sim$3\%, a factor of 7 improvement over previous EoR-band measurements.
 
@@
 two are found simultaneously by fitting the spectral extrapolations of several flux calibrators
-at once and account for the the majority of the error. Though past measurements suggested the possibility
+at once and account for about half of the error. Though past measurements suggested the possibility
 of spectral curvature below 200MHz we have found no evidence for this.  With these measurements we are able 
-to confirm single spectral index model for Pictor between 120MHz and 600MHz.
-
-A set of  61 verification sources were selected to be bright, previously cataloged
-and  distributed over
-the full 24 hours of Right Ascension coverage but only within 5 degrees
-declination of Pictor A.  Using a Bayesian analysis we conclude that most of
-these are consistent with previous measurements and provide useful new
-constraints. However, in a small remainder, the simple spectral model fails to
-adequately describe the data. In most cases the proximity to bright or extended
-structures implies side lobe contamination.  Therefore, though we include the
-model parameters, they are not meant to be definitive, but provide confidence
-that the reported PAPER flux values are on the correct global scale.
+to confirm a single spectral index model for Pictor between 120MHz and 600MHz.
+
+A set of  31 additional verification sources were also targeted to provide additional 
+characterization of the flux scale as well as an overall assessment of the catalog accuracy.
+.  Using a Bayesian analysis we conclude that most of
+these are consistent with previous measurements, provide useful new
+constraints and support the conclusion that the  Pictor A flux is likely on the correct scale.
 
@@
 
-\begin{figure*}
-\centering
-\includegraphics[width=0.9\textwidth]{plots/2250-412_2331-416_1932-464_0103-453_0547-408_0043-424_gain_mcmc_chain_gain_conf.png}
-\caption{
-The marginalized posterior of the PAPER flux scale factor relative to 2331-416. Given a joint fit to all the
- NED database listings for
-2250-412,2331-416,1932-464,0103-453,0547-408,0043-424 below 2GHz and the corresponding PAPER values. The 76\% confidence 
-interval on this distribution is used to set the overall flux scale. While the width is an additional fractional error to be added quadratically to the per-source uncertainty.  
-By averaging over many sources and and Baars calibrated data points, this uncertainty encapsulates error due to both primary beam model inaccuracy 
-as well as the average flux scale uncertainty due to extrapolating many absolutely calibrated measurements.
-\label{fig:gain}}
-\end{figure*}
-
 \begin{figure*}[htbp]
 \includegraphics[width=0.49\textwidth]{plots/pictor_spectrum.png}
-\includegraphics[width=0.49\textwidth]{plots/pic_SI_MCMC.png}
+\includegraphics[width=0.49\textwidth]{plots/pictor_spectrum_zoom.png}
 \caption{
@@
 the PAPER Pictor A spectrum with 2$\sigma$ error bars (x) and  MCMC fits (grey
-cloud). Inset allows comparison between the 10MHz averaged points with the
+cloud). On the right, the spectrum zoomed to highlight the PAPER data
+ allows comparison between the 10MHz averaged points with the
 403kHz points (grey). The oscillations in the PAPER spectrum are residual side
@@
 \cite{Otrupcek:1991p8780} and have been set to the (extrapolated)
-\citet{Baars:1977p9678} scale by  \cite{Kuehr:1981p9628}. A sub-sample of MCMC
-fits are shown in grey. On the right, the grey contour indicates the 76\%
-confidence interval for 150MHz flux and spectral index given the prior data.
-Black folds in the PAPER data.
+\citet{Baars:1977p9678} scale by  \cite{Kuehr:1981p9628}. 
 } \label{fig:pic_spectrum}
 \end{figure*}
-
-%%calibrators
-%%2250-412_2331-416_0043-424
-%\begin{figure*}[htbp]
-%\includegraphics[width=0.2\textwidth]{plots/2250-412_calfit.png}
-%\includegraphics[width=0.2\textwidth]{plots/2250-412_SI_MCMC.png}
-%\includegraphics[width=0.2\textwidth]{plots/2331-416_calfit.png}
-%\includegraphics[width=0.2\textwidth]{plots/2331-416_SI_MCMC.png}\\
-%\includegraphics[width=0.2\textwidth]{plots/0043-424_calfit.png}
-%\includegraphics[width=0.2\textwidth]{plots/0043-424_SI_MCMC.png}
-%\includegraphics[width=0.2\textwidth]{plots/1932-464_calfit.png}
-%\includegraphics[width=0.2\textwidth]{plots/1932-464_SI_MCMC.png}
-%
-%\caption{Sources used to calculate the flux scale. Catalog data for the three sources are used to simultaneously fit a 
-%single spectral index gain model for each source (grey contours) and a single PAPER gain parameter  .\label{fig:cals} }
-%
-%\end{figure*}
-%add calibrator
 
@@
 
-This work makes use of ]the ``MCMC Hammer" emcee python library \citep[
+This work makes use of the ``MCMC Hammer" emcee python library \citep[
 \url{http://danfm.ca/emcee/}]{ForemanMackey:2012p8684}  and the NASA/IPAC
@@
 \caption{
-PAPER spectra of 16 sources compared against existing data out of
-\cite{Vollmer:2010p6422} between 40MHz and 2GHz, otherwise as described in
-Figure \ref{fig:pic_spectrum}.\label{fig:srcs1}. Sources used to bootstrap the
+PAPER spectra of 31 sources compared against existing data out of
+\cite{Vollmer:2010p6422} between 40MHz and 2GHz and a sampling
+of spectra fits drawn from MCMC samples at greater than 76\% confidence. Sources used to bootstrap the
 flux calibration are noted with a * and are shown with the additional calibration data
 found in NED. Pictor A is shown separately in Figure \ref{fig:pic_spectrum}.
-}
+\label{fig:srcs1}}
 \end{figure*}
@@
 \end{center}
-\caption{Spectral model contours as described in Figure \ref{fig:pic_spectrum}. Sources marked with a
+\caption{Spectral model contours as described in Figure \ref{fig:pic_spectrum}. 
+Catalog fit in grey, black folds in the PAPER 
+data. Sources marked with a
 * were used to assess calibration error.
@@
 \end{center}
-\caption{Spectral model contours as described in Figure \ref{fig:pic_spectrum}. Sources marked with a
+\caption{Spectral model contours as described in Figure \ref{fig:pic_spectrum}. 
+Catalog fit in grey, black folds in the PAPER 
+data. 
+Sources marked with a
 * were used to assess calibration error.
@@
 \end{center}
-\caption{fits of the next 16 sources, as described in Figure \ref{fig:SI_contour_1}. Sources marked with a
+\caption{fits of the last three sources, as described in Figure \ref{fig:SI_contour_1}. 
+Catalog fit in grey, black folds in the PAPER 
+data. 
+Sources marked with a
 * were used to assess calibration error.
@@
 %END PASTE
-
-\begin{figure*}
-\includegraphics[width=\textwidth]{plots/psa64_pic_strip_positions_psa747_v2_annotated_cropped.png}
-\caption{
-A PAPER map of the radio sky centered on the south pole showing relative positions of targeted sources. The map was made using the July half of the
-data used in this catalog using the procedure described in \citet{Jacobs:2011p8438} to produce a lightly CLEANed map.
-The circular artifact around the south Celestial pole is due to residual instrumental cross-talk and appears to be highly localized below declinations of 75\arcdeg where PAPER's sensitivity is small.
-x's mark measured source locations and have size
-scaled by dis-agreement with prior data (inverse ``improvement index" from 
-\S\ref{sec:fits}). Smaller indicates better agreement with past data.  Orange dots indicate sources with no model overlap at 76\% \ref{fig:SI_contour_new}. 
-\label{fig:error_map}
-}
-\end{figure*}
 
@@
 
-%\begin{deluxetable}{ccccccccrrr}
-%%\begin{tabular}{ccccccccrrr}
-%\tablecolumns{12}
-%\tablecaption{Spectral fits for models shown in Figures \ref{fig:SI_contour_1} - \ref{fig:SI_contour_4}.
-%\tablehead{
-%\colhead{Ra} & \colhead{Dec} & \colhead{Name} & \colhead{S150} & 
-%\colhead{e_S150} & \colhead{SI} & \colhead{e_SI}
-%\startdata
-%
-%
-%\enddata
-%\tablecomments{}
-%\label{tab:data}
-%\end{deluxetable}
-
 \bibliography{library}

### 2013-06-13 plots/cal_select.py
adding my cal selection script

@@ -1,0 +1,65 @@
+#load all the src tracks.  
+from glob import glob
+import numpy as n,os
+
+
+def load_paper_spectra(filename):
+    lines = open(filename).readlines()
+    spectra ={}
+    for line in lines:
+        if line.startswith('#'):
+            if line.startswith('#FREQ'):
+                freqs = n.array(map(float,line.split('=')[1].split(','))).squeeze()
+            continue
+        line = line.split()
+        srcname = line[0]
+        fluxes = n.array(map(float,line[1].split(',')))
+        errors = n.array(map(float,line[2].split(',')))
+        spectra[srcname] = (freqs,fluxes,errors)
+    return spectra
+
+
+
+srctracks = glob('srctracks/*srctrack*npz')
+print "found %d source tracks"%(len(srctracks))
+
+FQ = 114
+chan = 3
+
+#load the reference calibrator first
+f = n.load('srctracks/2331-416__srctrack_2455748-2455749.npz')
+lst = f['lst']
+i = n.argsort(lst)
+
+trk = n.real(n.ma.masked_where(f['flags'],f['spec'])[i,FQ])
+az = n.arcsin(f['x'])*180/n.pi
+cal_az_count = n.ma.sum(n.abs(az)<10)
+
+
+#load the uncalibrated catalog
+PAPERcat  = 'psa64_pic_stripe_final.txt'
+PAPER = load_paper_spectra(PAPERcat)
+print "loaded %d sources from %s"%(len(PAPER),PAPERcat)
+cals = []
+for filename in srctracks:
+    f = n.load(filename)
+    srcname = os.path.basename(filename).split('__')[0]
+    try:
+        PAPER[srcname]
+    except(KeyError):
+        continue
+    if srcname=='pic':continue
+    i = n.argsort(f['x'])
+    maxbm_possible = n.max(f['beam'][i,FQ])
+    bm = n.ma.masked_where(n.logical_or(f['flags'],f['beam']==0),f['beam'])[i,FQ]
+    maxbm_achieved = bm.max()
+    if maxbm_achieved>=(0.75*maxbm_possible):
+        cals.append(srcname)
+    else:
+        print srcname,maxbm_achieved
+calfluxes = [n.median(PAPER[src][1]) for src in cals]
+fluxorder = n.argsort(calfluxes)[::-1]
+for i in fluxorder:
+    flux = PAPER[cals[i]][1][chan]
[…]

### 2013-06-13 ms.tex
Edits of abstract and S1, along with some random stuff throughout.

@@
 Daniel C. Jacobs\altaffilmark{1},
-Aaron R. Parsons\altaffilmark{2},
+Aaron R. Parsons\altaffilmark{2,8},
 James E. Aguirre\altaffilmark{3},
@@
 \begin{abstract}
-We present a catalog of broad-band spectral measurements from the 
+We present a catalog of spectral measurements covering a 100--200-MHz band for 32 sources, derived
+from observations with 
+a 64-antenna deployment of the 
 Donald C. Backer Precision Array for Probing
-the Epoch of Reionization (PAPER) in South Africa observed in July and
-September of 2011.  In order to reduce the impact of beam calibration, which proves to
-be a difficult endeavor for transit telescopes such as PAPER, on the determination
-of source spectra, we have focused on calibrating sources in a narrow declination range.
-Since each source follows a nearly identical path through the primary beam, this
-restriction allows beam calibration to be greatly reduced as a source of error,
-yielding a dramatic improvement in the accuracy of source spectra measured in the 
-100--200-MHz band which is receiving renewed attention by experiments seeking to
-measure 21cm emission from the Epoch of Reionization (EoR). Using beam forming
-and fringe-rate filtering we measure spectra for Pictor A, which provides a key flux reference for PAPER's EoR
-power spectrum analysis, 
-as well as \Nconf{} other sources at nearby declinations. Extrapolating from higher frequency
-catalogs we set the flux scale in a Monte-Carlo fit across multiple sources. This fit 
-propagates uncertainty from both catalog and measurement errors. Fitting new spectral 
-models to both catalog and the new PAPER data we find a Pictor A flux model accurate to
-1.4\%, confirming that Pictor A is a linear power law through the EoR band, and is an excellent calibrator. 
-This accuracy is limited by the uncertainty in the catalog measurements we use
-to estimate an absolute flux scale, and represents 
-an order of magnitude improvement over previous measurements in this band.  
-Comparing with prior measurements, 90\% are found to confirm and refine a power-law model for flux density.
-
+the Epoch of Reionization (PAPER) in South Africa.
+% ARP: don't think obs dates matter for abstract, observed in July and September of 2011.
+For transit telescopes such as PAPER, calibration of the primary beam is
+a difficult endeavor, and errors in this calibration are a major source of error in
+the determination of source spectra.
+In order to decrease reliance on accurate beam calibration,
+we focus on calibrating sources in a narrow declination range
+from -46\arcdeg{} to -40\arcdeg{}.
+Since sources at similar declinations follow nearly identical paths through the primary beam, this
+restriction greatly reduces errors associated with beam calibration,
+yielding a dramatic improvement in the accuracy of derived source spectra.
+Extrapolating from higher frequency
+catalogs, we derive the flux scale using a Monte-Carlo fit across multiple sources that 
+includes uncertainty from both catalog and measurement errors. Fitting spectral 
+models to catalog data and these new PAPER measurements, we derive new flux models for
+Pictor A and \Nconf{} other sources as nearby declinations, 
+90\% are found to confirm and refine a power-law model for flux density.
+Of particular importance is the new Pictor A flux model, which is accurate to
+1.4\% and shows, in contrast to previous models, that between 100 MHz and 2 GHz, the spectrum of Pictor A 
+is consistent with a single power law given by a flux at 150 MHz of
+381.9$\pm$5.4 Jy, and a spectral index of -0.76$\pm$0.01.  
+This accuracy represents 
+an order of magnitude improvement over previous measurements in this band, and
+is limited by the uncertainty in the catalog measurements used
+to estimate the absolute flux scale.  The simplicity and improved accuracy of Pictor A's spectrum
+make it an excellent calibrator in a band of
+importance to experiments seeking to
+measure 21cm emission from the Epoch of Reionization. 
 \end{abstract}
@@
 measurements of highly redshifted 21cm emission to inform our understanding of
-cosmic reionization in the redshift range $6< z<12$, corresponding to radio
+cosmic reionization in the redshift range $z>6$, corresponding to radio
 frequencies below 200 MHz (see reviews in
@@
 Signature (EDGES; \citealt{Bowman:2010p8546}), and interferometers aiming to
-measure the power spectrum of 21-cm EoR emission, such as the Giant Metre-wave
+measure the power spectrum of 21cm EoR emission, such as the Giant Metre-wave
 Radio Telescope (GMRT;
@@
 the $z=6$--13 redshift range expected to encompass reionization
-\citep{Furlanetto:2006p2267}.
+\citep{Furlanetto:2006p2267}. % XXX I think this sentence is a repeat from another paper
 In particular, the spectral properties of extra-galactic point-sources are important
 both because they are valuable calibration references
-and because they are strong foreground emitters that must be removed from 21-cm EoR measurements.
+and because they are strong foreground emitters that must be removed from 21cm EoR measurements.
 With the sparse availability of measured foreground properties in the
@@
 foreground characterization is a
-vital step en route to any 21-cm EoR detection.
+vital step en route to any 21cm EoR detection.
 At these low
-frequencies the Southern sky is much less well known than the North, 
-with catalog source fluxes at 150MHz being inaccurate at the 20\% level
+frequencies, the Southern sky is much less well known than the North;
+catalog source fluxes at 150MHz are inaccurate at the 20\% level
 for $\delta<-20$\arcdeg{} \citep{Slee:1995p7541,Vollmer:2005p6425}.
@@
 %TODO ARP wanted a cite for the above.  I really don't know of a good one. Its it a bit of a broad statement
+% XXX how about Parsons 2012a, Beardsley 2012, and jelic 2008 (i think it has sensitivty for lofar)
 Adding to the challenge, these telescopes 
@@
 \citep{Pober:2012p8800}, and comprises a large fraction of the 20\% difference between current telescopes \citep{Jacobs:2013p9908}.
+% XXX difference of what?
 
@@
 
-In section \ref{sec:background} we provide some background on uncertainty in early EoR-band catalogs,
-and explain our choice of calibrator. Section \ref{sec:approach} gives an overview 
-of our approach to making the measurement and motivates our data processing steps, which 
-are described in detail in section \ref{sec:Observations}. In section
-
-In section \ref{sec:approach} we describe our approach for measuring source spectra with
+In \S\ref{sec:background} we provide some background on uncertainty in early EoR-band catalogs,
+and explain our choice of calibrators.
+In \S\ref{sec:approach} we describe our approach for measuring source spectra with
 drift-scan observations and deriving an absolute flux scale from catalog data.  
@@
 \ref{fig:gain} detail our approach for fitting a global flux scale and spectral models for each source.
-We use these fits in section \ref{sec:results} to understand how well PAPER data agree
-with previous measurements and conclude in \ref{sec:Conclusion}.
+We use these fits in \S\ref{sec:results} to understand how well PAPER data agree
+with previous measurements and conclude in \S\ref{sec:Conclusion}.
 
@@
 EoR measurements in the southern sky have focused on the coldest regions where
-galactic foregrounds are minimal. With the majority of possible observing time falling on 
+galactic foregrounds are minimal. With the majority of possible observing time falling around
 RA=4h,Dec=-30. The brightest and least-resolved calibrator in this region is Pictor A 
-(5h19m49.1 -45d46m45.0). Pictor A is a nearby FR-II type radio galaxy 
- similar to Cygnus A.  At $\sim$400Jy Pictor is bright and sufficiently distant from other 
+(5h19m49.1,-45d46m45.0). Pictor A is a nearby FR-II type radio galaxy 
+ similar to Cygnus A.  At $\sim$400Jy, Pictor is bright and sufficiently distant from other 
 bright sources to make it eminently suitable as both a phase and flux calibrator. Its apparent
-size of $\sim$8\arcmin{} is smaller than the scales being probed by current EoR instruments , 
-making resolution effects, making it suitable for precision calibration.  However, 
+size of $\sim$8\arcmin{} is smaller than the scales being probed by current EoR instruments, 
+making it suitable for precision calibration, with only a modest
+level of resolution effects.
+However, 
 like most other sources, precise flux measurements in the EoR band are not available.
-The current best EoR band measurement
+The previous best EoR band measurement
 is uncertain to 12\% and appears to imply spectral flattening in the EoR band
@@
 of sources which may be used for flux calibration. Drift scanning across the sky with a 45\arcdeg{} FWHM
-primary beam there are very few unresolved, bright sources which are far from the galactic plane. 
+primary beam, there are very few unresolved, bright sources which are far from the galactic plane. 
 Pictor A is bright and well enough separated from other emission to dominate the visibilities for a good fraction of
-the EoR observing season, making it an ideal flux calibrator.
+the EoR observing season, making it an excellent flux calibrator.
 
@@
 shape is also critical to measuring and subtracting foregrounds 
-\cite{Bernardi:2012p9020,Sullivan:2012p9457,Morales:2012p8790} a process which, to be affective, must be done to better than 1\%
+\cite{Bernardi:2012p9020,Sullivan:2012p9457,Morales:2012p8790} a process which, to be effective, must be done to better than 1\%
 precision for the brightest sources \citet{Liu:2009p4762,Bowman:2009p7816} .
@@
 number of antennae and other variables. The Pober method emphasized the need
+% XXX mention key assumption of 180deg rotational symmetry
 for many repeated measurements of each alt-az pointing. Further investigation
@@
 In this paper we provide a set of detailed total flux measurements aimed at providing
-an absolute flux calibration for southern hemisphere EoR studies as well as a
+an absolute flux calibration for southern hemisphere EoR studies, as well as a
 small set of verification fluxes suitable for constraining future primary beam studies.
@@
 The circular artifact around the south Celestial pole is due to residual instrumental cross-talk and appears to be highly localized below declinations of 75\arcdeg{} where PAPER's sensitivity is small.
-x's mark measured source locations and have size
-scaled by dis-agreement with prior data (inverse ``improvement index" from 
-\S\ref{sec:results}). Smaller indicates better agreement with past data.  Orange dots indicate sources with no model overlap at 76\% \ref{fig:SI_contour_new}. 
+`x''s mark measured source locations and have size
+scaled by disagreement with prior data (inverse ``improvement index" from 
+\S\ref{sec:results}). Smaller indicates better agreement with past data.  Orange dots indicate sources with no model overlap at 76\% in Figure \ref{fig:SI_contour_new}. 
 \label{fig:error_map}
@@
 The spectra reported here are measured by beam-forming ---phasing the visibilities to
-the target location and summing to produce a spectral time series of perceived flux $S_p$. The spectrum is then isolated
-from neighboring sources by filtering and averaged in the time domain.  This time average is 
-weighted by a model of PAPER's primary beam response ($B$).  
+the target location and summing over baselines to produce a spectral time series of perceived flux $S_p$,
+which is given by the true source flux, $S$, illuminated by the true beam pattern $B$, according to
+% XXX would be nice to capture here and below that B, B_M, and S_p are vectors indexed by t.  would
+% suggest subscript, except you already have B_M.  Could use B^\prime (and S^\prime) instead...
+\begin{equation}
+S_p=BS.
+\end{equation}
+The spectrum is then isolated
+from neighboring sources by filtering and averaged in the time domain.  This time-average is 
+weighted by a model of PAPER's primary beam response ($B_M$).  
 \begin{align}
@@
 \end{align}
-
+% XXX where g and \delta are...?  Should connect this nomeclature to J2331-416 language below (i.e. solving for g)
 As the perceived flux is already weighted once by the true beam $B$ this weighted sum is an effective approximation of inverse-variance weighting \citep{Pober:2012p8800}.
 
-The pre factor in Eq \ref{eq:g} has been integrated in time over the full azimuthal sweep across the sky and therefor depends only on declination. The rate at which this factor
+The pre-factor in Eq \ref{eq:g} has been integrated in time over the full azimuthal sweep across the sky and therefore depends only on declination. The rate at which this factor
 changes with declination defines maximum declination distance we can observe from our calibrator. 
 In simulation we multiplied an early holographic beam map \cite{Pober:2012p8800}
+% XXX to simulate what?  need to say something like:
+% To simulate the effect of beam model errors on ???, we used simulations derived from the holographic
+% beam map measured in \citet{Pober:2012p8800} weighted by a beam model derived from electromagnetic
+% simulations, and find that ...
 by electromagnetic simulations and find that it 
@@
  catalog data points below 2GHz. 
+% XXX clarify that this is not the last correction; there is one more flux cal that is derived from MCMC
+% over several calibrator sources (Figure XXX).
 
@@
 catalog data. These catalogs
-have all been set, as best as possible, to the Baars et al scale to which all other points are tied \citep{Baars:1977p9678}. Using a Bayesian analysis we compute the 
+have all been set, as best as possible, to the \citet{Baars:1977p9678} scale to which all other points are tied. Using a Bayesian analysis we compute the 
 variation in the flux scale implied by comparing many sources to prior catalog models. By including sources from across
@@
 
-Small gain variations between antennae and over time introduce significant systematic effects which degrade 
+Small time- and antenna-dependent gain variations time introduce significant systematic effects that degrade 
 instrument performance. Temporal variations are dominated by changes in ambient temperature. 
-Measurements of ambient temperature versus time on the balun amplifier of a fiducial antenna and near
-receiver amplifiers were used to divide out the predicted gain variation versus temperature that these amplifiers
+We use measurements of ambient temperature versus time on the balun amplifier of a fiducial antenna and near
+receiver amplifiers to divide out the predicted gain variation versus temperature that these amplifiers
 are known to exhibit.
@@
 which was found to significantly improve the agreement (see Figure \ref{fig:auto_compare}).
+% XXX When comparing autos from different JDs, the change in position of sun can substantially affect signal level
+% I'm worried this is the cause of the dither on either end of Figure 3, unless you've been conservative about
+% what data you've included here.
 \label{fig:autos_tempcorr}}
@@
 the average auto correlation before ({\color{orange} orange}) and after (black) application of the temperature dependent gain. \label{fig:auto_compare}}
+% XXX why does the gap in data in the top plot not match the bottom?
 \end{figure}
@@
 This calibration is only relative between antennae, bandpass and absolute flux calibration
-comes after time and frequency averaging in sections \ref{sec:Calibration} \ref{sec:flux_scale}.   
+comes after time and frequency averaging in sections \ref{sec:Calibration} and \ref{sec:flux_scale}.   
 The antenna delays and amplitudes were found by fitting a point source visibility
@@
 of spectra fits drawn from MCMC samples at greater than 76\% confidence. Sources used to bootstrap the
-flux calibration are noted with a * and are shown with the additional calibration data
+flux calibration are noted with a `*' and are shown with the additional calibration data
 found in NED. Pictor A is shown separately in Figure \ref{fig:pic_spectrum}.
@@
 data. Sources marked with a
-* were used to assess calibration error.
+`*' were used to assess calibration error.
 }\label{fig:SI_contour_1}
@@
 Sources marked with a
-* were used to assess calibration error.
+`*' were used to assess calibration error.
 }\label{fig:SI_contour_2}
@@
 Sources marked with a
-* were used to assess calibration error.
+`*' were used to assess calibration error.
 }\label{fig:SI_contour_3}
@@
 
+% XXX re-check arxiv cites in bib for finishing peer review.  Paciga 2013, Pober 2013, Moore 2013, and Stefan 2013
+% all published now.  what is bernardi 2012 submitted?
+
 \end{document}

### 2013-06-13 ms.tex
Created a new "Background" section that incorporates and organizes S1.1, S1.2, and some of S2.  Re-wrote beginning of S2 to give an overview of the approach.

@@
 
-\subsection{The sources and instrument}
-EoR measurements in the southern sky have focused on the coldest regions where
+\section{Background}
+\label{sec:background}
+
+Historically, the best Southern Hemisphere 
+EoR band data were by \citet{Slee:1995p7541} with Culgoora Circular
+Array\footnote{Known during daylight hours as Culgoora Radio Heliograph} and
+various higher frequency measurements with Parkes.  These data are typically
+uncertain to 20\% or higher and provide little coverage of the EoR band beyond
+a single narrow-band data point. 
+More recent surveys include narrow-band surveys by the GMRT \footnote{\url{http://tgss.ncra.tifr.res.in/}} and Mauritius \citep{Pandey:2005p8687}, a
+deep survey of the region near Hydra A by the 32 antenna MWA prototype
+\cite{Williams:2012p8768} and a wide field survey by PAPER, also with 32
+elements \cite{Jacobs:2011p8438}. Several sub-channels were provided in the
+Williams catalog, though with 60-80\% error bars ---large compared to the 30\%
+uncertainty on their wide band measurements.  The latter cover the band and
+spatial scales relevant to EoR measurements but are limited by the accuracy of
+the primary beam \citep{Jacobs:2013p9908} as well as the lack of precise in-band flux calibrators.
+
+The response of the primary beam is of critical importance to EoR measurements.
+Differences between the polarization responses cause leakage of polarized
+signals into the total intensity measurement possibly corrupting the 
+EoR power spectrum \citep{Moore:2013p9621}.  The primary beam 
+shape is also critical to measuring and subtracting foregrounds 
+\cite{Bernardi:2012p9020,Sullivan:2012p9457,Morales:2012p8790} a process which, to be effective, must be done to better than 1\%
+precision for the brightest sources \citet{Liu:2009p4762,Bowman:2009p7816} .
+A method for decoupling uncertain fluxes from the uncertain beam has been
+described by \citet{Pober:2012p8800}. In simulation the method was able to
+achieve 3 to 10\% accuracy in measuring the primary beam, depending on the
+number of antennae and other variables. The Pober method emphasized the need
+% XXX mention key assumption of 180deg rotational symmetry
+for many repeated measurements of each alt-az pointing. Further investigation
+is under way to improve and implement this method and would be greatly aided by
+the availability of precise flux measurements unaffected by primary beam
+uncertainty.
+
+EoR measurements by PAPER and the MWA in the southern hemisphere have focused on the coldest regions where
 galactic foregrounds are minimal. With the majority of possible observing time falling around
@@
 Pictor A is bright and well enough separated from other emission to dominate the visibilities for a good fraction of
-the EoR observing season, making it an excellent flux calibrator.
-
-\subsection{Primary beam}
-\label{sec:background}
-
-Historically, the best Southern Hemisphere 
-EoR band data were by \citet{Slee:1995p7541} with Culgoora Circular
-Array\footnote{Known during daylight hours as Culgoora Radio Heliograph} and
-various higher frequency measurements with Parkes.  These data are typically
-uncertain to 20\% or higher and provide little coverage of the EoR band beyond
-a single narrow-band data point.
-
-More recent surveys include narrow-band surveys by the GMRT \footnote{\url{http://tgss.ncra.tifr.res.in/}} and Mauritius \citep{Pandey:2005p8687}, a
-deep survey of the region near Hydra A by the 32 antenna MWA prototype
-\cite{Williams:2012p8768} and a wide field survey by PAPER, also with 32
-elements \cite{Jacobs:2011p8438}. Several sub-channels were provided in the
-Williams catalog, though with 60-80\% error bars ---large compared to the 30\%
-uncertainty on their wide band measurements.  The latter cover the band and
-spatial scales relevant to EoR measurements but are limited by the accuracy of
-the primary beam \citep{Jacobs:2013p9908} as well as the lack of precise in-band flux calibrators.
-
-The response of the primary beam is of critical importance to EoR measurements.
-Differences between the polarization responses cause leakage of polarized
-signals into the total intensity measurement possibly corrupting the 
-EoR power spectrum \citep{Moore:2013p9621}.  The primary beam 
-shape is also critical to measuring and subtracting foregrounds 
-\cite{Bernardi:2012p9020,Sullivan:2012p9457,Morales:2012p8790} a process which, to be effective, must be done to better than 1\%
-precision for the brightest sources \citet{Liu:2009p4762,Bowman:2009p7816} .
-
-A method for decoupling uncertain fluxes from the uncertain beam has been
-described by \citet{Pober:2012p8800}. In simulation the method was able to
-achieve 3 to 10\% accuracy in measuring the primary beam, depending on the
-number of antennae and other variables. The Pober method emphasized the need
-% XXX mention key assumption of 180deg rotational symmetry
-for many repeated measurements of each alt-az pointing. Further investigation
-is under way to improve and implement this method and would be greatly aided by
-the availability of precise flux measurements unaffected by primary beam
-uncertainty.
-
-In this paper we provide a set of detailed total flux measurements aimed at providing
-an absolute flux calibration for southern hemisphere EoR studies, as well as a
-small set of verification fluxes suitable for constraining future primary beam studies.
+the EoR observing season, making it a desireable source to use for flux calibration.
 
@@
 \label{sec:approach}
-In this section, we describe how we use PAPER in its imaging configuration
-to measure Pictor A and a  selection of known, bright sources. The fluxes are obtained
-by forming beams towards known sources as they drift through the primary beam, calibrating to a single source making a similar track.
-These long tracks allow us to sidestep primary beam uncertainty and measure accurately calibrated fluxes.
-
- In \citet{Jacobs:2013p9908} several errors were identified as originating in primary beam uncertainty.
+In this section, we describe our general approach to controlling the impact of beam model errors on measured
+spectra derived from 
+drift-scan observations 
+of Pictor A and a selection of known, bright sources.  Our approach uses a set of ``source tracks'' as
+a function of frequency and time.  Each source track is a beam, formed by phasing measured visibilities toward
+known source locations as they drift through the primary beam, and summing over antenna pairs, as
+described in \S\ref{sec:XXX}.  Since sources fall
+at different positions
+within the primary beam, it is generally not possible to relate the fluxes of sources at different positions to
+one another without an accurate beam model.  To date, the accuracy of source flux measurements in the
+southern hemisphere in the 100--200 MHz band have largely been limited by the accuracy of these beam models.
+
+We mitigate this problem by selecting sources within a narrow declination range, so that source tracks represent
+nearly identical cuts through the beam response pattern.  Using this fact, the relative amplitudes of sources
+can be deduced with minimal reliance on an accurate beam model.  In our analysis, a prior beam model is only
+necessary for extrapolating across a narrow declination range (we estimate the errors associated with this 
+extrapolation in \S\ref{sec:XXX}), and for approximating optimal inverse-variance weighting when averaging
+over source tracks to determine a single spectrum.
+
+This approach addresses several sources of error that were identified in \citet{Jacobs:2013p9908} 
+as originating from uncertainty in the primary beam model.
   First, under most imaging schemes, each source flux is measured at just a few 
@@
 
-\subsection{Selection of confirmation sources}
+The remainder of the analysis in this paper relates to calibrating the relative source amplitudes that we
+establish to an absolute flux scale as a function of frequency.  Given the shortcomings of 
+existing in-band measurements of sources
+in the southern hemisphere, we must bootstrap this flux scale from an ensemble of calibrator sources that
+exhibit simple power-law spectra.
+As described in \S\ref{sec:XXX},
+this proceeds by first using a single calibrator to set the relative amplitudes of spectral channels, and
+then using several sources, extrapolating across a large set of measurements 
+between 70 MHz and 2 GHz, in a Markov-Chain Monte Carlo simulation to establish an absolute flux scale
+for the measured spectra.
+
+\subsection{Selection of confirmation sources} % XXX what is meant by "confirmation source" ?  Maybe just "Source Selection"?
 As PAPER is a drift scan instrument, each declination describes a distinct path through the primary beam. The flux time seres of a beamform
@@
 susceptibility to localized primary beam error and find that limiting our source selection range to within 
-a declination range of 5\arcdeg{} around a calibrator is a good compromise. In section\ref{fig:gain}
+a declination range of 5\arcdeg{} around a calibrator is a good compromise. In \S\ref{fig:gain},
 we estimate the error resulting from this limited scope application of the primary beam model.
@@
 
+This paper presents a set of detailed total flux measurements, providing
+an absolute flux calibration for southern hemisphere EoR studies, as well as a
+modest set of verification fluxes for other sources suitable for constraining future primary beam studies.
 Here we have provided a measurement of Pictor A with enough precision to confirm
@@
 primary beam response.
+Although we focus on a narrow declination range in this paper, the techniques we describe
+may be applied over any declination range.  Future work will aim to extend this analysis
+to other declination ranges, and to tie the flux calibration of these other declination ranges
+back to the absolute flux scale we derive here.
 

### 2013-06-13 ms.tex
Minor formatting tweaks.

@@
 
-\subsection*{Data Processing Overview}
+\subsection{Data Processing Overview}
 \label{sec:data_overview}
@@
 \end{figure*}
-
-\subsection{Observations}
 
@@
 
-This paper presents a set of detailed total flux measurements, providing
+This paper presents a set of total flux measurements at multiple frequencies within
+a 100--200-MHz band, providing
 an absolute flux calibration for southern hemisphere EoR studies, as well as a
 modest set of verification fluxes for other sources suitable for constraining future primary beam studies.
-Here we have provided a measurement of Pictor A with enough precision to confirm
-a highly linear spectral index between 150 and 600MHz. We then used the same
-filtered beam form method to measure the spectra of bright sources with similar
+We have provided a measurement of Pictor A with enough precision to confirm
+a linear spectral index between 150 and 600MHz. We apply the same
+filtered beamforming method to measure the spectra of bright sources with similar
 primary beam response.
-Although we focus on a narrow declination range in this paper, the techniques we describe
-may be applied over any declination range.  Future work will aim to extend this analysis
-to other declination ranges, and to tie the flux calibration of these other declination ranges
-back to the absolute flux scale we derive here.
 
 The measurements provided
-here are the first, calibrated, broad-band spectra to cover the EoR band. Existing EoR band measurements
+here are the first calibrated, broad-band spectra to cover the EoR band. Existing EoR band measurements
 are accurate to 20\% implying a 40\% uncertainty in the absolute power spectrum
@@
 characterization of the flux scale as well as an overall assessment of the catalog accuracy.
-.  Using a Bayesian analysis we conclude that most of
+Using a Bayesian analysis, we conclude that most of
 these are consistent with previous measurements, provide useful new
-constraints and support the conclusion that the  Pictor A flux is likely on the correct scale.
+constraints and support the conclusion that the Pictor A flux is on the correct scale.
 
@@
 both image and power spectrum flux.
+Although we have focused on a narrow declination range in this paper, the techniques we describe
+may be applied over any declination range.  Future work will also aim to extend this analysis
+to other declination ranges, and to tie the flux calibration of these other declination ranges
+back to the absolute flux scale we derive here.
 
@@
 Astronomical Association.
-
 This work makes use of the ``MCMC Hammer" emcee python library \citep[

### 2013-06-18 ms.tex
Incorporating changes from Adrian and Judd. Answering residual notes from Aaron.

@@
 Radio Telescope (GMRT;
-\citealt{Paciga:2011p9470,Paciga:2013p9627})\footnote{\url{http://gmrt.ncra.tifr.res.in/}},
+\citealt{Paciga:2011p9470,Paciga:2013p9943})\footnote{\url{http://gmrt.ncra.tifr.res.in/}},
 the LOw Frequency ARray (LOFAR;
 \citealt{Yatawatta:2013p9699})\footnote{\url{http://www.lofar.org/}}, the
-Murchison Widefield Array (MWA;  \citealt{Bowman:2012p9138};
+Murchison Widefield Array (MWA;  \citealt{Bowman:2013p9950};
 \citealt{Tingay:2013p9022}))\footnote{\url{http://www.mwatelescope.org/}}, and
 the Donald C. Backer Precision Array for Probing the Epoch of Reionization
-(PAPER; \citealt{Parsons:2010p6757,Pober:2013p9567})\footnote{\url{http://eor.berkeley.edu/}}.
-
-As such, there has been a renewed interest in the spectral and spatial variation of
-foreground emission in the 100--200 MHz frequency band that covers
-the $z=6$--13 redshift range expected to encompass reionization
-\citep{Furlanetto:2006p2267}. % XXX I think this sentence is a repeat from another paper
+(PAPER; \citealt{Parsons:2010p6757,Pober:2013p9942})\footnote{\url{http://eor.berkeley.edu/}}.
+
+%As such, there has been a renewed interest in the spectral and spatial variation of
+%foreground emission in the 100--200 MHz frequency band that covers
+%the $z=6$--13 redshift range expected to encompass reionization
+%\citep{Furlanetto:2006p2267}. % XXX I think this sentence is a repeat from another paper
 In particular, the spectral properties of extra-galactic point-sources are important
@@
 phased and/or correlated dipoles to achieve the aggressive sensitivity requirements
-for measuring the 21cm power spectrum of reionization.
-%TODO ARP wanted a cite for the above.  I really don't know of a good one. Its it a bit of a broad statement
-% XXX how about Parsons 2012a, Beardsley 2012, and jelic 2008 (i think it has sensitivty for lofar)
+for measuring the 21cm power spectrum of reionization \citep{Parsons:2012p9028,Beardsley:2012p9136,Jelic:2008p2130}.
 Adding to the challenge, these telescopes 
@@
 This direction dependent gain is currently uncertain to 10\% or higher
-\citep{Pober:2012p8800}, and comprises a large fraction of the 20\% difference between current telescopes \citep{Jacobs:2013p9908}.
-% XXX difference of what?
+\citep{Pober:2012p8800}, and comprises a large fraction of the 20\% flux uncertainty between current telescopes \citep{Jacobs:2013p9908}.
 
@@
 signals into the total intensity measurement possibly corrupting the 
-EoR power spectrum \citep{Moore:2013p9621}.  The primary beam 
+EoR power spectrum \citep{Moore:2013p9941}.  The primary beam 
 shape is also critical to measuring and subtracting foregrounds 
-\cite{Bernardi:2012p9020,Sullivan:2012p9457,Morales:2012p8790} a process which, to be effective, must be done to better than 1\%
+\cite{Bernardi:2013p9859,Sullivan:2012p9457,Morales:2012p8790} a process which, to be effective, must be done to better than 1\%
 precision for the brightest sources \citet{Liu:2009p4762,Bowman:2009p7816} .
@@
 achieve 3 to 10\% accuracy in measuring the primary beam, depending on the
-number of antennae and other variables. The Pober method emphasized the need
-% XXX mention key assumption of 180deg rotational symmetry
-for many repeated measurements of each alt-az pointing. Further investigation
+number of antennae and other variables. In particular, it emphasized the need
+for many repeated measurements of each alt-az pointing, which in that
+case were found by assuming 180\arcdeg{} symmetry. Further investigation
 is under way to improve and implement this method and would be greatly aided by
@@
 Pictor A is bright and well enough separated from other emission to dominate the visibilities for a good fraction of
-the EoR observing season, making it a desireable source to use for flux calibration.
+the EoR observing season, making it a desirable source to use for flux calibration.
 
@@
 known source locations as they drift through the primary beam, and summing over antenna pairs, as
-described in \S\ref{sec:XXX}.  Since sources fall
+described in \S\ref{sec:beamforming}.  Since sources fall
 at different positions
@@
 necessary for extrapolating across a narrow declination range (we estimate the errors associated with this 
-extrapolation in \S\ref{sec:XXX}), and for approximating optimal inverse-variance weighting when averaging
+extrapolation in \S\ref{sec:flux_scale}), and for approximating optimal inverse-variance weighting when averaging
 over source tracks to determine a single spectrum.
@@
  Using the drift scan-beamforming technique, each 
-source is measured thousands of times at a variety of different primay beam values to provide a complete sample of the
+source is measured thousands of times at a variety of different primary beam values to provide a complete sample of the
 flux variance due to primary beam variation.  Second, the flux calibration was found to vary over the 
@@
 exhibit simple power-law spectra.
-As described in \S\ref{sec:XXX},
+As described in \S\ref{sec:flux_scale},
 this proceeds by first using a single calibrator to set the relative amplitudes of spectral channels, and
@@
 
-\subsection{Selection of confirmation sources} % XXX what is meant by "confirmation source" ?  Maybe just "Source Selection"?
-As PAPER is a drift scan instrument, each declination describes a distinct path through the primary beam. The flux time seres of a beamform
+\subsection{Source Selection} 
+As PAPER is a drift scan instrument, each declination describes a distinct path through the primary beam. The flux time series of a beamform
  provides a detailed sample of the primary beam relative to the peak of the trace, however,
-a model is still required to calibrate between declinations. Below we argue that be averaging over long tracks, we minimize our 
+a model is still required to calibrate between declinations. Below we argue that by averaging over long tracks, we minimize our 
 susceptibility to localized primary beam error and find that limiting our source selection range to within 
@@
 which is given by the true source flux, $S$, illuminated by the true beam pattern $B$, according to
-% XXX would be nice to capture here and below that B, B_M, and S_p are vectors indexed by t.  would
-% suggest subscript, except you already have B_M.  Could use B^\prime (and S^\prime) instead...
 \begin{equation}
-S_p=BS.
+S_p=B(t)S.
 \end{equation}
@@
 weighted by a model of PAPER's primary beam response ($B_M$).
+As the perceived flux is already weighted once by the true beam $B$ this weighted sum is an effective approximation of inverse-variance weighting \citep{Pober:2012p8800}.
 \begin{align}
-S_\textrm{est} &= \frac{\sum_t B_M S_p}{\sum_t B^2_M} \nonumber \\ 
-&= \frac{\sum_t B_M B}{\sum_t B^2_M} S  \nonumber \\
-&= g(\delta) S  \label{eq:g}
+S_\textrm{est} &= \frac{\sum_t B(t)_M S_p}{\sum_t B(t)^2_M} \nonumber \\ 
+&= \frac{\sum_t B(t)_M B(t)}{\sum_t B(t)^2_M} S  \nonumber \\
+&\equiv g(\delta) S  \label{eq:g}
 \end{align}
-% XXX where g and \delta are...?  Should connect this nomeclature to J2331-416 language below (i.e. solving for g)
-As the perceived flux is already weighted once by the true beam $B$ this weighted sum is an effective approximation of inverse-variance weighting \citep{Pober:2012p8800}.
-
-The pre-factor in Eq \ref{eq:g} has been integrated in time over the full azimuthal sweep across the sky and therefore depends only on declination. The rate at which this factor
+The net time integrated, weighted beam response $g$ is purely a function of declination $\delta$.The rate at which this factor
 changes with declination defines maximum declination distance we can observe from our calibrator. 
-In simulation we multiplied an early holographic beam map \cite{Pober:2012p8800}
-% XXX to simulate what?  need to say something like:
-% To simulate the effect of beam model errors on ???, we used simulations derived from the holographic
-% beam map measured in \citet{Pober:2012p8800} weighted by a beam model derived from electromagnetic
-% simulations, and find that ...
-by electromagnetic simulations and find that it 
-diverges slowly with declination, with a maximum of 10\% over 5\arcdeg{} of declination range, though most are less. 
-We estimate this spectral dependent gain at a reference declination of 41\arcdeg{}36\arcmin{}   using (J2331-416) fitting a spectral index model to the
- catalog data points below 2GHz. 
-% XXX clarify that this is not the last correction; there is one more flux cal that is derived from MCMC
-% over several calibrator sources (Figure XXX).
-
+To simulate this affect we we multiplied a measurement of the primary beam \citep{Pober:2012p8800}
+by electromagnetic simulations \citep{Parsons:2010p6757} and find that $g$ 
+diverges slowly with declination, with a maximum of 10\% over 5\arcdeg{} of declination range, though most are less. Thus, to first order,
+calibration to a single declination will remove most of the variation with declination.
+We estimate this spectral dependent $g$ at a reference declination of 41\arcdeg{}36\arcmin{}  using (J2331-416) fitting a spectral index model to the
+ catalog data points below 2GHz. This levels the bandpass due to spectral dependence  of the primary bean 
+ and puts all the sources on approximately the same flux scale.  
  Finally we average the spectra from a resolution of 400kHz to 10MHz bins, adding the individual errors in quadrature
@@
 
- Measurements are derived from observations using  the east-west dipole arms of
+ Measurements are derived from observations using two nights on the east-west dipole arms of
 64 PAPER antennas deployed in a minimum-redundancy imaging configuration
@@
 Right Ascension. The July portion of the dataset comes from the same observing
-campaign described by \cite{Pober:2013p9567} and \cite{Stefan:2012p9707}. 
+campaign described by \cite{Pober:2013p9942} and \cite{Stefan:2013p9926}. 
 %July (\#40,\#55), September (\#7,\#28)
@@
 \includegraphics[width=0.9\textwidth]{plots/auto_tempcorr.png}
-\caption{Calibrating the temperature coefficient  between the July and October observing runs.
+\caption{Calibrating the temperature coefficient  between the July and October nights.
 Here we plot the ratio of auto-correlations (averaged over frequency and antenna) against the temperature difference between the two nights.
@@
 % what data you've included here.
+% There is no sun data.  Changed "observing runs" to "nights". Is that what you meant? --DCJ
 \label{fig:autos_tempcorr}}
@@
 \includegraphics[width=0.9\textwidth]{plots/auto_balance.png}
-\caption{Gain differences between the July and October nights are dominated by temperature variation. Here we see the affect on 
-the average auto correlation before ({\color{orange} orange}) and after (black) application of the temperature dependent gain. \label{fig:auto_compare}}
-% XXX why does the gap in data in the top plot not match the bottom?
+\caption{Gain differences between the July and October nights are dominated by temperature variation. Here we see the effect on 
+the average auto correlation before ({\color{orange} orange}) and after (black) application of the temperature dependent gain.
+\label{fig:auto_compare}}.
+Note that the span of the data in the bottom fractional difference plot is limited to points occurring in both nights and does not cover the full range seen in the top.
 \end{figure}
@@
 averaging over the three independent solutions. These same calibration
-solutions have been successfully applied in \citet{Pober:2013p9567} and \citet{Stefan:2012p9707}.
+solutions have been successfully applied in \citet{Pober:2013p9942} and \citet{Stefan:2013p9926}.
 for power-spectrum analysis of foregrounds and imaging of Centaurus A, respectively.
@@
 The October per-antenna gains were found by computing the average ratio of the auto correlations
-against the July data. Delays were help constant as in \citet{Jacobs:2011p8438}.
+against the July data. Delays were held constant as in \citet{Jacobs:2011p8438}.
 
@@
 \subsection{Beamforming}
-
+\label{sec:beamforming}
 Spectral time-series are computed by beam-forming to the selected sky
@@
  to remove 
-the residual bandpass due to the net effect of the primary beam as discussed in section \ref{sec:approach}. 
+the residual bandpass $g$ from equation \ref{eq:g} caused by the net effect of the primary beam as discussed in section \ref{sec:approach}. 
 This source
@@
 though curvature or other
-deviation from a power-law is not-uncommon.
+deviation from a power-law is not uncommon.
 
@@
 to avoid making the error of falsely including erroneously matched 
-data points but benefiting from some measurements not included.
+data points.
 
@@
 J2331-416. The accuracy of this fit, and the implied uncertainty in the flux
-scale, limits the accuracy of the PAPER measurements..  To refine the flux
+scale, limits the accuracy of the PAPER measurements.  To refine the flux
 scale and estimate our flux scale uncertainty, we bootstrap a single global flux scale 
@@
 These spectra provide tighter constraints on many of the EoR band fluxes, while
-limiting the pernicious affect of primary beam uncertainty.  Future work will use these
+limiting the pernicious effect of primary beam uncertainty.  Future work will use these
 fluxes to further refine the primary beam models of these experiments which is crucial to properly reconstructing
@@
 
-% XXX re-check arxiv cites in bib for finishing peer review.  Paciga 2013, Pober 2013, Moore 2013, and Stefan 2013
 % all published now.  what is bernardi 2012 submitted?

### 2013-06-19 ms.tex
Jonnie's edits of overview section
Signed-off-by: Danny Jacobs <daniel.c.jacobs@asu.edu>

@@
 
-\subsection{Data Processing Overview}
+\subsection{Analysis Overview}
 \label{sec:data_overview}
-The spectra reported here are measured by beam-forming ---phasing the visibilities to
-the target location and summing over baselines to produce a spectral time series of perceived flux $S_p$,
-which is given by the true source flux, $S$, illuminated by the true beam pattern $B$, according to
+The spectra reported here are measured by beam-forming --- phasing the visibilities to
+the target location and summing over baselines to produce a spectral time series of ``perceived'' flux $S_p$.
+We define a perceived flux as the true source flux density, $S$, illuminated by the true beam pattern $B$:
 \begin{equation}
-S_p=B(t)S.
+S_p=B(t)S,
 \end{equation}
-The spectrum is then isolated
-from neighboring sources by filtering and averaged in the time domain.  This time-average is 
-weighted by a model of PAPER's primary beam response ($B_M$).
-As the perceived flux is already weighted once by the true beam $B$ this weighted sum is an effective approximation of inverse-variance weighting \citep{Pober:2012p8800}.
+where $B$ is a function of time because the observations are taken as a drift
+scan.
+The desired source spectrum is then isolated
+from neighboring sources by filtering.%XXX what kind of filtering?
+We then average the spectrum in the time domain,
+weighting by a model of PAPER's primary beam response ($B_M$); as the perceived flux is already weighted once by the true beam $B$, this weighted sum is an effective approximation of inverse-variance weighting \citep{Pober:2012p8800}.
+Mathematically, our estimated source flux density is given by: 
 \begin{align}
@@
 &= \frac{\sum_t B(t)_M B(t)}{\sum_t B(t)^2_M} S  \nonumber \\
-&\equiv g(\delta) S  \label{eq:g}
+&\equiv g(\delta) S  \label{eq:g},
 \end{align}
-The net time integrated, weighted beam response $g$ is purely a function of declination $\delta$.The rate at which this factor
-changes with declination defines maximum declination distance we can observe from our calibrator. 
+where the subscript $M$ indicates a model beam, and the $S$ without subscript is the true flux density of the source.
+The net time integrated, weighted beam response $g$ is purely a function of declination $\delta$.  The rate at which this factor
+changes with declination defines the declination range over which our calibrator source can be used to set the gain scale of the observations.
 To simulate this affect we we multiplied a measurement of the primary beam \citep{Pober:2012p8800}
 by electromagnetic simulations \citep{Parsons:2010p6757} and find that $g$ 
-diverges slowly with declination, with a maximum of 10\% over 5\arcdeg{} of declination range, though most are less. Thus, to first order,
-calibration to a single declination will remove most of the variation with declination.
-We estimate this spectral dependent $g$ at a reference declination of 41\arcdeg{}36\arcmin{}  using (J2331-416) fitting a spectral index model to the
- catalog data points below 2GHz. This levels the bandpass due to spectral dependence  of the primary bean 
- and puts all the sources on approximately the same flux scale.  
+diverges slowly with declination, with a maximum of 10\% over 5\arcdeg{} of declination range, though most are less. %XXX most what are less?
+Thus, to first order,
+we can use our calibrator source to calibrate sources within 5\arcdeg{} of declination and remove most of the variation with declination.
+We estimate this spectral dependent $g$ at a reference declination of 41\arcdeg{}36\arcmin{} using (J2331-416), fitting a spectral index model to the
+ catalog data points below 2GHz. This levels the bandpass due to spectral dependence of the primary beam, and allows us to place our measured source flux
+estimates
+on approximately the same flux scale.  
  Finally we average the spectra from a resolution of 400kHz to 10MHz bins, adding the individual errors in quadrature
@@
 First, we remove known RFI transmission bands and analog filter edges, and then
-flag outliers at 6$\sigma$ to remove RFI events.  Next, we suppress sky-like
+flag outliers in the frequency and time derivative at 6$\sigma$ to remove RFI events.  Next, we suppress sky-like
 emission by applying a DDR filter to remove delays and delay-rates within the

### 2013-06-19 ms.tex
minor minor fixes
Closing in on submission. small small changes and a recompile

@@
 phased and/or correlated dipoles to achieve the aggressive sensitivity requirements
-for measuring the 21cm power spectrum of reionization \citep{Parsons:2012p9028,Beardsley:2012p9136,Jelic:2008p2130}.
+for measuring the 21cm power spectrum of reionization \citep{Parsons:2012p9028,Beardsley:2013p9952,Jelic:2008p2130}.
 Adding to the challenge, these telescopes 
